### 2020-02-11 paper.tex
day one--just setting up

\documentclass{article}
\title{Reading Notes}

\begin{document}
\title{}

today I got this repo set up. Next time, I'll reskim these papers:

MARTINI\cite{Marrink2007}

VOTCA\cite{Ruhle2009}

TraPPE\cite{Maerzke2011}

and read this: \cite{Chakraborty2018a}

\bibliography{library}
\bibliographystyle{ieeetr}
\end{document}

### 2020-02-12 paper.tex
trying to form a habit. mornings are hard
habit :) tomorrow reskim existing paper

@@
 
+got busy with fancy-ing up the GIXStapose repo, helping rachel, office hours, and atom-typing with gaff-foyer with ryan and chris.
+Briefly skimmed the chakraborty paper-- they consider all possible mappings that a cg compound can have in order to systematically pick a cging scheme.
+OK Chakraborty notes:
+-exclude cg mapping schemes to those that maintain symmetry
+-Zhang and Voth designed CG mapping operators by preserving "essential dynamics"
+-Cao and Voth worked on centering functions COM vs center of charge. They found center of change was better for preserving intermolecular structure.
+-Wagner generalize centering functions to arbitrary thermodynamic quantities
+-Marrink grouped four heavy atoms and showed that this simple consistent scheme works.
+CG models are validated by preservation of rdfs and velocity autocorrelation functions (vacfs)
+mapping operator tree
+
 \bibliography{library}

### 2020-02-13 paper.tex
lesgo habit

@@
 
+Today I'm reading the VOTCA\cite{Ruhle2009} paper with the goal of answering these questions:
+how do they choose a chromophore?
+
+how do they calculate the transfer integral?
+
+how do they do backmapping?
+
+other notes:
+CG methods--IBI, force matching, inverse MC. This paper goes over details of these and how they're implemented in votca. This wasn't really what I wanted to read about so I skimmed.
+They use ESPResSo++ for quantum calculations
+OK, this isn't the right paper to read about CT stuff or backmapping. Let's look at some of these [http://www.votca.org/citations/using-votca](http://www.votca.org/citations/using-votca)
+Also I'm noticing in this list of papers--Marrink (cited by chakraborty) is here and there is a paper mentioning the importance of side-chains for charge-mobility! \cite{May2011}
+Next time read about tie-chains \cite{May2011} and/or charge mobility \cite{Lukyanov2010}
 \bibliography{library}

### 2020-02-14 paper.tex
quick habit

@@
 Next time read about tie-chains \cite{May2011} and/or charge mobility \cite{Lukyanov2010}
+Lukyanov--sounds a lot like morphct, gaussian density of states?
+I thought their (votca's) method was like morphct but now I'm not sure...
+It seems like they're using a simplification and not doing dft.
 \bibliography{library}

### 2020-02-17 paper.tex
reading about ct in votca still

@@
 It seems like they're using a simplification and not doing dft.
+
+https://pubs.acs.org/doi/10.1021/ja104380c - 
+rubrene record charge carrier 15 cm^2/(V s) single crystal by vapor deposition. typical for thin-film is 1 cm^2/(V s)
+good discussion of some of the assumption of marcus theory. 
+They start with single crystal structures from xray data. They calculate reorganization energies with b3lyp 6-311G(d,p) and transfer integrals with ZINDO. (check their SI)
+
 \bibliography{library}

### 2020-02-18 paper.tex
working on same paper trying to understand results

--- 2020-02-14 paper.tex
@@
 It seems like they're using a simplification and not doing dft.
+
+\cite{Vehoff2010a}
+rubrene record charge carrier 15 cm^2/(V s) single crystal by vapor deposition. typical for thin-film is 1 cm^2/(V s)
+good discussion of some of the assumption of marcus theory. 
+Drude model (electrons bounce off stationary nuclei like a pinball machine) works for perfect crystals at low temp.
+At RT it doesn't work.
+Marcus theory assumes nuclear dynamics much slower (Borne-Oppenheimer) and electronic coupling is weak (what does this mean exactly?).
+Static disorder is based on the electronic DOS and the hopping rate between localized states.
+(As opposed to what?)
+They start with single crystal structures from xray data. They calculate reorganization energies with b3lyp 6-311G(d,p) and transfer integrals with ZINDO. (check their SI)
+How are they able to calculate direction-resolved transfer integrals?? very cool. What exactly do the transfer integral graphs mean? (Figure 2)
+
 \bibliography{library}

### 2020-02-18 paper.tex
more for today

@@
 They start with single crystal structures from xray data. They calculate reorganization energies with b3lyp 6-311G(d,p) and transfer integrals with ZINDO. (check their SI)
-How are they able to calculate direction-resolved transfer integrals?? very cool. What exactly do the transfer integral graphs mean? (Figure 2)
+How are they able to calculate direction-resolved transfer integrals??
+very cool.
+What exactly do the transfer integral graphs mean?
+(Figure 2) Had a helpful chat with Chris about this and it helped me to think through the figures.
+The y-axis on the transfer integral is counts and the x-axis is energies--it makes sense that movement of an electron in different directions would require different energies and/or be more likely.
+Still not sure how to calculate it though.
 

### 2020-02-24 paper.tex
added ruehle paper
notes about how kmc works in votca and how crap its tutorials are.

@@
 \cite{Vehoff2010a}
-rubrene record charge carrier 15 cm^2/(V s) single crystal by vapor deposition. typical for thin-film is 1 cm^2/(V s)
+rubrene record charge carrier $15 \frac{cm^{2}}{V s}$ single crystal by vapor deposition. typical for thin-film is $1 \frac{cm^{2}}{V s}$
 good discussion of some of the assumption of marcus theory. 
@@
 
+Today I'm digging around in more of the votca stuff to try and figure out how to run kmc there.
+They use ORCA too!
+Also their tutorials and documentation REALLY SUCK.
+[https://github.com/votca/xtp-tutorials](https://github.com/votca/xtp-tutorials) in particular I'm looking at LAMMPS/KMC\_Thiophene.
+OK.
+either I am dumb or that tutorial sucks.
+I can tell that they're using orca and the inputs/oputputs the use but there's no explanation of what they're doing.
+It looks like they calculate the reorganization energy, but they don't define a chromophore--which makes sense for thiophene but what about when your molecule is ginormous?
+\cite{Ruhle2011b} discusses charge transport in amorphous films of [tris-(8-hydroxyquinoline)aluminum](https://en.wikipedia.org/wiki/Tris(8-hydroxyquinolinato)aluminium).
+Oh Figure 1 is nice--it is a workflow of what can be done in votca.
+11A talks about how to parameterize new contributions to a force-field using first-principles.
+11B choosing a "chromophore"-- rigid fragments vs conjugated segments.
+they broke apart the chromophore in a polymer like p3ht using the dihedral angle--although they validated this choice with other methods.
+Interesting-- they replace the chromophores with those which have been geometry optimized using DFT.
+then they make a neighbor list
+I'll come back to this paper later. I at least was able to answer some of my questions about choosing a chromophore.
+11C talks about calculating the transfer integral for each pair and why ZINDO works and when it breaks down.
+
 \bibliography{library}

### 2020-03-02 paper.tex
reread perspective paper
meeting notes

--- 2020-02-18 paper.tex
@@
 
-\cite{Vehoff2010a}
-rubrene record charge carrier 15 cm^2/(V s) single crystal by vapor deposition. typical for thin-film is 1 cm^2/(V s)
+https://pubs.acs.org/doi/10.1021/ja104380c - 
+rubrene record charge carrier $15 \frac{cm^{2}}{(V s)}$ single crystal by vapor deposition. typical for thin-film is $1 {cm^{2}}{(V s)}$
 good discussion of some of the assumption of marcus theory. 
-Drude model (electrons bounce off stationary nuclei like a pinball machine) works for perfect crystals at low temp.
-At RT it doesn't work.
-Marcus theory assumes nuclear dynamics much slower (Borne-Oppenheimer) and electronic coupling is weak (what does this mean exactly?).
-Static disorder is based on the electronic DOS and the hopping rate between localized states.
-(As opposed to what?)
 They start with single crystal structures from xray data. They calculate reorganization energies with b3lyp 6-311G(d,p) and transfer integrals with ZINDO. (check their SI)
-How are they able to calculate direction-resolved transfer integrals?? very cool. What exactly do the transfer integral graphs mean? (Figure 2)
 
+Matt Thompson got a job at OpenFF, one of the tools they list as desirable for applicants is knowledge of psi4:
+https://pubs.acs.org/doi/abs/10.1021/acs.jctc.8b00286
+
+read official papers for mosdef. check github.
 \bibliography{library}

### 2020-03-06 paper.tex
reading and writing for today :)

--- 2020-02-24 paper.tex
@@
 
+rereading the perspective paper \cite{Jankowski2019} looking for things to read next:
+Braun 2018 foundations in molecular simulation
+https://doi.org/10.33011/ livecoms.1.1.5957
+74-89 are relevant to coarse-graining
+92-95 start here for opvs
+
+Today I'm thinking about some of the big picture stuff related to my proposal:
+Science-wise I am thinking of my proposal like this: Humans use energy and burning fossil fuels to get that energy really sucks.
+rising CO2 concentration in the atmosphere contributes to global warming.
+Sustainable, low-carbon footprint energy generation is vital to protect the precious climate which sustains all life.
+Energy generation using OPV devices is one form of alternative energy.
+But there are a lot of potential OPV molecules out there!
+So how can we develop inexpensive, fast methods for screening this ZOO of compounds?
+Well we can use modelling techniques and a computer.
+Computational simulations of organic photovoltaics suffer from a problem of length scales: OPV morphologies can have bulk features on the scale of 10s of nanometers (BHJ, exciton dissociation length, pi-stacking) which affect the morphology, yet still we are interested in the electronic properties of this system--a fundementally quantum mechanical property--taking place on the angstrom scale where with current computers we can only realistically look at up to 100's of atoms.
+<so we break apart the problem MD to get a morphology, Zindo to calculate energy splitting of neighbors-->transfer integral, KMC to estimate CT, talk about results of evan/matty/votca> What am I going to add?
+more robust/automated coarse-graining and backmapping, calculation of reorganization energy, chromophore detection.
+Things I care about: The environment--I like working on a project that theoretically could help find the next molecule for OPV technology.
+Sometimes it seems very far removed, but having sustainable technology as an ultimate goal matters to me.
+I also care a lot about help make science more accessible to everyone: I find myself really excited about creating tools which help to visualize the unseeable and to communicate complex ideas in a simple understandable way.
+I'm not sure this has anything to do with anything, but it's definitely a developing passion.
+
+I'm also reading this paper today https://arxiv.org/pdf/2003.02031.pdf which is a bout TRUE simulations.
+notes:
+GUI's hurt reproducibility, MS Excel hides the formula's and order of calculation (p 4)
+poorly documented code and raw data files dont help reproducibility (looking at you votca) (p4)
+*I want to include start to finish notebooks with any paper I publish...* Also docker containers with my exact software stack.
+I love the examples in this paper :) It feels a lot like our perspective paper! I'm skimming them but I love that notebooks are included in the SI.
+They qualify the GUI's are bad statement saying that GUIs are only bad *if they hide the workflow details.*
+
 \bibliography{library}

### 2020-03-20 paper.tex
merge

--- 2020-02-24 paper.tex
@@
 
-\cite{Vehoff2010a}
-rubrene record charge carrier $15 \frac{cm^{2}}{V s}$ single crystal by vapor deposition. typical for thin-film is $1 \frac{cm^{2}}{V s}$
+https://pubs.acs.org/doi/10.1021/ja104380c - 
+rubrene record charge carrier $15 \frac{cm^{2}}{(V s)}$ single crystal by vapor deposition. typical for thin-film is $1 {cm^{2}}{(V s)}$
+
 good discussion of some of the assumption of marcus theory. 
@@
 Still not sure how to calculate it though.
+
+\cite{Vehoff2010a}
+rubrene record charge carrier $15 \frac{cm^{2}}{V s}$ single crystal by vapor deposition. typical for thin-film is $1 \frac{cm^{2}}{V s}$
 
@@
 
+rereading the perspective paper \cite{Jankowski2019} looking for things to read next:
+Braun 2018 foundations in molecular simulation
+https://doi.org/10.33011/ livecoms.1.1.5957
+74-89 are relevant to coarse-graining
+92-95 start here for opvs
+
+Matt Thompson got a job at OpenFF, one of the tools they list as desirable for applicants is knowledge of psi4:
+https://pubs.acs.org/doi/abs/10.1021/acs.jctc.8b00286
+
+read official papers for mosdef. check github.
 \bibliography{library}

### 2020-03-20 paper.tex

--- 2020-03-06 paper.tex
@@
 
+Matt Thompson got a job at OpenFF, one of the tools they list as desirable for applicants is knowledge of psi4:
+https://pubs.acs.org/doi/abs/10.1021/acs.jctc.8b00286
+
+read official papers for mosdef. check github.
 \bibliography{library}

### 2020-04-07 paper.tex
reading about smiles

@@
 read official papers for mosdef. check github.
+
+Reading \cite{Hanson2016} also my mendeley overwriting my files because it thinks they are duplicates or something? It keeps losing the pdf even though I've uploaded it. :(
+SMILES - simplified molecular-input line-entry system
+SMARTS - smiles arbitrary target specification
+around since 1980s
+alternatives SLN, MQL, CSRML.
+This paper is about specifically Jmol smiles so I'm skipping to a different one.
+\cite{Weininger1988} First paper about smiles- how do we unambiguously represent a chemical structure? historically CAS, graph theory, IUPAC.
+human-readable and machine readable
+hydrogens, single bond don't need to be specified. designed for organic molecules.
+
 \bibliography{library}

### 2020-05-06 paper.tex
transferred proposal mendeley folder to cmelab
lil bit of readin
added a bunch of new papers an summarized the one I was already familiar with

@@
 
+\cite{Smith2018} reading about psi4: free and open source with python api that uses blas and c under the hood.
+has jupyter notebooks tutorials.
+This paper reads like our perspective paper in tone :hearteyes: 2.2 -2.3 kinda lost me.
+I should look at their jupyter notebooks.
+
+Today searched "coarse grain backmapping" in the library and got the following papers:
+\cite{Alessandri2017b}
+
+\cite{Haxton2015a}
+\cite{Wassenar2104b}
+\cite{Peng2019a}
+\cite{Rolland2020a}
+
+This is the paper we reviewed in lab meeting!
+CG -> backmap -> mobility.
+AA MD can reproduce XRD patterns pi-pi stacking, formation of lamellar structure, change in morphology at high oxidation levels, mobility dependence on chain-length (* looks into ref 26 and compare to evan's tie chain paper)
+CG allows us to look at larger lengthscales and with backmapping we can restore atomistic details, but is there a cost?
+ref 44 model HOTT molecules as ellipsoids with Gay Berne interactions (I'm thinking of this as anisotropic--i.e., directionally dependent so good for ellipsoids--Lennard Jones.
+Often used in liquid crystal systems.)
+They use the same backmapping as us ref 13.
+Many CG papers verify by XRD buyt they claim same XRD can result in very different mobility.
+ref 26.
+They use Wassenar's backward.py script.
+-- He is from the university which makes GROMACS
+CG overestimates density--backmapping fixes it.
+XRD of backmapped AA match AA.
+pipi stacking is corrected and lamellar structure present.
+Mobility also good.
+They explain the differences between the AA and CG mobilities saying that the AA one is smaller so it's a size effect due to over estimated percolation threshhold--i.e.
+the connectivity is overestimated because the periodic volume is small enough that the periodic image has an effect.
+
+\cite{Poblete2018a}
+
 \bibliography{library}

### 2020-05-07 paper.tex
reading today about backwards.py script

@@
 \cite{Wassenar2104b}
+
+This paper is about backwards.py.
+The authors are from university of groeningen where GROMACS is made.
+however this tool is generic and not specific to gromacs.
+it uses geometric projection and position restrained MD relaxation--same as what Matty did.
+can map between anything just needs a mapping.
+Good overview of CG methods:
+Rzepiela - randomly place atomistic beads on small spheres around CG beads.
+Requires many steps, specific to one verison of GROMACS, but can be made specific with correspondence between atoms and beads.
+Brocos - lipid micelles. placing atoms on a trace through the CG bead and adding peripheral atoms at offset. 
+A good CG model should yield correct structures and be simple quick and flexible.
+Should be generic (ff and system type) and require little information.
+Then information provided should be the CG coordinates, the atomistic topology and the correspondence mapping between the atomistic and CG particles.
+They go from MARTINI-CG to GROMOS 54a7 UA to CHARMM36 AA.
+Some matrix mapping that I don't totally understand. Confusing between A the matrix and A the atom position. :/
+Fig 5 is neat! c: shows a helical protein at each step of the CG->AA process. their procedure appears to improve upon the simulated anealing of rzepiela. 
+* look at backwards.py with the intent of better understanding the Matrix transformation.
+
 \cite{Peng2019a}

### 2020-05-08 paper.tex
read alessandri paper.

@@
 
+Coarse graining in OPV bulk heterojunctions!
+p3ht and pcbm, solvent evaporation.
+morphologies need large interfacial area between donor and acceptor and relatively high crystallinity and connection to the electrode.How can we investigate the processing conditions that achieve the highest performance?
+Analysis of OPVs include AFM, SEM, TEM - provide info about interpenetration (how the two phases are dispersed.) Electron tomography can study 3d morphology., but has limited contrast in organic material due to low scattering.
+GIXD, GISAXS quantifies the degree of crystallinity but averages over the structure.
+CG allows us to look at these systems but CG models are currently not transferrable meaning that for each new system a new CG model must be developed which is slow.
+Simulated annealing is often used but a more relevant to experiment method is simulated evaporation.
+This paper used CG model like Lee and Pao (read this paper) but also based on finer model like martini. Martini does backmapping. (backwards.py) 
+They use explicit solvent (CB/benzene) and they remove molecules randomly as the simulation progresses.
+Longer drying time results in larger crystallites/ fewer D-A contacts.
+P3ht shows backbone (pi-pi) stacking at a distance of 4.5 A in the CG morphology.
+They use backwards.py to do their backmapping.
+They use 3 beads to represent thiophene in p3ht with no explicitly anisotropic interaction.
+Carillo (ref 26) used anisotropic addition onto very simplified model (thiophene is single bead) of lee (ref 22).
+(read these) The model used here thiophene is a triangle and they think this helps it stay planar and stack.
+Figure 5 is beautiful.
+
 \cite{Haxton2015a}

### 2020-05-11 paper.tex
read haxton--CG beads with orientation

@@
 \cite{Haxton2015a}
-\cite{Wassenar2104b}
+CG beads with orientation.
+They use the word "stiffest" to describe degrees of freedom--they mean bond stretching, angle bending, and torsion within rings.
+They suggest there are two separate ways to improve CG: better mapping between AA and CG or better CG interactions.
+The seconds can be helped with IBI, entropy minimization...
+First one is what the authors will focus on.
+Point-site method maps groups of atoms onto a bead--bead potential is spherically symmetric, but some models use neighboring sites to introduce some directionality.
+e.g., Alemani et al created a protein model where the dipole interaction was a function of the alpha-carbon angle.
+Here they add orientation to the point-site model.
+This increases the degrees of freedom for each site from 3 to 6, but they model bonds and angles as stiff and dihedral angles (except rings and double bonds) as soft.
+They also map about 8 atomns to a site.
+They use backmapping from ref 64--not backwards.py.
+They simplify the ideal interactions of the CG model (many-body problem) to pai potentials.
+They show how to calculate to error in an observable calculated on backmapped structure.
+C code used for backmapping in SI.
+mapping ratio - atomic DOF / CG DOF.
+PRIMO on average is 3.0, UNRES, MARTINI, MS-CG are 8.2, 7.1, and 6.0.
+I think this paper aims to improve on PRIMO by adding directionality?
+they measure accuracy with rmsd and efficiency with mapping ratio.
+
+\cite{Wassenar2014b}
 

### 2020-05-12 paper.tex
read peng paper about expensive but accurate cg technique

@@
 \cite{Peng2019a}
+
+biomolecules.
+Backmapping based on Bayesian inference and restrained MD.
+cgmap.py -- they tell us the names of their codes but don't provide them??
+They try multiple CG methods: Martini (twice with different initial structure), UNRES, ENM.
+Martini had the lowest RMSD but it is also the finest grain method.
+They have an ultra coarse method that only use 5 beads for a small protein; it gets impressive results (RMSD 0.47 angstrom) for how sparse it is!
+But it is not sufficiently accurate to predict structure-- other RMSD > 10angstrom.
+their method is more expensive.
+I don't quite understand how they get some of the probabilities for the Bayesian part, but my takeaway from this paper is that the logrestraints work a lot better for them and Bayesian inference, although expensive, allows them to skip the AA MD simulation at the end?
+
 \cite{Rolland2020a}

### 2020-05-13 paper.tex
read poblete--steered MD using a particular RMSD for RNA

@@
 \cite{Poblete2018a}
+RNA - backmapping steered MDaimed at minimizing a particular RMSD (ERMSD) between atomic and target structure.
+target structure were found to be recovered by this backmapping except in the case where there were unpaired bases.
+folding pathway dependent on parameters used in ERMSD.
+need AA strutures to validate with experiment (x-ray or neutron scattering) backmapping usually involves placing atomistic coordinates relative to the beads and then minimizing the energy of the structure using steepest descent or short MD runs (could use position restraint).
+Atomistic can even be mapped onto the whole trajectory.
+This work describes the backmapping of the SPlit and conQueR (SPQR) method.
+Minimizes the ERMSD distance between solvated AA strand of the CG structure (RNA).
+ERMSD : origin is set to CoM of C2 C4 and C6 atoms of each base (see ref 23), then for each pair of bases, rij is the center of base i in the coord system of base j.
+In order to account for anisotropy, the scaling for the z-direction is different (does this mean the strand is oriented to z in some way??) This metric shows the difference between arrangement of nucleobases of two RNA structures.
+Backbone and sugar interactions are unrestrained.
+The paper will show results on the backbone conformation.
+They use steered MD with ERMSD as the steering parameter.
+(How does steered MD work?) Look like they use and external pulling force which depend on ERMSD.
 

### 2020-05-13 checkbibs.py
add a script to check if my bibfile is broken and added a bunch of new papers to start reading

@@ -1,0 +1,37 @@
+import subprocess as sp
+
+
+def tag_only(line):
+    """get just the tag from the line with '@article'"""
+    start = line.index("{")
+    end = line.index(",")
+    return line[start+1:end]
+
+def main():
+    """I'm always worried that Mendeley is losing my papers.
+    This script is to give me some peace of mind that
+    my bibs aren't disappearing before I commit the new bib file.
+    """
+    command = ["git", "diff", "library.bib"]
+    p = sp.run(command, capture_output=True)
+    lines = p.stdout.decode("utf-8").split("\n")
+    tags = [line for line in lines if "@article" in line]
+    plus = {tag_only(tag) for tag in tags if tag[0] == "+"}
+    minus = {tag_only(tag) for tag in tags if tag[0] == "-"}
+    if minus.issubset(plus):
+        print("All good! No bibs missing")
+    else:
+        missing = []
+        check = minus - plus
+        for tag in check:
+            # check if just an 'a', 'b' got added/removed etc
+            if tag[:-1] not in plus:
+                missing.append(tag)
+        if missing:
+            print("These bibs were missing: ", missing)
+        else:
+            print("All good! No bibs missing")
+
+
+if __name__ == "__main__":
+    main()

### 2020-05-14 paper.tex
add a script to check if my bibfile is broken and added a bunch of new papers to start reading
started reading, will need to come back

@@
 
+Of these the Alessandri paper was the best and  most interesting/relevant. I am pulling some refs from here for next time:
+
+\cite{Mikhnenko2012}
+Exciton diffusion length (EDL) in narrow bangap polymers.
+photoluminescense decay time is related and measurable.
+PCBM and PCDTBTs modeled with Monte Carlo--code available.
+They used P3HT as reference (5.4+/-0.7nm exciton diffusion length).
+Exciton diffusion is essential for organic solar cells.
+excitons are electron hole pairs created by excitation due to light absorption.
+they are separated into free charges at an interface which creates current.
+the movement of the excitons through hopping is what is refered to as diffusion.
+Exciton diffusion length is a factor in device efficiency.
+Other methods to measure EDL are fluorescence quenching - the dependence of the exciton quenching efficiency vs semiconductor thickness is fit to 1D diffusion equation.
+Pros: direct measuremnt, cons: difficult experimentally and there are many things to consider in the model (FRET, effect of polymer-vaccuum interface, optical interference).
+This paper uses MC to model PL decay.
+(Losing focus come back tomorrow)
+\cite{Alessandri2017b}
+\cite{Scharber2013}
+\cite{Scharber2006a}
+\cite{Yu1995}
+\cite{Halls1995}
+\cite{Kim2006}
+\cite{Lee2011}
+\cite{Huang2010}
+\cite{Jankowski2013}
+\cite{Marsh2014}
+\cite{}
+\cite{}
+\cite{}
+\cite{}
+\cite{}
+\cite{}
+\cite{}
+\cite{}
+\cite{}
+\cite{}
+\cite{}
+\cite{}
+
 \bibliography{library}

### 2020-05-15 paper.tex
fixed mendeley library finally? reading opv review

@@
 (Losing focus come back tomorrow)
-\cite{Alessandri2017b}
+
+Ugh. I think I've finally fixed my Mendeley library?
 \cite{Scharber2013}
+Review of state-of-the-art OPV BHJ solar cells. 
+pros: thin/light, semitransparent, cheap, continuous production process, short payback times, easy to integrate into new and existing products. 
+History of development from 2001 2.5\% PCE to 2011 10\% PCE.
+Most degrade when exposed to air and sunlight within a few years.
+Molecular structure including side chains affects stability.
+Electron affinity of the acceptor determines degradation rate of the semiconductor.
+Changing the elctrode and using the inverted design(?
+read waldauf) helps the electrode oxidation.
+This requires no vacuum
+They discuss BHJ morphology and how the A and D regions need to be small enough that an exciton could find it's way to an interface but not so small that once the charge is separated and current is generated at that interface that the current couldn't get to the electrode.
+The ideal is an interlocked comb structure but in reality solution processed OPVs form patches.
+This review is not about morphology (they recommened Hoppe2004).
+Morphology can only effect the efficiency of an AD pair, not the ultimately efficiency limit.
+This depends on the bandgap and electron affinities of the DA moeities.
+fig 5 explains inverted design a bit. 
+They discuss costs and efficiencies.
+Should probably read about Shockley Queisser Limit.
+(ref 47) based on analysis of pn solar cell they say the max efficiency is 30\% and the optimum band gap in 1.1 eV.
+Archer and Bolton roughly confirm this -- much of the light energy is lost because the photon is too small to excite the absorber, other loss is due to intraband thermalization of charge carriers (?), 12\% entropic loss, 1\% radiative recombination.
+Assumption of the Shockley Queisser limit
+1. each absorbed photon generates and e/hole pair
+2. perfect charge collection
+3. radiative recombination as the only recombination.
+Based on this work and the external radiative efficiency (ERE) proposed by Green, and actual max of 15-16\% efficiency is predicted.
+(continue from 5)
+\cite{Waldauf2006}
+Read this with intention of understanding inverted design only
+\cite{Hoppe2004}
 \cite{Scharber2006a}

### 2020-05-18 paper.tex
read solar cell review

@@
 \cite{Waldauf2006}
-Read this with intention of understanding inverted design only
+Read this with intention of understanding inverted design
 \cite{Hoppe2004}
+Overview of organic solar cells.
+sp2 hybridization of carbon is what allows organics to absorb in the uv-vis range.
+(conjugated pi orbitals.) In comparison, inorganic semiconductors have low mobilities but very high absorption coefficients.
+The exciton diffusion length is shorter in OPVs too.
+Most OPV are hole conductors and have band gap around 2 eV, which is higher than silicon. But the ability to modify and tune the chemistry as well as the cheap, mass production makes OPVs enticing.
+history: 
+first OPVs were single organics layers sandwiched between two metals with different work functions. (Evac - Efermi) 0.7\% PCE
+next bilayer heterojuctions-- two organic layers between electrodes (e.g. perylene and phtalocyanine) 1\% PCE
+C60 introduced, polymer fullerene bilayer heterojunction.
+Bulk heterojunction 2\% PCE
+(This article only discusses up to 4\% PCE and does not provide specific explanation for the increase)
+common structure is hole-conducting polymer with electron acceptor (C60 as in PCBM).
+Solution processable due to side chains.
+Preferential orientation of polymer backbones parallel to the substrate gives rise to anisotropic CT.
+In BHJ cells CT is sensitive to the morphology.
+OPV energy generation steps: 
+1. absorption
+2. exciton diffusion
+3. charge separation
+4. charge transport
+PCE depends on # photons absorbed, dissociated, and that reach the electrode.
+Number absorbed depends on the absorption spectrum, absorption coefficient and layer thickness.
+The fraction of excitons which dissociate depends on the exciton dissociation length and the charge separation probability at the interface.
+Finally the the number of charges which reach the electrode depends on the driving force or gradient resulting from the potentials of the elctrons and holes.
+thin films (<100nm) are usually field drift dominated others have enough screening are dominated by concentration gradients at the contacts.
+I skipped over devices.
+concepts for improvement:
+metal electrodes quench electrons in C60 so an transparent, exciton-blocking layer is between electrode and layer with C60. ultrathin LiF interfacial layer is one example. 
+Increase the absorption range. smaller band gap <2eV ~800-900 nm.
+morphology controls.
+to control size of fullerene domains in p3ht/fullerene, a plasticizer was added.
+This increase miscibility of polymer and fullerene creating smaller domains.
+Solvent/evaporation time, surface interaction, and annealing all have a large effect of the morphology.
+
 \cite{Scharber2006a}

### 2020-05-20 paper.tex
reading about PCE of donor molecules in BHJ

@@
 \cite{Scharber2006a}
+Design rules for donor in BHJ solar cells
+interpenetrating network of C60 and conjugated polymer have shown ultrafast charge transfer (~40 fs).
+There is no competing decay process in this timeframe.
+optimized mixture with C60 converts absorbed photons to electrons with efficiency close to 100\%.
+At time of publishing best PCE is ~5\%.
+Efficiency is limited by low open circuit voltage of device under illumination.
+Organic semiconductors with bandgap of 2eV are used but observed $V_{oc}$ is in the range of 0.5-1 V.
+$V_{oc}$ in a metal-insulator-metal is equal to the work-function difference of the two electrodes.
+In polymer-fullerene $V_{oc}$ is affected by the morphology of active layer, electrochemical potential of the cathode.
+Ref 15 (Gadisa) studied correlation between electrochemistry andVoc of  polymer fullerene with PCBM and polythiophene and found that variation of the oxidation potential of the polymer caused variation in the photovoltage.
+(This is not the same as $V_{oc}$ ?) This paper suggests that Voc is related to HOMO of the polymer.
+and thus the maximum efficiency can be predicted.
+I am confused by a lot in the paper and don't understand why Voc is the limiting factor.
+Fig 2 is interesting, shows how they predict PCE from HOMO/LUMO and bandgap.
+Should Eg (bandgap) be LUMO acceptor - HOMO donor?
+OK so they don't really give suggestions for what kind of chemistry makes a better donor, but they do say that measuring the HOMO of the donor can tell a lot about the PCE of the device.
+
 \cite{Yu1995}

### 2020-05-22 paper.tex
older paper about BHJ efficieny

@@
 \cite{Yu1995}
+
+Older paper about BHJs. (is this maybe the first about ADA BHJ?) MEH-PPV efficient charge transfer result from bicontinuous network
+time scale for CT from donor to acceptor is <picosecond, $10^{3}$ x faster than radiative/nonradiative decay, so efficiency is near 100\%.
+Just adding 1\% C60 increase photoconductivity by order of magnitude.
+conversion efficiency in a bilayer heterojunction device is limited when photoexcited exciton can't get to the interface.
+So an interpenetrating network is ideal because it maximizes interfacial area and minimizes the distance and exciton must travel to reach an interface.and if the network is bicontinuous then transfer of the charge to the electrode should be just as efficient.
+ITO (indium tin oxide) I thought was to prevent the active layer being quenched by the metal but they're saying it's the anode? PCBM is a soluble C60 derivitive. Ca electrode used.
+Pure MEH-PPV Voc 1.6V is consistent with the difference in work function of Ca and ITO. In the MEH-PPV/PCBM mix the turn on current shifts lower by 0.8V thus LUMO of PCBM is 0.8eV below Efermi of Ca. 
+They predict greater efficiencies if the morphology is optimized.
+
 \cite{Halls1995}

### 2020-05-26 paper.tex
reading older paper about PPV mixture photodetector

@@
 \cite{Halls1995}
+another older paper.
+Cavendish lab!
+Photovoltaic effect - production of electrons/holes under illumination.
+Molecular semiconductors produce excitons instead of free charges.
+Charge collection requires dissociation, which is efficient at interfaces of different electron affinities and ionization potentials.
+(electron goes to larger electron affinity and hole to lower ionization potential.) A layered structure then seems ideal, but Exciton diffusion length is much shorter than the absorption depth.
+so an interpenetrating network is shwon in this paper to be ideal.
+poly-phenylenevinylene derivitive mixture MEH-PPV and CN-PPV.
+spin coating on glass slide.
+they claim phase separation on the scale of 10-100nm this measurement relied on ferric chloride doping MEH-PPV but not the CN derivitive.
+The current vs Voltage graph for the mixture was very different under illumination.
+they predict these sort of flexible polymer photodetectors will be useful in medical imaging.
 \cite{Kim2006}

### 2020-05-27 paper.tex
add gartner to read
reading arthi's paper!

@@
 they predict these sort of flexible polymer photodetectors will be useful in medical imaging.
+
+\cite{Gartner2019a}
+Somehow didn't add this!
+University of delaware. There is a Jankowski/Marsh image in Fig 1!
+OMG I just realised this is Arthi from the MoSDeF calls. :D No wonder this paper is so approachable!! 
+Atomistic structures, not always more accurate, can't compute polymer chain level rearrangement
+CG -- chemists might not like them but physicists do
+atomistic simulations are good when you already know the chain configuration at a state point.
+Atomistic FF are still tailored to fit the properties of specific systems.
+got distracted today...
+will continue with II.B tomorrow
 \cite{Kim2006}

### 2020-05-28 paper.tex
more reading need to add ref about systematic CGing!

@@
 will continue with II.B tomorrow
+OK back to it
+CG - intermediate resolution (group of atoms within a monomer), CG monomer (whole monomer), mesoscale CG model (group of monomers on the length of a Kuhn segment or the whole chain.
+Finer models are parameterized to represent specific chemistries while coarse models are more generic.
+finer models can be parameterized with IBI for structure or force matching or relative entropy matching.
+the level of coarseness should depend on what features you want to examine.
+MARTINI - generic model 3-5 heavy atoms are grouped together each bead is assigned polar/apolar/donor/acceptor etc based on the chemistry/connectivity.
+soft potentials can be used for CG beads like DPD -- can have unphysically high compressibility
+!!! Systematic coarse graining approaches refs (87,91,269-273)
+start reading tomorrow at pt III
 \cite{Kim2006}

### 2020-05-29 paper.tex
added new refs from arthi's paper!
reading more arthis paper--very good but LOGN

@@
 start reading tomorrow at pt III
+
+simulation method (MC or MD) three steps
+1. create/initialize system
+2. equilibrate
+3. sample
+all steps should avoid bias.
+also choose ensemble, thermostat, barostat...
+choose for what you want to know.
+e.g.
+phase behavior - GCMC or GEMC phase coexistence with bead insertion/deletion.
+don't have to model the interface.
+Ref 308 is a GEMD method devolped by Arthi's group!
+
+Size: big enough that you can observe the phenomena you looking for.
+Calculating Flory-Huggins or polymer-polymer second virial coeff require long length scales.
+phase separations must also be larger than the length scale of the concentration fluctuations.
+However if interested indilute-soln properties like chain configuration or scaling laws--single chain even can be appropriate.
+finite size effects emerge from self interaction with the periodic image and limited size of box/system.
+smaller size can lead to pressure and stress fluctuation preventing calculation of mechanical properties.
+good rule of thumb -- box length to radius of gyration should be L/Rg >= 5.
+
+initialization: random initialization might be fine if system is isotropic but not at high density.
+A procedure to initialize high density CG polymer melts which uses MC with no intrachain moves and soft MD is described.
+an important metric for chain configuration is mean squared internal distance (measure of atoms or beads separated by n bonds along the chain).
+shows perturbations in internal chain not shown by the radius of gyration or end to end distance.
+We use a shrink-step, but that isn't mentioned here...
+
+Equilibration:
+relaxation in chain configuration is slow compared to relaxation of chain level metrics (like the mean squared interanl distance) or check MSD of CoM of polymer chains -- if they diffuse nultiples of Rg over equilibration, the system is relaxed.
+annealing processes (change T and P (also V???)) can help equillibrate.
+also mimic experiment.
+Start again at p.11 Sampling
+\cite{Muller-Plathe2002}
+\cite{Ayton2007a}
+\cite{Peter2009c}
+\cite{Baschnagel2000}
+\cite{Brini2013}
+\cite{Murtola2009a}
+\cite{Peter2009d}
+
 \cite{Kim2006}
@@
 \cite{Marsh2014}
-\cite{}
-\cite{}
-\cite{}
-\cite{}
-\cite{}
-\cite{}
-\cite{}
-\cite{}
-\cite{}
-\cite{}
-\cite{}
-\cite{}
 

### 2020-06-01 paper.tex
reading more of arthis paper. lots of useful info!

@@
 Start again at p.11 Sampling
+decorrelation is expecially important for polymers as the relax very slowly.
+Calculate the decorrelation time of a property of interest like Rg (for polymers this might be better than the decorrelation of the potential energy!)
+for systems with high energy barriers to rearrangement, small independent simulations may be better than independent snapshots from one simulation.
+Advanced sampling techniques: umbrella, Wang-Landau, adaptive force biasing, etc. used to explore free energy landscapes with mulitple barrier between minima more efficiently.
+Analysis - focused on structural and thermodynamic properties -- not dynamic properties.
+Looking at simulations is great, but it must be paired with quantitative analysis.
+Always report error bars.
+good way to do this is block averaging: simulation (trajectory?) is split into blocks the mean value of a quantity of interest is computed in each block, the average and std dev of the mean from each block which then become the ensemble average and std err for the entire simulation.
+RDF and structure factor characterize system of many length scales as well as allow access to thermodynamic quantities of interest.
+Sq can be directly compared with experiment and analysis of low q (long length scale) provides insight about phase separation and concentration/density fluctuations.
+However--range of q that can be accessed in simulations is limited to longest real-space distance that can be reliably sampled in box.
+Two methods to calculate Sq (fourier transform of g(r) and summation method) the fourier transform can introduce unphysical artifacts because it is only rigorously defined over infinite spatial domain (impossible for a simulation box.)
+other scattering techniques include reflectivity, small-angle/wide-angle scattering, diffraction (jankowski marsh paper cited!).
+They even mention dynamic S(q,t) can be used to understand chain relaxation.
+Flory Huggin parameter - lattice model of thermodynamics of polymer solutions takes into account different molecular sizes when calculating entropy of mixing.
+(this paper goes into depth about a specific thing about this parameter but as I have only just heard of it -- the summary above is from wikipedia-- I don't understand what it is talking about yet)
+Phase Transitions - different order parameters (Rg, end-to-end distance, etc) may be necessary to find a phase transition. Simulations that use a temp/pressure ramp may show hysteresis. 
+Using analysis software - make sure to validate using previously published results.
+Made it to section IV! finish paper tomorrow. :)
 \cite{Muller-Plathe2002}

### 2020-06-02 paper.tex
finished arthi's paper

@@
 Made it to section IV! finish paper tomorrow. :)
+Comparison with experiments - CG model can have quantitative agreement with universal parameters based on polymer physics like polymer chain size scaling with MW.
+Otherwise it is unreasonable to expect quantitative agreement.
+Although they may have agreement for more physical parameters, same goes for atomistic systems.
+Always need to recognise the limits of your model and have good expectations.
+Example: Tg in glassy polymers often found by the intersection of linear fits of density vs temperature above and below transition temp.
+To obtain density vs T the system is gradually cooled but even the slowest cooling rate is ~10 orders of magnitude faster than experiment.
+This is known to raise Tg significantly.
+Tg needs correction.
+but it is useful to examine trends in Tg--polymer architecture, chemistry, MW.
+and expect similar trends in experiment.
+Because of free energy landscape flattening in CG, dynamics can only be qualitatively compared. Also keep in mind when comparing to an instrumental analysis, the limits of the instrument.
+Comparison to theory - limitations include finite size effects, inability to capture phenomena without advanced sampling, inability to capture time scales (fast molecular vibrations vs polymer relaxation).
+Combined simulation with theory where simulation feeds parameters into the theory model.
+DFT-with MD/MC can be used to calculate the free energies in structure during solvent evaporation.
+PRISM - don't quite understand what this is something like a way of understanding the structure of a polymer morphology?
+Finished! OK paper takeaways -- autocorrelation for polymers shouldn't be based on PE, need to learn how to calculated some of the polymer metrics.
 \cite{Muller-Plathe2002}

### 2020-06-03 paper.tex
reading about CG/backmapping

@@
 Finished! OK paper takeaways -- autocorrelation for polymers shouldn't be based on PE, need to learn how to calculated some of the polymer metrics.
+
 \cite{Muller-Plathe2002}
+
+linking length and time scales.
+Analogy plant cell metabolism is very fast but tree death due to pollution is very slow; it is unecessary to measure tree dieback every milisecond.
+this analogy in chemistry ca go from observing bonding with electron wavefunctions, to modelling solvation with explicit water and FF, to modelling the flow of bulk water with a continuum characterized with various parameters.
+coarse grain models are built rigorously through converting the results of a fine grain system to the parameters of the coarser system.
+This efficiency gain allows us to indirectly predict large-scale and long-time quantities.
+Backmapping allows the coarse method to generate *samples* for the fine-grain method.
+mapping atom to coarse grain bead reduces the DOF and the effective potential account for the missing DOF.
+CG potentials are usually softer which allows larger time-steps.
+CG models are specific, tuned to a specific chemistry and to reproduce a specific structural or thermodynamic feature.
+A penalty function can be used to determine how far off the CG model is.
+The degree of coarse-graining and where the beads are placed can affect the success of reproducing the structural/thermo feature.
+They show an example of a diphenyl carbonate represented by 3,2,1 beads.
+The 3 bead structure easily replicates the atomistic RDF with just LJ6-12, the 2 and 1 bead structures do not, but the 1 bead structure can be made to fit the atomistic rdf if a piecewise potential is used (overfitting?)
+Cg optimization procedures: two procedure are describe here the first optimizes Gaussian functions--I don't understand what or how they are optimizing.
+the other uses elliptical potentials to give space filling at experimental density.
+start next time at section 3.3
+
+\cite{Reith2003a}
 \cite{Ayton2007a}

### 2020-06-05 paper.tex
finished muller-plathe

@@
 start next time at section 3.3
-
+Using a DOF distribution (pairwise, bond stretch, angle) to get a CG potential.
+An analitical function.
+the potential obtained this way really is a free energy not a potential energy.
+It incorporates effects from finite temperature and neglected degrees of freedom.
+IBI is a way to get a numerical potential (For IBI Reith is cited -- he appears to be Muller-Plathe's PhD student.) The description of IBI is really concise and clear.
+:) IBI is a tabulated potential.
+They describe two other methods.
+Potentials can also be optimized to match thermodynamic targets. They discuss how to add a cutoff value to IBI potential. also cite a paper that adds pressure information to numerical potentials.
+skipping lattice models.
+Atomistic -> derived CG potential -> CG sim -> backmap to atomistic -> local relax. 
+Seems roundabout but it's not!
+Smoothing of the PE surface in CG allows easier access to polymer morphology.
+CG can provide starting structures to atomistic MD.
+which can then be inputs to electronic structure calculations.
+CG is so much more efficient we can calculate chain properties. AUTOMIZATION IS KEY (IBI, simplex). The intellectually challenging part of CGing is where to place the beads!!
+errors in atomistic FF will filter to CG ff.
+CG models are specific to the conditions under which the parameterization is performed.
 \cite{Reith2003a}

### 2020-06-08 paper.tex
read Reith paper -- I think I had read this one before, but now I'm aware it's the first IBI CG paper :)

@@
 CG models are specific to the conditions under which the parameterization is performed.
+
 \cite{Reith2003a}
+IBI algorithm is made in this paper! Uses potentials of mean force. IBI potentials are nontransferrable--they work best for the system they are optimized for.
+CG allows chain behavior to be studied.
+History: bead spring polymer chains in a melt to a soft-core liquid ellipsoidal particles with anisotropic gaussian potential.
+polymer melt cg-ing.
+None of these derived an automated optimization scheme to conserve the chemical nature of the underlying atomistic model in a standardized way as we do.
+PRISM theory combined with MC can predict long and short range structures of polymer chains but can't produce CG potentials.
+Reverce MC can reproduce RDF without a need for potential. lack of potential limits usefulness though because RMC uses knowledge of RDF without knowing underlying forces.
+Description of IBI algorithm: potential of mean force IS boltzmann inversion of RDF. (Free energy NOT potential energy.) Bending potentials before nonbonded potentials.
+They used a five point running average to smooth the potentials
+bond stretch -> angle bend -> nonbonded -> dihedral
+They started with monoatomic liquids with LJ and WCA potentials (1) they used the correct potential as V0. (2) then they used the boltzmann inverse of the RDF. 
+Conclusions:
+start with small range (cutoff?) and increase until RDF matches. CG FF for polyisoprene are different between solution and melt.
 \cite{Ayton2007a}

### 2020-06-09 paper.tex
reading about force matching -- alternative to IBI

@@
 start with small range (cutoff?) and increase until RDF matches. CG FF for polyisoprene are different between solution and melt.
+
 \cite{Ayton2007a}
+Coarse graining scheme, systematic, for biological systems.
+If CGing is done systematicall it retains important averaged atomistic level interations.
+Connecting length and time scales.Systematic methods for making CG systems: RMC, this paper will focus on multiscale coarse graining (MS-CG) uses force matching algorithm
+Variational.
+Some of the math does not make sense but it appears to only be based on positions of atomistic and CG particles.
+They make the free energies of the atomisitic and CG systems the same.
+Many atomistic frames are mapped to CG beads and the potentials are based in the gradient of the forces felt by the beads.
+The algorithm minimizes a residual function.
+Summary: works, RDFs match.
+Enables calculation of CG force fields without resolving many-dimensional potential of mean force.
+(but honestly IBI seems so much simpler.
+Is there something I'm missing?
+is boltzmann inverse of RDF not PMF??
+This paper was published after Reith paper...
+when is force matching better?)
+
 \cite{Peter2009c}

### 2020-06-11 paper.tex
start CG/backmap review paper from max planck institute

@@
 \cite{Peter2009c}
+Review paper- coarse grained models linked to atomistic models. 
+They mention the good, marginal, and poor solvent parameter Theta.
+models can be linked sequentially, hybrid - both level present at once and interacting, or adaptive - individual molecules switch on the fly depending on e.g., spatial coordinates.
+CG target can be thermodynamic or structural.
+Structure based: boltzmann inversion of distribution with constant to set minimum to 0.
+Free energy vs PMF?
+Boltzmann inversion usually results in a tabulated potential but by fitting to gaussians it can be mapped to an analytical function.
+Bonded potential can be determined on a single polymer chain in vacuo but then the nonbonded interactions have to be considered carefully to avoid double counting.
+However bonded and nonbonded can be obtained from the same atomistic simulation of polymer melt iteratively.
+This makes the potentials interdepent.
+IBI can also consider other thermodynamic quantities like pressure and compressibility. IBI not useful for dilute solutions
+start next time at backmapping
+
 \cite{Baschnagel2000}

### 2020-06-12 paper.tex
finished CG review paper

@@
 start next time at backmapping
+backmapping has no one unique soln.
+every CG structure corresponds to an ensemble of atomistic microstates.
+reinsert theatomistic structure so that the atoms still satisfy the CG mapping and then relax the atoms with position restraint to the CG position.
+CG backmapped to atomistic allows better comparison with experiment than atomistic alone by giving access to larger length and time scales.
+e.g., NMR timescales are too long to simulate with atomistic alone, yet atomistic coordinates are necessary.
+Dynamics: the CG model is independent and has it's own timestep. dynamics are accelerated.
 

### 2020-06-15 paper.tex
started v long review -- skim!!

@@
 \cite{Baschnagel2000}
+
+Bridging the gap between coarse and atomistic.
+Specific to polymers.
+This paper focuses on the mapping of atomistic to CG.
+(cool!
+first paper to focus there.) also discussed backmapping.
+Just noticed this paper is 150 PAGES LONG!
+OK time to skim.
+Polymers have properties which can be measured at many different length scales. diffusions constant can be measured by monitoring the center of gravity of the chains.
+It is too big and too slow and also just a bad idea to simulate huge boxes of atomistic polymers.
+Even if the simulation was to complete, there would be too much information to process accurately.
+CGing allows scientists to FOCUS their experiments.
+start next time section 2 (p8 of 116)
+
 \cite{Brini2013}

### 2020-06-16 paper.tex
:c this paper isnt as good as I thought

@@
 start next time section 2 (p8 of 116)
-
+Frozen nuclei approximation is incorrectly referred to as the Born-Oppenheimer approximation?
+Quantum chemistry is good for predicting bond and angle potentials but not for LJ because you would need huge basis sets and high order electron correlation.
+DFT has similar issues LDA results in overbinding and GCA no attraction.
+partial charges are conformation dependent.
+Quantum chem is very useful for parameterizing dihedrals!
+I skimmed this section v heavily but my takeaway is that if you need to know about a chemical reaction (transfer of electrons) it makes sense to consider QC methods.
+Also QC methods are not the cure-all for making forcefields.
+section 3 - how do we get dense systems?
+it is hard to change the system once it gets to a dense atomistic representation. so one should start with a good systm! (like from coarse-grain)
+This is tough because polymers are dense, amorphous, and highly-connected. three methods exist:
+1. add new segments according to the metropolis criterion
+2. coarse initials guesses created on a lattice
+3. low density condensed step by step using NPT
+they described a method of initializing using stream lines and vector fields which results in polymers of constant curvature.
+They describe a new rotational move that does a dihedral cis-trans flip.
+next time skim through the rest of this paper. I'm over it
 \cite{Brini2013}

### 2020-06-23 paper.tex
good section about chemistries of A/D in OPV

@@
 next time skim through the rest of this paper. I'm over it
+read mazzio paper!
+gave up on baschnagel paper--switching to mazzio!
+
+\cite{Mazzio2015}
+
+oh this paper is so much better. 
+opvs are lightwieght, low cost, flexible. Metrics for evaluating these are PCE, Levelized cost of energy (LCOE) and energy payback time (EPBT).
+LCOE is life cycle cost/energy produced. EPBT is how long it takes for a device to pay for itself.
+start next time at section 2
+inorganic: absorptions of photons with energies greater than the band gap results in free charge carriers that can separate at an p-n junction.
+they can diffuse under external electric field to electrodes.
+organic: lower dielectric constant which prevents screening of the attraction between electrons and holes this results in exciton formation rather than free charges.
+separation of the exciton requires an acceptor/donor interface.
+if the exciton doesn't reach an interface it will decay back to ground state resulting in the loss of that energy.
+donor: large ionization potential acceptor: high electron affinity.
+different loss mechanisms are discussed: geminate recombination is where the separated charges recombine across the interface.
+charge recombination where free charges recombine with unassociates charge carriers in a device.
+There is some about electrochem which I am reading but not understanding :( external quantum efficiency is a measure of how much current will be produced by a particular wavelength of light.
+it depends on the efficiency of photoabsorption, exciton diffusion, charge transfer, charge collection.
+CHARGE TRANSFER is not the same as CHARGE TRANSPORT
+ASTM reference spectra are used now to characterize and standardize OPV
+3. Device architectures
+some history about opvs: Tang 1979 introduced the two-component donor acceptor active layer with thermally evaporated small molecules. bilayer structure. limited by exciton diffusion length. 
+BHJ with fullerene acceptor reported by Yu in 1995 -still state of the art morphology.
+diagrams of different device architectures.
+start next time on section 4
+materials design (aka the good part :D )
+good opv acceptor/donors are solution processable, have appropriate band gaps and energy levels, and long planar pi-stacking for good charge carrier mobilities.
+regioregularity (head-tail vs head-head p3ht).
+Mn is the number average molecular weight of the polymers.
+weight of all polymers/number of chains.
+Mw is the molecular weight per unit weight of polymer (accounts for size distribution).
+dispersity is Mw/Mn.
+commonly used materials: initially poly(p-phenylene vinylene) (PPV) was very poplar.
+It was mixed with PCBM (c60) in first reported BHJ solar cells.
+now we have shifted away towards poly alkyl thiophenes like p3ht.
+p3ht/pcbm was max EQE of 76\%.
+post processing like thermal annealing with externall electric field produced devices with max PCE of 3.5\%.
+it has been shown the p3ht and pcbm have strong dependence on regioregularity.
+longer chains are shown to perform better, due to increased mobility with polymer aggregation.
+ways to decrease the band gap have become popular using DA polymers (alternating electron rich and electron poor heterocycles) PCDTBT achieved efficiency of 7.5\%.
+PTB7 had PCE of 7\% and then over 9\% due to promotion of the quinoidal resonance structure using thienothiophene.
+quinoidal stabilization improves shortcircuit current (Jsc) and fill factor (FF) which increase EQE and IQE so it has good exciton dissociation, charge transport and extraction.
+Some small molecule (not polymer) devices show promise.
+fullerenes are commonly used as acceptors.
+the added groups are to help solubility.
+pc61bm has limited absorption and deep lumo so it can be improved by using pc71bm which is less symmetric and has more allowed optical transitions.
+indeneC60 is being used to adjust the LUMO level.
+next time section5
+
 \cite{Brini2013}

### 2020-06-24 paper.tex
finsihed mazzio

@@
 next time section5
+morphology
+the ideal is an interpenetrating network of d-a materials with domain sizes on the order of the exciton diffusion length (10 nm).
+Enough interfacial area to dissociate lots of excitons while maintaining continuous charge transport pathways.
+Parameters that affect the active layer are solvent donor/acceptor concentrations, thermal annealing times/temps, solvent annealing, additives, and interlayer surface energies.
+solvent - vapor pressure, boiling point, viscosity, polarity, solubility, wettability dictate much of the initial film forming.
+solute properties like concentration, blend ratio, solubility also important.
+and finally the method of deposition matters-- high-throughput processing will require alternatives to spin coating but spin-coating is most widely used so it's what this review covers.
+switching the solvent in a PPV/PCBM from toluene to chlorobenzene improved performance by nearly three fold!
+the solvent allowed more mixed/smaller domain sizes.
+fullerene has better solubility in chlorobenzene.
+same active layer compounds in chlorobenzene or toluene, switching the total solute concentration and the ratios had an effect on the morphology but chlorobenzene prevented fullerene aggregation until very high loading.
+a study also showed that slow evaporation allowed for separation of p3ht/pcbm but fat allowed for formation of an amorphous glass.
+Thermal and solvent annealing allows for larger domains in p3ht/pcbm. annealing increase the hole mobility --> this is the most important factor in increased performance!
+Chen (ref 41) studied p3ht/pcbm with GIXD. found that annealing results in bicontinuous network of polymer/fullerene with domains on the order of the exciton diffusion length.
+Solvent annealing where layer is annealed under vapor.
+shown that poor solvents better enchance performance then good solvents.
+good solvents develop greater self-organization of p3ht -- but the domain were too big.
+solvent annealing promoted PCBM separatiun to the top of the device.
+interpentrating network has been the ideal, but crystalline regions of acceptor donor with mixed amorphous regions is more realistic.
 

### 2020-06-25 paper.tex
read about polymers next

@@
 \cite{Brini2013}
+review of systematic coarse-graining for soft materials
+focuses on representability (how well a system predicts properties at the statepoint it was optimized for) and transferrability ( how well it can be used for other statepoints.)
+effective pair potentials are used for CG instead of the expensive many-body potentials.
+averaging over fast degrees of freddom removes their entropic contribution.
+to compensate for this, the pair potentials are softer resulting in a smoothed energy landscape.
+this affects the thermodynamic properties-- e.g., the heat capacity, which is related to the entropy fluctions at constant t and p is underestimated by a cg model (because the fluctuations arent as large).
+while compressibility related to volume fluctuation will be over estimated (i think because the potentials are so soft.) The thermal expansion coefficient which is related to both may well be represented accurately.
+parameterized vs derived CG potentials - 1st one atomistic simulations are used to calculate target properties (pair correlations, force distributions) IBI is this.
+2nd one atomistic interaction are used directly.
+not optimized to reproduce selected tragets, therefore all properties are predictions of the model.
+Parameterized methods: IBI method described. 
+Inverse Monte Carlo - also an iteractive scheme that corrects a guessed interaction potential in order to reproduce a target radial distribution function, but the guess is based on statistical mechanics that take into account that a variation of the potential at a given distance r can lead to a variation of the RDF at all other distances.
+more expensive than IBI requires longer sims to calculate correlations.
+Can also include target thermo properties like surface tension.
+Both IBI and IMC are cases of relative entropy -- a measure of the amount of information lost upon coarse-graining and is defined in term of propability distributions of atomistic and CG systems.
+both methods minimize the discrepancy between the atomistic and CG distributions.
+Another method is force matching. effective pair potentials match the mean force on a particle through the atomistic force field.
+Derived methods: These potentials have a clear physical meaning (why?) potential of mean force calculated at LOW concentration. fragment based coarse graining
+skipped ahead to polymers
+
 \cite{Murtola2009a}

### 2020-06-26 paper.tex
finished polymer section and quick letter

@@
 skipped ahead to polymers
+polymers are important for cg because the volumes needed to observe their long length scale properties in atomistic md are prohibitively expensive.
+pressure-corrected IBI scheme for polystyrene matched gyration radius and Flory characteristic ratio at 500 K.
+(flory ratio relates to chain stiffness?) but entanglement length was overestimated.
 
 \cite{Murtola2009a}
+quick letter - to get the full picture we have to consider multiple length scales.
+abstracting small length scales is necessary for time/resources.
+probably dont include this in references, it's so short.
+
 \cite{Peter2009d}
+ooh this one looks cool. starts with history of membrane models, goes to cging, then moves to cg dynamics. for next time
 

### 2020-06-29 paper.tex
read berendsen concluding remarsk

@@
 
+\cite{Berendsen2010}
+ooh this one looks cool. starts with history of membrane models, goes to cging, then moves to cg dynamics. for next time
+many realistic process could not--and would never--be solvable by atomistic simulations.
+he describes a very simplified model of transport of a single water molecule through a membrane.
+reduce the system to motion in one reaction coordinate.
+the heart of coarse-graining is the reduction of degrees of freedom.
+then describing the dynamics of the reduced system so that it reproduces the projection of the complete system.
+this is only possible when the reduced and the removed degrees of freedom are well-separated (the removed are much faster).
+If the time scales are not separate the dynamic behavior will not be accurate but the probability distributions and thus the thermodynamic properties may still be.
+The choice of relevant dof is made on an intuitive basis and depends on what properties are wished to study. Note that atomistic md is already concerned reduced--no electronic dof.
+if a CG model does not predict any properties beyond the ones you have used for parameterization--you have achieved nothing! always require your model to predict something unknown.
+the motions in reduced space: the equations of motion are no longer hamiltonian--forces depend not only on the present but also the past configuration.
+Forces proportional to the velocity are non-conservative (kinetic energy is lost).
+in order to maintain average KE and T noise must be added.
+I skimmed the sections on dynamic equations and modelling fluids.
+simple methods that are easy to understand and implement--provided they are correct and work--will always prevail over complex methods, even if the latter are more accurate.
+
 \cite{Peter2009d}
-ooh this one looks cool. starts with history of membrane models, goes to cging, then moves to cg dynamics. for next time
 

### 2020-07-08 paper.tex
finished lee 2011

@@
 \cite{Vehoff2010a}
+
 rubrene record charge carrier $15 \frac{cm^{2}}{V s}$ single crystal by vapor deposition. typical for thin-film is $1 \frac{cm^{2}}{V s}$
@@
 It looks like they calculate the reorganization energy, but they don't define a chromophore--which makes sense for thiophene but what about when your molecule is ginormous?
-\cite{Ruhle2011b} discusses charge transport in amorphous films of [tris-(8-hydroxyquinoline)aluminum](https://en.wikipedia.org/wiki/Tris(8-hydroxyquinolinato)aluminium).
+
+\cite{Ruhle2011b}
+
+discusses charge transport in amorphous films of [tris-(8-hydroxyquinoline)aluminum](https://en.wikipedia.org/wiki/Tris(8-hydroxyquinolinato)aluminium).
 Oh Figure 1 is nice--it is a workflow of what can be done in votca.
@@
 
-Reading \cite{Hanson2016} also my mendeley overwriting my files because it thinks they are duplicates or something? It keeps losing the pdf even though I've uploaded it. :(
+Reading
+
+\cite{Hanson2016}
+
+also my mendeley overwriting my files because it thinks they are duplicates or something? It keeps losing the pdf even though I've uploaded it. :(
 SMILES - simplified molecular-input line-entry system
@@
 This paper is about specifically Jmol smiles so I'm skipping to a different one.
-\cite{Weininger1988} First paper about smiles- how do we unambiguously represent a chemical structure? historically CAS, graph theory, IUPAC.
+
+\cite{Weininger1988}
+
+First paper about smiles- how do we unambiguously represent a chemical structure? historically CAS, graph theory, IUPAC.
 human-readable and machine readable
@@
 
-\cite{Smith2018} reading about psi4: free and open source with python api that uses blas and c under the hood.
+\cite{Smith2018}
+
+reading about psi4: free and open source with python api that uses blas and c under the hood.
 has jupyter notebooks tutorials.
@@
 Today searched "coarse grain backmapping" in the library and got the following papers:
+
 \cite{Alessandri2017b}
@@
 \cite{Haxton2015a}
+
 CG beads with orientation.
@@
 \cite{Poblete2018a}
+
 RNA - backmapping steered MDaimed at minimizing a particular RMSD (ERMSD) between atomic and target structure.
@@
 \cite{Mikhnenko2012}
+
 Exciton diffusion length (EDL) in narrow bangap polymers.
@@
 Ugh. I think I've finally fixed my Mendeley library?
+
 \cite{Scharber2013}
+
 Review of state-of-the-art OPV BHJ solar cells. 
@@
 (continue from 5)
+
 \cite{Waldauf2006}
+
 Read this with intention of understanding inverted design
+
 \cite{Hoppe2004}
+
 Overview of organic solar cells.
@@
 \cite{Halls1995}
+
 another older paper.
@@
 \cite{Gartner2019a}
+
 Somehow didn't add this!
@@
 \cite{Reith2003a}
+
 IBI algorithm is made in this paper! Uses potentials of mean force. IBI potentials are nontransferrable--they work best for the system they are optimized for.
@@
 \cite{Ayton2007a}
+
 Coarse graining scheme, systematic, for biological systems.
@@
 
-\cite{Peter2009c}
+\cite{Peter2009d}
+
 Review paper- coarse grained models linked to atomistic models. 
@@
 \cite{Brini2013}
+
 review of systematic coarse-graining for soft materials
@@
 \cite{Murtola2009a}
+
 quick letter - to get the full picture we have to consider multiple length scales.
@@
 \cite{Berendsen2010}
+
 ooh this one looks cool. starts with history of membrane models, goes to cging, then moves to cg dynamics. for next time
@@
 
-\cite{Peter2009d}
+\cite{Kim2006}
 
-\cite{Kim2006}
+experiemental paper about effect of p3ht regioregularity in p3ht/fullerene blends on device performance--PCE.
+really useful schematic of GIXS experiment. (GIXRD)
+interplane pi-pi stacking is parallel to the substrate--enhanced interplane interactions with high RR p3ht benefit vertical (J-V) more than lateral (field-effect) transport.
+TOF hole mobility in p3ht films show neglible influence of RR.
+inteplane stacking does not affect vertical transport in pristine crystal.
+in the blend dark-current densities and TOF mobilities show stronger dependence on regioregularity.
+highest device efficiency achieved with RR p3ht
+
 \cite{Lee2011}
+
+multiscale simulation of p3ht and pcbm. 1 bead per p3ht and pcbm. They used IBI to get their force field.
+they use a penalty function to minimize their lj parameters-- I think this is different from IBI in that it doesn't use a table potential.
+their reverse mapping method could use a little clarification but it sounds like they replace CG bead (p3ht or pcbm monomer) with equilibrated atomisitc structure and then do only rotation moves until the whole system is relaxed.
+(thats kind of cool actually!) after MC they do quick MD.
+smoothing of the energy barriers i the CG sim accelerates the dynamics.
+CG morphology is in good agreement with TEM and electron tomography.
+with backmapping even pi-pi stacking was observed.
+they use a spatial discretization scheme to simplify the volume into voxels and quantify the interfacial area to volume ratio.
+as time goes on in the simulation the p3ht domain sizes grow and the interface to volume ratio decreases--this is a bad thing?
+is this related to the quick annealing having better results??
 \cite{Huang2010}

### 2020-07-09 paper.tex
read jankowski

@@
 is this related to the quick annealing having better results??
+
 \cite{Huang2010}
+
+CG polymer fullerene simulation of opvs.
+parameterized at two state points.
+it is still not know how to predict phase behavior based on components and processing.
+the molecular scale structure often has to be inferred.
+the relationship between phase behanvior and charge transport has been investigated but there is some disagreement.
+this is where simulation comes in. systems of only a few nm can be studied--but the exciton diffusion length is ~5-10 nm --> CG
+ff for super atoms are parameterized using atomistic ff.
+OPLS-AA 3-site p3ht and one site fullerene.
+They use IBI to parameterize their ff.
+they use a a scaling function to match the pressure.
+(i don't understand how this works exactly)
+they found that their model could be useful outside of the temps it was parameterized at. 
+they calculated the time scale of the cg model.
+they were able to compute 768 p3ht 48mers and (110592 beads) with 4608 pcbm beads in a 25 nm^3 box in about 24hr.
+
 \cite{Jankowski2013}
+
+opv performance strongly depends on morphology. ideal is to have high interfacial area while maintaining high connectivity. 
+choosing a model: sufficient chemical and physcial detail without too much to prevent sufficient sampling at relevant length and time scales.
+if the model is too coarse we miss intecalation of the fullerene between the side chains.
+order-disorder trainsition for neat polymers depend on side chain orientation (regioregularity?) and orientation along th polymer backbone. 
+immiscible acceptor in blends do not change the morphology compared to neat but increase the ODT.
+CG model gives backbone persistence lengths that match experiment. (has to do with bending stiffness of polymer)
+how were LJ params obtained for CG model?
+how to quantify interfacial area--acceptor-backbone correlation rdf first peak, 
+intercalated layer are seen as the acceptor miscibility is increased-- mostly with the most sparse polymer (do the acceptors feel the most attraction to the backbone?
+new lattices predicted--have these been observed?
+
 \cite{Marsh2014}

### 2020-07-09 paper.tex
reading some mosdef references

@@
 
+\cite{Cummings2019}
+each research group used to maintain their own code ,but now these codes are general purpose and shared.
+open source aid reproducibility because (1) users can look at the source code to find bug and these can be very quickly fixed, (2) monetary cost can exclude users who can't afford it.
+a disadvantage is that open source software may be less new user friendly and instead of a gui may use scripts.
+scripts are an advantage to reproducability however because they allow for user to show and version control exactly what they did with little to no ambiguity.
+GUI's may obscure the actual mehtod.
+ooh I want to look at etomica. hmm. doesnt work in my browser.
+overall this was a good summary of what exists but no big takeaways
+
 \bibliography{library}

### 2020-07-13 paper.tex
finished and added new paper to bib

@@
 \cite{Marsh2014}
+coarse grain simulations of thiophene polymers (3 site model).
+changing the spacing and regioregularity of the side chains results in different morphologies and can be related to different real compounds.
+orientation of side chains along the backbone is more significant than side chain density, side chain-side chain interactions, or side chain length.
+side chains on boths sides form lamellae--on one side form hexagonally packed cylinder which can transition at low temp to lamellae or ribbons depending on side chain interaction strength.
+interaction strength affects order-disorder transition temperature (ODT) stronger attraction=higher ODT.
+side chain length modulates the spacing between features such as cylinders or lamellae.
+mentions atomistic and 1 site model of p3ht.
+atomistic does not access time scales long enough to observe lamellae formation.
+1 site model couldn't see lamellae probably because there are no side chains.
+The CG model parameter are obtained in ref 29 added below. LJ potential is used for nonbonded. Harmonic bonding used.
+
+\cite{Schwarz2013}
+read this with the intention of understanding how the CG potentials were derived.
 
@@
 
+\cite{li2020}
+excited to read this! Andrew White was Rainier's advisor.
+
 \bibliography{library}

### 2020-07-14 reading-notes.tex
read Schwarz

--- 2020-07-13 paper.tex
@@
 read this with the intention of understanding how the CG potentials were derived.
+OK I don't know what Langevin dynamics are but I think it means modelling molecular systems with reduced degrees of freedom and accounting for omitted dof using random kicks to the system??
+Mimics solvent or atmospheric effects.
+CG model matches experimental phase behaviour. 
+ooh really nice figure showing the different length scales (diffraction peaks) in p3ht
+diffraction can't resolve molecular level interactions.
+this paper describes p3ht nanostructure formation in solution
+model: equilibrium bond lengths, angles, charges from DFT. Based on OPLSAA. model agrees with density crystal structure, heat of sublimation. CG FF determined using IBI.
+Simulations appear really low density compared to what I'm used to seeing.
 

### 2020-07-15 reading-notes.tex
writing for the day about what automated mapping exists
read Zhang

@@
 \cite{Cummings2019}
+
 each research group used to maintain their own code ,but now these codes are general purpose and shared.
@@
 
+\cite{Zhang2008}
+
+next time read this and write about mapping operators
+essential dynamics coarse-graining.
+replacing large and complex domains of biomolecules with relatively few CG sites.
+CG map variationally determined to best reflect the essential dynamics.
+CG model designed to explore protein conformational space.
+processes tht occur on length and time sclaes far beyond simulations with atomic resolution (virus capsid assembly,etc) 
+two facets -- number of CG sites and location.
+for lipids or peptides it is reasonable to replace each functional group with a bead.
+different levels of resolution for each amino acid.
+but when looking at HIV capsid composed of thousand of CA protein dimers each CA composed of >200 residues we need a few CG sites per dimer.
+actin filaments are a similar problem.
+other solutions: 
+- (shape focused) rigid units defined by a topological algorithm (like a hard polygon?)  
+- (movement focused) CG map that reflects collective motions determined by principle component analysis.
+small number of PCA modes which define essential dynamics.
+basically this article is about choosing sites that will best reflect the movements of a protein using math.
+
+\cite{Cao2015a}
+
 \cite{li2020}

### 2020-07-15 reading-notes.tex
chores done for today--learned that martini isn't as cool as I thought for new molecules!!

@@
 \cite{Cao2015a}
+if the properties you are interested in a electrostatic, then a CG mapping operator based on centers of charge in the molecule should be best.
+mapping operators are chosen based on desired resolution and the information to be extracted.
+straightforward way is to group three or four heavy atoms together.
+In the MARTINI force field four types of atoms are grouped and the bead is classified as polar, non-polar, apolar, or charged.
+use chemical intuition--e.g. what parts of the molecule shouldn't be allowed to bend?
 

### 2020-07-16 reading-notes.tex
reading about trappe next time write about CG models

@@
 TraPPE\cite{Maerzke2011}
+it is generally assumed that coarse-grain potentials are not transferrable to different systems or state points (T and P).
+This model tries to fix that.
+uses IBI for bonded interactions and parameterize nonbonded interaction by fitting to vapor-liquid coexistence curves.
+parameters yield accurate vapor-liquid equilibria, first RDF peak, and coordination number for the solvation shell.
+PMF represents enemble average free energy of FG model therefore it is limited to the same thermodynamic conditions.
+But the CG potential can also be viewed as an effective potential that is able to represent the interaction over wider range of condition--like how LJ represents pair and many-body interactions.
+Transferrable potentials may sacrifice accuracy at a specific potential.
+IBI matches the shape but not the depth of the potential.
+structure of a liquid is mostly determined by repulsive interactions.
+Ref 17 was able to recover correct potential (after 1000 iter!) even though rdf appeared converged after 10(!!).
+adding pressure or energy to the iterative scheme sped up the convergence.
+Pressure and energy corrections can improve performance.
+Force matching does not rely on ensemble averaged property and has sounds statistical mechanics basis. variational.
+MARTINI uses shifted LJ and params were fit to free energies of vaporization/hydration/partitioning between water/organics phases at 300K. 
+the params of these ffs may be transferrable to different molecules (eg. alkyl chain can be used in different molecules) but not across different state points.
+TraPPE-CG - minimize number of atom types.
+parameterized to TraPPE UA based on saturated vapor/liquid densities, internal energy of vaporization, transfer free energies are given greatest weight, rdf also considered.
+tabulated potential spaced by 0.05 A with linear interpolation.
+shifted so that U=0 at rcut=14A
+
+Check ref 29 -- popular cg model
+
+\cite{Shelley2001}
 
@@
 excited to read this! Andrew White was Rainier's advisor.
+automated mapping. treats mapping operators and a graph segmentation problemusing a neural network. the network is trained on a dataset of molecule with expert annotated mapping. 
+how do they rate the results?
+they try to see if their network can predict the human chosen mappings. I wonder how it'll do with new molecules?? CG mappings are usually designed for a specific property.
+chakraborty graph method used to atoselect based on entropy flattening
+what is entropy flattening?
+
+ref 35 sounds interesting--auto encoder that learns CG mapping and FF at once!
+ref 21 suggests low-res CG models are information limited not representation limited--maybe there is a way to enhance CG model without increasing complexity.
+supported by ref 5 saying alkane model performance was not correlated to resolution (skeptic??)
+mappings currently are intuition based with some rules
+using clustering (like k-means) to choose mapping
+this method uses clustering and graph
+they use scikit learn!
+they try out new mapping of sars-cov-2! (training dataset did not contain peptides...) prediction is similar to spectral clustering
+compared to martini and used again on peptides, mixed results.
 

### 2020-07-17 reading-notes.tex
reading Moore and writing about CG potential dev

@@
 
+\cite{Moore2014}
+IBI that includes data from multiple targets to yield a less state dependent potential.
+i feel pretty confident in my understanding of ibi after making my own MWE
+how are the state points combined?
+separate potentials are required to capture solid and fluid structures of a pure simple lipid ref 46
+IBI potentials are sometimes transferrable and it is not clear why sometimes they are and sometimes they aren't.
+the potentials are an average, basically of the potentials at the different states with a weighting function to put emphasis on the desired state
+Don't pick states that are too similar because then the overlap region is too large and there are too many possible solutions.
+for some systems there may not be a potential that represents all states-- this is not unique to coarse potentials, atomistic potentials also have this limitation.
+
 \bibliography{library}

### 2020-07-20 reading-notes.tex
reading about CG lipid bilayers

@@
 \cite{Shelley2001}
+CG model for phospholipids.
+parameterized to mimic structural properties--which ones?
+they were fit to bond distributions (algorithm sounds like IBI but they don't say IBI...
+anyway it's iterative based on Boltzmann inverse of RDF)
+reproduces structure of bilayer--property that was not directly fit. The initial configuration was random. 
+how do they verify that it reproduces the bilayer? rdfs, density maps, also snapshots.
 

### 2020-07-22 outline.tex
reading/writing for the day

# what has been done
<should I start with simulation in general?>
<start with what simplifying assumptions MD already makes>
##coarse graining
Coarse-grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models. Coarse-graining refers to grouping atom in a structure into a "super-atom" and using an effective potential to represent the resulting coarse grain site. The resolution of coarse-grain systems is broad: simply grouping hydrogens with the heavy atom they are bonded to (united-atom model) <what to say about united atom?>\cite{Paul1995a, Yang2006a,}, grouping functional groups together <cite>, or as far a representing an entire amino acid with a single site <cite>. Which model is right depends on the length and time scale on which the property of interest can be observed. 
General coarse grain models of opv thiophene polymers where only the spacing, regioregularity of the side chains were varied were able to predict different order disorder transitions and calculated scattering patterns of these simple simples were comparable to those obtained from experiment \cite{Jankowski2013, Marsh2014} 
A coarse-grain model for phospholipids has allowed for bilayer formation from an initial random configuration to be observed even though the model was parameterized to the vapor-liquid phase transition. \cite{Shelley2001}
<how cg potentials have been obtained>
<IBI>
<why are IBI potentials not transferrable? the RDF is a property of the ensemble average at a given statepoint so the potential derived from this property is also limited.>
separate potentials are required to capture solid and fluid structures of a pure simple lipid <Moore2014 ref 46>
<IBI potentials are sometimes transferrable and it is not clear why sometimes they are and sometimes they aren't.> \cite{Moore2014}

Multistate iterative Boltzmann inversion (MS IBI) includes data from multiple targets to yield a less state dependent potential. \cite{Moore2014}
The MS IBI potential is an average of the single state potentials with a weighting function to prioritize a state of interest.
This method has been shown to accurately reproduce the true potential in monoatomic LJ fluid. 
When using the MS IBI method, it is important to choose dissimilar states to minimize the potential overlap region. If this overlap region is large, there are many potentials which will provide matching RDFs. For some systems there may not be a potential that represents all states-- this is not unique to coarse potentials, atomistic potentials also have this limitation.

TraPPE fits CG potentials using vapor-liquid equilibria to improve transferrability across thermodynamic states\cite{Maerzke2011}
<Talk about what exists and why it is not enough>
<votca, Peng2019a>

reproducibility crisis.\cite{Cummings2019} \cite{Thompson2020} (TRUE paper) poorly documented code and raw data doesn't help. 
instead example workflows with docker containers to build software stack. help make science more accessible and reprodicible.

the one part of coarse graining that is not yet automated is choosing a mapping scheme or a mapping operator. A mapping operator defines which atoms are grouped into a "super atom" represented by one coarse grain site and an effective potential and where in the site is placed relative to the atom group.
mapping operators are chosen based on desired resolution of the coarse grain system and the information to be extracted. 
A straightforward way to define a mapping operator is to group a set number of heavy atoms (non hydrogen) together--this is the method used in the MARTINI force field. \cite{Marrink2007} In this scheme, four atoms (except rings, which are treated differently) are grouped and the site is classified as polar, non-polar, apolar, or charged depending on the atoms it is composed of. When parameterizing a new molecule you must pick a mapping and thencompare the resulting beads to existing beads--time consuming and error prone.\cite{http://www.cgmartini.nl/index.php/tutorials-general-introduction-gmx5/parametrzining-new-molecule-gmx5} This force field was designed for lipids and has shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.
use chemical intuition--e.g. what parts of the molecule shouldn't be allowed to bend?
there have been efforts to create mapping schemes for automating the process of deciding which atoms are grouped in a "super-atom" bead. 
As the number of atoms in the fine grain structure increases, the number of possible mappings increase drastically. The number of allowed mappings can be reduced by only allowing those which do not change the symmetry group, then an algorithm can iterate over a graph of all possible mappings the "best" mapping being the one which minimizes the difference between the mapped RDF and velocity autocorrelation function. \cite{Chakraborty2018a}
Another mapping scheme uses principle component analysis to choose a mapping scheme for biomolecules that best represents th essential dynamics. \cite{Zhang2008}
\cite{li2020} mapping operators can be automated using a machine learning: clustering methods combined with graph analysis were shown to predict the "expert" mapping chosen using chemical intuition reliably.
In order to probe electrostatic properties, a mapping operator based on the centers of charge is described\cite{Cao2015a}
We do not propose a new automated mapping, but instead a way to make the mapping and backmapping process easier for the user.
Simplified Molecular Input Line Entry System or SMILES \cite{Weininger} was designed to represent organic molecules in an unambiguous way (similar to IUPAC) but in a line-entry system which is also readable by a computer.
This makes it a good candidate for specifying a coarse-grain mapping scheme.The open-source package, Openbabel, allows for a SMILES string to be converted to a chemical structure and vice versa. <cite openbabel,SMILES, SMARTS> SMARTS is similar to SMILES but instead of representing a single molecule unambiguously, it has multiple wildcards which can be used for pattern matching. This pattern matching is also implemented in the Openbabel package. If we know the SMARTS string for any given CG mapping we can map the CG site to it's center of mass or geometric center.
I have developed a minimum working example of how this can be done <cite grits> and then how the atomistic structure can be recovered. It could be fairly straightforward to implement a lookup to check if bead parameters already exist--say for the MARTINI model-- by going through and writing out the SMARTS pattern for each existing bead type. An initial headache that could make parameterizing new compounds for the MARTINI method more foolproof.

A similar package already exists. Versatile Object-oriented Toolkit for Coarse-graining Applications (VOTCA) \cite{Ruhle2011b}
this package includes a coarse-graining, forecefield creation with reverse MC or IBI, and back-mapping module. It also allows for charge transport calculations using KMC similar to MorphCT <cite>

<coarse-graining, backmapping, charge transport>

# what remains to be done

# Why should the work be done?
# what specific problems will it solve?

# how will the work be done?
- I will build on existing tools (signac,freud,mbuild,foyer,tim moore's msibi)
- create signac workflow which takes equilibrated atomistic trajectory (maybe checks if it's equilibrated?) maps the CG beads to it, runs IBI, gets tabulated FF, creates larger CG sim, runs it, does backmapping, then could do: RDF, charge transport, diffraction... if this workflow is streamlined--it can be applied to many different compounds allowing for us to compare the analyses between our zoo of compounds.
- maybe the workflow could even involve getting the equilibrated trajectory (atomtyping/fill box/run) with the new hoomd 3 api we could even set decorrelation time as a stop trigger...

# what have you accomplished already? what remains?
- contributed to development of open-source packages: mbuild, foyer, signac, fresnel
 this has helped me learn best software development practices like writing documentation, using version control, writing unit tests, employing CI, fork/pull model, etc. using these tools will help me to me a more efficient developer. It's also helped me to learn how to work as part of a team.
 - created MWE of coarse-graining and backmapping with smiles-- these will need furthertesting as we try them on different compounds but the proof of concept is there.
 - created tutorial examples to help current and future students understand scientific concepts and how to use computational tools
 - created GIXStapose (presented at SciPy2020) an interactive diffraction/structure viewer. This may seem unrelated but we can use diffraction to verify our opv morphologies and compare them to experiment. GIXStapose helps to beeter connect the physical structure with the diffraction pattern.
- started development on UFF repo for foyer. This is an example of how to create a version controlled forcefield which can be automatically applied to a compound. (atom typing is a pain)

#what is the timeline?
#what answers will be immediately forthcoming?
#what additional major research will result?

#will the work involve an outreach component?

#Intellectual merit and broader impacts?

Garbage first pass at abstract--probably just delete.

In order to make the most efficient opvs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds. With minor modifcations the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
by using a simulation pipeline, we can help to streamline the process of determining which opv materials will help to solve the energy crisis
simulation also helps to give us insight into the atomic interaction which drive self assembly.
a complication of this simulation is that the features which are important to the performance of an opv span multiple length scales. The electronic properties are important for light absorption, charge transfer <morehere>
while the bulk morphological properties are important: an exciton needs to be able to find an interface at which to dissociate before it decays through one of its non-radiative processes and one the charges are separated they need to reach an electrode in order to generate current and produce electricity. <interfacial area and connectivity>
it is not only computationally intractable to try and simulate the electron density of an opv polymer melt on length scales proportional to the exciton dissociation length (~5-10 nm) -- it is the wrong tool for the job. if what we are interested in is the properties of the polymer in the bulk heterojunction then it is wise to abstract away any degrees of freedom which do not directly contribute to the self-assembly of the structure. once a good bulk structure has been achieved these details can be reintegrated much more easily. This is the idea behind a coarse grain model.
my proposal is to develop a coarse-graining pipeline which will simplify the process mapping the coarse grain model onto the structure, parameterizing the forces and backmapping to retrieve atomistic details. 
<electronic structure, quantum > MD atomistic, classical forces> but each atom is represented > CG multiple atoms can be grouped together to form a super atom and then the effective force can be iteratively approximated using Boltzmann inversion (IBI). 
this has already been done-- lots of CG force fields already exist. The martini method <more> 
my idea is to use a systematic language for specifying chemical structure (SMARTS) to automate the bead mapping and backmapping. 
By creating an automation scheme which is understandable and makes chemical sense, we hope to simplify the process of creating and using a coarse-grain model.
we can use this do develop new coarse-grain models and test their efficacy in predicting charge transport.

### 2020-07-23 reading-notes.tex
reading/writing for the day
read paper about how forcefields fare when evaluating h-bonding and pistacking

@@
 TraPPE\cite{Maerzke2011}
-it is generally assumed that coarse-grain potentials are not transferrable to different systems or state points (T and P).
+
+It is generally assumed that coarse-grain potentials are not transferrable to different systems or state points (T and P).
 This model tries to fix that.
@@
 parameters yield accurate vapor-liquid equilibria, first RDF peak, and coordination number for the solvation shell.
+
 PMF represents enemble average free energy of FG model therefore it is limited to the same thermodynamic conditions.
@@
 
-\cite{Shelley2001}
+\cite{Shelley2001}√
 CG model for phospholipids.
@@
 
-and read this: \cite{Chakraborty2018a}
+and read this: \cite{Chakraborty2018a} √
 
@@
 
+\cite{Paton2009a}
+
+comparing forcefields to DFT specifically seeing if force field can accurately represent hydrogen bonding, pi-stacking, and other non-bonded interactions.
+dispersion forces are very important for DNA stabilization
+this paper looks at small molecule dimers which are relelvant to biomolecules in the gas phase (e.g., adenine/thymine dna base pair)
+the break apart the molecules based on what is the dominant interaction: h-bonded, dispersion, or mixed.
+All FFs underestimated hydrogen bonding but overall structures/energies are not bad.
+
+\cite{Paul1995a}
+\cite{Yang2006a}
+\cite{McCoy1998a}
 \bibliography{library}

### 2020-07-23 outline.tex
reorganizing a bit and writing better words also delete bad first try

@@
 Which model is right depends on the length and time scale on which the property of interest can be observed.
+
+For many systems however, we are interested in properties which span length scales.
+For instance in a system like a opv polymer melt, it is not only computationally intractable to try and simulate the electron density on length scales proportional to the exciton dissociation length (~5-10 nm) -- it is the wrong tool for the job.
+If what we are interested in is the properties of the polymer in the bulk heterojunction, then it is wise to abstract away any degrees of freedom which do not directly contribute to the self-assembly of the structure.
+Once a good bulk structure has been achieved the atomistic details can be reintegrated much more easily--a process called backmapping.
+In the same way that a coarse grain model can be mapped onto an atomistic one, we can get a reasonable starting structure for an atomistic simualtion from a coarse grain structure.
+The large length scale, polymer level properties can be equilibrated during the coarse grain simulation and then the atomic interactions can be equilibrated during the backmapped atomistic simulation.
+This can allow us the calculate properties such as charge transport, which depends upon the electronic structure of individual chromophores and the connectivity of these chromophores over distances proportional to the exciton dissociation length.
 General coarse grain models of opv thiophene polymers where only the spacing, regioregularity of the side chains were varied were able to predict different order disorder transitions and calculated scattering patterns of these simple simples were comparable to those obtained from experiment \cite{Jankowski2013, Marsh2014}
@@
 <votca, Peng2019a> 
+Versatile Object-oriented Toolkit for Coarse-graining Applications (VOTCA) \cite{Ruhle2011b}
+includes a coarse-graining, forcefield creation with reverse MC or IBI, and back-mapping modules. It also allows for charge transport calculations using KMC similar to MorphCT <cite>
 
@@
 the one part of coarse graining that is not yet automated is choosing a mapping scheme or a mapping operator.
-A mapping operator defines which atoms are grouped into a "super atom" represented by one coarse grain site and an effective potential and where in the site is placed relative to the atom group.
+A mapping operator defines which atoms are grouped into a "super atom" represented by one coarse grain site and where in the site is placed relative to the atom group.
 mapping operators are chosen based on desired resolution of the coarse grain system and the information to be extracted. 
@@
 \cite{Marrink2007} In this scheme, four atoms (except rings, which are treated differently) are grouped and the site is classified as polar, non-polar, apolar, or charged depending on the atoms it is composed of.
-When parameterizing a new molecule you must pick a mapping and thencompare the resulting beads to existing beads--time consuming and error prone.\cite{http://www.cgmartini.nl/index.php/tutorials-general-introduction-gmx5/parametrzining-new-molecule-gmx5} This force field was designed for lipids and has shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.
+When parameterizing a new molecule you must pick a mapping and thencompare the resulting beads to existing beads--time consuming and error prone.\cite{http://www.cgmartini.nl/index.php/tutorials-general-introduction-gmx5/parametrzining-new-molecule-gmx5} The MARTINI force field was first designed for lipids--further parameterization for proteins and nuclei acids have been added<cite--and has shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.
 use chemical intuition--e.g. what parts of the molecule shouldn't be allowed to bend?
@@
 
-A similar package already exists. Versatile Object-oriented Toolkit for Coarse-graining Applications (VOTCA) \cite{Ruhle2011b}
-this package includes a coarse-graining, forecefield creation with reverse MC or IBI, and back-mapping module. It also allows for charge transport calculations using KMC similar to MorphCT <cite>
-
 <coarse-graining, backmapping, charge transport>
@@
 # what specific problems will it solve?
+In order to make the most efficient opvs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
+With minor modifcations the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
+By using a simulation pipeline, we can help to streamline the process of determining which opv materials will help to solve the energy crisis
+Simulation also helps to give us insight into the atomic interaction which drive self assembly.
+A complication of this simulation is that the features which are important to the performance of an opv span multiple length scales.
+The electronic properties are important for light absorption, charge transfer <morehere>
+while the bulk morphological properties are important: an exciton needs to be able to find an interface at which to dissociate before it decays through one of its non-radiative processes and one the charges are separated they need to reach an electrode in order to generate current and produce electricity.
+<interfacial area and connectivity>
 
@@
 #Intellectual merit and broader impacts?
-
-Garbage first pass at abstract--probably just delete.
-
-In order to make the most efficient opvs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
-With minor modifcations the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
-by using a simulation pipeline, we can help to streamline the process of determining which opv materials will help to solve the energy crisis
-simulation also helps to give us insight into the atomic interaction which drive self assembly.
-a complication of this simulation is that the features which are important to the performance of an opv span multiple length scales.
-The electronic properties are important for light absorption, charge transfer <morehere>
-while the bulk morphological properties are important: an exciton needs to be able to find an interface at which to dissociate before it decays through one of its non-radiative processes and one the charges are separated they need to reach an electrode in order to generate current and produce electricity.
-<interfacial area and connectivity>
-it is not only computationally intractable to try and simulate the electron density of an opv polymer melt on length scales proportional to the exciton dissociation length (~5-10 nm) -- it is the wrong tool for the job.
-if what we are interested in is the properties of the polymer in the bulk heterojunction then it is wise to abstract away any degrees of freedom which do not directly contribute to the self-assembly of the structure.
-once a good bulk structure has been achieved these details can be reintegrated much more easily.
-This is the idea behind a coarse grain model.
-my proposal is to develop a coarse-graining pipeline which will simplify the process mapping the coarse grain model onto the structure, parameterizing the forces and backmapping to retrieve atomistic details.
-<electronic structure, quantum > MD atomistic, classical forces> but each atom is represented > CG multiple atoms can be grouped together to form a super atom and then the effective force can be iteratively approximated using Boltzmann inversion (IBI).
-this has already been done-- lots of CG force fields already exist. The martini method <more> 
-my idea is to use a systematic language for specifying chemical structure (SMARTS) to automate the bead mapping and backmapping. 
-By creating an automation scheme which is understandable and makes chemical sense, we hope to simplify the process of creating and using a coarse-grain model.
-we can use this do develop new coarse-grain models and test their efficacy in predicting charge transport.

### 2020-07-24 outline.tex
comparing votca and grits with cognitive load lens

@@
 instead example workflows with docker containers to build software stack. help make science more accessible and reprodicible.
+
+<compare VOTCA's backmapping to my proposed scheme>
+VOTCA makes some progress towards a TRUE simulation pipeline: they include a docker container with their pre-built software stack and example input files <see https://github.com/votca/votca -- using this code via docker> (but some of these input files don't work and the codecoverage on their repo as of time of writing is 0\%), and while including example inputs is a good first step, very little walkthrough (aside from code comments buried in the xml) is given.
+A manual is provided but there is some disconnect between the example files and those given in the manual <https://github.com/votca/csg-manual/releases>.
+the code is a mix of C++, shell commands, python, and interacts with compiled programs through the command-line and mpi.
+which makes their working a little tenuous.
+And judging by the amount of confusion in their mailing list <https://groups.google.com/forum/#!forum/votca> there is room for improvement in the API.
+Overall though this is program has many features, interfaces with many popular MD engines (lammps, gromacs, hoomd), and is under active, collaborative development.
+A good question might be if I'm so into OSS and collaboration--why don't I just contribute an MSIBI package to VOTCA.
+This is a reasonable question.
+The answer is because I find VOTCA to be near-overwhelming in it's scope and the cognitive load of trying to fit this whole project into my brain is not ideal.
+I also don't like their API.
+by choosing a pure python API I will be able to make use of jupyter notebooks which can be run on cloud servers using tools like mybinder <link mybinder, link to tutorials I;ve made> which can combine executable code with markdown text and images.
+In this way a tutorial can provide exact commands needed to reproduce the example intimately connected with the rationale and justification of that example.
+I would like to think that my code speaks for itself, but after reading other people's code, I have a renewed appreciation for explanations in paragraph form, diagrams, and figures.
+
+For an example of what I mean by cognitive load, let's compare an example of my proposed coarse-graining scheme to VOTCAs.
+In the following example we will take a hexane molecule and map it to three coarse grain sites (two carbon atoms per site).
+VOTCA uses an xml file to do this:
+<insert hexane.xml>
+It may be easy to think that because what we are doing--mapping two carbons and their attached hydrogens to a single bead so that six alkyl carbons becomes A-B-A--that the process will also be simple.
+In order to specify a bead-mapping, we need to know the residue number, the residue name, and the atom name.
+For a six atom system this is not too bad, but this could get tedious and error-prone for larger systems.
+VOTCA's scheme also requires that you specify the bonding and the angles resulting from those bonds--I will discuss this more after discussing my scheme below:
+\begin{lstlisting}
+hexane_sites = [("_A", "CC[H3]"), ("_B", "CC")]
+\end{lstlisting}
+The result of using this code in the `coarse` function <link to grits> is a three-site hexane model A-B-A.
+The mapping here is specified as a list of bead name / smarts string pairs.
+Although they do add some element of cognitive load, SMARTS strings are designed to be human and machine readable and can match atoms based on their chemical environment.
+No need to look up the name or number of each residue simply say I want two alkyl carbons (CC) specifying that it is an alkyl chain tail by requiring one carbon to have three attached hydrogens (C[H3]).
+The bonding of the coarse grain beads is then inferred based on the bonding of the mapped atoms.
 

### 2020-07-27 reading-notes.tex
reading and writing, mostly organizing cleanup

@@
 \cite{Paul1995a}
+
+united atom model for alkane chain melts.
+terminal methyl has deeper well than internal methylene groups.
+compared to experiments and all-atom model.
+good agreement for phase behavior, chain conformations, x-ray scattering profiles.
+Large-scale dynamics like self-diffusion agree with experiment and are 30\% faster!
+first intro paragraph really concise c: remind us about the difficulty in selecting a model and there are many competing model for a system as simple as n-alkanes.
+
 \cite{Yang2006a}

### 2020-07-27 paper.tex
not an outline anymore haha

--- 2020-07-09 paper.tex
@@
-\documentclass{article}
-\title{Reading Notes}
+# what has been done
+<should I start with simulation in general?>
+<start with what simplifying assumptions MD already makes>
+##coarse graining
+Coarse-grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models.
+Coarse-graining refers to grouping atoms in a structure into a "super-atom" and using an effective potential to represent the resulting coarse grain site.
+The resolution of coarse grain systems is broad:
+Simply grouping hydrogens with the heavy atom they are bonded to, called the united-atom model, has been shown to speed up dynamics and make polymer length scales more easily accesible \cite{Paul1995a, Yang2006a,}.
+Other goarse-graining schemes may group functional groups together <cite> or even represent an entire amino acid with a single site <cite>.
+General coarse grain models of opv thiophene polymers where only the spacing, regioregularity of the side chains were varied were able to predict different order disorder transitions and calculated scattering patterns of these simple systems were comparable to those obtained from experiment \cite{Jankowski2013, Marsh2014}
+A coarse-grain model for phospholipids has allowed for bilayer formation from an initial random configuration to be observed even though the model was parameterized to the vapor-liquid phase transition.\cite{Shelley2001}
+Which model is right depends on the length and time scale on which the property of interest can be observed.
 
-\begin{document}
-\title{}
+For many systems, however, we are interested in properties which span length scales.
+For instance, in a system like a opv polymer melt, it is not only computationally intractable to try and simulate the electron density on length scales proportional to the exciton dissociation length (~5-10 nm)<cite> -- it is the wrong tool for the job.
+If what we are interested in is the properties of the polymer in the bulk heterojunction, then it is wise to abstract away any degrees of freedom which do not directly contribute to the self-assembly of the structure.
+Once a good bulk structure has been achieved, the atomistic details can be reintegrated much more easily--a process called backmapping.
+In the same way that a coarse grain model can be mapped onto an atomistic one, we can get a reasonable starting structure for an atomistic simulation from a coarse grain structure.
+The large length scale, polymer level properties can be equilibrated during the coarse grain simulation, and then the atomic interactions can be equilibrated during the backmapped atomistic simulation.
+This can allow us the calculate properties such as charge transport, which depends upon the electronic structure of individual chromophores and the connectivity of these chromophores over distances proportional to the exciton dissociation length.
+<what stands in our way?>
 
-today I got this repo set up. Next time, I'll reskim these papers:
+<coarse-grain models are specific>
 
-MARTINI\cite{Marrink2007}
+<segue from automated creation of forcefields to...>
+<mapping operator has to be decided by hand> <is this section too big?>
+Part of coarse graining that is not yet automated is choosing a mapping scheme or a mapping operator.
+A mapping operator defines which atoms are grouped into a "super atom" represented by one coarse grain site and where in the site is placed relative to the atom group.
+Mapping operators are chosen based on desired resolution of the coarse grain system and the information to be extracted.
+A straightforward way to define a mapping operator is to group a set number of heavy atoms (non hydrogen) together--this is the method used in the MARTINI force field\cite{Marrink2007}.
+In this scheme, four atoms (except rings, which are treated differently) are grouped and the site is classified as polar, non-polar, apolar, or charged depending on the atoms it is composed of.
+When parameterizing a new molecule you must pick a mapping and then compare the resulting beads to existing beads--a process which is time consuming and error prone\cite{http://www.cgmartini.nl/index.php/tutorials-general-introduction-gmx5/parametrzining-new-molecule-gmx5}.
+The MARTINI force field was first designed for lipids--further parameterization for proteins and nuclei acids have been added<cite--and has shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.
+Many mapping schemes are simply based on the user's chemical intuition (e.g., what parts of the molecule shouldn't be allowed to bend?<cite any model where rings are one bead> What groups have the most dominant interactions in this structure <cite dna cg model>).
+As the number of atoms in the fine grain structure increases, the number of possible mappings increase drastically.
+There have been efforts to create mapping schemes for automating the process of deciding which atoms are grouped in a "super-atom" bead.
+One study reduced the number of allowed mappings by only allowing those which do not change the symmetry group, then iterated over a graph of all possible mappings to find the "best" mapping by comparing the difference between the mapped RDF and velocity autocorrelation function \cite{Chakraborty2018a}.
+Another mapping scheme uses principle component analysis to choose a mapping scheme for biomolecules that best represents th essential dynamics\cite{Zhang2008}.
+Mapping operators can be automated using machine learning: clustering methods combined with graph analysis were shown to predict the "expert" mapping chosen using chemical intuition reliably\cite{li2020}.
+A mapping operator based on the centers of charge was shown to accurately model electrostatic properties\cite{Cao2015a}.
 
-VOTCA\cite{Ruhle2009}
+<how cg potentials have been obtained>
+<IBI>
+<why are IBI potentials not transferrable? the RDF is a property of the ensemble average at a given statepoint so the potential derived from this property is also limited.>
+separate potentials are required to capture solid and fluid structures of a pure simple lipid <Moore2014 ref 46>
+<IBI potentials are sometimes transferrable and it is not clear why sometimes they are and sometimes they aren't.> \cite{Moore2014}
 
-TraPPE\cite{Maerzke2011}
+Multistate iterative Boltzmann inversion (MS IBI) includes data from multiple targets to yield a less state dependent potential.
+\cite{Moore2014}
+The MS IBI potential is an average of the single state potentials with a weighting function to prioritize a state of interest.
+This method has been shown to accurately reproduce the true potential in monoatomic LJ fluid.
 
-and read this: \cite{Chakraborty2018a}
+When using the MS IBI method, it is important to choose dissimilar states to minimize the potential overlap region.
+If this overlap region is large, there are many potentials which will provide matching RDFs.
+For some systems there may not be a potential that represents all states-- this is not unique to coarse potentials, atomistic potentials also have this limitation.
 
-got busy with fancy-ing up the GIXStapose repo, helping rachel, office hours, and atom-typing with gaff-foyer with ryan and chris.
-Briefly skimmed the chakraborty paper-- they consider all possible mappings that a cg compound can have in order to systematically pick a cging scheme.
-OK Chakraborty notes:
--exclude cg mapping schemes to those that maintain symmetry
--Zhang and Voth designed CG mapping operators by preserving "essential dynamics"
--Cao and Voth worked on centering functions COM vs center of charge. They found center of change was better for preserving intermolecular structure.
--Wagner generalize centering functions to arbitrary thermodynamic quantities
--Marrink grouped four heavy atoms and showed that this simple consistent scheme works.
-CG models are validated by preservation of rdfs and velocity autocorrelation functions (vacfs)
-mapping operator tree
+TraPPE fits CG potentials using vapor-liquid equilibria to improve transferrability across thermodynamic states\cite{Maerzke2011}
+<Talk about what exists and why it is not enough>
+<votca, Peng2019a> 
+Versatile Object-oriented Toolkit for Coarse-graining Applications (VOTCA) \cite{Ruhle2011b}
+includes a coarse-graining, forcefield creation with reverse MC or IBI, and back-mapping modules.
+It also allows for charge transport calculations using KMC similar to MorphCT <cite>
 
-Today I'm reading the VOTCA\cite{Ruhle2009} paper with the goal of answering these questions:
-how do they choose a chromophore?
+reproducibility crisis.\cite{Cummings2019} \cite{Thompson2020} (TRUE paper) poorly documented code and raw data doesn't help.
 
-how do they calculate the transfer integral?
+instead example workflows with docker containers to build software stack.
+help make science more accessible and reprodicible.
 
-how do they do backmapping?
+<compare VOTCA's backmapping to my proposed scheme>
+VOTCA makes some progress towards a TRUE simulation pipeline: they include a docker container with their pre-built software stack and example input files <see https://github.com/votca/votca -- using this code via docker> (but some of these input files don't work and the codecoverage on their repo as of time of writing is 0\%), and while including example inputs is a good first step, very little walkthrough (aside from code comments buried in the xml) is given.
+A manual is provided but there is some disconnect between the example files and those given in the manual <https://github.com/votca/csg-manual/releases>.
+the code is a mix of C++, shell commands, python, and interacts with compiled programs through the command-line and mpi.
+which makes their working a little tenuous.
+And judging by the amount of confusion in their mailing list <https://groups.google.com/forum/#!forum/votca> there is room for improvement in the API.
+Overall though this is program has many features, interfaces with many popular MD engines (lammps, gromacs, hoomd), and is under active, collaborative development.
+A good question might be if I'm so into OSS and collaboration--why don't I just contribute an MSIBI package to VOTCA.
+This is a reasonable question.
+The answer is because I find VOTCA to be near-overwhelming in it's scope and the cognitive load of trying to fit this whole project into my brain is not ideal.
+I also don't like their API.
+by choosing a pure python API I will be able to make use of jupyter notebooks which can be run on cloud servers using tools like mybinder <link mybinder, link to tutorials I;ve made> which can combine executable code with markdown text and images.
+In this way a tutorial can provide exact commands needed to reproduce the example intimately connected with the rationale and justification of that example.
+I would like to think that my code speaks for itself, but after reading other people's code, I have a renewed appreciation for explanations in paragraph form, diagrams, and figures.
 
-other notes:
-CG methods--IBI, force matching, inverse MC. This paper goes over details of these and how they're implemented in votca. This wasn't really what I wanted to read about so I skimmed.
-They use ESPResSo++ for quantum calculations
-OK, this isn't the right paper to read about CT stuff or backmapping. Let's look at some of these [http://www.votca.org/citations/using-votca](http://www.votca.org/citations/using-votca)
-Also I'm noticing in this list of papers--Marrink (cited by chakraborty) is here and there is a paper mentioning the importance of side-chains for charge-mobility! \cite{May2011}
-Next time read about tie-chains \cite{May2011} and/or charge mobility \cite{Lukyanov2010}
-Lukyanov--sounds a lot like morphct, gaussian density of states?
-I thought their (votca's) method was like morphct but now I'm not sure...
-It seems like they're using a simplification and not doing dft.
+For an example of what I mean by cognitive load, let's compare an example of my proposed coarse-graining scheme to VOTCAs.
+In the following example we will take a hexane molecule and map it to three coarse grain sites (two carbon atoms per site).
+VOTCA uses an xml file to do this:
+<insert hexane.xml>
+It may be easy to think that because what we are doing--mapping two carbons and their attached hydrogens to a single bead so that six alkyl carbons becomes A-B-A--that the process will also be simple.
+In order to specify a bead-mapping, we need to know the residue number, the residue name, and the atom name.
+For a six atom system this is not too bad, but this could get tedious and error-prone for larger systems.
+And keep in mind that these xml files need to be created manually for each compound which is backmapped.
+VOTCA's scheme also requires that you specify the bonding and the angles resulting from those bonds, another process which is tedious, error-prone, and probably unecessary--I will discuss this more after discussing my scheme below:
+\begin{lstlisting}
+hexane_sites = [("_A", "CC[H3]"), ("_B", "CC")]
+\end{lstlisting}
+The result of using this code in the `coarse` function <link to grits> is a three-site hexane model A-B-A.
+The mapping here is specified as a list of bead name / smarts string pairs.
+Although they do add some element of cognitive load, SMARTS strings are designed to be human and machine readable and can match atoms based on their chemical environment.
+With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (CC) requiring that one be a termial carbon by including that it has three attached hydrogens (C[H3]).
+The bonding and angles of the resulting coarse grain beads is then inferred based on the bonding of the mapped atoms.
+There are even benefits to the mapping being inline with the code:
+This allows the user to see the mapping as they progress through the workflow without having to search for multiple files and it may prevent common errors caused by manual file IO such as operating system specific line endings or whitespace characters like tab or space being treated differently.
+Having the mapping in-line with the workflow also allows for the user to check that the mapping is correct with built in interactive visualizations, which can display the mapping as an overlay.
 
-https://pubs.acs.org/doi/10.1021/ja104380c - 
-rubrene record charge carrier $15 \frac{cm^{2}}{(V s)}$ single crystal by vapor deposition. typical for thin-film is $1 {cm^{2}}{(V s)}$
+We do not propose a new automated mapping, but instead a way to make the mapping and backmapping process easier for the user.
+Simplified Molecular Input Line Entry System or SMILES \cite{Weininger} was designed to represent organic molecules in an unambiguous way (similar to IUPAC) but in a line-entry system which is also readable by a computer.
+This makes it a good candidate for specifying a coarse-grain mapping scheme.The open-source package, Openbabel, allows for a SMILES string to be converted to a chemical structure and vice versa.
+<cite openbabel,SMILES, SMARTS> SMARTS is similar to SMILES but instead of representing a single molecule unambiguously, it has multiple wildcards which can be used for pattern matching.
+This pattern matching is also implemented in the Openbabel package.
+If we know the SMARTS string for any given CG mapping we can map the CG site to it's center of mass or geometric center.
+I have developed a minimum working example of how this can be done <cite grits> and then how the atomistic structure can be recovered.
+It could be fairly straightforward to implement a lookup to check if bead parameters already exist--say for the MARTINI model-- by going through and writing out the SMARTS pattern for each existing bead type.
+An initial headache that could make parameterizing new compounds for the MARTINI method more foolproof.
 
-good discussion of some of the assumption of marcus theory. 
-Drude model (electrons bounce off stationary nuclei like a pinball machine) works for perfect crystals at low temp.
-At RT it doesn't work.
-Marcus theory assumes nuclear dynamics much slower (Borne-Oppenheimer) and electronic coupling is weak (what does this mean exactly?).
-Static disorder is based on the electronic DOS and the hopping rate between localized states.
-(As opposed to what?)
-They start with single crystal structures from xray data. They calculate reorganization energies with b3lyp 6-311G(d,p) and transfer integrals with ZINDO. (check their SI)
-How are they able to calculate direction-resolved transfer integrals??
-very cool.
-What exactly do the transfer integral graphs mean?
-(Figure 2) Had a helpful chat with Chris about this and it helped me to think through the figures.
-The y-axis on the transfer integral is counts and the x-axis is energies--it makes sense that movement of an electron in different directions would require different energies and/or be more likely.
-Still not sure how to calculate it though.
+<coarse-graining, backmapping, charge transport>
 
-\cite{Vehoff2010a}
+# what remains to be done
 
-rubrene record charge carrier $15 \frac{cm^{2}}{V s}$ single crystal by vapor deposition. typical for thin-film is $1 \frac{cm^{2}}{V s}$
+# Why should the work be done?
+# what specific problems will it solve?
+In order to make the most efficient opvs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
+With minor modifcations the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
+By using a simulation pipeline, we can help to streamline the process of determining which opv materials will help to solve the energy crisis
+Simulation also helps to give us insight into the atomic interaction which drive self assembly.
+A complication of this simulation is that the features which are important to the performance of an opv span multiple length scales.
+The electronic properties are important for light absorption, charge transfer <morehere>
+while the bulk morphological properties are important: an exciton needs to be able to find an interface at which to dissociate before it decays through one of its non-radiative processes and one the charges are separated they need to reach an electrode in order to generate current and produce electricity.
+<interfacial area and connectivity>
 
-Today I'm digging around in more of the votca stuff to try and figure out how to run kmc there.
-They use ORCA too!
-Also their tutorials and documentation REALLY SUCK.
-[https://github.com/votca/xtp-tutorials](https://github.com/votca/xtp-tutorials) in particular I'm looking at LAMMPS/KMC\_Thiophene.
-OK.
-either I am dumb or that tutorial sucks.
-I can tell that they're using orca and the inputs/oputputs the use but there's no explanation of what they're doing.
-It looks like they calculate the reorganization energy, but they don't define a chromophore--which makes sense for thiophene but what about when your molecule is ginormous?
+# how will the work be done?
+- I will build on existing tools (signac,freud,mbuild,foyer,tim moore's msibi)
+- create signac workflow which takes equilibrated atomistic trajectory (maybe checks if it's equilibrated?) maps the CG beads to it, runs IBI, gets tabulated FF, creates larger CG sim, runs it, does backmapping, then could do: RDF, charge transport, diffraction...
+if this workflow is streamlined--it can be applied to many different compounds allowing for us to compare the analyses between our zoo of compounds.
+- maybe the workflow could even involve getting the equilibrated trajectory (atomtyping/fill box/run) with the new hoomd 3 api we could even set decorrelation time as a stop trigger...
 
-\cite{Ruhle2011b}
+# what have you accomplished already? what remains?
+- contributed to development of open-source packages: mbuild, foyer, signac, fresnel
+ this has helped me learn best software development practices like writing documentation, using version control, writing unit tests, employing CI, fork/pull model, etc.
+using these tools will help me to me a more efficient developer.
+It's also helped me to learn how to work as part of a team.
+ - created MWE of coarse-graining and backmapping with smiles-- these will need furthertesting as we try them on different compounds but the proof of concept is there.
+ - created tutorial examples to help current and future students understand scientific concepts and how to use computational tools
+ - created GIXStapose (presented at SciPy2020) an interactive diffraction/structure viewer.
+This may seem unrelated but we can use diffraction to verify our opv morphologies and compare them to experiment.
+GIXStapose helps to beeter connect the physical structure with the diffraction pattern.
+- started development on UFF repo for foyer.
+This is an example of how to create a version controlled forcefield which can be automatically applied to a compound.
+(atom typing is a pain)
 
-discusses charge transport in amorphous films of [tris-(8-hydroxyquinoline)aluminum](https://en.wikipedia.org/wiki/Tris(8-hydroxyquinolinato)aluminium).
-Oh Figure 1 is nice--it is a workflow of what can be done in votca.
-11A talks about how to parameterize new contributions to a force-field using first-principles.
-11B choosing a "chromophore"-- rigid fragments vs conjugated segments.
-they broke apart the chromophore in a polymer like p3ht using the dihedral angle--although they validated this choice with other methods.
-Interesting-- they replace the chromophores with those which have been geometry optimized using DFT.
-then they make a neighbor list
-I'll come back to this paper later. I at least was able to answer some of my questions about choosing a chromophore.
-11C talks about calculating the transfer integral for each pair and why ZINDO works and when it breaks down.
+#what is the timeline?
+#what answers will be immediately forthcoming?
+#what additional major research will result?
 
-rereading the perspective paper \cite{Jankowski2019} looking for things to read next:
-Braun 2018 foundations in molecular simulation
-https://doi.org/10.33011/ livecoms.1.1.5957
-74-89 are relevant to coarse-graining
-92-95 start here for opvs
+#will the work involve an outreach component?
 
-Today I'm thinking about some of the big picture stuff related to my proposal:
-Science-wise I am thinking of my proposal like this: Humans use energy and burning fossil fuels to get that energy really sucks.
-rising CO2 concentration in the atmosphere contributes to global warming.
-Sustainable, low-carbon footprint energy generation is vital to protect the precious climate which sustains all life.
-Energy generation using OPV devices is one form of alternative energy.
-But there are a lot of potential OPV molecules out there!
-So how can we develop inexpensive, fast methods for screening this ZOO of compounds?
-Well we can use modelling techniques and a computer.
-Computational simulations of organic photovoltaics suffer from a problem of length scales: OPV morphologies can have bulk features on the scale of 10s of nanometers (BHJ, exciton dissociation length, pi-stacking) which affect the morphology, yet still we are interested in the electronic properties of this system--a fundementally quantum mechanical property--taking place on the angstrom scale where with current computers we can only realistically look at up to 100's of atoms.
-<so we break apart the problem MD to get a morphology, Zindo to calculate energy splitting of neighbors-->transfer integral, KMC to estimate CT, talk about results of evan/matty/votca> What am I going to add?
-more robust/automated coarse-graining and backmapping, calculation of reorganization energy, chromophore detection.
-Things I care about: The environment--I like working on a project that theoretically could help find the next molecule for OPV technology.
-Sometimes it seems very far removed, but having sustainable technology as an ultimate goal matters to me.
-I also care a lot about help make science more accessible to everyone: I find myself really excited about creating tools which help to visualize the unseeable and to communicate complex ideas in a simple understandable way.
-I'm not sure this has anything to do with anything, but it's definitely a developing passion.
-
-I'm also reading this paper today https://arxiv.org/pdf/2003.02031.pdf which is a bout TRUE simulations.
-notes:
-GUI's hurt reproducibility, MS Excel hides the formula's and order of calculation (p 4)
-poorly documented code and raw data files dont help reproducibility (looking at you votca) (p4)
-*I want to include start to finish notebooks with any paper I publish...* Also docker containers with my exact software stack.
-I love the examples in this paper :) It feels a lot like our perspective paper! I'm skimming them but I love that notebooks are included in the SI.
-They qualify the GUI's are bad statement saying that GUIs are only bad *if they hide the workflow details.*
-
-Matt Thompson got a job at OpenFF, one of the tools they list as desirable for applicants is knowledge of psi4:
-https://pubs.acs.org/doi/abs/10.1021/acs.jctc.8b00286
-
-read official papers for mosdef. check github.
-
-Reading
-
-\cite{Hanson2016}
-
-also my mendeley overwriting my files because it thinks they are duplicates or something? It keeps losing the pdf even though I've uploaded it. :(
-SMILES - simplified molecular-input line-entry system
-SMARTS - smiles arbitrary target specification
-around since 1980s
-alternatives SLN, MQL, CSRML.
-This paper is about specifically Jmol smiles so I'm skipping to a different one.
-
-\cite{Weininger1988}
-
-First paper about smiles- how do we unambiguously represent a chemical structure? historically CAS, graph theory, IUPAC.
-human-readable and machine readable
-hydrogens, single bond don't need to be specified. designed for organic molecules.
-
-\cite{Smith2018}
-
-reading about psi4: free and open source with python api that uses blas and c under the hood.
-has jupyter notebooks tutorials.
-This paper reads like our perspective paper in tone :hearteyes: 2.2 -2.3 kinda lost me.
-I should look at their jupyter notebooks.
-
-Today searched "coarse grain backmapping" in the library and got the following papers:
-
-\cite{Alessandri2017b}
-
-Coarse graining in OPV bulk heterojunctions!
-p3ht and pcbm, solvent evaporation.
-morphologies need large interfacial area between donor and acceptor and relatively high crystallinity and connection to the electrode.How can we investigate the processing conditions that achieve the highest performance?
-Analysis of OPVs include AFM, SEM, TEM - provide info about interpenetration (how the two phases are dispersed.) Electron tomography can study 3d morphology., but has limited contrast in organic material due to low scattering.
-GIXD, GISAXS quantifies the degree of crystallinity but averages over the structure.
-CG allows us to look at these systems but CG models are currently not transferrable meaning that for each new system a new CG model must be developed which is slow.
-Simulated annealing is often used but a more relevant to experiment method is simulated evaporation.
-This paper used CG model like Lee and Pao (read this paper) but also based on finer model like martini. Martini does backmapping. (backwards.py) 
-They use explicit solvent (CB/benzene) and they remove molecules randomly as the simulation progresses.
-Longer drying time results in larger crystallites/ fewer D-A contacts.
-P3ht shows backbone (pi-pi) stacking at a distance of 4.5 A in the CG morphology.
-They use backwards.py to do their backmapping.
-They use 3 beads to represent thiophene in p3ht with no explicitly anisotropic interaction.
-Carillo (ref 26) used anisotropic addition onto very simplified model (thiophene is single bead) of lee (ref 22).
-(read these) The model used here thiophene is a triangle and they think this helps it stay planar and stack.
-Figure 5 is beautiful.
-
-\cite{Haxton2015a}
-
-CG beads with orientation.
-They use the word "stiffest" to describe degrees of freedom--they mean bond stretching, angle bending, and torsion within rings.
-They suggest there are two separate ways to improve CG: better mapping between AA and CG or better CG interactions.
-The seconds can be helped with IBI, entropy minimization...
-First one is what the authors will focus on.
-Point-site method maps groups of atoms onto a bead--bead potential is spherically symmetric, but some models use neighboring sites to introduce some directionality.
-e.g., Alemani et al created a protein model where the dipole interaction was a function of the alpha-carbon angle.
-Here they add orientation to the point-site model.
-This increases the degrees of freedom for each site from 3 to 6, but they model bonds and angles as stiff and dihedral angles (except rings and double bonds) as soft.
-They also map about 8 atomns to a site.
-They use backmapping from ref 64--not backwards.py.
-They simplify the ideal interactions of the CG model (many-body problem) to pai potentials.
-They show how to calculate to error in an observable calculated on backmapped structure.
-C code used for backmapping in SI.
-mapping ratio - atomic DOF / CG DOF.
-PRIMO on average is 3.0, UNRES, MARTINI, MS-CG are 8.2, 7.1, and 6.0.
-I think this paper aims to improve on PRIMO by adding directionality?
-they measure accuracy with rmsd and efficiency with mapping ratio.
-
-\cite{Wassenar2014b}
-
-This paper is about backwards.py.
-The authors are from university of groeningen where GROMACS is made.
-however this tool is generic and not specific to gromacs.
-it uses geometric projection and position restrained MD relaxation--same as what Matty did.
-can map between anything just needs a mapping.
-Good overview of CG methods:
-Rzepiela - randomly place atomistic beads on small spheres around CG beads.
-Requires many steps, specific to one verison of GROMACS, but can be made specific with correspondence between atoms and beads.
-Brocos - lipid micelles. placing atoms on a trace through the CG bead and adding peripheral atoms at offset. 
-A good CG model should yield correct structures and be simple quick and flexible.
-Should be generic (ff and system type) and require little information.
-Then information provided should be the CG coordinates, the atomistic topology and the correspondence mapping between the atomistic and CG particles.
-They go from MARTINI-CG to GROMOS 54a7 UA to CHARMM36 AA.
-Some matrix mapping that I don't totally understand. Confusing between A the matrix and A the atom position. :/
-Fig 5 is neat! c: shows a helical protein at each step of the CG->AA process. their procedure appears to improve upon the simulated anealing of rzepiela. 
-* look at backwards.py with the intent of better understanding the Matrix transformation.
-
-\cite{Peng2019a}
-
-biomolecules.
-Backmapping based on Bayesian inference and restrained MD.
-cgmap.py -- they tell us the names of their codes but don't provide them??
-They try multiple CG methods: Martini (twice with different initial structure), UNRES, ENM.
-Martini had the lowest RMSD but it is also the finest grain method.
-They have an ultra coarse method that only use 5 beads for a small protein; it gets impressive results (RMSD 0.47 angstrom) for how sparse it is!
-But it is not sufficiently accurate to predict structure-- other RMSD > 10angstrom.
-their method is more expensive.
-I don't quite understand how they get some of the probabilities for the Bayesian part, but my takeaway from this paper is that the logrestraints work a lot better for them and Bayesian inference, although expensive, allows them to skip the AA MD simulation at the end?
-
-\cite{Rolland2020a}
-
-This is the paper we reviewed in lab meeting!
-CG -> backmap -> mobility.
-AA MD can reproduce XRD patterns pi-pi stacking, formation of lamellar structure, change in morphology at high oxidation levels, mobility dependence on chain-length (* looks into ref 26 and compare to evan's tie chain paper)
-CG allows us to look at larger lengthscales and with backmapping we can restore atomistic details, but is there a cost?
-ref 44 model HOTT molecules as ellipsoids with Gay Berne interactions (I'm thinking of this as anisotropic--i.e., directionally dependent so good for ellipsoids--Lennard Jones.
-Often used in liquid crystal systems.)
-They use the same backmapping as us ref 13.
-Many CG papers verify by XRD buyt they claim same XRD can result in very different mobility.
-ref 26.
-They use Wassenar's backward.py script.
--- He is from the university which makes GROMACS
-CG overestimates density--backmapping fixes it.
-XRD of backmapped AA match AA.
-pipi stacking is corrected and lamellar structure present.
-Mobility also good.
-They explain the differences between the AA and CG mobilities saying that the AA one is smaller so it's a size effect due to over estimated percolation threshhold--i.e.
-the connectivity is overestimated because the periodic volume is small enough that the periodic image has an effect.
-
-\cite{Poblete2018a}
-
-RNA - backmapping steered MDaimed at minimizing a particular RMSD (ERMSD) between atomic and target structure.
-target structure were found to be recovered by this backmapping except in the case where there were unpaired bases.
-folding pathway dependent on parameters used in ERMSD.
-need AA strutures to validate with experiment (x-ray or neutron scattering) backmapping usually involves placing atomistic coordinates relative to the beads and then minimizing the energy of the structure using steepest descent or short MD runs (could use position restraint).
-Atomistic can even be mapped onto the whole trajectory.
-This work describes the backmapping of the SPlit and conQueR (SPQR) method.
-Minimizes the ERMSD distance between solvated AA strand of the CG structure (RNA).
-ERMSD : origin is set to CoM of C2 C4 and C6 atoms of each base (see ref 23), then for each pair of bases, rij is the center of base i in the coord system of base j.
-In order to account for anisotropy, the scaling for the z-direction is different (does this mean the strand is oriented to z in some way??) This metric shows the difference between arrangement of nucleobases of two RNA structures.
-Backbone and sugar interactions are unrestrained.
-The paper will show results on the backbone conformation.
-They use steered MD with ERMSD as the steering parameter.
-(How does steered MD work?) Look like they use and external pulling force which depend on ERMSD.
-
-Of these the Alessandri paper was the best and  most interesting/relevant. I am pulling some refs from here for next time:
-
-\cite{Mikhnenko2012}
-
-Exciton diffusion length (EDL) in narrow bangap polymers.
-photoluminescense decay time is related and measurable.
-PCBM and PCDTBTs modeled with Monte Carlo--code available.
-They used P3HT as reference (5.4+/-0.7nm exciton diffusion length).
-Exciton diffusion is essential for organic solar cells.
-excitons are electron hole pairs created by excitation due to light absorption.
-they are separated into free charges at an interface which creates current.
-the movement of the excitons through hopping is what is refered to as diffusion.
-Exciton diffusion length is a factor in device efficiency.
-Other methods to measure EDL are fluorescence quenching - the dependence of the exciton quenching efficiency vs semiconductor thickness is fit to 1D diffusion equation.
-Pros: direct measuremnt, cons: difficult experimentally and there are many things to consider in the model (FRET, effect of polymer-vaccuum interface, optical interference).
-This paper uses MC to model PL decay.
-(Losing focus come back tomorrow)
-
-Ugh. I think I've finally fixed my Mendeley library?
-
-\cite{Scharber2013}
-
-Review of state-of-the-art OPV BHJ solar cells. 
-pros: thin/light, semitransparent, cheap, continuous production process, short payback times, easy to integrate into new and existing products. 
-History of development from 2001 2.5\% PCE to 2011 10\% PCE.
-Most degrade when exposed to air and sunlight within a few years.
-Molecular structure including side chains affects stability.
-Electron affinity of the acceptor determines degradation rate of the semiconductor.
-Changing the elctrode and using the inverted design(?
-read waldauf) helps the electrode oxidation.
-This requires no vacuum
-They discuss BHJ morphology and how the A and D regions need to be small enough that an exciton could find it's way to an interface but not so small that once the charge is separated and current is generated at that interface that the current couldn't get to the electrode.
-The ideal is an interlocked comb structure but in reality solution processed OPVs form patches.
-This review is not about morphology (they recommened Hoppe2004).
-Morphology can only effect the efficiency of an AD pair, not the ultimately efficiency limit.
-This depends on the bandgap and electron affinities of the DA moeities.
-fig 5 explains inverted design a bit. 
-They discuss costs and efficiencies.
-Should probably read about Shockley Queisser Limit.
-(ref 47) based on analysis of pn solar cell they say the max efficiency is 30\% and the optimum band gap in 1.1 eV.
-Archer and Bolton roughly confirm this -- much of the light energy is lost because the photon is too small to excite the absorber, other loss is due to intraband thermalization of charge carriers (?), 12\% entropic loss, 1\% radiative recombination.
-Assumption of the Shockley Queisser limit
-1. each absorbed photon generates and e/hole pair
-2. perfect charge collection
-3. radiative recombination as the only recombination.
-Based on this work and the external radiative efficiency (ERE) proposed by Green, and actual max of 15-16\% efficiency is predicted.
-(continue from 5)
-
-\cite{Waldauf2006}
-
-Read this with intention of understanding inverted design
-
-\cite{Hoppe2004}
-
-Overview of organic solar cells.
-sp2 hybridization of carbon is what allows organics to absorb in the uv-vis range.
-(conjugated pi orbitals.) In comparison, inorganic semiconductors have low mobilities but very high absorption coefficients.
-The exciton diffusion length is shorter in OPVs too.
-Most OPV are hole conductors and have band gap around 2 eV, which is higher than silicon. But the ability to modify and tune the chemistry as well as the cheap, mass production makes OPVs enticing.
-history: 
-first OPVs were single organics layers sandwiched between two metals with different work functions. (Evac - Efermi) 0.7\% PCE
-next bilayer heterojuctions-- two organic layers between electrodes (e.g. perylene and phtalocyanine) 1\% PCE
-C60 introduced, polymer fullerene bilayer heterojunction.
-Bulk heterojunction 2\% PCE
-(This article only discusses up to 4\% PCE and does not provide specific explanation for the increase)
-common structure is hole-conducting polymer with electron acceptor (C60 as in PCBM).
-Solution processable due to side chains.
-Preferential orientation of polymer backbones parallel to the substrate gives rise to anisotropic CT.
-In BHJ cells CT is sensitive to the morphology.
-OPV energy generation steps: 
-1. absorption
-2. exciton diffusion
-3. charge separation
-4. charge transport
-PCE depends on # photons absorbed, dissociated, and that reach the electrode.
-Number absorbed depends on the absorption spectrum, absorption coefficient and layer thickness.
-The fraction of excitons which dissociate depends on the exciton dissociation length and the charge separation probability at the interface.
-Finally the the number of charges which reach the electrode depends on the driving force or gradient resulting from the potentials of the elctrons and holes.
-thin films (<100nm) are usually field drift dominated others have enough screening are dominated by concentration gradients at the contacts.
-I skipped over devices.
-concepts for improvement:
-metal electrodes quench electrons in C60 so an transparent, exciton-blocking layer is between electrode and layer with C60. ultrathin LiF interfacial layer is one example. 
-Increase the absorption range. smaller band gap <2eV ~800-900 nm.
-morphology controls.
-to control size of fullerene domains in p3ht/fullerene, a plasticizer was added.
-This increase miscibility of polymer and fullerene creating smaller domains.
-Solvent/evaporation time, surface interaction, and annealing all have a large effect of the morphology.
-
-\cite{Scharber2006a}
-Design rules for donor in BHJ solar cells
-interpenetrating network of C60 and conjugated polymer have shown ultrafast charge transfer (~40 fs).
-There is no competing decay process in this timeframe.
-optimized mixture with C60 converts absorbed photons to electrons with efficiency close to 100\%.
-At time of publishing best PCE is ~5\%.
-Efficiency is limited by low open circuit voltage of device under illumination.
-Organic semiconductors with bandgap of 2eV are used but observed $V_{oc}$ is in the range of 0.5-1 V.
-$V_{oc}$ in a metal-insulator-metal is equal to the work-function difference of the two electrodes.
-In polymer-fullerene $V_{oc}$ is affected by the morphology of active layer, electrochemical potential of the cathode.
-Ref 15 (Gadisa) studied correlation between electrochemistry andVoc of  polymer fullerene with PCBM and polythiophene and found that variation of the oxidation potential of the polymer caused variation in the photovoltage.
-(This is not the same as $V_{oc}$ ?) This paper suggests that Voc is related to HOMO of the polymer.
-and thus the maximum efficiency can be predicted.
-I am confused by a lot in the paper and don't understand why Voc is the limiting factor.
-Fig 2 is interesting, shows how they predict PCE from HOMO/LUMO and bandgap.
-Should Eg (bandgap) be LUMO acceptor - HOMO donor?
-OK so they don't really give suggestions for what kind of chemistry makes a better donor, but they do say that measuring the HOMO of the donor can tell a lot about the PCE of the device.
-
-\cite{Yu1995}
-
-Older paper about BHJs. (is this maybe the first about ADA BHJ?) MEH-PPV efficient charge transfer result from bicontinuous network
-time scale for CT from donor to acceptor is <picosecond, $10^{3}$ x faster than radiative/nonradiative decay, so efficiency is near 100\%.
-Just adding 1\% C60 increase photoconductivity by order of magnitude.
-conversion efficiency in a bilayer heterojunction device is limited when photoexcited exciton can't get to the interface.
-So an interpenetrating network is ideal because it maximizes interfacial area and minimizes the distance and exciton must travel to reach an interface.and if the network is bicontinuous then transfer of the charge to the electrode should be just as efficient.
-ITO (indium tin oxide) I thought was to prevent the active layer being quenched by the metal but they're saying it's the anode? PCBM is a soluble C60 derivitive. Ca electrode used.
-Pure MEH-PPV Voc 1.6V is consistent with the difference in work function of Ca and ITO. In the MEH-PPV/PCBM mix the turn on current shifts lower by 0.8V thus LUMO of PCBM is 0.8eV below Efermi of Ca. 
-They predict greater efficiencies if the morphology is optimized.
-
-\cite{Halls1995}
-
-another older paper.
-Cavendish lab!
-Photovoltaic effect - production of electrons/holes under illumination.
-Molecular semiconductors produce excitons instead of free charges.
-Charge collection requires dissociation, which is efficient at interfaces of different electron affinities and ionization potentials.
-(electron goes to larger electron affinity and hole to lower ionization potential.) A layered structure then seems ideal, but Exciton diffusion length is much shorter than the absorption depth.
-so an interpenetrating network is shwon in this paper to be ideal.
-poly-phenylenevinylene derivitive mixture MEH-PPV and CN-PPV.
-spin coating on glass slide.
-they claim phase separation on the scale of 10-100nm this measurement relied on ferric chloride doping MEH-PPV but not the CN derivitive.
-The current vs Voltage graph for the mixture was very different under illumination.
-they predict these sort of flexible polymer photodetectors will be useful in medical imaging.
-
-\cite{Gartner2019a}
-
-Somehow didn't add this!
-University of delaware. There is a Jankowski/Marsh image in Fig 1!
-OMG I just realised this is Arthi from the MoSDeF calls. :D No wonder this paper is so approachable!! 
-Atomistic structures, not always more accurate, can't compute polymer chain level rearrangement
-CG -- chemists might not like them but physicists do
-atomistic simulations are good when you already know the chain configuration at a state point.
-Atomistic FF are still tailored to fit the properties of specific systems.
-got distracted today...
-will continue with II.B tomorrow
-OK back to it
-CG - intermediate resolution (group of atoms within a monomer), CG monomer (whole monomer), mesoscale CG model (group of monomers on the length of a Kuhn segment or the whole chain.
-Finer models are parameterized to represent specific chemistries while coarse models are more generic.
-finer models can be parameterized with IBI for structure or force matching or relative entropy matching.
-the level of coarseness should depend on what features you want to examine.
-MARTINI - generic model 3-5 heavy atoms are grouped together each bead is assigned polar/apolar/donor/acceptor etc based on the chemistry/connectivity.
-soft potentials can be used for CG beads like DPD -- can have unphysically high compressibility
-!!! Systematic coarse graining approaches refs (87,91,269-273)
-start reading tomorrow at pt III
-
-simulation method (MC or MD) three steps
-1. create/initialize system
-2. equilibrate
-3. sample
-all steps should avoid bias.
-also choose ensemble, thermostat, barostat...
-choose for what you want to know.
-e.g.
-phase behavior - GCMC or GEMC phase coexistence with bead insertion/deletion.
-don't have to model the interface.
-Ref 308 is a GEMD method devolped by Arthi's group!
-
-Size: big enough that you can observe the phenomena you looking for.
-Calculating Flory-Huggins or polymer-polymer second virial coeff require long length scales.
-phase separations must also be larger than the length scale of the concentration fluctuations.
-However if interested indilute-soln properties like chain configuration or scaling laws--single chain even can be appropriate.
-finite size effects emerge from self interaction with the periodic image and limited size of box/system.
-smaller size can lead to pressure and stress fluctuation preventing calculation of mechanical properties.
-good rule of thumb -- box length to radius of gyration should be L/Rg >= 5.
-
-initialization: random initialization might be fine if system is isotropic but not at high density.
-A procedure to initialize high density CG polymer melts which uses MC with no intrachain moves and soft MD is described.
-an important metric for chain configuration is mean squared internal distance (measure of atoms or beads separated by n bonds along the chain).
-shows perturbations in internal chain not shown by the radius of gyration or end to end distance.
-We use a shrink-step, but that isn't mentioned here...
-
-Equilibration:
-relaxation in chain configuration is slow compared to relaxation of chain level metrics (like the mean squared interanl distance) or check MSD of CoM of polymer chains -- if they diffuse nultiples of Rg over equilibration, the system is relaxed.
-annealing processes (change T and P (also V???)) can help equillibrate.
-also mimic experiment.
-Start again at p.11 Sampling
-decorrelation is expecially important for polymers as the relax very slowly.
-Calculate the decorrelation time of a property of interest like Rg (for polymers this might be better than the decorrelation of the potential energy!)
-for systems with high energy barriers to rearrangement, small independent simulations may be better than independent snapshots from one simulation.
-Advanced sampling techniques: umbrella, Wang-Landau, adaptive force biasing, etc. used to explore free energy landscapes with mulitple barrier between minima more efficiently.
-Analysis - focused on structural and thermodynamic properties -- not dynamic properties.
-Looking at simulations is great, but it must be paired with quantitative analysis.
-Always report error bars.
-good way to do this is block averaging: simulation (trajectory?) is split into blocks the mean value of a quantity of interest is computed in each block, the average and std dev of the mean from each block which then become the ensemble average and std err for the entire simulation.
-RDF and structure factor characterize system of many length scales as well as allow access to thermodynamic quantities of interest.
-Sq can be directly compared with experiment and analysis of low q (long length scale) provides insight about phase separation and concentration/density fluctuations.
-However--range of q that can be accessed in simulations is limited to longest real-space distance that can be reliably sampled in box.
-Two methods to calculate Sq (fourier transform of g(r) and summation method) the fourier transform can introduce unphysical artifacts because it is only rigorously defined over infinite spatial domain (impossible for a simulation box.)
-other scattering techniques include reflectivity, small-angle/wide-angle scattering, diffraction (jankowski marsh paper cited!).
-They even mention dynamic S(q,t) can be used to understand chain relaxation.
-Flory Huggin parameter - lattice model of thermodynamics of polymer solutions takes into account different molecular sizes when calculating entropy of mixing.
-(this paper goes into depth about a specific thing about this parameter but as I have only just heard of it -- the summary above is from wikipedia-- I don't understand what it is talking about yet)
-Phase Transitions - different order parameters (Rg, end-to-end distance, etc) may be necessary to find a phase transition. Simulations that use a temp/pressure ramp may show hysteresis. 
-Using analysis software - make sure to validate using previously published results.
-Made it to section IV! finish paper tomorrow. :)
-Comparison with experiments - CG model can have quantitative agreement with universal parameters based on polymer physics like polymer chain size scaling with MW.
-Otherwise it is unreasonable to expect quantitative agreement.
-Although they may have agreement for more physical parameters, same goes for atomistic systems.
-Always need to recognise the limits of your model and have good expectations.
-Example: Tg in glassy polymers often found by the intersection of linear fits of density vs temperature above and below transition temp.
-To obtain density vs T the system is gradually cooled but even the slowest cooling rate is ~10 orders of magnitude faster than experiment.
-This is known to raise Tg significantly.
-Tg needs correction.
-but it is useful to examine trends in Tg--polymer architecture, chemistry, MW.
-and expect similar trends in experiment.
-Because of free energy landscape flattening in CG, dynamics can only be qualitatively compared. Also keep in mind when comparing to an instrumental analysis, the limits of the instrument.
-Comparison to theory - limitations include finite size effects, inability to capture phenomena without advanced sampling, inability to capture time scales (fast molecular vibrations vs polymer relaxation).
-Combined simulation with theory where simulation feeds parameters into the theory model.
-DFT-with MD/MC can be used to calculate the free energies in structure during solvent evaporation.
-PRISM - don't quite understand what this is something like a way of understanding the structure of a polymer morphology?
-Finished! OK paper takeaways -- autocorrelation for polymers shouldn't be based on PE, need to learn how to calculated some of the polymer metrics.
-
-\cite{Muller-Plathe2002}
-
-linking length and time scales.
-Analogy plant cell metabolism is very fast but tree death due to pollution is very slow; it is unecessary to measure tree dieback every milisecond.
-this analogy in chemistry ca go from observing bonding with electron wavefunctions, to modelling solvation with explicit water and FF, to modelling the flow of bulk water with a continuum characterized with various parameters.
-coarse grain models are built rigorously through converting the results of a fine grain system to the parameters of the coarser system.
-This efficiency gain allows us to indirectly predict large-scale and long-time quantities.
-Backmapping allows the coarse method to generate *samples* for the fine-grain method.
-mapping atom to coarse grain bead reduces the DOF and the effective potential account for the missing DOF.
-CG potentials are usually softer which allows larger time-steps.
-CG models are specific, tuned to a specific chemistry and to reproduce a specific structural or thermodynamic feature.
-A penalty function can be used to determine how far off the CG model is.
-The degree of coarse-graining and where the beads are placed can affect the success of reproducing the structural/thermo feature.
-They show an example of a diphenyl carbonate represented by 3,2,1 beads.
-The 3 bead structure easily replicates the atomistic RDF with just LJ6-12, the 2 and 1 bead structures do not, but the 1 bead structure can be made to fit the atomistic rdf if a piecewise potential is used (overfitting?)
-Cg optimization procedures: two procedure are describe here the first optimizes Gaussian functions--I don't understand what or how they are optimizing.
-the other uses elliptical potentials to give space filling at experimental density.
-start next time at section 3.3
-Using a DOF distribution (pairwise, bond stretch, angle) to get a CG potential.
-An analitical function.
-the potential obtained this way really is a free energy not a potential energy.
-It incorporates effects from finite temperature and neglected degrees of freedom.
-IBI is a way to get a numerical potential (For IBI Reith is cited -- he appears to be Muller-Plathe's PhD student.) The description of IBI is really concise and clear.
-:) IBI is a tabulated potential.
-They describe two other methods.
-Potentials can also be optimized to match thermodynamic targets. They discuss how to add a cutoff value to IBI potential. also cite a paper that adds pressure information to numerical potentials.
-skipping lattice models.
-Atomistic -> derived CG potential -> CG sim -> backmap to atomistic -> local relax. 
-Seems roundabout but it's not!
-Smoothing of the PE surface in CG allows easier access to polymer morphology.
-CG can provide starting structures to atomistic MD.
-which can then be inputs to electronic structure calculations.
-CG is so much more efficient we can calculate chain properties. AUTOMIZATION IS KEY (IBI, simplex). The intellectually challenging part of CGing is where to place the beads!!
-errors in atomistic FF will filter to CG ff.
-CG models are specific to the conditions under which the parameterization is performed.
-
-\cite{Reith2003a}
-
-IBI algorithm is made in this paper! Uses potentials of mean force. IBI potentials are nontransferrable--they work best for the system they are optimized for.
-CG allows chain behavior to be studied.
-History: bead spring polymer chains in a melt to a soft-core liquid ellipsoidal particles with anisotropic gaussian potential.
-polymer melt cg-ing.
-None of these derived an automated optimization scheme to conserve the chemical nature of the underlying atomistic model in a standardized way as we do.
-PRISM theory combined with MC can predict long and short range structures of polymer chains but can't produce CG potentials.
-Reverce MC can reproduce RDF without a need for potential. lack of potential limits usefulness though because RMC uses knowledge of RDF without knowing underlying forces.
-Description of IBI algorithm: potential of mean force IS boltzmann inversion of RDF. (Free energy NOT potential energy.) Bending potentials before nonbonded potentials.
-They used a five point running average to smooth the potentials
-bond stretch -> angle bend -> nonbonded -> dihedral
-They started with monoatomic liquids with LJ and WCA potentials (1) they used the correct potential as V0. (2) then they used the boltzmann inverse of the RDF. 
-Conclusions:
-start with small range (cutoff?) and increase until RDF matches. CG FF for polyisoprene are different between solution and melt.
-
-\cite{Ayton2007a}
-
-Coarse graining scheme, systematic, for biological systems.
-If CGing is done systematicall it retains important averaged atomistic level interations.
-Connecting length and time scales.Systematic methods for making CG systems: RMC, this paper will focus on multiscale coarse graining (MS-CG) uses force matching algorithm
-Variational.
-Some of the math does not make sense but it appears to only be based on positions of atomistic and CG particles.
-They make the free energies of the atomisitic and CG systems the same.
-Many atomistic frames are mapped to CG beads and the potentials are based in the gradient of the forces felt by the beads.
-The algorithm minimizes a residual function.
-Summary: works, RDFs match.
-Enables calculation of CG force fields without resolving many-dimensional potential of mean force.
-(but honestly IBI seems so much simpler.
-Is there something I'm missing?
-is boltzmann inverse of RDF not PMF??
-This paper was published after Reith paper...
-when is force matching better?)
-
-\cite{Peter2009d}
-
-Review paper- coarse grained models linked to atomistic models. 
-They mention the good, marginal, and poor solvent parameter Theta.
-models can be linked sequentially, hybrid - both level present at once and interacting, or adaptive - individual molecules switch on the fly depending on e.g., spatial coordinates.
-CG target can be thermodynamic or structural.
-Structure based: boltzmann inversion of distribution with constant to set minimum to 0.
-Free energy vs PMF?
-Boltzmann inversion usually results in a tabulated potential but by fitting to gaussians it can be mapped to an analytical function.
-Bonded potential can be determined on a single polymer chain in vacuo but then the nonbonded interactions have to be considered carefully to avoid double counting.
-However bonded and nonbonded can be obtained from the same atomistic simulation of polymer melt iteratively.
-This makes the potentials interdepent.
-IBI can also consider other thermodynamic quantities like pressure and compressibility. IBI not useful for dilute solutions
-start next time at backmapping
-backmapping has no one unique soln.
-every CG structure corresponds to an ensemble of atomistic microstates.
-reinsert theatomistic structure so that the atoms still satisfy the CG mapping and then relax the atoms with position restraint to the CG position.
-CG backmapped to atomistic allows better comparison with experiment than atomistic alone by giving access to larger length and time scales.
-e.g., NMR timescales are too long to simulate with atomistic alone, yet atomistic coordinates are necessary.
-Dynamics: the CG model is independent and has it's own timestep. dynamics are accelerated.
-
-\cite{Baschnagel2000}
-
-Bridging the gap between coarse and atomistic.
-Specific to polymers.
-This paper focuses on the mapping of atomistic to CG.
-(cool!
-first paper to focus there.) also discussed backmapping.
-Just noticed this paper is 150 PAGES LONG!
-OK time to skim.
-Polymers have properties which can be measured at many different length scales. diffusions constant can be measured by monitoring the center of gravity of the chains.
-It is too big and too slow and also just a bad idea to simulate huge boxes of atomistic polymers.
-Even if the simulation was to complete, there would be too much information to process accurately.
-CGing allows scientists to FOCUS their experiments.
-start next time section 2 (p8 of 116)
-Frozen nuclei approximation is incorrectly referred to as the Born-Oppenheimer approximation?
-Quantum chemistry is good for predicting bond and angle potentials but not for LJ because you would need huge basis sets and high order electron correlation.
-DFT has similar issues LDA results in overbinding and GCA no attraction.
-partial charges are conformation dependent.
-Quantum chem is very useful for parameterizing dihedrals!
-I skimmed this section v heavily but my takeaway is that if you need to know about a chemical reaction (transfer of electrons) it makes sense to consider QC methods.
-Also QC methods are not the cure-all for making forcefields.
-section 3 - how do we get dense systems?
-it is hard to change the system once it gets to a dense atomistic representation. so one should start with a good systm! (like from coarse-grain)
-This is tough because polymers are dense, amorphous, and highly-connected. three methods exist:
-1. add new segments according to the metropolis criterion
-2. coarse initials guesses created on a lattice
-3. low density condensed step by step using NPT
-they described a method of initializing using stream lines and vector fields which results in polymers of constant curvature.
-They describe a new rotational move that does a dihedral cis-trans flip.
-next time skim through the rest of this paper. I'm over it
-read mazzio paper!
-gave up on baschnagel paper--switching to mazzio!
-
-\cite{Mazzio2015}
-
-oh this paper is so much better. 
-opvs are lightwieght, low cost, flexible. Metrics for evaluating these are PCE, Levelized cost of energy (LCOE) and energy payback time (EPBT).
-LCOE is life cycle cost/energy produced. EPBT is how long it takes for a device to pay for itself.
-start next time at section 2
-inorganic: absorptions of photons with energies greater than the band gap results in free charge carriers that can separate at an p-n junction.
-they can diffuse under external electric field to electrodes.
-organic: lower dielectric constant which prevents screening of the attraction between electrons and holes this results in exciton formation rather than free charges.
-separation of the exciton requires an acceptor/donor interface.
-if the exciton doesn't reach an interface it will decay back to ground state resulting in the loss of that energy.
-donor: large ionization potential acceptor: high electron affinity.
-different loss mechanisms are discussed: geminate recombination is where the separated charges recombine across the interface.
-charge recombination where free charges recombine with unassociates charge carriers in a device.
-There is some about electrochem which I am reading but not understanding :( external quantum efficiency is a measure of how much current will be produced by a particular wavelength of light.
-it depends on the efficiency of photoabsorption, exciton diffusion, charge transfer, charge collection.
-CHARGE TRANSFER is not the same as CHARGE TRANSPORT
-ASTM reference spectra are used now to characterize and standardize OPV
-3. Device architectures
-some history about opvs: Tang 1979 introduced the two-component donor acceptor active layer with thermally evaporated small molecules. bilayer structure. limited by exciton diffusion length. 
-BHJ with fullerene acceptor reported by Yu in 1995 -still state of the art morphology.
-diagrams of different device architectures.
-start next time on section 4
-materials design (aka the good part :D )
-good opv acceptor/donors are solution processable, have appropriate band gaps and energy levels, and long planar pi-stacking for good charge carrier mobilities.
-regioregularity (head-tail vs head-head p3ht).
-Mn is the number average molecular weight of the polymers.
-weight of all polymers/number of chains.
-Mw is the molecular weight per unit weight of polymer (accounts for size distribution).
-dispersity is Mw/Mn.
-commonly used materials: initially poly(p-phenylene vinylene) (PPV) was very poplar.
-It was mixed with PCBM (c60) in first reported BHJ solar cells.
-now we have shifted away towards poly alkyl thiophenes like p3ht.
-p3ht/pcbm was max EQE of 76\%.
-post processing like thermal annealing with externall electric field produced devices with max PCE of 3.5\%.
-it has been shown the p3ht and pcbm have strong dependence on regioregularity.
-longer chains are shown to perform better, due to increased mobility with polymer aggregation.
-ways to decrease the band gap have become popular using DA polymers (alternating electron rich and electron poor heterocycles) PCDTBT achieved efficiency of 7.5\%.
-PTB7 had PCE of 7\% and then over 9\% due to promotion of the quinoidal resonance structure using thienothiophene.
-quinoidal stabilization improves shortcircuit current (Jsc) and fill factor (FF) which increase EQE and IQE so it has good exciton dissociation, charge transport and extraction.
-Some small molecule (not polymer) devices show promise.
-fullerenes are commonly used as acceptors.
-the added groups are to help solubility.
-pc61bm has limited absorption and deep lumo so it can be improved by using pc71bm which is less symmetric and has more allowed optical transitions.
-indeneC60 is being used to adjust the LUMO level.
-next time section5
-morphology
-the ideal is an interpenetrating network of d-a materials with domain sizes on the order of the exciton diffusion length (10 nm).
-Enough interfacial area to dissociate lots of excitons while maintaining continuous charge transport pathways.
-Parameters that affect the active layer are solvent donor/acceptor concentrations, thermal annealing times/temps, solvent annealing, additives, and interlayer surface energies.
-solvent - vapor pressure, boiling point, viscosity, polarity, solubility, wettability dictate much of the initial film forming.
-solute properties like concentration, blend ratio, solubility also important.
-and finally the method of deposition matters-- high-throughput processing will require alternatives to spin coating but spin-coating is most widely used so it's what this review covers.
-switching the solvent in a PPV/PCBM from toluene to chlorobenzene improved performance by nearly three fold!
-the solvent allowed more mixed/smaller domain sizes.
-fullerene has better solubility in chlorobenzene.
-same active layer compounds in chlorobenzene or toluene, switching the total solute concentration and the ratios had an effect on the morphology but chlorobenzene prevented fullerene aggregation until very high loading.
-a study also showed that slow evaporation allowed for separation of p3ht/pcbm but fat allowed for formation of an amorphous glass.
-Thermal and solvent annealing allows for larger domains in p3ht/pcbm. annealing increase the hole mobility --> this is the most important factor in increased performance!
-Chen (ref 41) studied p3ht/pcbm with GIXD. found that annealing results in bicontinuous network of polymer/fullerene with domains on the order of the exciton diffusion length.
-Solvent annealing where layer is annealed under vapor.
-shown that poor solvents better enchance performance then good solvents.
-good solvents develop greater self-organization of p3ht -- but the domain were too big.
-solvent annealing promoted PCBM separatiun to the top of the device.
-interpentrating network has been the ideal, but crystalline regions of acceptor donor with mixed amorphous regions is more realistic.
-
-\cite{Brini2013}
-
-review of systematic coarse-graining for soft materials
-focuses on representability (how well a system predicts properties at the statepoint it was optimized for) and transferrability ( how well it can be used for other statepoints.)
-effective pair potentials are used for CG instead of the expensive many-body potentials.
-averaging over fast degrees of freddom removes their entropic contribution.
-to compensate for this, the pair potentials are softer resulting in a smoothed energy landscape.
-this affects the thermodynamic properties-- e.g., the heat capacity, which is related to the entropy fluctions at constant t and p is underestimated by a cg model (because the fluctuations arent as large).
-while compressibility related to volume fluctuation will be over estimated (i think because the potentials are so soft.) The thermal expansion coefficient which is related to both may well be represented accurately.
-parameterized vs derived CG potentials - 1st one atomistic simulations are used to calculate target properties (pair correlations, force distributions) IBI is this.
-2nd one atomistic interaction are used directly.
-not optimized to reproduce selected tragets, therefore all properties are predictions of the model.
-Parameterized methods: IBI method described. 
-Inverse Monte Carlo - also an iteractive scheme that corrects a guessed interaction potential in order to reproduce a target radial distribution function, but the guess is based on statistical mechanics that take into account that a variation of the potential at a given distance r can lead to a variation of the RDF at all other distances.
-more expensive than IBI requires longer sims to calculate correlations.
-Can also include target thermo properties like surface tension.
-Both IBI and IMC are cases of relative entropy -- a measure of the amount of information lost upon coarse-graining and is defined in term of propability distributions of atomistic and CG systems.
-both methods minimize the discrepancy between the atomistic and CG distributions.
-Another method is force matching. effective pair potentials match the mean force on a particle through the atomistic force field.
-Derived methods: These potentials have a clear physical meaning (why?) potential of mean force calculated at LOW concentration. fragment based coarse graining
-skipped ahead to polymers
-polymers are important for cg because the volumes needed to observe their long length scale properties in atomistic md are prohibitively expensive.
-pressure-corrected IBI scheme for polystyrene matched gyration radius and Flory characteristic ratio at 500 K.
-(flory ratio relates to chain stiffness?) but entanglement length was overestimated.
-
-\cite{Murtola2009a}
-
-quick letter - to get the full picture we have to consider multiple length scales.
-abstracting small length scales is necessary for time/resources.
-probably dont include this in references, it's so short.
-
-\cite{Berendsen2010}
-
-ooh this one looks cool. starts with history of membrane models, goes to cging, then moves to cg dynamics. for next time
-many realistic process could not--and would never--be solvable by atomistic simulations.
-he describes a very simplified model of transport of a single water molecule through a membrane.
-reduce the system to motion in one reaction coordinate.
-the heart of coarse-graining is the reduction of degrees of freedom.
-then describing the dynamics of the reduced system so that it reproduces the projection of the complete system.
-this is only possible when the reduced and the removed degrees of freedom are well-separated (the removed are much faster).
-If the time scales are not separate the dynamic behavior will not be accurate but the probability distributions and thus the thermodynamic properties may still be.
-The choice of relevant dof is made on an intuitive basis and depends on what properties are wished to study. Note that atomistic md is already concerned reduced--no electronic dof.
-if a CG model does not predict any properties beyond the ones you have used for parameterization--you have achieved nothing! always require your model to predict something unknown.
-the motions in reduced space: the equations of motion are no longer hamiltonian--forces depend not only on the present but also the past configuration.
-Forces proportional to the velocity are non-conservative (kinetic energy is lost).
-in order to maintain average KE and T noise must be added.
-I skimmed the sections on dynamic equations and modelling fluids.
-simple methods that are easy to understand and implement--provided they are correct and work--will always prevail over complex methods, even if the latter are more accurate.
-
-\cite{Kim2006}
-
-experiemental paper about effect of p3ht regioregularity in p3ht/fullerene blends on device performance--PCE.
-really useful schematic of GIXS experiment. (GIXRD)
-interplane pi-pi stacking is parallel to the substrate--enhanced interplane interactions with high RR p3ht benefit vertical (J-V) more than lateral (field-effect) transport.
-TOF hole mobility in p3ht films show neglible influence of RR.
-inteplane stacking does not affect vertical transport in pristine crystal.
-in the blend dark-current densities and TOF mobilities show stronger dependence on regioregularity.
-highest device efficiency achieved with RR p3ht
-
-\cite{Lee2011}
-
-multiscale simulation of p3ht and pcbm. 1 bead per p3ht and pcbm. They used IBI to get their force field.
-they use a penalty function to minimize their lj parameters-- I think this is different from IBI in that it doesn't use a table potential.
-their reverse mapping method could use a little clarification but it sounds like they replace CG bead (p3ht or pcbm monomer) with equilibrated atomisitc structure and then do only rotation moves until the whole system is relaxed.
-(thats kind of cool actually!) after MC they do quick MD.
-smoothing of the energy barriers i the CG sim accelerates the dynamics.
-CG morphology is in good agreement with TEM and electron tomography.
-with backmapping even pi-pi stacking was observed.
-they use a spatial discretization scheme to simplify the volume into voxels and quantify the interfacial area to volume ratio.
-as time goes on in the simulation the p3ht domain sizes grow and the interface to volume ratio decreases--this is a bad thing?
-is this related to the quick annealing having better results??
-
-\cite{Huang2010}
-
-CG polymer fullerene simulation of opvs.
-parameterized at two state points.
-it is still not know how to predict phase behavior based on components and processing.
-the molecular scale structure often has to be inferred.
-the relationship between phase behanvior and charge transport has been investigated but there is some disagreement.
-this is where simulation comes in. systems of only a few nm can be studied--but the exciton diffusion length is ~5-10 nm --> CG
-ff for super atoms are parameterized using atomistic ff.
-OPLS-AA 3-site p3ht and one site fullerene.
-They use IBI to parameterize their ff.
-they use a a scaling function to match the pressure.
-(i don't understand how this works exactly)
-they found that their model could be useful outside of the temps it was parameterized at. 
-they calculated the time scale of the cg model.
-they were able to compute 768 p3ht 48mers and (110592 beads) with 4608 pcbm beads in a 25 nm^3 box in about 24hr.
-
-\cite{Jankowski2013}
-
-opv performance strongly depends on morphology. ideal is to have high interfacial area while maintaining high connectivity. 
-choosing a model: sufficient chemical and physcial detail without too much to prevent sufficient sampling at relevant length and time scales.
-if the model is too coarse we miss intecalation of the fullerene between the side chains.
-order-disorder trainsition for neat polymers depend on side chain orientation (regioregularity?) and orientation along th polymer backbone. 
-immiscible acceptor in blends do not change the morphology compared to neat but increase the ODT.
-CG model gives backbone persistence lengths that match experiment. (has to do with bending stiffness of polymer)
-how were LJ params obtained for CG model?
-how to quantify interfacial area--acceptor-backbone correlation rdf first peak, 
-intercalated layer are seen as the acceptor miscibility is increased-- mostly with the most sparse polymer (do the acceptors feel the most attraction to the backbone?
-new lattices predicted--have these been observed?
-
-\cite{Marsh2014}
-
-\bibliography{library}
-\bibliographystyle{ieeetr}
-\end{document}
+#Intellectual merit and broader impacts?

### 2020-07-28 reading-notes.tex
read yang2006

@@
 \cite{Yang2006a}
+reduced models include solvent in the effective parameters.
+Amber UA for proeins.
+groups hydrogens with carbons except on backbone.
+United atom model dates back to 1970s the UNICEPP ff.
+nonpolar hydrogens are implicit.
+efficiency gain is.
+system size can reduce by roughly half since many hydrogens in biological/organic systems.
+fewer nonbonded and internal dof.
+larger dynamics step sizes since small hydrogen mass requires a smaller time step.
+and hydrogen position is not usually helpful for analysis methods like x-ray crystallography.
+by representing polar hydrogens this model can gain the benefits of UA while minimizing some disadvantages like UA ff not representing h-bonding or pi-stacking.
+
+\cite{Levitt1976}
+one cg bead per residue
+
 \cite{McCoy1998a}

### 2020-07-28 1summ.tex
copied over stuff from Mike's proposal. Made my timeline.

%%%%%%%%% PROJECT SUMMARY -- 1 page, third person
% e.g:  "The PI will prove" not "I will prove"

%Below are the pagination, font size, spacing and margin
%instructions for NSF proposals: \\
%
%FastLane does not automatically paginate a proposal.
%Each section of the proposal must be individually
%paginated prior to upload to the system. \\
%
%Use Computer Modern family of fonts at a font size of 11 points or
%larger. A font size of less than 10 points may be used for mathematical
%formulas or equations, figure, table or diagram captions and when
%using a Symbol font to insert Greek letters or special characters.
%The text must still be readable. The use of small type not in compliance with the NSF guidelines
%may be grounds for NSF to return the proposal without review. \\
%
%No more than 6 lines of text within a vertical space of 1 inch. \\
%
%Margins, in all directions, must be at least an inch. \\
%
%

\begin{center}
\large{\textbf{<Title>}}
%\large{\textbf{ADVANCEMENT OF ORGANIC PHOTOVOLTAICS THROUGH ARTIFICIAL NEURAL NETWORKS}}
\end{center}
\begin{center}
    Jenny W. Fothergill
\end{center}
\begin{center}
    \textbf{Project Summary}
\end{center}

%\begin{center}
%\emph{Maximum of 1 page}
%\end{center}
% This should be a brief statement of the problem you plan to address.
% It should look something like an abstract.

%The project summary should be a description of the proposed activity suitable
%for publication, no more than one page in length. It should not be
%an abstract of the proposal, but rather a self-contained description of
%the activity that would result if the proposal were funded. The summary
%should be written in the third person and include a statement of objectives
%and methods to be employed. It should be informative to other persons
%working in the same or related fields and understandable to a scientifically
%or technically literate lay reader. \\
%
%The summary must clearly address in separate statements (within the one-page summary):
%the intellectual merit of the proposed activity; and the broader impacts
%resulting from the proposed activity. Proposals that do not separately
%address both criteria within the one-page Project Summary will be returned without
%review. \\

\begin{center}
    \textbf{Intellectual Merit}
\end{center}
% This is why your project is interesting and will help further
% knowledge in the field of science. 
%How important is the proposed activity to advancing
%knowledge and understanding within its own field or across different fields?
%How well qualified is the proposer (individual or team) to conduct the project?
%(If appropriate, the reviewer will comment on the quality of prior work.)
%To what extent does the proposed activity suggest and explore creative, original,
%or potentially transformative concepts? How well conceived and organized is the
%proposed activity? Is there sufficient access to resources?  \\

%\required{Broader Impacts}
\begin{center}
    \textbf{Broader Impacts}
\end{center}
% There are 4 kinds of broader impacts.
% 1. advance discovery and understanding while promoting teaching,
% training and learning
% 2. broaden the participation of underrepresented groups
% 3. disseminated broadly to enhance scientific and technological
% understanding
% 4. benefits of the proposed activity to society

%OPV devices reaching consistent efficacies of 15\% have the potential to create a global energy revolution.
%At this efficiency, OPV devices will surpass inorganic solar cells, and even gas and coal in terms of cost per watt of electricity generation.
%Thus, regardless of the current administration's reluctance to accept the reality of climate change, OPV devices will be seen superior to 'dirty' power production methods due to their competitive price.

### 2020-07-28 2pd.tex
copied over stuff from Mike's proposal. Made my timeline.

\section*{Motivation}

\section*{Research Objectives}

\section*{Background}

\subsection*{Organic Photovoltaics}

\subsection*{Molecular Dynamics}

\subsection*{Multi-State Iterative Boltzmann Inversion}

\subsection*{Mesoscale Device Simulation}

\section*{Preliminary Work}

\section*{Research Plan}
\subsection*{Objective 1}

\section*{Predicted Outcomes}

\section*{Contingency Analysis}

\section*{Timeline for Implementation and Evaluation}
\begin{table}[h]
    \resizebox{\columnwidth}{!}{
%\resizebox{\textwidth}{!}
    %\centering
    \renewcommand{\arraystretch}{1.1}
    \begin{tabular}{| c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c |}
        \hline
        \multirow{2}{*}{PROJECT TASK}& \multicolumn{4}{c}{YEAR 1} &  \multicolumn{4}{|c}{YEAR 2} & \multicolumn{4}{|c}{YEAR 3} & \multicolumn{4}{|c|}{YEAR 4} & \multicolumn{4}{c|}{YEAR 5} \\ 
        \hhline{~--------------------}
             & 1  & 2  & 3  & 4  & 1  & 2  & 3  & 4  & 1  & 2  & 3  & 4  & 1  & 2  & 3  & 4 & 1  & 2  & 3  & 4\\
        \hline
           Complete Coursework & \multicolumn{10}{|c|}{ {\cellcolor{lgray}} } &  &  &  &  &  &  &  &  &  &\\
        \hline
           Present at a Conference  &  &  &  &  &  &  &  &  &  &  & x &  &  &  &  &  &  &  &  &\\
        \hline
           Publish a First Author Paper  &  &  &  &  &  & x  &  &  &  &  &  &  &  &  &  &  &  &  &  &\\
        \hline
           Proposal and Comprehensive Exam  &  &  &  &  &  &  &  &  &  &  &  & * &  &  &  &  &  &  &  &\\
        \hline
           Expand Functionality of Open Source Packages & & & & & & \multicolumn{11}{|c|}{{\cellcolor{lgray}}} & & & &\\
        \hline
           Develop Coarse Graining Package              & & & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
        \hline
           Develop Automated MS-IBI Code                & & & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
        \hline
           Develop Backmapping Package                  & & & & & & & & & & & & \multicolumn{5}{|c|}{{\cellcolor{lgray}}}& & & &\\
        \hline
           Generate Coarse-Grain Morphologies           & & & & & & & & & & & & & & \multicolumn{4}{|c|}{{\cellcolor{lgray}}}& & &\\
        \hline
           Evaluate OPV Device Performance & & & & & & & & & & & & & & \multicolumn{4}{|c|}{{\cellcolor{lgray}}} & & &\\
        \hline
           Write Dissertation & & & & & & & & & & & & & & & &{\cellcolor{lgray}}& {\cellcolor{lgray}}& {\cellcolor{lgray}} &  &\\
        \hline
           Present Dissertation Defense  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &&  & {\cellcolor{lgray}} &  &\\
        \hline
             %Saved row template
             %&  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
    \end{tabular}}
    \caption{Anticipated timeline. * indicates right now, X indicates already accomplished.}
\end{table}

### 2020-07-29 reading-notes.tex
adding a bunch of papers to compare data to

@@
 \cite{Levitt1976}
-one cg bead per residue
+protein cg model--backbone represented by 3 beads (alpha-C, O, N) one bead per sidechain.
+protein sequence dictates folding so simplifying to one bead per amino acid seems reasonable.
+challenges: too many atoms, proteins fold in water at RT (opposed to small molecule crystals which can be calculated in vacuum at low temp)
 
 \cite{McCoy1998a}
+backmapping from UA to AA. ugh maybe skip this.
+
+\cite{Yi2018a}
+PTB7-Th:ITIC/SF-PDI4 PCEs, mobilities, 1D scattering
+
+\cite{S.Gurney2019b}
+PTB7-Th ITIC PCE scattering patterns
+
+\cite{Swick2019a}
+ITIC derivatives, dft, crystal structures
+
+\cite{Hammond2011a}
+PTB7:PC71BM scattering PCE
+
+\cite{Qin2016}
+P3HT, PDCBT:ITIC scattering PCE
+
+\cite{Pan2018c}
+ITIC: PBDB-T and PBQ-0F molecular dynamics and dft
+
+\cite{Shi2017d}
+4TIC, PTB7-Th PCE scattering
+
+\cite{Wang2019c}
+PBTZF4, ITIC-Th experimental PCE values, mobilities
+
 \bibliography{library}

### 2020-07-29 1summ.tex
brief placeholder for summaries

@@
 \end{center}
-
 %\begin{center}
@@
 %review. \\
+design a simple coarse-graining backmapping package with a focus on opvs
 
@@
 %proposed activity? Is there sufficient access to resources?  \\
+a coarse graining pipeline will help make multi-scale simulations more accesible/useable for others. This can be useful for screening of potential OPV compounds
 
@@
 %Thus, regardless of the current administration's reluctance to accept the reality of climate change, OPV devices will be seen superior to 'dirty' power production methods due to their competitive price.
+
+Helping to make research transferrable, reproducible, useable, and extensible. Software carpentry instructor training. software dev best practices.

### 2020-07-29 2pd.tex
reorganized paper.tex into 2pd

@@
 \section*{Motivation}
+<why do opvs matter>
+In order to make the most efficient opvs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
+<opv performance is intimately linked with structure>
+With minor modifcations the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
+By using a simulation pipeline, we can help to streamline the process of determining which opv materials will help to solve the energy crisis
+Simulation also helps to give us insight into the atomic interaction which drive self assembly.
+A complication of this simulation is that the features which are important to the performance of an opv span multiple length scales.
+The electronic properties are important for light absorption, charge transfer <morehere>
+while the bulk morphological properties are important: an exciton needs to be able to find an interface at which to dissociate before it decays through one of its non-radiative processes and one the charges are separated they need to reach an electrode in order to generate current and produce electricity.
 
@@
 
+\subsection*{Coarse Grain Models}
+
+Coarse-grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models.
+Coarse-graining refers to grouping atoms in a structure into a "super-atom" and using an effective potential to represent the resulting coarse grain site.
+The resolution of coarse grain systems is broad:
+Simply grouping hydrogens with the heavy atom they are bonded to, called the united-atom model, has been shown to speed up dynamics and make polymer length scales more easily accesible \cite{Paul1995a, Yang2006a,}.
+Other goarse-graining schemes may group functional groups together <cite> or even represent an entire amino acid with a single site <cite>.
+General coarse grain models of opv thiophene polymers where only the spacing, regioregularity of the side chains were varied were able to predict different order disorder transitions and calculated scattering patterns of these simple systems were comparable to those obtained from experiment \cite{Jankowski2013, Marsh2014}
+A coarse-grain model for phospholipids has allowed for bilayer formation from an initial random configuration to be observed even though the model was parameterized to the vapor-liquid phase transition.\cite{Shelley2001}
+Which model is right depends on the length and time scale on which the property of interest can be observed.
+
+For many systems, however, we are interested in properties which span length scales.
+For instance, in a system like a opv polymer melt, it is not only computationally intractable to try and simulate the electron density on length scales proportional to the exciton dissociation length (~5-10 nm)<cite> -- it is the wrong tool for the job.
+If what we are interested in is the properties of the polymer in the bulk heterojunction, then it is wise to abstract away any degrees of freedom which do not directly contribute to the self-assembly of the structure.
+Once a good bulk structure has been achieved, the atomistic details can be reintegrated much more easily--a process called backmapping.
+In the same way that a coarse grain model can be mapped onto an atomistic one, we can get a reasonable starting structure for an atomistic simulation from a coarse grain structure.
+The large length scale, polymer level properties can be equilibrated during the coarse grain simulation, and then the atomic interactions can be equilibrated during the backmapped atomistic simulation.
+This can allow us the calculate properties such as charge transport, which depends upon the electronic structure of individual chromophores and the connectivity of these chromophores over distances proportional to the exciton dissociation length.
+<what stands in our way?>
+
+<coarse-grain models are specific>
+
+<segue from automated creation of forcefields to...>
+<mapping operator has to be decided by hand> <is this section too big?>
+Part of coarse graining that is not yet automated is choosing a mapping scheme or a mapping operator.
+A mapping operator defines which atoms are grouped into a "super atom" represented by one coarse grain site and where in the site is placed relative to the atom group.
+Mapping operators are chosen based on desired resolution of the coarse grain system and the information to be extracted.
+A straightforward way to define a mapping operator is to group a set number of heavy atoms (non hydrogen) together--this is the method used in the MARTINI force field\cite{Marrink2007}.
+In this scheme, four atoms (except rings, which are treated differently) are grouped and the site is classified as polar, non-polar, apolar, or charged depending on the atoms it is composed of.
+When parameterizing a new molecule you must pick a mapping and then compare the resulting beads to existing beads--a process which is time consuming and error prone\cite{http://www.cgmartini.nl/index.php/tutorials-general-introduction-gmx5/parametrzining-new-molecule-gmx5}.
+The MARTINI force field was first designed for lipids--further parameterization for proteins and nuclei acids have been added<cite--and has shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.
+Many mapping schemes are simply based on the user's chemical intuition (e.g., what parts of the molecule shouldn't be allowed to bend?<cite any model where rings are one bead> What groups have the most dominant interactions in this structure <cite dna cg model>).
+As the number of atoms in the fine grain structure increases, the number of possible mappings increase drastically.
+There have been efforts to create mapping schemes for automating the process of deciding which atoms are grouped in a "super-atom" bead.
+One study reduced the number of allowed mappings by only allowing those which do not change the symmetry group, then iterated over a graph of all possible mappings to find the "best" mapping by comparing the difference between the mapped RDF and velocity autocorrelation function \cite{Chakraborty2018a}.
+Another mapping scheme uses principle component analysis to choose a mapping scheme for biomolecules that best represents th essential dynamics\cite{Zhang2008}.
+Mapping operators can be automated using machine learning: clustering methods combined with graph analysis were shown to predict the "expert" mapping chosen using chemical intuition reliably\cite{li2020}.
+A mapping operator based on the centers of charge was shown to accurately model electrostatic properties\cite{Cao2015a}.
+
 \subsection*{Multi-State Iterative Boltzmann Inversion}
+<how cg potentials have been obtained>
+<IBI>
+<why are IBI potentials not transferrable? the RDF is a property of the ensemble average at a given statepoint so the potential derived from this property is also limited.>
+separate potentials are required to capture solid and fluid structures of a pure simple lipid <Moore2014 ref 46>
+<IBI potentials are sometimes transferrable and it is not clear why sometimes they are and sometimes they aren't.> \cite{Moore2014}
+
+Multistate iterative Boltzmann inversion (MS IBI) includes data from multiple targets to yield a less state dependent potential.
+\cite{Moore2014}
+The MS IBI potential is an average of the single state potentials with a weighting function to prioritize a state of interest.
+This method has been shown to accurately reproduce the true potential in monoatomic LJ fluid.
+
+When using the MS IBI method, it is important to choose dissimilar states to minimize the potential overlap region.
+If this overlap region is large, there are many potentials which will provide matching RDFs.
+For some systems there may not be a potential that represents all states-- this is not unique to coarse potentials, atomistic potentials also have this limitation.
+
+TraPPE fits CG potentials using vapor-liquid equilibria to improve transferrability across thermodynamic states\cite{Maerzke2011}
 
@@
 \section*{Preliminary Work}
+<Talk about what exists and why it is not enough>
+<votca, Peng2019a> 
+Versatile Object-oriented Toolkit for Coarse-graining Applications (VOTCA) \cite{Ruhle2011b}
+includes a coarse-graining, forcefield creation with reverse MC or IBI, and back-mapping modules.
+It also allows for charge transport calculations using KMC similar to MorphCT <cite>
+
+reproducibility crisis.\cite{Cummings2019} \cite{Thompson2020} (TRUE paper) poorly documented code and raw data doesn't help.
+
+instead example workflows with docker containers to build software stack.
+help make science more accessible and reprodicible.
+
+<compare VOTCA's backmapping to my proposed scheme>
+VOTCA makes some progress towards a TRUE simulation pipeline: they include a docker container with their pre-built software stack and example input files <see https://github.com/votca/votca -- using this code via docker> (but some of these input files don't work and the codecoverage on their repo as of time of writing is 0\%), and while including example inputs is a good first step, very little walkthrough (aside from code comments buried in the xml) is given.
+A manual is provided but there is some disconnect between the example files and those given in the manual <https://github.com/votca/csg-manual/releases>.
+the code is a mix of C++, shell commands, python, and interacts with compiled programs through the command-line and mpi.
+which makes their working a little tenuous.
+And judging by the amount of confusion in their mailing list <https://groups.google.com/forum/#!forum/votca> there is room for improvement in the API.
+Overall though this is program has many features, interfaces with many popular MD engines (lammps, gromacs, hoomd), and is under active, collaborative development.
+A good question might be if I'm so into OSS and collaboration--why don't I just contribute an MSIBI package to VOTCA.
+This is a reasonable question.
+The answer is because I find VOTCA to be near-overwhelming in it's scope and the cognitive load of trying to fit this whole project into my brain is not ideal.
+I also don't like their API.
+by choosing a pure python API I will be able to make use of jupyter notebooks which can be run on cloud servers using tools like mybinder <link mybinder, link to tutorials I;ve made> which can combine executable code with markdown text and images.
+In this way a tutorial can provide exact commands needed to reproduce the example intimately connected with the rationale and justification of that example.
+I would like to think that my code speaks for itself, but after reading other people's code, I have a renewed appreciation for explanations in paragraph form, diagrams, and figures.
+
+For an example of what I mean by cognitive load, let's compare an example of my proposed coarse-graining scheme to VOTCAs.
+In the following example we will take a hexane molecule and map it to three coarse grain sites (two carbon atoms per site).
+VOTCA uses an xml file to do this:
+<insert hexane.xml>
+It may be easy to think that because what we are doing--mapping two carbons and their attached hydrogens to a single bead so that six alkyl carbons becomes A-B-A--that the process will also be simple.
+In order to specify a bead-mapping, we need to know the residue number, the residue name, and the atom name.
+For a six atom system this is not too bad, but this could get tedious and error-prone for larger systems.
+And keep in mind that these xml files need to be created manually for each compound which is backmapped.
+VOTCA's scheme also requires that you specify the bonding and the angles resulting from those bonds, another process which is tedious, error-prone, and probably unecessary--I will discuss this more after discussing my scheme below:
+\begin{lstlisting}
+hexane_sites = [("_A", "CC[H3]"), ("_B", "CC")]
+\end{lstlisting}
+The result of using this code in the `coarse` function <link to grits> is a three-site hexane model A-B-A.
+The mapping here is specified as a list of bead name / smarts string pairs.
+Although they do add some element of cognitive load, SMARTS strings are designed to be human and machine readable and can match atoms based on their chemical environment.
+With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (CC) requiring that one be a termial carbon by including that it has three attached hydrogens (C[H3]).
+The bonding and angles of the resulting coarse grain beads is then inferred based on the bonding of the mapped atoms.
+There are even benefits to the mapping being inline with the code:
+This allows the user to see the mapping as they progress through the workflow without having to search for multiple files and it may prevent common errors caused by manual file IO such as operating system specific line endings or whitespace characters like tab or space being treated differently.
+Having the mapping in-line with the workflow also allows for the user to check that the mapping is correct with built in interactive visualizations, which can display the mapping as an overlay.
+
+We do not propose a new automated mapping, but instead a way to make the mapping and backmapping process easier for the user.
+Simplified Molecular Input Line Entry System or SMILES \cite{Weininger} was designed to represent organic molecules in an unambiguous way (similar to IUPAC) but in a line-entry system which is also readable by a computer.
+This makes it a good candidate for specifying a coarse-grain mapping scheme.The open-source package, Openbabel, allows for a SMILES string to be converted to a chemical structure and vice versa.
+<cite openbabel,SMILES, SMARTS> SMARTS is similar to SMILES but instead of representing a single molecule unambiguously, it has multiple wildcards which can be used for pattern matching.
+This pattern matching is also implemented in the Openbabel package.
+If we know the SMARTS string for any given CG mapping we can map the CG site to it's center of mass or geometric center.
+I have developed a minimum working example of how this can be done <cite grits> and then how the atomistic structure can be recovered.
+It could be fairly straightforward to implement a lookup to check if bead parameters already exist--say for the MARTINI model-- by going through and writing out the SMARTS pattern for each existing bead type.
+An initial headache that could make parameterizing new compounds for the MARTINI method more foolproof.
+
+- contributed to development of open-source packages: mbuild, foyer, signac, fresnel
+ this has helped me learn best software development practices like writing documentation, using version control, writing unit tests, employing CI, fork/pull model, etc.
+using these tools will help me to me a more efficient developer.
+It's also helped me to learn how to work as part of a team.
+ - created MWE of coarse-graining and backmapping with smiles-- these will need furthertesting as we try them on different compounds but the proof of concept is there.
+ - created tutorial examples to help current and future students understand scientific concepts and how to use computational tools
+ - created GIXStapose (presented at SciPy2020) an interactive diffraction/structure viewer.
+This may seem unrelated but we can use diffraction to verify our opv morphologies and compare them to experiment.
+GIXStapose helps to beeter connect the physical structure with the diffraction pattern.
+- started development on UFF repo for foyer.
+This is an example of how to create a version controlled forcefield which can be automatically applied to a compound.
+(atom typing is a pain)
 
 \section*{Research Plan}
+- I will build on existing tools (signac,freud,mbuild,foyer,tim moore's msibi)
+- create signac workflow which takes equilibrated atomistic trajectory (maybe checks if it's equilibrated?) maps the CG beads to it, runs IBI, gets tabulated FF, creates larger CG sim, runs it, does backmapping, then could do: RDF, charge transport, diffraction...
+if this workflow is streamlined--it can be applied to many different compounds allowing for us to compare the analyses between our zoo of compounds.
+- maybe the workflow could even involve getting the equilibrated trajectory (atomtyping/fill box/run) with the new hoomd 3 api we could even set decorrelation time as a stop trigger...
 \subsection*{Objective 1}

### 2020-07-29 2pd.tex
shitty first draft plan

@@
 - maybe the workflow could even involve getting the equilibrated trajectory (atomtyping/fill box/run) with the new hoomd 3 api we could even set decorrelation time as a stop trigger...
-\subsection*{Objective 1}
+\subsection*{Objective 1: Develop a coarse graining workflow}
+build on existing tools (mbuild, openbabel)
+use SMARTS matching to specify mapping operators with relative ease
+use MSIBI to parameterize forcefield parameters
+
+\subsection*{Objective 2: Develop a backmapping workflow}
+Given an equilibrated CG morphology, retrieve the atomistic one by mapping the SMARTS structures onto the position of the CG beads and then relaxing them with some position restraint.
+
+\subsection*{Objective 3: Run CG simulation sweep of non-fullerene acceptor blends}
+use signac to organize data
+I think there are not great CG models for these compounds (ITIC PTB7) I found this paper \cite{Meng2019} that claims to do CGMD with PTB7 ITIC but the details are hidden in the SI and seem fishy.
+seems like they use IBI but they dont say how they got their target distributions.
+can easily test out different mappings and other "processing" conditions
+
+\subsection*{Objective 4: Analysis}
+Use charge transfer, diffraction to tell which models are the best
 
 \section*{Predicted Outcomes}
+-understanding coarse graining (i'm stealing this from mike because I like it) how coarse is too coarse? for these new systems what is the minimal model which can reproduce the structural features
+-understanding the interactions which guide BHJ self assembly. understanding which functionalizations/processing conditions make best morphology
 
 \section*{Contingency Analysis}
+what's going to be hard?
 

### 2020-07-29 2pd.tex
add todo notes

@@
 Use charge transfer, diffraction to tell which models are the best
+<cite a bunch of experimental papers we can compare to>
+<cite our papers that show we can do this comparison already>
 

### 2020-07-30 2pd.tex
added <> for ideas to get going in each section

@@
 \section*{Research Objectives}
+<gain insight into the limits of coarse graining>
+<create models for new opv compounds>
+<create a workflow that will make creating new models more accessible>
+<develop new tools that help humans do science>
+<I don't know where to put this but I want a section on best practices>
+By making our code open source and freely availiable, we contribute to the knowledge of a global community. But just because something is availiable doesn't mean it is accessible. 
+lazy refactoring--get something working first then update it when needed, keep code small and modular to make this easier and more understandable\cite{Adorf2018a} 
+Best practices for jupyter notebooks -- like a lab notebook-- can show the process and the story of each assignment and the exact steps and results to get there\cite{Rule2019a}
+Using software carpentry principles to keep in mind how people learn when introducing a new concept\cite{https://v4.software-carpentry.org/softeng/principles.html}
+reducing cognitive load \cite{Jankowski2019}
+using the tools, not fighting them--version control, automation \cite{Wilson2014}
+TRUE\cite{Thompson2020}
 
@@
 \subsection*{Organic Photovoltaics}
+<history>
+<how opvs work>
+<why morphology matters>
+<segue into simulation>
 
 \subsection*{Molecular Dynamics}
+
+<md in general>
+<what assumptions does md make?>
+<what are the limits of atomistic md?>
 
@@
 
+<how cg potentials have been attained>
 \subsection*{Multi-State Iterative Boltzmann Inversion}
-<how cg potentials have been obtained>
 <IBI>
@@
 \subsection*{Mesoscale Device Simulation}
+<how morphct pipeline would work: cg-backmap-ct>
+<how kmc works>
+<cite morphct papers>
 
 \section*{Preliminary Work}
+- contributed to development of open-source packages: mbuild, foyer, signac, fresnel
+ this has helped me learn best software development practices like writing documentation, using version control, writing unit tests, employing CI, fork/pull model, etc.
+using these tools will help me to me a more efficient developer.
+It's also helped me to learn how to work as part of a team.
+ - created MWE of coarse-graining and backmapping with smiles-- these will need furthertesting as we try them on different compounds but the proof of concept is there.
+ - created tutorial examples to help current and future students understand scientific concepts and how to use computational tools
+ - created GIXStapose (presented at SciPy2020) an interactive diffraction/structure viewer.
+This may seem unrelated but we can use diffraction to verify our opv morphologies and compare them to experiment.
+GIXStapose helps to beeter connect the physical structure with the diffraction pattern.
+- started development on UFF repo for foyer.
+This is an example of how to create a version controlled forcefield which can be automatically applied to a compound.
+<atom typing is a pain and doing it manually is bad cite foyer paper>
+
 <Talk about what exists and why it is not enough>
@@
 
-- contributed to development of open-source packages: mbuild, foyer, signac, fresnel
- this has helped me learn best software development practices like writing documentation, using version control, writing unit tests, employing CI, fork/pull model, etc.
-using these tools will help me to me a more efficient developer.
-It's also helped me to learn how to work as part of a team.
- - created MWE of coarse-graining and backmapping with smiles-- these will need furthertesting as we try them on different compounds but the proof of concept is there.
- - created tutorial examples to help current and future students understand scientific concepts and how to use computational tools
- - created GIXStapose (presented at SciPy2020) an interactive diffraction/structure viewer.
-This may seem unrelated but we can use diffraction to verify our opv morphologies and compare them to experiment.
-GIXStapose helps to beeter connect the physical structure with the diffraction pattern.
-- started development on UFF repo for foyer.
-This is an example of how to create a version controlled forcefield which can be automatically applied to a compound.
-(atom typing is a pain)
-
 \section*{Research Plan}
@@
 \section*{Contingency Analysis}
-what's going to be hard?
+<what's going to be hard?>
 

### 2020-07-30 2pd.tex
added notes from swc papers

@@
 <develop new tools that help humans do science>
+<use that science to help solve energy crisis???????>
 <I don't know where to put this but I want a section on best practices>
@@
 Using software carpentry principles to keep in mind how people learn when introducing a new concept\cite{https://v4.software-carpentry.org/softeng/principles.html}
+Software carpentry using version control, building, scripting, testing, debugging,\cite{Wilson2006}
+live coding, interactive \cite{Wilson2016}
 reducing cognitive load \cite{Jankowski2019}

### 2020-07-31 2pd.tex
bit by bit

@@
 <why do opvs matter>
+<energy demand is increasing and we need a nonpolluting cost-efficient way to provide electricity>
+Global energy consumption 17 TW in 2010 to 27 TW in 2040 \cite{Maziio2015}
+Renewable energy is necessary.
+Organic photovoltaics (OPVs) are a potential solution.
+<image from nrel about solar cells efficiency>\cite{https://www.nrel.gov/pv/cell-efficiency.html}
+OPVs are lightweight, low-cost, and flexible--in order to become the best solution they need better efficiency \cite{Mazzioi2015}.
+Currently OPV devices are not efficient enough to solve this problem.
 In order to make the most efficient opvs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
 <opv performance is intimately linked with structure>
+the interfacial area of the acceptor/donor regions \cite{mazzio} the regioregularity of the polymer \cite{Kim2006} and electronic properties (HOMO level) of the compounds \cite{Scharber2006a}
 With minor modifcations the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
+Functionalizing a molecule like ITIC can change how it packs in a crystal \cite{Swick2019a}.
 By using a simulation pipeline, we can help to streamline the process of determining which opv materials will help to solve the energy crisis
@@
 A complication of this simulation is that the features which are important to the performance of an opv span multiple length scales.
-The electronic properties are important for light absorption, charge transfer <morehere>
+The electronic properties are important for light absorption, charge transfer \cite{Scharber2006,Hoppe2004,Mazzio2015}
 while the bulk morphological properties are important: an exciton needs to be able to find an interface at which to dissociate before it decays through one of its non-radiative processes and one the charges are separated they need to reach an electrode in order to generate current and produce electricity.
+<how do we model this system?>
 
@@
 <how opvs work>
+The compounds which compose an OPV are synthesizable molecules (often polymers) composed of abundant elements (carbon, hydrogen, nitrogen, sulfur, oxygen).
+Due to the conjugated pi-orbitals in these molecules the absorption of sunlight can be used to generate excitons.
+OPVs are made as a mixture of electron-donor and electron-acceptor compounds in a structure called a bulk-heterojunction.
+Depending on the bulk morphology of these compounds, the exciton can travel to an accepto-donor interface and dissociate into free electron and hole then these free charges generate current if they can subsequently make their way to an electrode.
 <why morphology matters>

### 2020-08-04 1summ.tex
writing for today. good progress on summary c:

--- 2020-07-28 1summ.tex
@@
 
+Already the effects of human-influenced climate change are <hurtng everyone in particular poor and disadvantaged groups>.
+Burning fossil fuels for energy contributes to rising $CO_{2}$ levels.
+And the energy demand is only increasing.
+This makes finding efficient, renewable energy technologies of the utmost importance.
+Harvesting solar energy is one way to help this problem.
+Organic photovoltaic (OPV) devices have recieved attention for their simple, inexpensive manufacture.
+Generally OPV devices are made of a multicompound mixture: usually an electron donor and acceptor which form a mosaic-like structure called a bulk-heterojunction (BHJ).
+The compounds and polymers used in OPVs are made of common elements and can be synthesized with relative ease.
+<opvs work by... sunlight excites an electron, forms an exciton, exciton travels to an interface, is dissociated, then the free charge travels to an electrode and generates current.>
+And the OPV BHJ can often be assembled using simple techniques like roll-to-roll printing in ambient conditions.
+However, in order for OPV devices to be a viable solution, they need to be more efficient.
+The efficiency of an OPV device can be improved by changing the chemistry of the electron acceptor and donor compounds, the polymer properties, and tuning the processing conditions of the BHJ.
+With so many parameters, quickly this becomes an intractable problem for experiments to solve.
+This is where molecular simulation comes in. 
+Molecular dynamics (MD), a simulation technique where atoms are represented by classical forces and their interactions are specified by attractive/repulsive potentials, can be used to probe the thermodynamic processes which determine how OPV compounds will self-assemble into a BHJ morphology.
+Then we can use kinetic monte carlo (KMC) in concert with quantum chemical calculations (QCCs) to determine the charge mobility through these simulated morphologies.
+By understanding how charge move through these systems, one can predict which OPVs will be most efficient.
+However, this simulation workflow suffers from a problem of length scales:
+Probing charge transport properties with QCCs requires the calculation of electron densities around each atom. 
+But equilibrating this morphology at volumes which exceed the exciton dissociation length (~5-10 nm) is prohibitive if every individual atom is considered.
+Coarse grain (CG) models, which group multiple atoms together into "super atoms" and using an effective potential to specify the forces acting upon the site, can be used to access length and time scales more relevant to the bulk polymer morphology.
+After a bulk morphology is obtained, we can use backmapping, a process in which the atomistic detail can be reintegrated into a coarse grain model, can be used to restore atomistic detail for use in simulations like KMC/QCC.
+This multiscale simulation workflow allows for OPV morphologiesto be equilibrated at length scales relevant to the bulk polymerand to regain the atomistic detail necessary later and from a better starting structure.
+Currently software packages exist that do this but they require tedious manual input and are highly susceptible to user error.
+PI Fothergill will design a simple, chemically sensible coarse-graining and backmapping package based on the SMILES chemical input language with a focus on OPVs.
+This will allow for easier setup and execution of multiscale simulation, which can be part of the process to finding the next great OPV technology.
+
 \begin{center}
@@
 %proposed activity? Is there sufficient access to resources?  \\
+
+A coarse graining pipeline will help make multi-scale simulations more accesible and useable for others. 
+This can be useful for screening of potential OPV compounds.
+<talk about VOTCA?>
+<talk about TRUE simulations and reproducibility in the field>
+<talk about our supercomputer allocations?>
+<talk about what I've done already?>
 
@@
 %Thus, regardless of the current administration's reluctance to accept the reality of climate change, OPV devices will be seen superior to 'dirty' power production methods due to their competitive price.
+
+Helping to make research transferrable, reproducible, useable, and extensible. 
+Wriitng tutorials and documentation while keep in mind principles of oftware carpentry instructor training. 
+Using software dev best practices to be efficient and make sure that I'm not making code for someone else to struggle through later. 
+Training/teaching undergrads.
+Working as part of a team.

### 2020-08-04 2pd.tex
writing for today. good progress on summary c:

@@
 <energy demand is increasing and we need a nonpolluting cost-efficient way to provide electricity>
-Global energy consumption 17 TW in 2010 to 27 TW in 2040 \cite{Maziio2015}
+Global energy consumption 17 TW in 2010 to 27 TW in 2040 \cite{Mazzio2015}
 Renewable energy is necessary.
@@
 <how do we model this system?>
+
+<justification for what I'm doing>
+the number of opv compounds to test quickly becomes intractable when we consider that the power conversion efficiency is strongly linked to minor chemical modifications or functionalization, device processing, and the interplay between donor and acceptor\cite{Mazzio2015,Swick2019a}.
+There are countless variations of electron donor polymers, fullerene acceptors, and more recently small molecule, non-fullerene acceptors (NFAs) have been recieving attention for their potential to achieve higher efficiencies\cite{dou2013}.
+A P3HT:NFA blend was shown to have 11\% PCE, compared to the state-of-the-art 6.4\% in P3HT:PCBM. \cite{Baran2017}
+Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70-80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h) \cite{Baran2017}.
+It is necessary to develop a simple easy to use pipeline to adapt to the constant changing chemistries of current OPV technologies. 
+we need a flexible pipeline for coarse grain model generation for these new chemistries
 
@@
 <history>
+inorganic PV devices came first and are still most efficient, but they are more costly to produce, use rare elements, other environmental issue--they aren't the best solution for solar energy harvesting.
+first opv was tang1986<cite> used a bilyaer structure
+Saricifti and Heeger 1992 <cite> discovered BHJ
+BHJ with fullerene acceptor reported by Yu in 1995 -still state of the art morphology. <cite>
+non fullerene acceptors, like ITIC, are helping to increase PCE \cite{S.Gurney2019}
+A-D-A \cite{Yi2018} has some mention of the A-D-A moeity and why it is good <read further>
 <how opvs work>

### 2020-08-04 2pd.tex
quick note about nfas

@@
 non fullerene acceptors, like ITIC, are helping to increase PCE \cite{S.Gurney2019}
-A-D-A \cite{Yi2018} has some mention of the A-D-A moeity and why it is good <read further>
+The planar A-D-A structure may have more efficient exciton splitting, as compared to a fullerene accpetor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer \cite{Yi2018}.
+
 <how opvs work>

### 2020-08-05 1summ.tex
summary draft done

@@
 Already the effects of human-influenced climate change are <hurtng everyone in particular poor and disadvantaged groups>.
-Burning fossil fuels for energy contributes to rising $CO_{2}$ levels.
-And the energy demand is only increasing.
-This makes finding efficient, renewable energy technologies of the utmost importance.
-Harvesting solar energy is one way to help this problem.
-Organic photovoltaic (OPV) devices have recieved attention for their simple, inexpensive manufacture.
+Burning fossil fuels for energy is the main contributor to rising $CO_{2}$ levels, and the energy demand is only increasing.
+This increase in energy demand along with the need to protect our precious climate makes finding efficient, renewable energy technologies of the utmost importance.
+Harvesting the abundant solar energy is a <good solution because it is renewable, non-polluting, sustainable>.
+Devices which convert light to electricity, called photovoltaics, were originally made of silicon and required rare elements and careful, clean-room processing.
+More recently, organic photovoltaic (OPV) devices have recieved attention for their simple, inexpensive manufacture.
 Generally OPV devices are made of a multicompound mixture: usually an electron donor and acceptor which form a mosaic-like structure called a bulk-heterojunction (BHJ).
 The compounds and polymers used in OPVs are made of common elements and can be synthesized with relative ease.
-<opvs work by... sunlight excites an electron, forms an exciton, exciton travels to an interface, is dissociated, then the free charge travels to an electrode and generates current.>
 And the OPV BHJ can often be assembled using simple techniques like roll-to-roll printing in ambient conditions.
+The process for OPV to generate electricity is as follows: 
+Sunlight excites an electron, which forms an exciton.
+This exciton travels to an acceptor/donor interface and is dissociated into free electron and hole
+Then the free charges travel to an electrode which generates current.
 However, in order for OPV devices to be a viable solution, they need to be more efficient.
@@
 However, this simulation workflow suffers from a problem of length scales:
-Probing charge transport properties with QCCs requires the calculation of electron densities around each atom. 
+Probing charge transport properties with QCCs requires the calculation of electron densities around each atom, which requires knowing the positions of each atom.
 But equilibrating this morphology at volumes which exceed the exciton dissociation length (~5-10 nm) is prohibitive if every individual atom is considered.

### 2020-08-05 2pd.tex
replaced all missing citations

@@
 <why do opvs matter>
+<the climate is in crisis, energy consumption of fossil fuels strongly increases CO2 output which affects our climate>\cite{Solomon2009a}
 <energy demand is increasing and we need a nonpolluting cost-efficient way to provide electricity>
@@
 inorganic PV devices came first and are still most efficient, but they are more costly to produce, use rare elements, other environmental issue--they aren't the best solution for solar energy harvesting.
-first opv was tang1986<cite> used a bilyaer structure
-Saricifti and Heeger 1992 <cite> discovered BHJ
-BHJ with fullerene acceptor reported by Yu in 1995 -still state of the art morphology. <cite>
+first opv was \cite{Tang1986b} used a bilyaer structure
+Saricifti and Heeger 1992 \cite{Saricifti1992} used polymer:fullerene mixture.
+BHJ with fullerene acceptor reported by Yu in 1995 -still state of the art morphology. \cite{Yu1995}
 non fullerene acceptors, like ITIC, are helping to increase PCE \cite{S.Gurney2019}
@@
 Coarse-graining refers to grouping atoms in a structure into a "super-atom" and using an effective potential to represent the resulting coarse grain site.
+It is too big and too slow and also just a bad idea to simulate huge boxes of atomistic polymers.
+Even if the simulation was to complete, there would be too much information to process accurately.
+CGing allows scientists to FOCUS their experiments.\cite{Baschnagel2000}
 The resolution of coarse grain systems is broad:
 Simply grouping hydrogens with the heavy atom they are bonded to, called the united-atom model, has been shown to speed up dynamics and make polymer length scales more easily accesible \cite{Paul1995a, Yang2006a,}.
-Other goarse-graining schemes may group functional groups together <cite> or even represent an entire amino acid with a single site <cite>.
+Other coarse-graining schemes may group functional groups together \cite{Berendsen2010, Jankowski2013, Marsh2014}, one bead per repeat unit in a polymer\cite{Lee2011}, or even represent an entire amino acid with a single site\cite{Peng2019a}.
+
 General coarse grain models of opv thiophene polymers where only the spacing, regioregularity of the side chains were varied were able to predict different order disorder transitions and calculated scattering patterns of these simple systems were comparable to those obtained from experiment \cite{Jankowski2013, Marsh2014}
@@
 For many systems, however, we are interested in properties which span length scales.
-For instance, in a system like a opv polymer melt, it is not only computationally intractable to try and simulate the electron density on length scales proportional to the exciton dissociation length (~5-10 nm)<cite> -- it is the wrong tool for the job.
+For instance, in a system like a opv polymer melt, it is not only computationally intractable to try and simulate the electron density on length scales proportional to the exciton dissociation length (~5-10 nm)\cite{Huang2010} -- it is the wrong tool for the job.
 If what we are interested in is the properties of the polymer in the bulk heterojunction, then it is wise to abstract away any degrees of freedom which do not directly contribute to the self-assembly of the structure.
@@
 includes a coarse-graining, forcefield creation with reverse MC or IBI, and back-mapping modules.
-It also allows for charge transport calculations using KMC similar to MorphCT <cite>
+It also allows for charge transport calculations using KMC similar to MorphCT \cite{Lukyanov2010}
 

### 2020-08-06 2pd.tex
dded some notes and commands for ej and cj to comment

@@
+\newcommand{\ej}[1]{\textcolor{red}{\textit{#1} -- EJ.}}
+\newcommand{\cj}[1]{\textcolor{orange}{\textit{#1} -- CJ.}}
 \section*{Motivation}
@@
 <opv performance is intimately linked with structure>
-the interfacial area of the acceptor/donor regions \cite{mazzio} the regioregularity of the polymer \cite{Kim2006} and electronic properties (HOMO level) of the compounds \cite{Scharber2006a}
+the interfacial area of the acceptor/donor regions \cite{Mazzio2015} the regioregularity of the polymer \cite{Kim2006} and electronic properties (HOMO level) of the compounds \cite{Scharber2006a}
 With minor modifcations the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
@@
 the number of opv compounds to test quickly becomes intractable when we consider that the power conversion efficiency is strongly linked to minor chemical modifications or functionalization, device processing, and the interplay between donor and acceptor\cite{Mazzio2015,Swick2019a}.
-There are countless variations of electron donor polymers, fullerene acceptors, and more recently small molecule, non-fullerene acceptors (NFAs) have been recieving attention for their potential to achieve higher efficiencies\cite{dou2013}.
+There are countless variations of electron donor polymers, fullerene acceptors, and more recently small molecule, non-fullerene acceptors (NFAs) have been recieving attention for their potential to achieve higher efficiencies\cite{Dou2013}.
 A P3HT:NFA blend was shown to have 11\% PCE, compared to the state-of-the-art 6.4\% in P3HT:PCBM. \cite{Baran2017}
@@
 <history>
+<what is PCE>
 inorganic PV devices came first and are still most efficient, but they are more costly to produce, use rare elements, other environmental issue--they aren't the best solution for solar energy harvesting.
-first opv was \cite{Tang1986b} used a bilyaer structure
-Saricifti and Heeger 1992 \cite{Saricifti1992} used polymer:fullerene mixture.
-BHJ with fullerene acceptor reported by Yu in 1995 -still state of the art morphology. \cite{Yu1995}
-non fullerene acceptors, like ITIC, are helping to increase PCE \cite{S.Gurney2019}
+first opv was \cite{Tang1986b} used a bilyaer structure copper phthalocyanine and a perylene derivitive (PCE 0.95\%)
+Saricifti and Heeger 1992 \cite{Saricifti1992} were the first to report using fullerene as an electron acceptor in a fullerene:polymer mixture.
+Yu in 1995 described the first BHJ, an interpenetrating network of donor and acceptor that maximizes the interfacial area, which is still the state of the art morphology. \cite{Yu1995}
+Non-fullerene acceptors, like ITIC, are helping to increase PCE \cite{S.Gurney2019}
 The planar A-D-A structure may have more efficient exciton splitting, as compared to a fullerene accpetor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer \cite{Yi2018}.
@@
 Another mapping scheme uses principle component analysis to choose a mapping scheme for biomolecules that best represents th essential dynamics\cite{Zhang2008}.
-Mapping operators can be automated using machine learning: clustering methods combined with graph analysis were shown to predict the "expert" mapping chosen using chemical intuition reliably\cite{li2020}.
+Mapping operators can be automated using machine learning: clustering methods combined with graph analysis were shown to predict the "expert" mapping chosen using chemical intuition reliably\cite{Li2020}.
 A mapping operator based on the centers of charge was shown to accurately model electrostatic properties\cite{Cao2015a}.

### 2020-08-06 2pd.tex
writing. filling in gaps

@@
 \subsection*{Organic Photovoltaics}
+<what is PCE>
+The power conversion efficiency (PCE or sometimes $\eta_{e}$) is the ratio of electrical power produced by the device over the power of incedent photons.
+Higher PCE means the device is more effecient.
+The PCE depends on the number of photons absorbed, excitons dissociated, and free charges that reach the electrode.
+The absorption efficiency depends on the absorption spectrum, absorption coefficient, and layer thickness.
+The fraction of excitons which dissociate depends on the exciton dissociation length and the charge separation probability at the interface.
+Finally, the the number of charges which reach the electrode depends on the driving force or gradient resulting from the potentials of the electrons and holes.\cite{Hoppe2004}
 <history>
-<what is PCE>
-inorganic PV devices came first and are still most efficient, but they are more costly to produce, use rare elements, other environmental issue--they aren't the best solution for solar energy harvesting.
-first opv was \cite{Tang1986b} used a bilyaer structure copper phthalocyanine and a perylene derivitive (PCE 0.95\%)
+Inorganic PV devices came first and are still most efficient, but they are more costly to produce, use rare elements, other environmental issue--they aren't the best solution for solar energy harvesting.
+First opv was \cite{Tang1986b} used a bilyaer structure copper phthalocyanine and a perylene derivitive (PCE 0.95\%)
 Saricifti and Heeger 1992 \cite{Saricifti1992} were the first to report using fullerene as an electron acceptor in a fullerene:polymer mixture.
@@
 The planar A-D-A structure may have more efficient exciton splitting, as compared to a fullerene accpetor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer \cite{Yi2018}.
-
 <how opvs work>
 The compounds which compose an OPV are synthesizable molecules (often polymers) composed of abundant elements (carbon, hydrogen, nitrogen, sulfur, oxygen).
-Due to the conjugated pi-orbitals in these molecules the absorption of sunlight can be used to generate excitons.
+Due to the conjugated pi-orbitals in these molecules the absorption of sunlight can excite an electron into a frontier orbital and generate an exciton.
 OPVs are made as a mixture of electron-donor and electron-acceptor compounds in a structure called a bulk-heterojunction.
-Depending on the bulk morphology of these compounds, the exciton can travel to an accepto-donor interface and dissociate into free electron and hole then these free charges generate current if they can subsequently make their way to an electrode.
+Depending on the bulk morphology of these compounds, the exciton can travel to an acceptor-donor interface and dissociate into free electron and hole then these free charges generate current if they can subsequently make their way to an electrode.
 <why morphology matters>
@@
 
+Coarse-graining refers to grouping atoms in a structure into a "super-atom" and using an effective potential to represent the resulting coarse grain site.
 Coarse-grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models.
-Coarse-graining refers to grouping atoms in a structure into a "super-atom" and using an effective potential to represent the resulting coarse grain site.
+<how do cg models let us access long length/time??>
+Similarly to how we don't need to look at the working of a plant cell to understand the growth of a forest \cite{Muller-Plathe2002}, we don't need to consider atomic level properties when we are interested in the bulk morphology.
+The heart of coarse graining is the removal of degrees of freedom.
+This effective potential used to represent the reduced system results in a smoothed free energy landscape.
+Processes which may have taken many time steps in an all atom simulation can take fewer time steps in a coarse simulation.\cite{Berendsen2010}
+Due to their long length and time scales, coarse grain models are ideal for examining polymer properties.\cite{Gartner2019a}
 It is too big and too slow and also just a bad idea to simulate huge boxes of atomistic polymers.
@@
 Other coarse-graining schemes may group functional groups together \cite{Berendsen2010, Jankowski2013, Marsh2014}, one bead per repeat unit in a polymer\cite{Lee2011}, or even represent an entire amino acid with a single site\cite{Peng2019a}.
-
+<examples of cg models and the cool hings they do>
 General coarse grain models of opv thiophene polymers where only the spacing, regioregularity of the side chains were varied were able to predict different order disorder transitions and calculated scattering patterns of these simple systems were comparable to those obtained from experiment \cite{Jankowski2013, Marsh2014}
@@
 Which model is right depends on the length and time scale on which the property of interest can be observed.
-
+<multiscale sims>
 For many systems, however, we are interested in properties which span length scales.
@@
 \subsection*{Multi-State Iterative Boltzmann Inversion}
+
+There are numerous methods for deriving coarse grain potentials from atomistic ones (e.g., force-matching, reverse Monte Carlo), but in this proposal we will focus on Iterative Boltzmann Inversion (IBI).
 <IBI>
-<why are IBI potentials not transferrable? the RDF is a property of the ensemble average at a given statepoint so the potential derived from this property is also limited.>
-separate potentials are required to capture solid and fluid structures of a pure simple lipid <Moore2014 ref 46>
+IBI is where a coarse grain potential is iteratively tuned to fit a target distribution. \cite{Reith2003a}
+Here is the algorithm for determining the non-bonded potentials:
+First the coarse grain system is mapped onto an equilibrated atomistic one.
+Then the radial distribution function (RDF) of the mapped systems is calculated over the equilibrated frames of the trajectory--This is the target distribution.
+Given any particle, the RDF gives the probability of finding a neighboring particle at distance r.
+Taking the Boltzmann Inverse of the RDF results in the potential of mean force (PMF). <add equation>
+Then a CG simulation can be run using the PMF as the non-bonded potential to achieve a new distribution.
+Then the difference between the new and target distribution can be accounted for in the next iteration accoring to equation <add equation>.
+This process is repeated until the difference between the result and the target are sufficiently similar.
+
+The coarse grain potential derived from IBI is not transferrable to different thermodynamic statepoints.
+This is because the RDF is a property of the ensemble average at a given statepoint, so the potential derived from this property is also limited.
+For example, separate potentials are required to capture solid and fluid structures of a pure simple lipid \cite{Hadley2010a}.
+There are many attempts to create transferrable CG potentials, for example:
+The TraPPE force-field fits CG potentials using vapor-liquid equilibria to improve transferrability across thermodynamic states\cite{Maerzke2011}
+But optimization to the liquid-vapor equilibriai, although useful for prediction of thermodynamic properties, may not be ideal for prediction of structure which will strongly influence charge transport.
+<so we probably want to create our own potentials>
 <IBI potentials are sometimes transferrable and it is not clear why sometimes they are and sometimes they aren't.> \cite{Moore2014}
@@
 When using the MS IBI method, it is important to choose dissimilar states to minimize the potential overlap region.
-If this overlap region is large, there are many potentials which will provide matching RDFs.
+If this overlap region is large, there are many potentials which will provide matching RDFs. <show fig from moore>
 For some systems there may not be a potential that represents all states-- this is not unique to coarse potentials, atomistic potentials also have this limitation.
 
-TraPPE fits CG potentials using vapor-liquid equilibria to improve transferrability across thermodynamic states\cite{Maerzke2011}
-
 \subsection*{Mesoscale Device Simulation}
+<I DONT WANT TO FOCUS ON THIS TOO MUCH. It's only here as a rationale for why backmapping>
 <how morphct pipeline would work: cg-backmap-ct>

### 2020-08-07 2pd.tex
more writing

@@
 <why do opvs matter>
-<the climate is in crisis, energy consumption of fossil fuels strongly increases CO2 output which affects our climate>\cite{Solomon2009a}
-<energy demand is increasing and we need a nonpolluting cost-efficient way to provide electricity>
-Global energy consumption 17 TW in 2010 to 27 TW in 2040 \cite{Mazzio2015}
-Renewable energy is necessary.
-Organic photovoltaics (OPVs) are a potential solution.
+The global climate crisis is one of the most pressing issue humanity faces today.
+Consumption of fossil fuels for energy and transportation strongly contributes to atmospheric $CO_2$ the affects of which are global, long-term, and devastating\cite{Solomon2009a}.
+In our technology driven society, it is unrealistic to think that energy demand will lessen, in fact global energy consumption is predicted to increase from 17 TW in 2010 to 27 TW in 2040 \cite{Mazzio2015}.
+In order to protect our precious climate, we need a non-polluting, cost-efficient way to provide electricity.
+Harnessing solar energy is an important part of a green energy solution.
+Traditionally, photovoltaic devices, materials which can convert incedent light into electric current, were made of inorganic materials like silicon.
+But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative.
+The advantage of OPVs over inorganic PV devices is that OPVs are lightweight, low cost, easier to produce, and flexible. 
+However, in order to become a viable, cost-effective option they need better efficiency \cite{Mazzio2015}.
 <image from nrel about solar cells efficiency>\cite{https://www.nrel.gov/pv/cell-efficiency.html}
-OPVs are lightweight, low-cost, and flexible--in order to become the best solution they need better efficiency \cite{Mazzioi2015}.
 Currently OPV devices are not efficient enough to solve this problem.
-In order to make the most efficient opvs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
-<opv performance is intimately linked with structure>
-the interfacial area of the acceptor/donor regions \cite{Mazzio2015} the regioregularity of the polymer \cite{Kim2006} and electronic properties (HOMO level) of the compounds \cite{Scharber2006a}
+In order to make the most efficient OPVs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
+The performance of an OPV device is intimately linked with the structure of the active layer:
+The interfacial area of the acceptor:donor regions \cite{Mazzio2015}, the regioregularity of the polymer \cite{Kim2006}, and electronic properties of the compounds \cite{Scharber2006a} all play an important role in the power conversion efficiency (PCE) of the device.
 With minor modifcations the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
-Functionalizing a molecule like ITIC can change how it packs in a crystal \cite{Swick2019a}.
-By using a simulation pipeline, we can help to streamline the process of determining which opv materials will help to solve the energy crisis
-Simulation also helps to give us insight into the atomic interaction which drive self assembly.
-A complication of this simulation is that the features which are important to the performance of an opv span multiple length scales.
-The electronic properties are important for light absorption, charge transfer \cite{Scharber2006,Hoppe2004,Mazzio2015}
-while the bulk morphological properties are important: an exciton needs to be able to find an interface at which to dissociate before it decays through one of its non-radiative processes and one the charges are separated they need to reach an electrode in order to generate current and produce electricity.
-<how do we model this system?>
+For example, simply changing the functional groups on the conjugated backbone of a molecule like ITIC can change how it packs in a crystal and thus its performance in a device\cite{Swick2019a}.
+By using a simulation pipeline, we can help to streamline the process of determining which OPV materials will help to solve the energy crisis.
+Simulation also helps to give us insight into the atomic interactions which drive self assembly.
+A complication of the simulation of OPV polymers is that the properties which predict a device's efficiency, for example charge transport, span multiple length scales.
+The atomic and electronic properties are important for light absorption, in which an exciton is created, and charge transfer, where the exciton is dissociated into a free electron and hole\cite{Scharber2006,Hoppe2004,Mazzio2015}.
+At the same time, the exciton finding an interface at which to dissociates depends on the bulk morphology, as do the charges, once separated, finding a path to an electrode in order to generate current and produce electricity.
+<So how can we model this system?>
 
 <justification for what I'm doing>
-the number of opv compounds to test quickly becomes intractable when we consider that the power conversion efficiency is strongly linked to minor chemical modifications or functionalization, device processing, and the interplay between donor and acceptor\cite{Mazzio2015,Swick2019a}.
+The number of opv compounds to test quickly becomes intractable when we consider that the power conversion efficiency is strongly linked to minor chemical modifications or functionalization, device processing, and the interplay between donor and acceptor\cite{Mazzio2015,Swick2019a}.
 There are countless variations of electron donor polymers, fullerene acceptors, and more recently small molecule, non-fullerene acceptors (NFAs) have been recieving attention for their potential to achieve higher efficiencies\cite{Dou2013}.
-A P3HT:NFA blend was shown to have 11\% PCE, compared to the state-of-the-art 6.4\% in P3HT:PCBM. \cite{Baran2017}
-Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70-80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h) \cite{Baran2017}.
+A P3HT:NFA blend was shown to have 11\% PCE, compared to the state-of-the-art 6.4\% in P3HT:PCBM\cite{Baran2017}.
+Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70-80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h)\cite{Baran2017}.
 It is necessary to develop a simple easy to use pipeline to adapt to the constant changing chemistries of current OPV technologies.
-we need a flexible pipeline for coarse grain model generation for these new chemistries
+We need a flexible pipeline for coarse grain model generation for these new chemistries.
 
@@
 The power conversion efficiency (PCE or sometimes $\eta_{e}$) is the ratio of electrical power produced by the device over the power of incedent photons.
-Higher PCE means the device is more effecient.
+Higher PCE means the device is more efficient.  
 The PCE depends on the number of photons absorbed, excitons dissociated, and free charges that reach the electrode.
@@
 <history>
-Inorganic PV devices came first and are still most efficient, but they are more costly to produce, use rare elements, other environmental issue--they aren't the best solution for solar energy harvesting.
-First opv was \cite{Tang1986b} used a bilyaer structure copper phthalocyanine and a perylene derivitive (PCE 0.95\%)
-Saricifti and Heeger 1992 \cite{Saricifti1992} were the first to report using fullerene as an electron acceptor in a fullerene:polymer mixture.
-Yu in 1995 described the first BHJ, an interpenetrating network of donor and acceptor that maximizes the interfacial area, which is still the state of the art morphology. \cite{Yu1995}
-Non-fullerene acceptors, like ITIC, are helping to increase PCE \cite{S.Gurney2019}
-The planar A-D-A structure may have more efficient exciton splitting, as compared to a fullerene accpetor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer \cite{Yi2018}.
+Inorganic PV devices came first and are still most efficient, but they are more costly to produce, use rare elements, and their production causes other environmental issues, so they aren't the best solution for solar energy harvesting.
+The first OPV was created by Tang in 1986 and \cite{Tang1986b} used a bilyaer structure containing copper phthalocyanine and a perylene derivitive. 
+This early device had a PCE of 0.95\%.
+In 1992, Saricifti and Heeger\cite{Saricifti1992} were the first to report using fullerene as an electron acceptor in a fullerene:polymer mixture.
+And in 1995, Yu described the first bulk heterojunction (BHJ), as an interpenetrating network of donor and acceptor that maximizes the interfacial area, which is still the state of the art morphology to this day\cite{Yu1995}.
+Most recently, non-fullerene acceptors (NFAs), like ITIC, are contributing to the PCE increase of modern OPVs \cite{S.Gurney2019}.
+The planar acceptor-donor-acceptor moeity seen in many NFA backbones <figure?> may have more efficient exciton splitting, as compared to a fullerene accpetor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer \cite{Yi2018}.
 <how opvs work>

### 2020-08-07 1summ.tex
add commenter commands
learning how to use latex

@@
 Sunlight excites an electron, which forms an exciton.
-This exciton travels to an acceptor/donor interface and is dissociated into free electron and hole
+This exciton travels to an acceptor/donor interface and is dissociated into free electron and hole.
 Then the free charges travel to an electrode which generates current.
@@
 This is where molecular simulation comes in.
+
 Molecular dynamics (MD), a simulation technique where atoms are represented by classical forces and their interactions are specified by attractive/repulsive potentials, can be used to probe the thermodynamic processes which determine how OPV compounds will self-assemble into a BHJ morphology.
@@
 But equilibrating this morphology at volumes which exceed the exciton dissociation length (~5-10 nm) is prohibitive if every individual atom is considered.
+
 Coarse grain (CG) models, which group multiple atoms together into "super atoms" and using an effective potential to specify the forces acting upon the site, can be used to access length and time scales more relevant to the bulk polymer morphology.
 After a bulk morphology is obtained, we can use backmapping, a process in which the atomistic detail can be reintegrated into a coarse grain model, can be used to restore atomistic detail for use in simulations like KMC/QCC.
-This multiscale simulation workflow allows for OPV morphologiesto be equilibrated at length scales relevant to the bulk polymerand to regain the atomistic detail necessary later and from a better starting structure.
+This multiscale simulation workflow allows for OPV morphologies to be equilibrated at length scales relevant to the bulk polymer and to regain the atomistic detail necessary later and from a better starting structure.
 Currently software packages exist that do this but they require tedious manual input and are highly susceptible to user error.
-PI Fothergill will design a simple, chemically sensible coarse-graining and backmapping package based on the SMILES chemical input language with a focus on OPVs.
+PI Fothergill will design a simple, chemically sensible coarse graining and backmapping package based on the SMILES chemical input language with a focus on OPVs.
 This will allow for easier setup and execution of multiscale simulation, which can be part of the process to finding the next great OPV technology.

### 2020-08-07 2pd.tex
learning how to use latex

@@
-\newcommand{\ej}[1]{\textcolor{red}{\textit{#1} -- EJ.}}
-\newcommand{\cj}[1]{\textcolor{orange}{\textit{#1} -- CJ.}}
 \section*{Motivation}
@@
 But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative.
+
 The advantage of OPVs over inorganic PV devices is that OPVs are lightweight, low cost, easier to produce, and flexible. 
@@
 Simulation also helps to give us insight into the atomic interactions which drive self assembly.
+
 A complication of the simulation of OPV polymers is that the properties which predict a device's efficiency, for example charge transport, span multiple length scales.
@@
 Finally, the the number of charges which reach the electrode depends on the driving force or gradient resulting from the potentials of the electrons and holes.\cite{Hoppe2004}
+
 <history>
@@
 The planar acceptor-donor-acceptor moeity seen in many NFA backbones <figure?> may have more efficient exciton splitting, as compared to a fullerene accpetor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer \cite{Yi2018}.
+
 <how opvs work>
@@
 VOTCA uses an xml file to do this:
-<insert hexane.xml>
+\lstinputlisting[breaklines]{hexane.xml}
 It may be easy to think that because what we are doing--mapping two carbons and their attached hydrogens to a single bead so that six alkyl carbons becomes A-B-A--that the process will also be simple.
@@
 \end{lstlisting}
-The result of using this code in the `coarse` function <link to grits> is a three-site hexane model A-B-A.
+The result of using this code in the `coarse` function <link to grits> is a three-site hexane model A-B-A, same as VOTCA.
 The mapping here is specified as a list of bead name / smarts string pairs.
 Although they do add some element of cognitive load, SMARTS strings are designed to be human and machine readable and can match atoms based on their chemical environment.
-With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (CC) requiring that one be a termial carbon by including that it has three attached hydrogens (C[H3]).
+With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (CC) requiring that one be a terminal carbon by including that it has three attached hydrogens (C[H3]).
 The bonding and angles of the resulting coarse grain beads is then inferred based on the bonding of the mapped atoms.
+Basically what VOTCA's xml file does in 51 lines, I can do in 1 which is easier to read and makes chemical sense. 
 There are even benefits to the mapping being inline with the code:
@@
 Having the mapping in-line with the workflow also allows for the user to check that the mapping is correct with built in interactive visualizations, which can display the mapping as an overlay.
+<show overlay>
 

### 2020-08-10 2pd.tex
i think this might be the first full draft--still garbage, but lots of it

@@
 Consumption of fossil fuels for energy and transportation strongly contributes to atmospheric $CO_2$ the affects of which are global, long-term, and devastating\cite{Solomon2009a}.
-In our technology driven society, it is unrealistic to think that energy demand will lessen, in fact global energy consumption is predicted to increase from 17 TW in 2010 to 27 TW in 2040 \cite{Mazzio2015}.
+In our technology-driven society, it is unrealistic to think that energy demand will lessen, in fact global energy consumption is predicted to increase from 17 TW in 2010 to 27 TW in 2040 \cite{Mazzio2015}.
 In order to protect our precious climate, we need a non-polluting, cost-efficient way to provide electricity.
@@
 But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative.
-
 The advantage of OPVs over inorganic PV devices is that OPVs are lightweight, low cost, easier to produce, and flexible. 
@@
 <image from nrel about solar cells efficiency>\cite{https://www.nrel.gov/pv/cell-efficiency.html}
-Currently OPV devices are not efficient enough to solve this problem.
 In order to make the most efficient OPVs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
+The active layer of an OPV is mixture of electron-donor and acceptor compounds: the ideal morphology is a micro phase-separated interpenetrating network called a bulk heterojunction (BHJ).
 The performance of an OPV device is intimately linked with the structure of the active layer:
 The interfacial area of the acceptor:donor regions \cite{Mazzio2015}, the regioregularity of the polymer \cite{Kim2006}, and electronic properties of the compounds \cite{Scharber2006a} all play an important role in the power conversion efficiency (PCE) of the device.
-With minor modifcations the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
-For example, simply changing the functional groups on the conjugated backbone of a molecule like ITIC can change how it packs in a crystal and thus its performance in a device\cite{Swick2019a}.
-By using a simulation pipeline, we can help to streamline the process of determining which OPV materials will help to solve the energy crisis.
-Simulation also helps to give us insight into the atomic interactions which drive self assembly.
-
+With minor modifcations, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
+For example, simply changing the functional groups on the conjugated backbone of a molecule like ITIC can change how it packs in a crystal, its electron affinity, and thus its performance in a device\cite{Swick2019a}.
+By using a simulation pipeline, we can help to streamline the process of determining which OPV materials will form the best morphology with the best charge transport, and in turn, help to solve the energy crisis.
+Molecular simulation also gives us insight into the atomic interactions which drive the self assembly of an OPV morphology.
 A complication of the simulation of OPV polymers is that the properties which predict a device's efficiency, for example charge transport, span multiple length scales.
@@
 At the same time, the exciton finding an interface at which to dissociates depends on the bulk morphology, as do the charges, once separated, finding a path to an electrode in order to generate current and produce electricity.
-<So how can we model this system?>
-
+So, in order to model this system, a multiscale approach is necessary.
+By breaking our simulation apart into separate steps and equilibrating different lengths scales individually, we can <get equilibrated morphologies on multiple length scales more efficiently>.
+<so what's the gist of what we're going to do?>
+<cg - get some polymer morphologies equilibrated on relevant length scales>
+<backmapping - get back the atomic positions in preparation for techniques which require atomic level resolutiuon e.g., charge transport>
+<kmc calc>
+<if we we're just to start with the atomistic sim, it wouldn't be as efficient and might even be less accurate because polymers are tough to equilibrate> <probably cite arthi's paper here Gartner2019?>
+<This efficiency is important because we got a lot of testing to do!>
 <justification for what I'm doing>
@@
 Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70-80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h)\cite{Baran2017}.
-It is necessary to develop a simple easy to use pipeline to adapt to the constant changing chemistries of current OPV technologies.
-We need a flexible pipeline for coarse grain model generation for these new chemistries.
+<there aren't a lot of cg models that already exist for these new compounds>
+It is necessary to develop a simple, useable, and flexible pipeline to adapt to the constantly changing chemistries of current OPV technologies.
 
@@
 Higher PCE means the device is more efficient.  
-The PCE depends on the number of photons absorbed, excitons dissociated, and free charges that reach the electrode.
+The material properties which determine the PCE of a device are those which affect the number of photons absorbed, excitons dissociated, and free charges that reach the electrode.
 The absorption efficiency depends on the absorption spectrum, absorption coefficient, and layer thickness.
@@
 Finally, the the number of charges which reach the electrode depends on the driving force or gradient resulting from the potentials of the electrons and holes.\cite{Hoppe2004}
+<is there a citation for why charge transport is a good proxy for PCE?>
 
@@
 Depending on the bulk morphology of these compounds, the exciton can travel to an acceptor-donor interface and dissociate into free electron and hole then these free charges generate current if they can subsequently make their way to an electrode.
+
 <why morphology matters>
+The morphology of the device can be affected by the processing conditions: temperature, solvents, and concentrations/ratios of the active compounds. <cite>
+These changes in structure can strongly affect the device performance <cite>.
+Molecular simulation allows us to "see" these atomic interaction and gain a deeper view into the driving forces behind the self assembly of these OPV morphologies and to understand what conditions create the best devices.
 <segue into simulation>
@@
 
+<I am borrowing heavily from Mike's MD section, so I need to come back through and rewrite this>
 <md in general>
+classical physics
+interactions between particles
+non bonded/bonded/angles/dihedrals
+integrates Newton's equations of motion to update the particle positions.
+iterated until thermodynamic equilibrium
+sample a thermodynamic ensemble
+First MD simulation \cite{Alder1957} system of 108 particles, 200 collisions in one hour on an IBM-704.
+Now GPUs 100 millions times faster
+<what is MD used for? why is MD the best technique for gettign these OPV morphologies?>
+protein folding \cite{levitt75}, other biological processes, polymers \cite{Gartner2019a}
+
 <what assumptions does md make?>
+bonds aren't formed or broken, electrons don't exist
+hydrogen bonding
+dispersion is tricky--electrons don't slosh around unless you use some fancy many-body potential
 <what are the limits of atomistic md?>
+<segue to why we need CG models>
 
@@
 Other coarse-graining schemes may group functional groups together \cite{Berendsen2010, Jankowski2013, Marsh2014}, one bead per repeat unit in a polymer\cite{Lee2011}, or even represent an entire amino acid with a single site\cite{Peng2019a}.
-<examples of cg models and the cool hings they do>
+<examples of cg models and the cool things they do>
 General coarse grain models of opv thiophene polymers where only the spacing, regioregularity of the side chains were varied were able to predict different order disorder transitions and calculated scattering patterns of these simple systems were comparable to those obtained from experiment \cite{Jankowski2013, Marsh2014}
@@
 <how cg potentials have been attained>
+
 \subsection*{Multi-State Iterative Boltzmann Inversion}
@@
 
-Multistate iterative Boltzmann inversion (MS IBI) includes data from multiple targets to yield a less state dependent potential.
-\cite{Moore2014}
+Multistate iterative Boltzmann inversion (MS IBI) includes data from multiple targets to yield a less state dependent potential.\cite{Moore2014}
 The MS IBI potential is an average of the single state potentials with a weighting function to prioritize a state of interest.
@@
 For some systems there may not be a potential that represents all states-- this is not unique to coarse potentials, atomistic potentials also have this limitation.
+<need some tie in back to why we would want to go from CG-->atomistic>
 
@@
 <how morphct pipeline would work: cg-backmap-ct>
-<how kmc works>
-<cite morphct papers>
+MorphCT, a software previously developed by our lab, can simulate charge transport through an OPV morphology using kinetic Monte Carlo\cite{Miller2018a,MorphCT,morphct2.2}.
+The kinetic Monte Carlo algorithm used by MorphCT uses the semi-empirical Zerner's Intermediate Neglect of Differential Overlap (ZINDO/S) quantum chemical calculation to obtain the molecular energy levels of chromophores in the morphology.
+The HOMO levels of each chromophore site and the energy splitting induced in the chromophore pairs is used in the Marcus equation to calculate the charge hopping rate between pairs.
+A Monte Carlo simulation can then be run using these hopping rates.
+Because this is a quantum chemical calculation, the position of each atom is needed--therefore a backmapping process is required to calculate the charge transport in a CG morphology.
+MorphCT has some builtin backmapping tools which use xml file (which i will discuss why these are bad in the next section) and the package is bulky/CLI/hard-to-use...
 
 \section*{Preliminary Work}
+<how do I relate this to what I want to do??>
 - contributed to development of open-source packages: mbuild, foyer, signac, fresnel
@@
 It's also helped me to learn how to work as part of a team.
- - created MWE of coarse-graining and backmapping with smiles-- these will need furthertesting as we try them on different compounds but the proof of concept is there.
+ - created MWE of coarse-graining and backmapping with smiles-- these will need further testing as we try them on different compounds but the proof of concept is there.
  - created tutorial examples to help current and future students understand scientific concepts and how to use computational tools

### 2020-08-10 2pd.tex
words about what i;ll do

@@
 - maybe the workflow could even involve getting the equilibrated trajectory (atomtyping/fill box/run) with the new hoomd 3 api we could even set decorrelation time as a stop trigger...
+
 \subsection*{Objective 1: Develop a coarse graining workflow}
-build on existing tools (mbuild, openbabel)
+build on existing tools (mbuild, openbabel, tim moores MSIBI code, hoomd, foyer?)
 use SMARTS matching to specify mapping operators with relative ease
@@
 seems like they use IBI but they dont say how they got their target distributions.
-can easily test out different mappings and other "processing" conditions
+can easily test out different mappings and "processing" conditions
 
@@
 <cite our papers that show we can do this comparison already>
+Our morphct paper says the mobilities we predict are 2x higher than experiment? why?
+
+<I need something in here about making morphct more user friendly and less hard-coded for p3ht.>
+<adding in calculation of reorganization energy??> 
+<or just ripping out the KMC bit and making it modular>
 
 \section*{Predicted Outcomes}
--understanding coarse graining (i'm stealing this from mike because I like it) how coarse is too coarse? for these new systems what is the minimal model which can reproduce the structural features
--understanding the interactions which guide BHJ self assembly. understanding which functionalizations/processing conditions make best morphology
+- understanding coarse graining (i'm stealing this from mike because I like it) how coarse is too coarse? for these new systems what is the minimal model which can reproduce the structural features
+- understanding the interactions which guide BHJ self assembly. understanding which functionalizations/processing conditions make best morphology
+- are smarts strings viable for use as mappings? where does using smarts strings break down?
+- does making science easier/more understandable make it better?
 

### 2020-08-10 2pd.tex
Small compilation edits for eric; Added NSF review rubric for BI/IM.

@@
 which makes their working a little tenuous.
-And judging by the amount of confusion in their mailing list <https://groups.google.com/forum/#!forum/votca> there is room for improvement in the API.
+And judging by the amount of confusion in their mailing list <https://groups.google.com/forum/\#!forum/votca> there is room for improvement in the API.
 Overall though this is program has many features, interfaces with many popular MD engines (lammps, gromacs, hoomd), and is under active, collaborative development.

### 2020-08-11 1summ.tex
pasted in NSF rubric as a guide

@@
 
+IM - Potential to advance knowledge and understanding within own and across different fields
+    - Activities explore creative, original, or potentially transformative concepts?
+    - Plan well-reasoned, well organized, based on sound rationale?
+    - Mechanism to assess success?
+    - How qualified is team?
+    - Adequate resources to carry out activities?
+
 %\required{Broader Impacts}
@@
 Working as part of a team.
+
+BI - Potential to benefit society, contribute to achievement of desired societal outcomes
+    - Activities explore creative, original, or potentially transformative concepts?
+    - Plan well-reasoned, well organized, based on sound rationale?
+    - Mechanism to assess success?
+    - How qualified is team?
+    - Adequate resources to carry out activities?

### 2020-08-11 2pd.tex
Sprint edits, comments

@@
 In order to protect our precious climate, we need a non-polluting, cost-efficient way to provide electricity.
-Harnessing solar energy is an important part of a green energy solution.
+%EJ: Nice- we'll mostly avoid adjectives unless they're specifically correct for something, so maybe we'd drop 'precious' here, but motivation good~
+Harnessing solar energy is an important part of a green energy solution. %EJ: Why? Green energy percentage breakdown?
 Traditionally, photovoltaic devices, materials which can convert incedent light into electric current, were made of inorganic materials like silicon.
-But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative.
+But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative. %EJ: Cite.
 The advantage of OPVs over inorganic PV devices is that OPVs are lightweight, low cost, easier to produce, and flexible. 
@@
 The interfacial area of the acceptor:donor regions \cite{Mazzio2015}, the regioregularity of the polymer \cite{Kim2006}, and electronic properties of the compounds \cite{Scharber2006a} all play an important role in the power conversion efficiency (PCE) of the device.
+%EJ: Getting into some technical details- we may  move this to a background section, but it can also work here.
 With minor modifcations, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
+%EJ: True- but we gotta make people feel this.
 For example, simply changing the functional groups on the conjugated backbone of a molecule like ITIC can change how it packs in a crystal, its electron affinity, and thus its performance in a device\cite{Swick2019a}.
@@
 By breaking our simulation apart into separate steps and equilibrating different lengths scales individually, we can <get equilibrated morphologies on multiple length scales more efficiently>.
+%EJ: cool
+%% One thing that's possibly missing in the motivation right now is a rundown of prior simulation techniques and coarse-graining strategies and where they've fallen short.
 <so what's the gist of what we're going to do?>
@@
 <there aren't a lot of cg models that already exist for these new compounds>
-It is necessary to develop a simple, useable, and flexible pipeline to adapt to the constantly changing chemistries of current OPV technologies.
+It is necessary to develop a simple, useable, and flexible pipeline to adapt to the constantly changing chemistries of current OPV technologies. %EJ: NIIICE SENTENCE.
 
 \section*{Research Objectives}
+%EJ: Nice. Attempting to reorder based on heirarchy
+<use that science to help solve energy crisis???????>
+<create models for new opv compounds>
 <gain insight into the limits of coarse graining>
-<create models for new opv compounds>
+<develop new tools that help humans do science>
 <create a workflow that will make creating new models more accessible>
-<develop new tools that help humans do science>
-<use that science to help solve energy crisis???????>
 <I don't know where to put this but I want a section on best practices>
+%EJ: Learning and incorporating best practices might actually be a new facet of your work.
+Like, we can point to the computational research papers that show how this wasn't done so much in the past, but it's happening better now, and we're going to lean into it- I think it fits.
 By making our code open source and freely availiable, we contribute to the knowledge of a global community. But just because something is availiable doesn't mean it is accessible. 
@@
 \subsection*{Molecular Dynamics}
-
+%EJ: Here or above: Why MD the right tool?
 <I am borrowing heavily from Mike's MD section, so I need to come back through and rewrite this>

### 2020-08-11 1summ.tex
moved some of my notes into the bullets

@@
 
+IM - Potential to advance knowledge and understanding within own and across different fields
+- Activities explore creative, original, or potentially transformative concepts?
 A coarse graining pipeline will help make multi-scale simulations more accesible and useable for others. 
 This can be useful for screening of potential OPV compounds.
-<talk about VOTCA?>
-<talk about TRUE simulations and reproducibility in the field>
-<talk about our supercomputer allocations?>
+
+- Plan well-reasoned, well organized, based on sound rationale?
+
+- Mechanism to assess success?
+<comparing mobilities, diffraction to experiment>
+
+- How qualified is team?
 <talk about what I've done already?>
 
-IM - Potential to advance knowledge and understanding within own and across different fields
-    - Activities explore creative, original, or potentially transformative concepts?
-    - Plan well-reasoned, well organized, based on sound rationale?
-    - Mechanism to assess success?
-    - How qualified is team?
 - Adequate resources to carry out activities?
+<talk about our supercomputer allocations?>
 
@@
 
+BI - Potential to benefit society, contribute to achievement of desired societal outcomes
+- Activities explore creative, original, or potentially transformative concepts?
+<talk about VOTCA?>
+<talk about TRUE simulations and reproducibility in the field>
+
+- Plan well-reasoned, well organized, based on sound rationale?
+
+- Mechanism to assess success?
+a sign of well-written, understandable code is if other people use it. 
+It's tricky because this is completely out of my control, but if other people find my code useful--it is a success.
+by integrating what I do with other existing codebases I can help to achieve this goal.
+Also having good tutorials and documentation.
+
+- How qualified is team?
 Helping to make research transferrable, reproducible, useable, and extensible. 
-Wriitng tutorials and documentation while keep in mind principles of oftware carpentry instructor training. 
+Writing tutorials and documentation while keep in mind principles of oftware carpentry instructor training. 
 Using software dev best practices to be efficient and make sure that I'm not making code for someone else to struggle through later. 
@@
 
-BI - Potential to benefit society, contribute to achievement of desired societal outcomes
-    - Activities explore creative, original, or potentially transformative concepts?
-    - Plan well-reasoned, well organized, based on sound rationale?
-    - Mechanism to assess success?
-    - How qualified is team?
 - Adequate resources to carry out activities?
+oss community
+software carpentry training
+experience with teaching/training undergrads

### 2020-08-11 2pd.tex
pre boss suggestions

--- 2020-08-10 2pd.tex
@@
 \section*{Motivation}
+
 <why do opvs matter>
@@
 \section*{Research Objectives}
+
 <gain insight into the limits of coarse graining>
@@
 \subsection*{Organic Photovoltaics}
+
 <what is PCE>
@@
 \subsection*{Mesoscale Device Simulation}
+
 <I DONT WANT TO FOCUS ON THIS TOO MUCH. It's only here as a rationale for why backmapping>
@@
 MorphCT has some builtin backmapping tools which use xml file (which i will discuss why these are bad in the next section) and the package is bulky/CLI/hard-to-use...
+<making morphct more modular to allow it to be used in a workflow not cli>
 
 \section*{Preliminary Work}
+
 <how do I relate this to what I want to do??>
@@
 \section*{Research Plan}
+
 - I will build on existing tools (signac,freud,mbuild,foyer,tim moore's msibi)
@@
 \subsection*{Objective 1: Develop a coarse graining workflow}
+
 build on existing tools (mbuild, openbabel, tim moores MSIBI code, hoomd, foyer?)
@@
 \subsection*{Objective 2: Develop a backmapping workflow}
+
 Given an equilibrated CG morphology, retrieve the atomistic one by mapping the SMARTS structures onto the position of the CG beads and then relaxing them with some position restraint.
@@
 \subsection*{Objective 3: Run CG simulation sweep of non-fullerene acceptor blends}
+
 use signac to organize data
@@
 \subsection*{Objective 4: Analysis}
+
 Use charge transfer, diffraction to tell which models are the best
@@
 \section*{Predicted Outcomes}
+
 - understanding coarse graining (i'm stealing this from mike because I like it) how coarse is too coarse? for these new systems what is the minimal model which can reproduce the structural features
@@
 \section*{Contingency Analysis}
+
 <what's going to be hard?> 
+maybe SMARTS SMILES won't work without careful choice of beads.
+This is a little annoying but still preferrable I think because at least the reasons may be understandable (the order of the beads matters) or chemically sensible (one SMILES string may contain another -- just as one chemical moeity may be composed of more submoeities <this is a word?>)
 

### 2020-08-11 2pd.tex

@@
 <there aren't a lot of cg models that already exist for these new compounds>
-It is necessary to develop a simple, useable, and flexible pipeline to adapt to the constantly changing chemistries of current OPV technologies.
+It is necessary to develop a simple, useable, and flexible pipeline to adapt to the constantly changing chemistries of current OPV technologies. %EJ: NIIICE SENTENCE.
 
@@
 <gain insight into the limits of coarse graining>
+%EJ: Nice. Attempting to reorder based on heirarchy
+<use that science to help solve energy crisis???????>
 <create models for new opv compounds>
+<gain insight into the limits of coarse graining>
+<develop new tools that help humans do science>
 <create a workflow that will make creating new models more accessible>
-<develop new tools that help humans do science>
-<use that science to help solve energy crisis???????>
 <I don't know where to put this but I want a section on best practices>
+%EJ: Learning and incorporating best practices might actually be a new facet of your work.
+Like, we can point to the computational research papers that show how this wasn't done so much in the past, but it's happening better now, and we're going to lean into it- I think it fits.
 By making our code open source and freely availiable, we contribute to the knowledge of a global community. But just because something is availiable doesn't mean it is accessible. 

### 2020-08-11 2pd.tex
couple comments

--- 2020-08-11 2pd.tex
@@
 \section*{Preliminary Work}
+% With lan - About excitonic splitting, using DFT, DNA. 
+% With Matt - What intermolecular interactions guide diphenylurea crystal formation
+% With us - Perspective paper about all things
+
 <how do I relate this to what I want to do??>

### 2020-08-11 2pd.tex
more comments from boss meeting

--- 2020-08-11 2pd.tex
@@
 %EJ: True- but we gotta make people feel this.
+Numbers money, time, etc
 For example, simply changing the functional groups on the conjugated backbone of a molecule like ITIC can change how it packs in a crystal, its electron affinity, and thus its performance in a device\cite{Swick2019a}.
@@
 %% One thing that's possibly missing in the motivation right now is a rundown of prior simulation techniques and coarse-graining strategies and where they've fallen short.
+%% think mosdef -- scale of the problem
+%% talk about best practices -- monolithic indecipherable code
+%% general vs specific -- make the thing that works right now
 <so what's the gist of what we're going to do?>
@@
 
-<gain insight into the limits of coarse graining>
 %EJ: Nice. Attempting to reorder based on heirarchy
@@
 %EJ: Here or above: Why MD the right tool?
+%% morphology matters - thermodynamics that govern self assembly
+%% the kinetics that follow the processing
+%% we can see the dynamics -- kinetic arresting, (if we want to probe the processing, need the dynamics)
+%% monte carlo inefficient for polymers - cluster moves, not parallelizable 
 <I am borrowing heavily from Mike's MD section, so I need to come back through and rewrite this>
@@
  - created tutorial examples to help current and future students understand scientific concepts and how to use computational tools
+ %% frame gixstapose as a tool for reproducible, approachable science
  - created GIXStapose (presented at SciPy2020) an interactive diffraction/structure viewer.
@@
 This is a little annoying but still preferrable I think because at least the reasons may be understandable (the order of the beads matters) or chemically sensible (one SMILES string may contain another -- just as one chemical moeity may be composed of more submoeities <this is a word?>)
+coarse-graining NFAs might be hard--planar backbones and floppy side chains
 

### 2020-08-12 2pd.tex
addressing some comments--got to the big one

@@
 In our technology-driven society, it is unrealistic to think that energy demand will lessen, in fact global energy consumption is predicted to increase from 17 TW in 2010 to 27 TW in 2040 \cite{Mazzio2015}.
-In order to protect our precious climate, we need a non-polluting, cost-efficient way to provide electricity.
-%EJ: Nice- we'll mostly avoid adjectives unless they're specifically correct for something, so maybe we'd drop 'precious' here, but motivation good~
-Harnessing solar energy is an important part of a green energy solution. %EJ: Why? Green energy percentage breakdown?
+In order to protect our climate, we need a non-polluting, cost-efficient way to provide electricity.
+Harnessing solar energy is an important part of a green energy solution.
+Renewable energy accounts for 11\% of the U.S. energy consumption in 2019 and of that 11\% 9\% was solar.\cite{https://www.eia.gov/energyexplained/renewable-sources/}
+Our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar. \cite{Wirth2017}
 Traditionally, photovoltaic devices, materials which can convert incedent light into electric current, were made of inorganic materials like silicon.
-But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative. %EJ: Cite.
+But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative.\cite{Tang1986b}
 The advantage of OPVs over inorganic PV devices is that OPVs are lightweight, low cost, easier to produce, and flexible. 
@@
 The performance of an OPV device is intimately linked with the structure of the active layer:
-The interfacial area of the acceptor:donor regions \cite{Mazzio2015}, the regioregularity of the polymer \cite{Kim2006}, and electronic properties of the compounds \cite{Scharber2006a} all play an important role in the power conversion efficiency (PCE) of the device.
-%EJ: Getting into some technical details- we may  move this to a background section, but it can also work here.
 With minor modifcations, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
-%EJ: True- but we gotta make people feel this.
-Numbers money, time, etc
-For example, simply changing the functional groups on the conjugated backbone of a molecule like ITIC can change how it packs in a crystal, its electron affinity, and thus its performance in a device\cite{Swick2019a}.
+Imagine, you are a chemist testing new OPVs: you are specifically looking at a mixture of a non-fullerene acceptor (ITIC) and a polymer donor (PTB7). 
+Each cost \$500 for 100 mg. \cite{sigmaaldrich.com}
+The solvent you use and the concentrations of your active compounds changes the device performance.\cite{Hoppe2004a}
+The amount of time the solvent is allowed to evaporate changes the device performance\cite{Li2007}.
+The time and temperature of the thermal annealing changes the device performance\cite{Ma2005}.
+The regioregularity of your polymer affects the device performance. \cite{Kim2006}
+The distribution of polymer lengths affects the device performance. \cite{Zhao2013b}
+Changing the functional groups on ITIC changes how it packs in a crystal, its electron affinity, and thus its performance in a device\cite{Swick2019a}.
+All this would be to determine the performance of just one donor/acceptor combination in one category of potential compounds\cite{Dou2013}
 By using a simulation pipeline, we can help to streamline the process of determining which OPV materials will form the best morphology with the best charge transport, and in turn, help to solve the energy crisis.
@@
 By breaking our simulation apart into separate steps and equilibrating different lengths scales individually, we can <get equilibrated morphologies on multiple length scales more efficiently>.
-%EJ: cool
 %% One thing that's possibly missing in the motivation right now is a rundown of prior simulation techniques and coarse-graining strategies and where they've fallen short.
@@
 
+The interfacial area of the acceptor:donor regions \cite{Mazzio2015}, the regioregularity of the polymer \cite{Kim2006}, and electronic properties of the compounds \cite{Scharber2006a} all play an important role in the power conversion efficiency (PCE) of the device.
+%EJ: Getting into some technical details- we may  move this to a background section, but it can also work here.
 <what is PCE>
@@
 \section*{Preliminary Work}
+% With lan - About excitonic splitting, using DFT, DNA. 
+% With Matt - What intermolecular interactions guide diphenylurea crystal formation
+% With us - Perspective paper about all things
 

### 2020-08-12 2pd.tex
intro draft done

--- 2020-08-11 2pd.tex
@@
 
-<why do opvs matter>
+%%<why do opvs matter>
 The global climate crisis is one of the most pressing issue humanity faces today.
@@
 In order to make the most efficient OPVs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
+
 The active layer of an OPV is mixture of electron-donor and acceptor compounds: the ideal morphology is a micro phase-separated interpenetrating network called a bulk heterojunction (BHJ).
 The performance of an OPV device is intimately linked with the structure of the active layer:
-The interfacial area of the acceptor:donor regions \cite{Mazzio2015}, the regioregularity of the polymer \cite{Kim2006}, and electronic properties of the compounds \cite{Scharber2006a} all play an important role in the power conversion efficiency (PCE) of the device.
-%EJ: Getting into some technical details- we may  move this to a background section, but it can also work here.
 With minor modifcations, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
-%EJ: True- but we gotta make people feel this.
-Numbers money, time, etc
-For example, simply changing the functional groups on the conjugated backbone of a molecule like ITIC can change how it packs in a crystal, its electron affinity, and thus its performance in a device\cite{Swick2019a}.
+Imagine, you are a chemist synthesizing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor (ITIC) and a polymer donor (PTB7). 
+Each compound costs \$500 for 100 mg. \cite{sigmaaldrich.com}
+The solvent you use and the concentrations of your active compounds changes the device performance.\cite{Hoppe2004a}
+The amount of time the solvent is allowed to evaporate changes the device performance\cite{Li2007}.
+The time and temperature of the thermal annealing changes the device performance\cite{Ma2005}.
+The regioregularity of your polymer affects the device performance. \cite{Kim2006}
+The distribution of polymer lengths affects the device performance. \cite{Zhao2013b}
+Changing the functional groups on ITIC changes how it packs in a crystal, its electron affinity, and thus its performance in a device\cite{Swick2019a}.
+All this would be to determine the performance of just one donor/acceptor combination in one category of potential compounds\cite{Dou2013}
 By using a simulation pipeline, we can help to streamline the process of determining which OPV materials will form the best morphology with the best charge transport, and in turn, help to solve the energy crisis.
+
 Molecular simulation also gives us insight into the atomic interactions which drive the self assembly of an OPV morphology.
@@
 So, in order to model this system, a multiscale approach is necessary.
-By breaking our simulation apart into separate steps and equilibrating different lengths scales individually, we can <get equilibrated morphologies on multiple length scales more efficiently>.
-%EJ: cool
-%% One thing that's possibly missing in the motivation right now is a rundown of prior simulation techniques and coarse-graining strategies and where they've fallen short.
-%% think mosdef -- scale of the problem
-%% talk about best practices -- monolithic indecipherable code
-%% general vs specific -- make the thing that works right now
-<so what's the gist of what we're going to do?>
-<cg - get some polymer morphologies equilibrated on relevant length scales>
-<backmapping - get back the atomic positions in preparation for techniques which require atomic level resolutiuon e.g., charge transport>
-<kmc calc>
-<if we we're just to start with the atomistic sim, it wouldn't be as efficient and might even be less accurate because polymers are tough to equilibrate> <probably cite arthi's paper here Gartner2019?>
-<This efficiency is important because we got a lot of testing to do!>
-<justification for what I'm doing>
+By breaking our simulation apart into separate steps and equilibrating different lengths scales individually, we can get equilibrated morphologies on multiple length scales more efficiently.
+
+Already good open-source packages exist to address the problem of coarse-graining and/or backmapping \cite{Marrink2007,Ruhle2009,Maerxke2011,MorphCT,Wassenaar2014b} %%these citations are martini, votca, trappe, morphct, backwards.py
+By making code open source and freely availiable, we contribute to the knowledge of a global community. 
+But just because something is availiable doesn't mean it is accessible: often just figuring out how to use an existing package can be very difficult. \cite{Cummings2019}
+These existing codebases can appear to a new user as monolithic and indecipherable because their design has been to solve a problem, which they do, instead of design with a focus on how people learn.
+These codebases also rely on users piecing together multiple, often incompatible, bits of software, using manually created xml files, or manually deciding how to classify a atom grouping based on the users chemical intuition.
+All of which contribute to a reproducibility crisis in the computational sciences\cite{Baker2016}
+By keeping <best software dev and teaching practices> in mind throughout development, we can strive to make tools which make science more transferrable, reproducibile, usable, and extensible (TRUE) \cite{Thompson2020} %%TRUE
+Instead aiming to keep code small and modular to make it easier to use and more understandable\cite{Adorf2018a} 
+This not only makes our code easy to use and debug, but reduce the cognitive load for a new user \cite{Jankowski2019}
+Jupyter Notebooks, which are a combination of interactive code and formatted text and images, can be used like a lab notebook for computational scientists in order to demonstrate the process, rationale, and the story of each experiment and the exact steps to get the results shown\cite{Rule2019a}
+Remember that the data never speaks for itself: although including input and output files of a calculation is a good first step, ideally this can be accompanied by the story of what this data means and how we know \cite{https://v4.software-carpentry.org/softeng/principles.html, Wilson2016}
+
+Use flexible method for specifying coarse grain models to obtain OPV polymer morphologies equilibrated on length scales relevant to charge transport.
+Use a backmapping method, which works on the same simple mapping operator, to restore the atomic positions in preparation for techniques which require atomic level resolutiuon e.g., charge transport calculations.
+This two step process is necessary because starting with the fully atomistic structure would not only be computationally inefficient the result may even be less accurate due to the difficulties of equilibrating polymers.
+\cite{Gartner2019}
+This efficiency is important because the scope of potential OPV compounds is vast and the energy crisis necessitates expediency.
 The number of opv compounds to test quickly becomes intractable when we consider that the power conversion efficiency is strongly linked to minor chemical modifications or functionalization, device processing, and the interplay between donor and acceptor\cite{Mazzio2015,Swick2019a}.

### 2020-08-12 2pd.tex
got through research objectives--rough

@@
 By keeping <best software dev and teaching practices> in mind throughout development, we can strive to make tools which make science more transferrable, reproducibile, usable, and extensible (TRUE) \cite{Thompson2020} %%TRUE
+%% unit tests, version control, continuous integration, 
 Instead aiming to keep code small and modular to make it easier to use and more understandable\cite{Adorf2018a} 
-This not only makes our code easy to use and debug, but reduce the cognitive load for a new user \cite{Jankowski2019}
+This not only makes our code easy to use and debug, but reduces the cognitive load for a new user \cite{Jankowski2019}
 Jupyter Notebooks, which are a combination of interactive code and formatted text and images, can be used like a lab notebook for computational scientists in order to demonstrate the process, rationale, and the story of each experiment and the exact steps to get the results shown\cite{Rule2019a}
@@
 %EJ: Nice. Attempting to reorder based on heirarchy
-<use that science to help solve energy crisis???????>
-<create models for new opv compounds>
-<gain insight into the limits of coarse graining>
-<develop new tools that help humans do science>
-<create a workflow that will make creating new models more accessible>
-<I don't know where to put this but I want a section on best practices>
-%EJ: Learning and incorporating best practices might actually be a new facet of your work.
-Like, we can point to the computational research papers that show how this wasn't done so much in the past, but it's happening better now, and we're going to lean into it- I think it fits.
-By making our code open source and freely availiable, we contribute to the knowledge of a global community. But just because something is availiable doesn't mean it is accessible. 
-lazy refactoring--get something working first then update it when needed, keep code small and modular to make this easier and more understandable\cite{Adorf2018a} 
-Best practices for jupyter notebooks -- like a lab notebook-- can show the process and the story of each assignment and the exact steps and results to get there\cite{Rule2019a}
-Using software carpentry principles to keep in mind how people learn when introducing a new concept\cite{https://v4.software-carpentry.org/softeng/principles.html}
-Software carpentry using version control, building, scripting, testing, debugging,\cite{Wilson2006}
-live coding, interactive \cite{Wilson2016}
-reducing cognitive load \cite{Jankowski2019}
-using the tools, not fighting them--version control, automation \cite{Wilson2014}
-TRUE\cite{Thompson2020}
+%%use that science to help solve energy crisis???????>
+Ultimately the goal is to help solve the global energy crisis. 
+Solar energy is a important part of a green energy solution.
+This research aims to gain insight about new OPV compound morphologies using molecular simulation.
+
+%%create models for new opv compounds>
+In order to model these polymer systems on relevant length scales, we are going to need to develop new coarse grain models.
+We will need a flexible and efficient coarse graining scheme, so that new models are easy and intuitive to create.
+
+%%gain insight into the limits of coarse graining>
+A benefit of this work is that we may gain insight into the features of an OPV which govern its self-assembly and the limits of coarse grain models.
+Currently there is no best scheme for a coarse grain mapping operator.
+By making our coarse graining tool simple and easy-to-use, we will be able to test many mapping operators and probe the limits of a minimal model: what is the minimum structure needed to represent a complex molecule?
+
+%%develop new tools that help humans do science>
+By making this tool simple and easy to use hopefully we will also make reproducibile science more achievable for the next generation. 
+Integrating this tool with existing open source software packages will make it the most useful to the most people and also increase its transferrability and usability.
+Using packages like signac for managing dataspaces, foyer for version control of forcefields, mbuild for building chemical structures, hoomd for running molecular dynamics simulations, freud for simulation trajectory analysis, openbabel for recognizing chemical patterns.
+
+%%create a workflow that will make creating new models more accessible>
+Demonstrating a workflow from start to finish with explanations using easy-to-understand language, diagrams, and figures makes a codebase more usable and approachable but does not interfere with it being modular or efficient.
+Ultimately a goal of this research is that it is used by others: as an example to build upon or as a template for setting up their own experiments.
 
@@
 
-The interfacial area of the acceptor:donor regions \cite{Mazzio2015}, the regioregularity of the polymer \cite{Kim2006}, and electronic properties of the compounds \cite{Scharber2006a} all play an important role in the power conversion efficiency (PCE) of the device.
-%EJ: Getting into some technical details- we may  move this to a background section, but it can also work here.
-<what is PCE>
+%% <what is PCE>
 The power conversion efficiency (PCE or sometimes $\eta_{e}$) is the ratio of electrical power produced by the device over the power of incedent photons.
@@
 
-<history>
+%% <history>
 Inorganic PV devices came first and are still most efficient, but they are more costly to produce, use rare elements, and their production causes other environmental issues, so they aren't the best solution for solar energy harvesting.
@@
 
-<how opvs work>
+%%<how opvs work>
 The compounds which compose an OPV are synthesizable molecules (often polymers) composed of abundant elements (carbon, hydrogen, nitrogen, sulfur, oxygen).
@@
 
-<why morphology matters>
-The morphology of the device can be affected by the processing conditions: temperature, solvents, and concentrations/ratios of the active compounds. <cite>
-These changes in structure can strongly affect the device performance <cite>.
+%%<why morphology matters>
+The morphology of the device can be affected by the processing conditions: temperature, solvents, and concentrations/ratios of the active compounds. \cite{Ma2005,Hoppe2004a,Li2007}
+The interfacial area of the acceptor:donor regions \cite{Mazzio2015}, the regioregularity of the polymer \cite{Kim2006}, and electronic properties of the compounds \cite{Scharber2006a} all play an important role in the power conversion efficiency (PCE) of the device.
+These changes in structure can strongly affect the device performance.
 Molecular simulation allows us to "see" these atomic interaction and gain a deeper view into the driving forces behind the self assembly of these OPV morphologies and to understand what conditions create the best devices.
-<segue into simulation>
+%%<segue into simulation>
 

### 2020-08-13 1summ.tex
more comments from boss meeting
replacing <> with %% comments

@@
 \begin{center}
-\large{\textbf{<Title>}}
+\large{\textbf{Title}} %%TODO
 %\large{\textbf{ADVANCEMENT OF ORGANIC PHOTOVOLTAICS THROUGH ARTIFICIAL NEURAL NETWORKS}}
@@
 
-Already the effects of human-influenced climate change are <hurtng everyone in particular poor and disadvantaged groups>.
+Already the effects of human-influenced climate change are %%<hurtng everyone in particular poor and disadvantaged groups>.
 Burning fossil fuels for energy is the main contributor to rising $CO_{2}$ levels, and the energy demand is only increasing.
 This increase in energy demand along with the need to protect our precious climate makes finding efficient, renewable energy technologies of the utmost importance.
-Harvesting the abundant solar energy is a <good solution because it is renewable, non-polluting, sustainable>.
+Harvesting the abundant solar energy is a %%<good solution because it is renewable, non-polluting, sustainable>.
 Devices which convert light to electricity, called photovoltaics, were originally made of silicon and required rare elements and careful, clean-room processing.
@@
 This can be useful for screening of potential OPV compounds.
+what makes a good NFA?
 
@@
 - Mechanism to assess success?
-<comparing mobilities, diffraction to experiment>
+%%<comparing mobilities, diffraction to experiment>
 
 - How qualified is team?
-<talk about what I've done already?>
+%%<talk about what I've done already?>
 
 - Adequate resources to carry out activities?
-<talk about our supercomputer allocations?>
+%%<talk about our supercomputer allocations?>
 
@@
 - Activities explore creative, original, or potentially transformative concepts?
-<talk about VOTCA?>
-<talk about TRUE simulations and reproducibility in the field>
+%%<talk about VOTCA?>
+%%<talk about TRUE simulations and reproducibility in the field>
 

### 2020-08-13 2pd.tex
adding in first figure
* replacing <> with %% comments

@@
 However, in order to become a viable, cost-effective option they need better efficiency \cite{Mazzio2015}.
-<image from nrel about solar cells efficiency>\cite{https://www.nrel.gov/pv/cell-efficiency.html}
+%%<image from nrel about solar cells efficiency>\cite{https://www.nrel.gov/pv/cell-efficiency.html}
 In order to make the most efficient OPVs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
@@
 All of which contribute to a reproducibility crisis in the computational sciences\cite{Baker2016}
-By keeping <best software dev and teaching practices> in mind throughout development, we can strive to make tools which make science more transferrable, reproducibile, usable, and extensible (TRUE) \cite{Thompson2020} %%TRUE
+By keeping %%<best software dev and teaching practices> in mind throughout development, we can strive to make tools which make science more transferrable, reproducibile, usable, and extensible (TRUE) \cite{Thompson2020} %%TRUE
 %% unit tests, version control, continuous integration, 
@@
 Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70-80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h)\cite{Baran2017}.
-<there aren't a lot of cg models that already exist for these new compounds>
+%%<there aren't a lot of cg models that already exist for these new compounds>
 It is necessary to develop a simple, useable, and flexible pipeline to adapt to the constantly changing chemistries of current OPV technologies. %EJ: NIIICE SENTENCE.
@@
 Finally, the the number of charges which reach the electrode depends on the driving force or gradient resulting from the potentials of the electrons and holes.\cite{Hoppe2004}
-<is there a citation for why charge transport is a good proxy for PCE?>
+%%<is there a citation for why charge transport is a good proxy for PCE?>
 
@@
 And in 1995, Yu described the first bulk heterojunction (BHJ), as an interpenetrating network of donor and acceptor that maximizes the interfacial area, which is still the state of the art morphology to this day\cite{Yu1995}.
-Most recently, non-fullerene acceptors (NFAs), like ITIC, are contributing to the PCE increase of modern OPVs \cite{S.Gurney2019}.
-The planar acceptor-donor-acceptor moeity seen in many NFA backbones <figure?> may have more efficient exciton splitting, as compared to a fullerene accpetor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer \cite{Yi2018}.
+Most recently, non-fullerene acceptors (NFAs), like 3,9-bis(2-methylene-(3-(1,1-dicyanomethylene)-indanone))-5,5,11,11-tetrakis(4-hexylphenyl)-dithieno[2,3-d:2’,3’-d’]-s-indaceno[1,2-b:5,6-b’]dithiophene (ITIC), are contributing to the PCE increase of modern OPVs \cite{S.Gurney2019}.
+\begin{wrapfigure}{L}{0.5\textwidth}
+    \centering
+    \includegraphics[width=0.4\textwidth]{images/ITIC.pdf}
+    \caption{ITIC chemical structure with \textcolor{red}{electron accepting regions in red} and \textcolor{blue}{electron donating regions in blue}}
+    \label{fig:itic}
+\end{wrapfigure}
+The planar acceptor-donor-acceptor moeity seen in many NFA backbones (see Figure \ref{fig:itic}) may have more efficient exciton splitting, as compared to a fullerene acceptor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer \cite{Yi2018}.
 
@@
 %% monte carlo inefficient for polymers - cluster moves, not parallelizable 
-<I am borrowing heavily from Mike's MD section, so I need to come back through and rewrite this>
-<md in general>
+%%<I am borrowing heavily from Mike's MD section, so I need to come back through and rewrite this>
+%%<md in general>
 classical physics
@@
 Now GPUs 100 millions times faster
-<what is MD used for? why is MD the best technique for gettign these OPV morphologies?>
+%%<what is MD used for? why is MD the best technique for gettign these OPV morphologies?>
 protein folding \cite{levitt75}, other biological processes, polymers \cite{Gartner2019a}
 
-<what assumptions does md make?>
+%%<what assumptions does md make?>
 bonds aren't formed or broken, electrons don't exist
@@
 dispersion is tricky--electrons don't slosh around unless you use some fancy many-body potential
-<what are the limits of atomistic md?>
-<segue to why we need CG models>
+%%<what are the limits of atomistic md?>
+%%<segue to why we need CG models>
 
@@
 Coarse-grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models.
-<how do cg models let us access long length/time??>
+%%<how do cg models let us access long length/time??>
 Similarly to how we don't need to look at the working of a plant cell to understand the growth of a forest \cite{Muller-Plathe2002}, we don't need to consider atomic level properties when we are interested in the bulk morphology.
@@
 Other coarse-graining schemes may group functional groups together \cite{Berendsen2010, Jankowski2013, Marsh2014}, one bead per repeat unit in a polymer\cite{Lee2011}, or even represent an entire amino acid with a single site\cite{Peng2019a}.
-<examples of cg models and the cool things they do>
+%%<examples of cg models and the cool things they do>
 General coarse grain models of opv thiophene polymers where only the spacing, regioregularity of the side chains were varied were able to predict different order disorder transitions and calculated scattering patterns of these simple systems were comparable to those obtained from experiment \cite{Jankowski2013, Marsh2014}
@@
 Which model is right depends on the length and time scale on which the property of interest can be observed.
-<multiscale sims>
+%%<multiscale sims>
 For many systems, however, we are interested in properties which span length scales.
@@
 This can allow us the calculate properties such as charge transport, which depends upon the electronic structure of individual chromophores and the connectivity of these chromophores over distances proportional to the exciton dissociation length.
-<what stands in our way?>
+%%<what stands in our way?>
 
-<coarse-grain models are specific>
+%%<coarse-grain models are specific>
 
-<segue from automated creation of forcefields to...>
-<mapping operator has to be decided by hand> <is this section too big?>
+%%<segue from automated creation of forcefields to...>
+%%<mapping operator has to be decided by hand> <is this section too big?>
 Part of coarse graining that is not yet automated is choosing a mapping scheme or a mapping operator.
@@
 When parameterizing a new molecule you must pick a mapping and then compare the resulting beads to existing beads--a process which is time consuming and error prone\cite{http://www.cgmartini.nl/index.php/tutorials-general-introduction-gmx5/parametrzining-new-molecule-gmx5}.
-The MARTINI force field was first designed for lipids--further parameterization for proteins and nuclei acids have been added<cite--and has shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.
-Many mapping schemes are simply based on the user's chemical intuition (e.g., what parts of the molecule shouldn't be allowed to bend?<cite any model where rings are one bead> What groups have the most dominant interactions in this structure <cite dna cg model>).
+The MARTINI force field was first designed for lipids--further parameterization for proteins and nuclei acids have been added%%<cite--and has shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.
+Many mapping schemes are simply based on the user's chemical intuition (e.g., what parts of the molecule shouldn't be allowed to bend?%%<cite any model where rings are one bead> What groups have the most dominant interactions in this structure <cite dna cg model>).
 As the number of atoms in the fine grain structure increases, the number of possible mappings increase drastically.
@@
 
-<how cg potentials have been attained>
+%%<how cg potentials have been attained>
 
@@
 There are numerous methods for deriving coarse grain potentials from atomistic ones (e.g., force-matching, reverse Monte Carlo), but in this proposal we will focus on Iterative Boltzmann Inversion (IBI).
-<IBI>
+%%<IBI>
 IBI is where a coarse grain potential is iteratively tuned to fit a target distribution. \cite{Reith2003a}
@@
 Given any particle, the RDF gives the probability of finding a neighboring particle at distance r.
-Taking the Boltzmann Inverse of the RDF results in the potential of mean force (PMF). <add equation>
+Taking the Boltzmann Inverse of the RDF results in the potential of mean force (PMF). %%<add equation>
 Then a CG simulation can be run using the PMF as the non-bonded potential to achieve a new distribution.
-Then the difference between the new and target distribution can be accounted for in the next iteration accoring to equation <add equation>.
+Then the difference between the new and target distribution can be accounted for in the next iteration accoring to equation %%<add equation>.
 This process is repeated until the difference between the result and the target are sufficiently similar.
@@
 But optimization to the liquid-vapor equilibriai, although useful for prediction of thermodynamic properties, may not be ideal for prediction of structure which will strongly influence charge transport.
-<so we probably want to create our own potentials>
-<IBI potentials are sometimes transferrable and it is not clear why sometimes they are and sometimes they aren't.> \cite{Moore2014}
+%%<so we probably want to create our own potentials>
+%%<IBI potentials are sometimes transferrable and it is not clear why sometimes they are and sometimes they aren't.> \cite{Moore2014}
 
@@
 When using the MS IBI method, it is important to choose dissimilar states to minimize the potential overlap region.
-If this overlap region is large, there are many potentials which will provide matching RDFs. <show fig from moore>
+If this overlap region is large, there are many potentials which will provide matching RDFs. %%<show fig from moore>
 For some systems there may not be a potential that represents all states-- this is not unique to coarse potentials, atomistic potentials also have this limitation.
-<need some tie in back to why we would want to go from CG-->atomistic>
+%%<need some tie in back to why we would want to go from CG-->atomistic>
 
@@
 
-<I DONT WANT TO FOCUS ON THIS TOO MUCH. It's only here as a rationale for why backmapping>
-<how morphct pipeline would work: cg-backmap-ct>
+%%<I DONT WANT TO FOCUS ON THIS TOO MUCH. It's only here as a rationale for why backmapping>
+%%<how morphct pipeline would work: cg-backmap-ct>
 MorphCT, a software previously developed by our lab, can simulate charge transport through an OPV morphology using kinetic Monte Carlo\cite{Miller2018a,MorphCT,morphct2.2}.
@@
 MorphCT has some builtin backmapping tools which use xml file (which i will discuss why these are bad in the next section) and the package is bulky/CLI/hard-to-use...
-<making morphct more modular to allow it to be used in a workflow not cli>
+%%<making morphct more modular to allow it to be used in a workflow not cli>
 
@@
 
-<how do I relate this to what I want to do??>
+%%<how do I relate this to what I want to do??>
 - contributed to development of open-source packages: mbuild, foyer, signac, fresnel
@@
 This is an example of how to create a version controlled forcefield which can be automatically applied to a compound.
-<atom typing is a pain and doing it manually is bad cite foyer paper>
+%%<atom typing is a pain and doing it manually is bad cite foyer paper>
 
-<Talk about what exists and why it is not enough>
-<votca, Peng2019a> 
+%%<Talk about what exists and why it is not enough>
+%%<votca, Peng2019a> 
 Versatile Object-oriented Toolkit for Coarse-graining Applications (VOTCA) \cite{Ruhle2011b}
@@
 
-<compare VOTCA's backmapping to my proposed scheme>
-VOTCA makes some progress towards a TRUE simulation pipeline: they include a docker container with their pre-built software stack and example input files <see https://github.com/votca/votca -- using this code via docker> (but some of these input files don't work and the codecoverage on their repo as of time of writing is 0\%), and while including example inputs is a good first step, very little walkthrough (aside from code comments buried in the xml) is given.
-A manual is provided but there is some disconnect between the example files and those given in the manual <https://github.com/votca/csg-manual/releases>.
+%%<compare VOTCA's backmapping to my proposed scheme>
+VOTCA makes some progress towards a TRUE simulation pipeline: they include a docker container with their pre-built software stack and example input files %%<see https://github.com/votca/votca -- using this code via docker> (but some of these input files don't work and the codecoverage on their repo as of time of writing is 0\%), and while including example inputs is a good first step, very little walkthrough (aside from code comments buried in the xml) is given.
+A manual is provided but there is some disconnect between the example files and those given in the manual %%<https://github.com/votca/csg-manual/releases>.
 the code is a mix of C++, shell commands, python, and interacts with compiled programs through the command-line and mpi.
 which makes their working a little tenuous.
-And judging by the amount of confusion in their mailing list <https://groups.google.com/forum/\#!forum/votca> there is room for improvement in the API.
+And judging by the amount of confusion in their mailing list %%<https://groups.google.com/forum/\#!forum/votca> there is room for improvement in the API.
 Overall though this is program has many features, interfaces with many popular MD engines (lammps, gromacs, hoomd), and is under active, collaborative development.
@@
 I also don't like their API.
-by choosing a pure python API I will be able to make use of jupyter notebooks which can be run on cloud servers using tools like mybinder <link mybinder, link to tutorials I;ve made> which can combine executable code with markdown text and images.
+by choosing a pure python API I will be able to make use of jupyter notebooks which can be run on cloud servers using tools like mybinder %%<link mybinder, link to tutorials I;ve made> which can combine executable code with markdown text and images.
 In this way a tutorial can provide exact commands needed to reproduce the example intimately connected with the rationale and justification of that example.
@@
 \end{lstlisting}
-The result of using this code in the `coarse` function <link to grits> is a three-site hexane model A-B-A, same as VOTCA.
+The result of using this code in the `coarse` function %%<link to grits> is a three-site hexane model A-B-A, same as VOTCA.
 The mapping here is specified as a list of bead name / smarts string pairs.
@@
 Having the mapping in-line with the workflow also allows for the user to check that the mapping is correct with built in interactive visualizations, which can display the mapping as an overlay.
-<show overlay>
+%%<show overlay>
 
@@
 This makes it a good candidate for specifying a coarse-grain mapping scheme.The open-source package, Openbabel, allows for a SMILES string to be converted to a chemical structure and vice versa.
-<cite openbabel,SMILES, SMARTS> SMARTS is similar to SMILES but instead of representing a single molecule unambiguously, it has multiple wildcards which can be used for pattern matching.
+%%<cite openbabel,SMILES, SMARTS> SMARTS is similar to SMILES but instead of representing a single molecule unambiguously, it has multiple wildcards which can be used for pattern matching.
 This pattern matching is also implemented in the Openbabel package.
 If we know the SMARTS string for any given CG mapping we can map the CG site to it's center of mass or geometric center.
-I have developed a minimum working example of how this can be done <cite grits> and then how the atomistic structure can be recovered.
+I have developed a minimum working example of how this can be done %%<cite grits> and then how the atomistic structure can be recovered.
 It could be fairly straightforward to implement a lookup to check if bead parameters already exist--say for the MARTINI model-- by going through and writing out the SMARTS pattern for each existing bead type.
@@
 Use charge transfer, diffraction to tell which models are the best
-<cite a bunch of experimental papers we can compare to>
-<cite our papers that show we can do this comparison already>
+%%<cite a bunch of experimental papers we can compare to>
+%%<cite our papers that show we can do this comparison already>
 Our morphct paper says the mobilities we predict are 2x higher than experiment? why?
 
-<I need something in here about making morphct more user friendly and less hard-coded for p3ht.>
-<adding in calculation of reorganization energy??> 
-<or just ripping out the KMC bit and making it modular>
+%%<I need something in here about making morphct more user friendly and less hard-coded for p3ht.>
+%%<adding in calculation of reorganization energy??> 
+%%<or just ripping out the KMC bit and making it modular>
 
@@
 
-<what's going to be hard?> 
+%%<what's going to be hard?> 
 maybe SMARTS SMILES won't work without careful choice of beads.
-This is a little annoying but still preferrable I think because at least the reasons may be understandable (the order of the beads matters) or chemically sensible (one SMILES string may contain another -- just as one chemical moeity may be composed of more submoeities <this is a word?>)
+This is a little annoying but still preferrable I think because at least the reasons may be understandable (the order of the beads matters) or chemically sensible (one SMILES string may contain another -- just as one chemical moeity may be composed of more submoeities %%<this is a word?>)
 coarse-graining NFAs might be hard--planar backbones and floppy side chains

### 2020-08-13 2pd.tex
messing around trying to get figure to not be bad

@@
 Most recently, non-fullerene acceptors (NFAs), like 3,9-bis(2-methylene-(3-(1,1-dicyanomethylene)-indanone))-5,5,11,11-tetrakis(4-hexylphenyl)-dithieno[2,3-d:2’,3’-d’]-s-indaceno[1,2-b:5,6-b’]dithiophene (ITIC), are contributing to the PCE increase of modern OPVs \cite{S.Gurney2019}.
-\begin{wrapfigure}{L}{0.5\textwidth}
+
+\begin{wrapfigure}{L}{0.5\linewidth}
     \centering
-    \includegraphics[width=0.4\textwidth]{images/ITIC.pdf}
+    \includegraphics[width=0.6\linewidth]{images/ITIC.pdf}
     \caption{ITIC chemical structure with \textcolor{red}{electron accepting regions in red} and \textcolor{blue}{electron donating regions in blue}}
@@
 \end{wrapfigure}
+
 The planar acceptor-donor-acceptor moeity seen in many NFA backbones (see Figure \ref{fig:itic}) may have more efficient exciton splitting, as compared to a fullerene acceptor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer \cite{Yi2018}.
@@
 VOTCA uses an xml file to do this:
-\lstinputlisting[breaklines]{hexane.xml}
+
+%%\lstinputlisting[breaklines]{hexane.xml}
+
+%%\begin{wrapfigure}{L}{0.6\textwidth}
+%%    \centering
+%%    \includegraphics[width=0.5\textwidth]{images/hexanexml.pdf}
+%%    \caption{XML file used by VOTCA to specify a three site coarse grain mapping of n-hexane}
+%%    \label{fig:hexanexml}
+%%\end{wrapfigure}
+
 It may be easy to think that because what we are doing--mapping two carbons and their attached hydrogens to a single bead so that six alkyl carbons becomes A-B-A--that the process will also be simple.

### 2020-08-13 2pd.tex
added nrel figure and citation

@@
 Consumption of fossil fuels for energy and transportation strongly contributes to atmospheric $CO_2$ the affects of which are global, long-term, and devastating\cite{Solomon2009a}.
-In our technology-driven society, it is unrealistic to think that energy demand will lessen, in fact global energy consumption is predicted to increase from 17 TW in 2010 to 27 TW in 2040 \cite{Mazzio2015}.
+In our technology-driven society, it is unrealistic to think that energy demand will lessen, in fact global energy consumption is predicted to increase from 17 TW in 2010 to 27 TW in 2040\cite{Mazzio2015}.
 In order to protect our climate, we need a non-polluting, cost-efficient way to provide electricity.
 Harnessing solar energy is an important part of a green energy solution.
-Renewable energy accounts for 11\% of the U.S. energy consumption in 2019 and of that 11\% 9\% was solar.\cite{https://www.eia.gov/energyexplained/renewable-sources/}
-Our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar. \cite{Wirth2017}
+Renewable energy accounts for 11\% of the U.S. energy consumption in 2019 and of that 11\% 9\% was solar\cite{https://www.eia.gov/energyexplained/renewable-sources/}.
+Our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar\cite{Wirth2017}.
 Traditionally, photovoltaic devices, materials which can convert incedent light into electric current, were made of inorganic materials like silicon.
-But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative.\cite{Tang1986b}
+But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative\cite{Tang1986b}.
 The advantage of OPVs over inorganic PV devices is that OPVs are lightweight, low cost, easier to produce, and flexible. 
-However, in order to become a viable, cost-effective option they need better efficiency \cite{Mazzio2015}.
-%%<image from nrel about solar cells efficiency>\cite{https://www.nrel.gov/pv/cell-efficiency.html}
+However, in order to become a viable, cost-effective option they need better efficiency\cite{Mazzio2015}.
+
+\begin{figure}[h!]
+    \includegraphics[width=0.9\linewidth]{images/NREL2020.pdf}
+    \caption{Efficiencies of photovoltaic technologies from 1976 to present.
+OPVS are denoted by red filled circles.
+The current state-of-the-art research cell achieves 17.4\% efficiency.
+Image taken from ref \cite{NREL2020}}
+    \label{fig:nrel}
+\end{figure}
+
 In order to make the most efficient OPVs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
@@
 Imagine, you are a chemist synthesizing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor (ITIC) and a polymer donor (PTB7). 
-Each compound costs \$500 for 100 mg. \cite{sigmaaldrich.com}
-The solvent you use and the concentrations of your active compounds changes the device performance.\cite{Hoppe2004a}
+Each compound costs \$500 for 100 mg\cite{sigmaaldrich.com}.
+The solvent you use and the concentrations of your active compounds changes the device performance\cite{Hoppe2004a}.
 The amount of time the solvent is allowed to evaporate changes the device performance\cite{Li2007}.
 The time and temperature of the thermal annealing changes the device performance\cite{Ma2005}.
-The regioregularity of your polymer affects the device performance. \cite{Kim2006}
-The distribution of polymer lengths affects the device performance. \cite{Zhao2013b}
+The regioregularity of your polymer affects the device performance\cite{Kim2006}.
+The distribution of polymer lengths affects the device performance\cite{Zhao2013b}.
 Changing the functional groups on ITIC changes how it packs in a crystal, its electron affinity, and thus its performance in a device\cite{Swick2019a}.
-All this would be to determine the performance of just one donor/acceptor combination in one category of potential compounds\cite{Dou2013}
+All this would be to determine the performance of just one donor/acceptor combination in one category of potential compounds\cite{Dou2013}.
 By using a simulation pipeline, we can help to streamline the process of determining which OPV materials will form the best morphology with the best charge transport, and in turn, help to solve the energy crisis.
@@
 
-Already good open-source packages exist to address the problem of coarse-graining and/or backmapping \cite{Marrink2007,Ruhle2009,Maerxke2011,MorphCT,Wassenaar2014b} %%these citations are martini, votca, trappe, morphct, backwards.py
+Already good open-source packages exist to address the problem of coarse-graining and/or backmapping\cite{Marrink2007,Ruhle2009,Maerxke2011,MorphCT,Wassenaar2014b}.
+%%these citations are martini, votca, trappe, morphct, backwards.py
 By making code open source and freely availiable, we contribute to the knowledge of a global community. 
-But just because something is availiable doesn't mean it is accessible: often just figuring out how to use an existing package can be very difficult. \cite{Cummings2019}
+But just because something is availiable doesn't mean it is accessible: often just figuring out how to use an existing package can be very difficult\cite{Cummings2019}.
 These existing codebases can appear to a new user as monolithic and indecipherable because their design has been to solve a problem, which they do, instead of design with a focus on how people learn.
 These codebases also rely on users piecing together multiple, often incompatible, bits of software, using manually created xml files, or manually deciding how to classify a atom grouping based on the users chemical intuition.
-All of which contribute to a reproducibility crisis in the computational sciences\cite{Baker2016}
-By keeping %%<best software dev and teaching practices> in mind throughout development, we can strive to make tools which make science more transferrable, reproducibile, usable, and extensible (TRUE) \cite{Thompson2020} %%TRUE
-%% unit tests, version control, continuous integration, 
-Instead aiming to keep code small and modular to make it easier to use and more understandable\cite{Adorf2018a} 
-This not only makes our code easy to use and debug, but reduces the cognitive load for a new user \cite{Jankowski2019}
+All of which contribute to a reproducibility crisis in the computational sciences\cite{Baker2016}.
+By keeping best practices for software development and teaching in mind throughout development, we can strive to make tools which make science more transferrable, reproducibile, usable, and extensible (TRUE)\cite{Thompson2020}.
+%%TRUE
+Best software development practices include using version control software, such as git, to facilitate the process of tracking and merging changes to a code repository, especially important when working collaboratively.
+Also among these best practices are using unit tests and continuous integration to ensure that errors are quickly and automatically caught\cite{Wilson2014}.
+Instead of writing dense, inseparable scripts which rely on the user manually following a command prompt or editing multiple text files, we aim to keep code small and modular to make it easier to use and understand\cite{Adorf2018a}.
+Following these guidelines not only makes our code easier to develop and debug, but reduces the cognitive load for a new user\cite{Jankowski2019}.
+Providing good documentation and tutorials is also imperative for onboarding new users.
 Jupyter Notebooks, which are a combination of interactive code and formatted text and images, can be used like a lab notebook for computational scientists in order to demonstrate the process, rationale, and the story of each experiment and the exact steps to get the results shown\cite{Rule2019a}
-Remember that the data never speaks for itself: although including input and output files of a calculation is a good first step, ideally this can be accompanied by the story of what this data means and how we know \cite{https://v4.software-carpentry.org/softeng/principles.html, Wilson2016}
+When writing these tutorials, it is wise to remember that the data never speaks for itself: although including input and output files of a calculation is a good first step, they must be accompanied by the story of what the data means and how a user can know that meaning for themselves\cite{https://v4.software-carpentry.org/softeng/principles.html, Wilson2016}.
 

### 2020-08-13 2pd.tex
adding websites to library

@@
 Harnessing solar energy is an important part of a green energy solution.
-Renewable energy accounts for 11\% of the U.S. energy consumption in 2019 and of that 11\% 9\% was solar\cite{https://www.eia.gov/energyexplained/renewable-sources/}.
+Renewable energy accounts for 11\% of the U.S. energy consumption in 2019 and of that 11\% 9\% was solar\cite{USEIA2020}.
 Our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar\cite{Wirth2017}.
@@
 Jupyter Notebooks, which are a combination of interactive code and formatted text and images, can be used like a lab notebook for computational scientists in order to demonstrate the process, rationale, and the story of each experiment and the exact steps to get the results shown\cite{Rule2019a}
-When writing these tutorials, it is wise to remember that the data never speaks for itself: although including input and output files of a calculation is a good first step, they must be accompanied by the story of what the data means and how a user can know that meaning for themselves\cite{https://v4.software-carpentry.org/softeng/principles.html, Wilson2016}.
+When writing these tutorials, it is wise to remember that the data never speaks for itself: although including input and output files of a calculation is a good first step, they must be accompanied by the story of what the data means and how a user can know that meaning for themselves\cite{SWC, Wilson2016}.
 
@@
 In this scheme, four atoms (except rings, which are treated differently) are grouped and the site is classified as polar, non-polar, apolar, or charged depending on the atoms it is composed of.
-When parameterizing a new molecule you must pick a mapping and then compare the resulting beads to existing beads--a process which is time consuming and error prone\cite{http://www.cgmartini.nl/index.php/tutorials-general-introduction-gmx5/parametrzining-new-molecule-gmx5}.
-The MARTINI force field was first designed for lipids--further parameterization for proteins and nuclei acids have been added%%<cite--and has shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.
-Many mapping schemes are simply based on the user's chemical intuition (e.g., what parts of the molecule shouldn't be allowed to bend?%%<cite any model where rings are one bead> What groups have the most dominant interactions in this structure <cite dna cg model>).
+When parameterizing a new molecule you must pick a mapping and then compare the resulting beads to existing beads--a process which is time consuming and error prone\cite{martini-tutorial}.
+The MARTINI force field was first designed for lipids--further parameterization for proteins and nuclei acids have been added--and has shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.%%<cite
+Many mapping schemes are simply based on the user's chemical intuition (e.g., what parts of the molecule shouldn't be allowed to bend?
+What groups have the most dominant interactions in this structure %%<cite any model where rings are one bead><cite dna cg model>).
 As the number of atoms in the fine grain structure increases, the number of possible mappings increase drastically.
@@
 %%<compare VOTCA's backmapping to my proposed scheme>
-VOTCA makes some progress towards a TRUE simulation pipeline: they include a docker container with their pre-built software stack and example input files %%<see https://github.com/votca/votca -- using this code via docker> (but some of these input files don't work and the codecoverage on their repo as of time of writing is 0\%), and while including example inputs is a good first step, very little walkthrough (aside from code comments buried in the xml) is given.
+VOTCA makes some progress towards a TRUE simulation pipeline: they include a docker container with their pre-built software stack and example input files  (but some of these input files don't work and the codecoverage on their repo as of time of writing is 0\%), and while including example inputs is a good first step, very little walkthrough (aside from code comments buried in the xml) is given.\cite{votca-github} %%using this code via docker>
 A manual is provided but there is some disconnect between the example files and those given in the manual %%<https://github.com/votca/csg-manual/releases>.

### 2020-08-13 2pd.tex
cleaned up citations

@@
 With minor modifcations, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
-Imagine, you are a chemist synthesizing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor (ITIC) and a polymer donor (PTB7). 
-Each compound costs \$500 for 100 mg\cite{sigmaaldrich.com}.
+Imagine, you are a chemist synthesizing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor, 3,9-bis(2-methylene-(3-(1,1-dicyanomethylene)-indanone))-5,5,11,11-tetrakis(4-hexylphenyl)-dithieno[2,3-d:2’,3’-d’]-s-indaceno[1,2-b:5,6-b’]dithiophene (ITIC), and a polymer donor,Poly({4,8-bis[(2-ethylhexyl)oxy]benzo[1,2-b:4,5-b′]dithiophene-2,6-diyl}{3-fluoro-2-[(2-ethylhexyl)carbonyl]thieno[3,4-b]thiophenediyl}) (PTB7).
+Each compound costs \$500 for 100 mg\cite{sigmaaldrich}.
 The solvent you use and the concentrations of your active compounds changes the device performance\cite{Hoppe2004a}.
@@
 A complication of the simulation of OPV polymers is that the properties which predict a device's efficiency, for example charge transport, span multiple length scales.
-The atomic and electronic properties are important for light absorption, in which an exciton is created, and charge transfer, where the exciton is dissociated into a free electron and hole\cite{Scharber2006,Hoppe2004,Mazzio2015}.
+The atomic and electronic properties are important for light absorption, in which an exciton is created, and charge transfer, where the exciton is dissociated into a free electron and hole\cite{Scharber2006a,Hoppe2004,Mazzio2015}.
 At the same time, the exciton finding an interface at which to dissociates depends on the bulk morphology, as do the charges, once separated, finding a path to an electrode in order to generate current and produce electricity.
@@
 
-Already good open-source packages exist to address the problem of coarse-graining and/or backmapping\cite{Marrink2007,Ruhle2009,Maerxke2011,MorphCT,Wassenaar2014b}.
+Already good open-source packages exist to address the problem of coarse-graining and/or backmapping\cite{Marrink2007,Ruhle2009,Maerzke2011,MorphCT,Wassenaar2014b}.
 %%these citations are martini, votca, trappe, morphct, backwards.py
@@
 Providing good documentation and tutorials is also imperative for onboarding new users.
-Jupyter Notebooks, which are a combination of interactive code and formatted text and images, can be used like a lab notebook for computational scientists in order to demonstrate the process, rationale, and the story of each experiment and the exact steps to get the results shown\cite{Rule2019a}
+Jupyter Notebooks, which are a combination of interactive code and formatted text and images, can be used like a lab notebook for computational scientists in order to demonstrate the process, rationale, and the story of each experiment and the exact steps to get the results shown\cite{Rule2019a}.
 When writing these tutorials, it is wise to remember that the data never speaks for itself: although including input and output files of a calculation is a good first step, they must be accompanied by the story of what the data means and how a user can know that meaning for themselves\cite{SWC, Wilson2016}.
@@
 Use a backmapping method, which works on the same simple mapping operator, to restore the atomic positions in preparation for techniques which require atomic level resolutiuon e.g., charge transport calculations.
-This two step process is necessary because starting with the fully atomistic structure would not only be computationally inefficient the result may even be less accurate due to the difficulties of equilibrating polymers.
-\cite{Gartner2019}
+This two step process is necessary because starting with the fully atomistic structure would not only be computationally inefficient the result may even be less accurate due to the difficulties of equilibrating polymers\cite{Gartner2019a}.
 This efficiency is important because the scope of potential OPV compounds is vast and the energy crisis necessitates expediency.
@@
 The fraction of excitons which dissociate depends on the exciton dissociation length and the charge separation probability at the interface.
-Finally, the the number of charges which reach the electrode depends on the driving force or gradient resulting from the potentials of the electrons and holes.\cite{Hoppe2004}
+Finally, the the number of charges which reach the electrode depends on the driving force or gradient resulting from the potentials of the electrons and holes\cite{Hoppe2004}.
 %%<is there a citation for why charge transport is a good proxy for PCE?>
@@
 Inorganic PV devices came first and are still most efficient, but they are more costly to produce, use rare elements, and their production causes other environmental issues, so they aren't the best solution for solar energy harvesting.
-The first OPV was created by Tang in 1986 and \cite{Tang1986b} used a bilyaer structure containing copper phthalocyanine and a perylene derivitive. 
+The first OPV was created by Tang in 1986 and used a bilyaer structure containing copper phthalocyanine and a perylene derivitive\cite{Tang1986b}. 
 This early device had a PCE of 0.95\%.
-In 1992, Saricifti and Heeger\cite{Saricifti1992} were the first to report using fullerene as an electron acceptor in a fullerene:polymer mixture.
+In 1992, Saricifti and Heeger were the first to report using fullerene as an electron acceptor in a fullerene:polymer mixture\cite{Saricifti1992}.
 And in 1995, Yu described the first bulk heterojunction (BHJ), as an interpenetrating network of donor and acceptor that maximizes the interfacial area, which is still the state of the art morphology to this day\cite{Yu1995}.
-Most recently, non-fullerene acceptors (NFAs), like 3,9-bis(2-methylene-(3-(1,1-dicyanomethylene)-indanone))-5,5,11,11-tetrakis(4-hexylphenyl)-dithieno[2,3-d:2’,3’-d’]-s-indaceno[1,2-b:5,6-b’]dithiophene (ITIC), are contributing to the PCE increase of modern OPVs \cite{S.Gurney2019}.
+Most recently, non-fullerene acceptors (NFAs), like ITIC, are contributing to the PCE increase of modern OPVs\cite{S.Gurney2019}.
 
@@
 
-The planar acceptor-donor-acceptor moeity seen in many NFA backbones (see Figure \ref{fig:itic}) may have more efficient exciton splitting, as compared to a fullerene acceptor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer \cite{Yi2018}.
+The planar acceptor-donor-acceptor moeity seen in many NFA backbones (see Figure \ref{fig:itic}) may have more efficient exciton splitting, as compared to a fullerene acceptor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer\cite{Yi2018}.
 
@@
 %%<why morphology matters>
-The morphology of the device can be affected by the processing conditions: temperature, solvents, and concentrations/ratios of the active compounds. \cite{Ma2005,Hoppe2004a,Li2007}
-The interfacial area of the acceptor:donor regions \cite{Mazzio2015}, the regioregularity of the polymer \cite{Kim2006}, and electronic properties of the compounds \cite{Scharber2006a} all play an important role in the power conversion efficiency (PCE) of the device.
+The morphology of the device can be affected by the processing conditions: temperature, solvents, and concentrations/ratios of the active compounds\cite{Ma2005,Hoppe2004a,Li2007}.
+The interfacial area of the acceptor:donor regions\cite{Mazzio2015}, the regioregularity of the polymer\cite{Kim2006}, and electronic properties of the compounds\cite{Scharber2006a} all play an important role in the power conversion efficiency (PCE) of the device.
 These changes in structure can strongly affect the device performance.
@@
 sample a thermodynamic ensemble
-First MD simulation \cite{Alder1957} system of 108 particles, 200 collisions in one hour on an IBM-704.
+First MD simulation system of 108 particles, 200 collisions in one hour on an IBM-704\cite{Alder1957}.
 Now GPUs 100 millions times faster
@@
 %%<how do cg models let us access long length/time??>
-Similarly to how we don't need to look at the working of a plant cell to understand the growth of a forest \cite{Muller-Plathe2002}, we don't need to consider atomic level properties when we are interested in the bulk morphology.
+Similarly to how we don't need to look at the working of a plant cell to understand the growth of a forest, we don't need to consider atomic level properties when we are interested in the bulk morphology\cite{Muller-Plathe2002}.
 The heart of coarse graining is the removal of degrees of freedom. 
 This effective potential used to represent the reduced system results in a smoothed free energy landscape. 
-Processes which may have taken many time steps in an all atom simulation can take fewer time steps in a coarse simulation.\cite{Berendsen2010}
-Due to their long length and time scales, coarse grain models are ideal for examining polymer properties.\cite{Gartner2019a}
+Processes which may have taken many time steps in an all atom simulation can take fewer time steps in a coarse simulation\cite{Berendsen2010}.
+Due to their long length and time scales, coarse grain models are ideal for examining polymer properties\cite{Gartner2019a}.
 It is too big and too slow and also just a bad idea to simulate huge boxes of atomistic polymers.
 Even if the simulation was to complete, there would be too much information to process accurately. 
-CGing allows scientists to FOCUS their experiments.\cite{Baschnagel2000}
+CGing allows scientists to FOCUS their experiments\cite{Baschnagel2000}.
 The resolution of coarse grain systems is broad:
-Simply grouping hydrogens with the heavy atom they are bonded to, called the united-atom model, has been shown to speed up dynamics and make polymer length scales more easily accesible \cite{Paul1995a, Yang2006a,}.
-Other coarse-graining schemes may group functional groups together \cite{Berendsen2010, Jankowski2013, Marsh2014}, one bead per repeat unit in a polymer\cite{Lee2011}, or even represent an entire amino acid with a single site\cite{Peng2019a}.
+Simply grouping hydrogens with the heavy atom they are bonded to, called the united-atom model, has been shown to speed up dynamics and make polymer length scales more easily accesible\cite{Paul1995a, Yang2006a}.
+Other coarse-graining schemes may group functional groups together\cite{Berendsen2010, Jankowski2013, Marsh2014}, one bead per repeat unit in a polymer\cite{Lee2011}, or even represent an entire amino acid with a single site\cite{Peng2019a}.
 %%<examples of cg models and the cool things they do>
-General coarse grain models of opv thiophene polymers where only the spacing, regioregularity of the side chains were varied were able to predict different order disorder transitions and calculated scattering patterns of these simple systems were comparable to those obtained from experiment \cite{Jankowski2013, Marsh2014}
-A coarse-grain model for phospholipids has allowed for bilayer formation from an initial random configuration to be observed even though the model was parameterized to the vapor-liquid phase transition.\cite{Shelley2001}
+General coarse grain models of opv thiophene polymers where only the spacing, regioregularity of the side chains were varied were able to predict different order disorder transitions and calculated scattering patterns of these simple systems were comparable to those obtained from experiment\cite{Jankowski2013, Marsh2014}.
+A coarse-grain model for phospholipids has allowed for bilayer formation from an initial random configuration to be observed even though the model was parameterized to the vapor-liquid phase transition\cite{Shelley2001}.
 Which model is right depends on the length and time scale on which the property of interest can be observed.
@@
 There have been efforts to create mapping schemes for automating the process of deciding which atoms are grouped in a "super-atom" bead.
-One study reduced the number of allowed mappings by only allowing those which do not change the symmetry group, then iterated over a graph of all possible mappings to find the "best" mapping by comparing the difference between the mapped RDF and velocity autocorrelation function \cite{Chakraborty2018a}.
+One study reduced the number of allowed mappings by only allowing those which do not change the symmetry group, then iterated over a graph of all possible mappings to find the "best" mapping by comparing the difference between the mapped RDF and velocity autocorrelation function\cite{Chakraborty2018a}.
 Another mapping scheme uses principle component analysis to choose a mapping scheme for biomolecules that best represents th essential dynamics\cite{Zhang2008}.
@@
 %%<IBI>
-IBI is where a coarse grain potential is iteratively tuned to fit a target distribution. \cite{Reith2003a}
+IBI is where a coarse grain potential is iteratively tuned to fit a target distribution\cite{Reith2003a}.
 Here is the algorithm for determining the non-bonded potentials:
@@
 There are many attempts to create transferrable CG potentials, for example:
-The TraPPE force-field fits CG potentials using vapor-liquid equilibria to improve transferrability across thermodynamic states\cite{Maerzke2011}
+The TraPPE force-field fits CG potentials using vapor-liquid equilibria to improve transferrability across thermodynamic states\cite{Maerzke2011}.
 But optimization to the liquid-vapor equilibriai, although useful for prediction of thermodynamic properties, may not be ideal for prediction of structure which will strongly influence charge transport.
@@
 
-Multistate iterative Boltzmann inversion (MS IBI) includes data from multiple targets to yield a less state dependent potential.\cite{Moore2014}
+Multistate iterative Boltzmann inversion (MS IBI) includes data from multiple targets to yield a less state dependent potential\cite{Moore2014}.
 The MS IBI potential is an average of the single state potentials with a weighting function to prioritize a state of interest.
@@
 %%<compare VOTCA's backmapping to my proposed scheme>
-VOTCA makes some progress towards a TRUE simulation pipeline: they include a docker container with their pre-built software stack and example input files  (but some of these input files don't work and the codecoverage on their repo as of time of writing is 0\%), and while including example inputs is a good first step, very little walkthrough (aside from code comments buried in the xml) is given.\cite{votca-github} %%using this code via docker>
+VOTCA makes some progress towards a TRUE simulation pipeline: they include a docker container with their pre-built software stack and example input files  (but some of these input files don't work and the codecoverage on their repo as of time of writing is 0\%), and while including example inputs is a good first step, very little walkthrough (aside from code comments buried in the xml) is given\cite{votca-github}.
+%%using this code via docker>
 A manual is provided but there is some disconnect between the example files and those given in the manual %%<https://github.com/votca/csg-manual/releases>.
@@
 We do not propose a new automated mapping, but instead a way to make the mapping and backmapping process easier for the user.
-Simplified Molecular Input Line Entry System or SMILES \cite{Weininger} was designed to represent organic molecules in an unambiguous way (similar to IUPAC) but in a line-entry system which is also readable by a computer.
+Simplified Molecular Input Line Entry System or SMILES was designed to represent organic molecules in an unambiguous way (similar to IUPAC) but in a line-entry system which is also readable by a computer\cite{Weininger}.
 This makes it a good candidate for specifying a coarse-grain mapping scheme.The open-source package, Openbabel, allows for a SMILES string to be converted to a chemical structure and vice versa.
-%%<cite openbabel,SMILES, SMARTS> SMARTS is similar to SMILES but instead of representing a single molecule unambiguously, it has multiple wildcards which can be used for pattern matching.
+SMARTS is similar to SMILES but instead of representing a single molecule unambiguously, it has multiple wildcards which can be used for pattern matching.%%<cite openbabel,SMILES, SMARTS>
 This pattern matching is also implemented in the Openbabel package.
-If we know the SMARTS string for any given CG mapping we can map the CG site to it's center of mass or geometric center.
-I have developed a minimum working example of how this can be done %%<cite grits> and then how the atomistic structure can be recovered.
+If we know the SMARTS string for any given CG mapping, we can map the CG site to its center of mass or geometric center.
+I have developed a minimum working example of how this can be done and then how the atomistic structure can be recovered.%%<cite grits>
 It could be fairly straightforward to implement a lookup to check if bead parameters already exist--say for the MARTINI model-- by going through and writing out the SMARTS pattern for each existing bead type.

### 2020-08-13 2pd.tex
making it so the chemical names dont break latex

@@
 With minor modifcations, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
-Imagine, you are a chemist synthesizing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor, 3,9-bis(2-methylene-(3-(1,1-dicyanomethylene)-indanone))-5,5,11,11-tetrakis(4-hexylphenyl)-dithieno[2,3-d:2’,3’-d’]-s-indaceno[1,2-b:5,6-b’]dithiophene (ITIC), and a polymer donor,Poly({4,8-bis[(2-ethylhexyl)oxy]benzo[1,2-b:4,5-b′]dithiophene-2,6-diyl}{3-fluoro-2-[(2-ethylhexyl)carbonyl]thieno[3,4-b]thiophenediyl}) (PTB7).
+Imagine, you are a chemist synthesizing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor, \textit{3,9-bis(2-ethylene-(3-(1,1-dicyanomethylene)-indanone))-5,5,11,11-tetrakis(4-hexylphenyl)-dithieno(2,3-d:2',3'-d')-s-indaceno(1,2-b:5,6-b')dithiophene} (\textbf{ITIC}), and a polymer donor, \textit{poly((4,8-bis((2ethylhexyl)oxy)benzo(1,2-b:4,5-b')dithiophene-2,6-diyl)(3-fluoro-2-((2-ethylhexyl)carbonyl)thieno(3,4-b)thiophenediyl))} (\textbf{PTB7}).
 Each compound costs \$500 for 100 mg\cite{sigmaaldrich}.

### 2020-08-14 2pd.tex
editing -- got to background

@@
 Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70-80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h)\cite{Baran2017}.
-%%<there aren't a lot of cg models that already exist for these new compounds>
+Coarse grain models do not yet exist for many of these NFAs, and with so many varieties an adaptable pipeline makes more sense than a single model.%%<there aren't a lot of cg models that already exist for these new compounds>
 It is necessary to develop a simple, useable, and flexible pipeline to adapt to the constantly changing chemistries of current OPV technologies. %EJ: NIIICE SENTENCE.
@@
 %%use that science to help solve energy crisis???????>
-Ultimately the goal is to help solve the global energy crisis. 
+Ultimately the goal this research is to help solve the global energy crisis. 
 Solar energy is a important part of a green energy solution.
@@
 %%create models for new opv compounds>
-In order to model these polymer systems on relevant length scales, we are going to need to develop new coarse grain models.
-We will need a flexible and efficient coarse graining scheme, so that new models are easy and intuitive to create.
+In order to model these OPV polymer systems on relevant length scales, it is necessary to develop new coarse grain models.
+A flexible and efficient coarse graining scheme will simplify the process of mapping and parameterizing (these coarse grain elements). %% reword
 
 %%gain insight into the limits of coarse graining>
-A benefit of this work is that we may gain insight into the features of an OPV which govern its self-assembly and the limits of coarse grain models.
-Currently there is no best scheme for a coarse grain mapping operator.
-By making our coarse graining tool simple and easy-to-use, we will be able to test many mapping operators and probe the limits of a minimal model: what is the minimum structure needed to represent a complex molecule?
+The flexibility of specifying a mapping will allow for the comparison of multiple mappings which may provide insight into the features of an OPV which govern its self-assembly and the limits of coarse grain models.
+Currently there is no agreed-upon ``best'' scheme for a coarse grain mapping operator.
+By making a simple and easy-to-use coarse graining tool, many mapping operators can be tested and the limits of a minimal model can be probed.
+%% What is the minimum structure needed to represent a complex molecule? %% reword? omit?
 
 %%develop new tools that help humans do science>
-By making this tool simple and easy to use hopefully we will also make reproducibile science more achievable for the next generation. 
-Integrating this tool with existing open source software packages will make it the most useful to the most people and also increase its transferrability and usability.
-Using packages like signac for managing dataspaces, foyer for version control of forcefields, mbuild for building chemical structures, hoomd for running molecular dynamics simulations, freud for simulation trajectory analysis, openbabel for recognizing chemical patterns.
+Making this tool usable will also hopefully contribute to reproducibile science. 
+Integrating with existing open source software packages will provide the most benefit and also increase transferrability and usability.
+We will use packages like signac for managing dataspaces, foyer for version control of forcefields, mbuild for building chemical structures, hoomd for running molecular dynamics simulations, freud for simulation trajectory analysis, and openbabel for recognizing chemical patterns.
+%%cite!
+These are established codebases which are actively developed and engine agnostic (except hoomd which is in itself an engine).
 

### 2020-08-14 2pd.tex
added hexane xml
oops--wrong smarts string

@@
 
-%%\begin{wrapfigure}{L}{0.6\textwidth}
-%%    \centering
-%%    \includegraphics[width=0.5\textwidth]{images/hexanexml.pdf}
-%%    \caption{XML file used by VOTCA to specify a three site coarse grain mapping of n-hexane}
-%%    \label{fig:hexanexml}
-%%\end{wrapfigure}
+\begin{wrapfigure}{L}{0.5\linewidth}
+    \centering
+    \includegraphics[width=0.6\linewidth]{images/hexanexml.pdf}
+    \caption{XML file used by VOTCA to specify a three site coarse grain mapping of n-hexane}
+    \label{fig:hexanexml}
+\end{wrapfigure}
 
@@
 \begin{lstlisting}
-hexane_sites = [("_A", "CC[H3]"), ("_B", "CC")]
+hexane_sites = [("_A", "C[CH3]"), ("_B", "CC")]
 \end{lstlisting}
-The result of using this code in the `coarse` function %%<link to grits> is a three-site hexane model A-B-A, same as VOTCA.
+The result of using this code in the `coarse` function is a three-site hexane model A-B-A, same as VOTCA.%%<link to grits>
 The mapping here is specified as a list of bead name / smarts string pairs.
 Although they do add some element of cognitive load, SMARTS strings are designed to be human and machine readable and can match atoms based on their chemical environment.
-With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (CC) requiring that one be a terminal carbon by including that it has three attached hydrogens (C[H3]).
+With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (using the SMARTS string "CC") and requiring that one be a terminal carbon by including that it has three attached hydrogens ("[CH3]").
+The order of the beads here matters--because technically all atoms could be mapped with the more general SMARTS string (CC), it is important to list the most specific strings first.
 The bonding and angles of the resulting coarse grain beads is then inferred based on the bonding of the mapped atoms.

### 2020-08-17 hexane.tex
update hexane images, tex file to generate small pdf

\documentclass[8pt]{extarticle}

\usepackage[paperwidth=90mm]{geometry}

%PUT YOUR MACROS HERE
\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,language=xml,aboveskip=3mm,belowskip=3mm,showstringspaces=false,columns=flexible,basicstyle={\small\ttfamily},numbers=none,numberstyle=\tiny\color{gray},keywordstyle=\color{blue},commentstyle=\color{dkgreen},stringstyle=\color{mauve},breaklines=true,breakatwhitespace=true,tabsize=4}

\begin{document}

\lstinputlisting{hexane.xml}

\end{document}

### 2020-08-17 2pd.tex
fixing citations

@@
 This early device had a PCE of 0.95\%.
-In 1992, Saricifti and Heeger were the first to report using fullerene as an electron acceptor in a fullerene:polymer mixture\cite{Saricifti1992}.
+In 1992, Saricifti and Heeger were the first to report using fullerene as an electron acceptor in a fullerene:polymer mixture\cite{Sariciftci1992}.
 And in 1995, Yu described the first bulk heterojunction (BHJ), as an interpenetrating network of donor and acceptor that maximizes the interfacial area, which is still the state of the art morphology to this day\cite{Yu1995}.
-Most recently, non-fullerene acceptors (NFAs), like ITIC, are contributing to the PCE increase of modern OPVs\cite{S.Gurney2019}.
+Most recently, non-fullerene acceptors (NFAs), like ITIC, are contributing to the PCE increase of modern OPVs\cite{S.Gurney2019b}.
 
@@
 
-The planar acceptor-donor-acceptor moeity seen in many NFA backbones (see Figure \ref{fig:itic}) may have more efficient exciton splitting, as compared to a fullerene acceptor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer\cite{Yi2018}.
+The planar acceptor-donor-acceptor moeity seen in many NFA backbones (see Figure \ref{fig:itic}) may have more efficient exciton splitting, as compared to a fullerene acceptor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer\cite{Yi2018a}.
 
@@
 Simply grouping hydrogens with the heavy atom they are bonded to, called the united-atom model, has been shown to speed up dynamics and make polymer length scales more easily accesible\cite{Paul1995a, Yang2006a}.
-Other coarse-graining schemes may group functional groups together\cite{Berendsen2010, Jankowski2013, Marsh2014}, one bead per repeat unit in a polymer\cite{Lee2011}, or even represent an entire amino acid with a single site\cite{Peng2019a}.
+Other coarse-graining schemes may group functional groups together\cite{Berendsen2010, Jankowski2013, Marsh2014}, one bead per repeat unit in a polymer\cite{Lee2011}, or even represent an entire amino acid with a single site\cite{Peng2019}.
 %%<examples of cg models and the cool things they do>
@@
 There have been efforts to create mapping schemes for automating the process of deciding which atoms are grouped in a "super-atom" bead.
-One study reduced the number of allowed mappings by only allowing those which do not change the symmetry group, then iterated over a graph of all possible mappings to find the "best" mapping by comparing the difference between the mapped RDF and velocity autocorrelation function\cite{Chakraborty2018a}.
+One study reduced the number of allowed mappings by only allowing those which do not change the symmetry group, then iterated over a graph of all possible mappings to find the "best" mapping by comparing the difference between the mapped RDF and velocity autocorrelation function\cite{Chakraborty2018b}.
 Another mapping scheme uses principle component analysis to choose a mapping scheme for biomolecules that best represents th essential dynamics\cite{Zhang2008}.
@@
 %%<IBI>
-IBI is where a coarse grain potential is iteratively tuned to fit a target distribution\cite{Reith2003a}.
+IBI is where a coarse grain potential is iteratively tuned to fit a target distribution\cite{Reith2003}.
 Here is the algorithm for determining the non-bonded potentials:
@@
 In the following example we will take a hexane molecule and map it to three coarse grain sites (two carbon atoms per site).
+
+\begin{wrapfigure}{L}{0.5\linewidth}
+    \centering
+    \includegraphics[width=0.6\linewidth]{images/hexane-compare.pdf}
+    \caption{top: hexane chemical structure, bottom: hexane overlaid with coarse grain mapping \textcolor{blue}{A}-\textcolor{orange}{B}-}\textcolor{blue}{A}
+    \label{fig:hexane}
+\end{wrapfigure}
+
 VOTCA uses an xml file to do this:

### 2020-08-17 2pd.tex
more citation fixing

@@
 We do not propose a new automated mapping, but instead a way to make the mapping and backmapping process easier for the user.
-Simplified Molecular Input Line Entry System or SMILES was designed to represent organic molecules in an unambiguous way (similar to IUPAC) but in a line-entry system which is also readable by a computer\cite{Weininger}.
+Simplified Molecular Input Line Entry System or SMILES was designed to represent organic molecules in an unambiguous way (similar to IUPAC) but in a line-entry system which is also readable by a computer\cite{Weininger1988}.
 This makes it a good candidate for specifying a coarse-grain mapping scheme.The open-source package, Openbabel, allows for a SMILES string to be converted to a chemical structure and vice versa.

### 2020-08-17 2pd.tex
writing about past work

@@
 \section*{Preliminary Work}
+My prior work has involved probing the intermolecular interactions which govern dimer and crystal formation.
 % With lan - About excitonic splitting, using DFT, DNA. 
+Using density functional theory (DFT) to probe the excitonic splitting observed in cyanine dye dimers\cite{Fothergill2018}.
+
 % With Matt - What intermolecular interactions guide diphenylurea crystal formation
+An investigation of the supramolecular interactions which guide crystal self-assembly in diphenylurea transition metal complexes using density functional theory\cite{Millard2019a}. 
 % With us - Perspective paper about all things
+My contributions to our perspective paper were mostly about my experience joining the lab and trying to reproduce and existing model--something which should be very straightforward in a computational field, but which any computational scientist can attest is not simple\cite{Jankowski2019}.
+ %% frame gixstapose as a tool for reproducible, approachable science
+I also presented a tool I've developed, called GIXStapose, at the Scientific Python conference (SciPy2020). %%cite scipy and gixstapose
+GIXStapose is an interactive structure viewer alongside its simulated diffraction pattern.
+This work had two goals: helping users to see the connections between a structure and it's diffraction pattern and making reproducible figure generation easier.
+The first goal is achieved through a graphical user interface (GUI) which allows users to interact with the structure using the mouse and the diffraction pattern is updated automatically.
+The second goal is accomplished by allowing all steps of the figure generation process (e.g., positioning the camera, setting the colors and lighting, etc) to be scripted and never \testit{requiring} use of the GUI.
+
+These prior works, although not directly related to OPVS or coarse grain models, have helped me think about how atomic interactions can shape a structure, the struggles that face a new computational scientist, and how I can help.
 
 %%<how do I relate this to what I want to do??>
-- contributed to development of open-source packages: mbuild, foyer, signac, fresnel
- this has helped me learn best software development practices like writing documentation, using version control, writing unit tests, employing CI, fork/pull model, etc.
-using these tools will help me to me a more efficient developer.
-It's also helped me to learn how to work as part of a team.
- - created MWE of coarse-graining and backmapping with smiles-- these will need further testing as we try them on different compounds but the proof of concept is there.
- - created tutorial examples to help current and future students understand scientific concepts and how to use computational tools
- %% frame gixstapose as a tool for reproducible, approachable science
- - created GIXStapose (presented at SciPy2020) an interactive diffraction/structure viewer.
-This may seem unrelated but we can use diffraction to verify our opv morphologies and compare them to experiment.
-GIXStapose helps to beeter connect the physical structure with the diffraction pattern.
-- started development on UFF repo for foyer.
-This is an example of how to create a version controlled forcefield which can be automatically applied to a compound.
+I have contributed to development of open-source packages: mbuild, foyer, signac, fresnel
+These contributions have given me ample opportunity to excercise best software development practices like writing good documentation, using version control, writing unit tests, employing CI, using a fork \& pull workflow, etc.
+This experience will help me to be more efficient in my future work.
+I've also gained valuable experience as working as part of a team.
+As I plan to integrate my future work with existing projects, good collaborate skills will be necessary.
+
+%% experience teaching and creating material for people to learn
+I have completed Software Carpentry training which has taught me how to break down complex ideas and give learners a chance to use their knowledge.
+With these principles in mind, I have created tutorial examples to help current and future students understand scientific concepts and how to use computational tools. %% cite notebook examples
+%%- started development on UFF repo for foyer.
+%%This is an example of how to create a version controlled forcefield which can be automatically applied to a compound.
 %%<atom typing is a pain and doing it manually is bad cite foyer paper>
+As for work towards my proposed plan, I have created a minimum working example of a coarse-graining and backmapping package which uses SMARTS strings to specify the bead chemistries. %%cite grits
+This package will need further testing as it is tested on different compounds, but the proof of concept exists.
 

### 2020-08-18 2pd.tex
fix typo. update library

@@
 The first goal is achieved through a graphical user interface (GUI) which allows users to interact with the structure using the mouse and the diffraction pattern is updated automatically.
-The second goal is accomplished by allowing all steps of the figure generation process (e.g., positioning the camera, setting the colors and lighting, etc) to be scripted and never \testit{requiring} use of the GUI.
+The second goal is accomplished by allowing all steps of the figure generation process (e.g., positioning the camera, setting the colors and lighting, etc) to be scripted and never \textit{requiring} use of the GUI.
 

### 2020-08-18 2pd.tex
adding md explanation and fig

@@
 %EJ: Here or above: Why MD the right tool?
-%% morphology matters - thermodynamics that govern self assembly
-%% the kinetics that follow the processing
-%% we can see the dynamics -- kinetic arresting, (if we want to probe the processing, need the dynamics)
-%% monte carlo inefficient for polymers - cluster moves, not parallelizable 
-%%<I am borrowing heavily from Mike's MD section, so I need to come back through and rewrite this>
+Molecular dynamics (MD) is a simulation tool which uses classical physics and statistical thermodynamics to sample the equilibrium states of a thermodynamic ensemble.
+It is the right tool for looking at the bulk structure of an OPV because we can simultaneously probe the thermodynamics which govern OPV self assembly and the kinetics that follow the device processing.
+Other tools, like Monte Carlo (MC), may allow us to sample equilibrium states of an ensemble, but we would lose information about the dynamics.
+MC is also inefficient for polymers because perturbing a long chain of particles requires a "cluster move", which is not parallelizable.
+
 %%<md in general>
-classical physics
-interactions between particles
-non bonded/bonded/angles/dihedrals
+MD separates the interactions between particles into non-bonded interactions and bond, angle, dihedral interactions.
+Non-bonded interactions are commonly modelled with a Lennard-Jones potential.
+$$ U_{LJ}(r_{i,j}) = 4\epsilon\big[\big(\frac{\sigma}{r_{i,j}}\big)^{12}-\big(\frac{\sigma}{r_{i,j}}\big)^{6}\big]$$
+Where $i$ and $j$ are the particles separated by distance $r_{i,j}$.
+The equilibrium distance between particles is controlled by $\sigma$ and the depth of the potential well is controlled by $\epsilon$ (see Figure \ref{fig:lj}).
+
+\begin{wrapfigure}{L}{0.5\linewidth}
+    \centering
+    \includegraphics[width=0.6\linewidth]{images/lj.pdf}
+    \caption{The Lennard-Jones potential with relevant distances labelled}
+    \label{fig:lj}
+\end{wrapfigure}
+
 integrates Newton's equations of motion to update the particle positions.

### 2020-08-18 2pd.tex
added bond angle dihedral figure

@@
 Molecular dynamics (MD) is a simulation tool which uses classical physics and statistical thermodynamics to sample the equilibrium states of a thermodynamic ensemble.
-It is the right tool for looking at the bulk structure of an OPV because we can simultaneously probe the thermodynamics which govern OPV self assembly and the kinetics that follow the device processing.
+The MD algorithm integrates Newton's equations of motion to update the particle positions.
+This process can be iterated until the system reaches equilibrium.
+MD is the right tool for looking at the bulk structure of an OPV because we can simultaneously probe the thermodynamics which govern OPV self assembly and the kinetics that follow the device processing.
 Other tools, like Monte Carlo (MC), may allow us to sample equilibrium states of an ensemble, but we would lose information about the dynamics.
@@
 The equilibrium distance between particles is controlled by $\sigma$ and the depth of the potential well is controlled by $\epsilon$ (see Figure \ref{fig:lj}).
+A distance cutoff, $r_{cut}$, is often used to reduce the number of pairwise interactions and improve performance.
 
@@
 
-integrates Newton's equations of motion to update the particle positions.
-iterated until thermodynamic equilibrium
-sample a thermodynamic ensemble
-First MD simulation system of 108 particles, 200 collisions in one hour on an IBM-704\cite{Alder1957}.
-Now GPUs 100 millions times faster
+Particles connected by bonds are also modelled by classical forces, for example the bond potential may be treated as a harmonic oscillator:
+
+\begin{wrapfigure}{L}{0.5\linewidth}
+    \centering
+    \includegraphics[width=0.6\linewidth]{images/bondangledihedral.pdf}
+    \caption{Bonded interactions: bond (top left), angle (top right), and dihedral (bottom). Image taken from \cite{punma}.
+    \label{fig:bad}
+\end{wrapfigure}
+
+$$V_{bond}(r) = \frac{1}{2}k(r-r_{0})^{2}$$
+Where $r$ is the bond length, $r_{0}$ is the equilibrium bond length, and $k$ is the spring constant for the bond.
+The angle potential is also treated as a harmonic oscillator:
+$$V_{angle}(\theta)=\frac{1}{2}k(\theta-\theta_{0})^{2}$$
+Where $\theta$ is the angle formed between three bonded particles, $\theta_{0}$ is the equilibrium angle, and $k$ is the spring contant for the angle.
+The dihedral potential can be defined by the follow Fourier series:
+$$V_{dihedral}(\phi)=\frac{1}{2}k_{1}(1-cos(\phi))+\frac{1}{2}k_{2}(1-cos(2\phi))+\frac{1}{2}k_{3}(1-cos(3\phi))\frac{1}{2}k_{4}(1-cos(4\phi))$$
+Where $\phi$ is the angle between planes formed by particles in the dihedral (see Figure \ref{fig:bad}) and $k_{n}$ are the force coeffients.
+
+The first MD simulation modelled a system of 108 particles, and completed 200 collisions in one hour on an IBM-704\cite{Alder1957}.
+Now GPUs are 100 millions times faster
 %%<what is MD used for? why is MD the best technique for gettign these OPV morphologies?>

### 2020-08-18 2pd.tex
fixed close }
good stopping point for md -- v rough

@@
     \centering
-    \includegraphics[width=0.6\linewidth]{images/bondangledihedral.pdf}
-    \caption{Bonded interactions: bond (top left), angle (top right), and dihedral (bottom). Image taken from \cite{punma}.
+    \includegraphics[width=0.4\linewidth]{images/bondangledihedral.pdf}
+    \caption{Bonded interactions: bond (top left), angle (top right), and dihedral (bottom). Image adapted from \cite{punma}.}
     \label{fig:bad}
@@
 Where $\phi$ is the angle between planes formed by particles in the dihedral (see Figure \ref{fig:bad}) and $k_{n}$ are the force coeffients.
-
+%% transition???
 The first MD simulation modelled a system of 108 particles, and completed 200 collisions in one hour on an IBM-704\cite{Alder1957}.
-Now GPUs are 100 millions times faster
+Now GPUs are 100 millions times faster.
 %%<what is MD used for? why is MD the best technique for gettign these OPV morphologies?>
-protein folding \cite{levitt75}, other biological processes, polymers \cite{Gartner2019a}
+Due to its efficient scaling, MD is now commonly used for modelling of protein folding \cite{levitt75} and other biological processes, and investigating the bulk properties of polymers \cite{Gartner2019a}.
 
 %%<what assumptions does md make?>
-bonds aren't formed or broken, electrons don't exist
-hydrogen bonding
-dispersion is tricky--electrons don't slosh around unless you use some fancy many-body potential
+Even all-atom MD is not without assumptions:
+In general, during an MD simulation bonds aren't formed or broken, so without careful consideration this prevents the study of chemical reactions.
+MD does not consider electrons, instead atoms are treated as point particles. 
+This makes modelling systems which depend on hydrogen bonding or dispersion more difficult.
+
 %%<what are the limits of atomistic md?>
+Even with these simplifications, we are still not able to simulate many systems efficiently on relevant length scales.
+Therefore we can use a technique called coarse graining to increase the length and time scale we can examine.
 %%<segue to why we need CG models>

### 2020-08-19 2pd.tex
cleaning up prior works

@@
 %%<how do I relate this to what I want to do??>
-I have contributed to development of open-source packages: mbuild, foyer, signac, fresnel
+I have contributed to development of open-source packages including mbuild, foyer, signac, and fresnel. %%cite
 These contributions have given me ample opportunity to excercise best software development practices like writing good documentation, using version control, writing unit tests, employing CI, using a fork \& pull workflow, etc.
@@
 I've also gained valuable experience as working as part of a team.
-As I plan to integrate my future work with existing projects, good collaborate skills will be necessary.
+As I plan to integrate my future work with existing projects, good collaborative skills will be necessary.
 
@@
 %%<atom typing is a pain and doing it manually is bad cite foyer paper>
+
 As for work towards my proposed plan, I have created a minimum working example of a coarse-graining and backmapping package which uses SMARTS strings to specify the bead chemistries. %%cite grits
 This package will need further testing as it is tested on different compounds, but the proof of concept exists.
-
 %%<Talk about what exists and why it is not enough>
 %%<votca, Peng2019a> 
-Versatile Object-oriented Toolkit for Coarse-graining Applications (VOTCA) \cite{Ruhle2011b}
-includes a coarse-graining, forcefield creation with reverse MC or IBI, and back-mapping modules.
-It also allows for charge transport calculations using KMC similar to MorphCT \cite{Lukyanov2010}
-
-reproducibility crisis.\cite{Cummings2019} \cite{Thompson2020} (TRUE paper) poorly documented code and raw data doesn't help.
-
-instead example workflows with docker containers to build software stack.
-help make science more accessible and reprodicible.
-
+Packages which do coarse-graining and backmapping already exist, so why is another one necessary?
+One such package, Versatile Object-oriented Toolkit for Coarse-graining Applications (VOTCA)\cite{Ruhle2011b}, includes a coarse-graining, forcefield creation with reverse MC or IBI, and back-mapping modules.
+It also allows for charge transport calculations using KMC similar to MorphCT\cite{Lukyanov2010}.
 %%<compare VOTCA's backmapping to my proposed scheme>
-VOTCA makes some progress towards a TRUE simulation pipeline: they include a docker container with their pre-built software stack and example input files  (but some of these input files don't work and the codecoverage on their repo as of time of writing is 0\%), and while including example inputs is a good first step, very little walkthrough (aside from code comments buried in the xml) is given\cite{votca-github}.
-%%using this code via docker>
-A manual is provided but there is some disconnect between the example files and those given in the manual %%<https://github.com/votca/csg-manual/releases>.
-the code is a mix of C++, shell commands, python, and interacts with compiled programs through the command-line and mpi.
-which makes their working a little tenuous.
-And judging by the amount of confusion in their mailing list %%<https://groups.google.com/forum/\#!forum/votca> there is room for improvement in the API.
-Overall though this is program has many features, interfaces with many popular MD engines (lammps, gromacs, hoomd), and is under active, collaborative development.
-A good question might be if I'm so into OSS and collaboration--why don't I just contribute an MSIBI package to VOTCA.
-This is a reasonable question.
-The answer is because I find VOTCA to be near-overwhelming in it's scope and the cognitive load of trying to fit this whole project into my brain is not ideal.
-I also don't like their API.
-by choosing a pure python API I will be able to make use of jupyter notebooks which can be run on cloud servers using tools like mybinder %%<link mybinder, link to tutorials I;ve made> which can combine executable code with markdown text and images.
+VOTCA makes some progress towards a TRUE simulation pipeline: they include a docker container with their pre-built software stack and example input files.
+However, some of these input files don't work and the unit test coverage on their examples repo at the of time of this writing is 0\%.
+While including example inputs and a prebuilt software stack via docker is a great first step, these tutorials give very little walkthrough aside from code comments buried in the xml\cite{votca-github}.
+A manual is provided but the example files and the explanation given in the manual is disconnected. %%cite <https://github.com/votca/csg-manual/releases>.
+The code is a mix of C++, shell commands, and python, and the user is required to interact with compiled programs through the command-line which makes adding this code into an existing workflow a little more difficult.
+And judging by the amount of confusion in their mailing list, there is room for improvement in the API.%% cite <https://groups.google.com/forum/\#!forum/votca>
+Overall though this project has many features, interfaces with many popular MD engines (LAMMPS, GROMACS, HOOMD), and is under active, collaborative development, it is near-overwhelming in its scope and is not designed for the new user.
+By choosing a pure python API I will be able to make use of Jupyter Notebooks which can be run on cloud servers using tools like MyBinder which can combine executable code with markdown text and images.%%<cite link mybinder, link to tutorials I;ve made>
 In this way a tutorial can provide exact commands needed to reproduce the example intimately connected with the rationale and justification of that example.
-I would like to think that my code speaks for itself, but after reading other people's code, I have a renewed appreciation for explanations in paragraph form, diagrams, and figures.
 
@@
 
-It may be easy to think that because what we are doing--mapping two carbons and their attached hydrogens to a single bead so that six alkyl carbons becomes A-B-A--that the process will also be simple.
-In order to specify a bead-mapping, we need to know the residue number, the residue name, and the atom name.
-For a six atom system this is not too bad, but this could get tedious and error-prone for larger systems.
-And keep in mind that these xml files need to be created manually for each compound which is backmapped.
-VOTCA's scheme also requires that you specify the bonding and the angles resulting from those bonds, another process which is tedious, error-prone, and probably unecessary--I will discuss this more after discussing my scheme below:
+It may be easy to think that because the goal is simple, mapping two carbons and their attached hydrogens to a single bead so that six alkyl carbons becomes three coarse grain sites (A-B-A), that the process will also be simple.
+In order to specify a bead-mapping using VOTCA, we need to know the residue number, the residue name, and the atom name.
+For a six atom system this is not too bad, but it could get tedious and error-prone for larger systems.
+And keep in mind that these xml files need to be created manually for each compound which is coarse grained or  backmapped.
+VOTCA's scheme also requires that the bonding and the angles resulting from those bonds are specified, another process which is tedious, error-prone, and probably unecessary. 
+To explain, let's discuss my proposed alternative:
 \begin{lstlisting}
@@
 The result of using this code in the `coarse` function is a three-site hexane model A-B-A, same as VOTCA.%%<link to grits>
-The mapping here is specified as a list of bead name / smarts string pairs.
+The mapping here is specified as a list of bead name SMARTS string pairs.
 Although they do add some element of cognitive load, SMARTS strings are designed to be human and machine readable and can match atoms based on their chemical environment.
-With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (using the SMARTS string "CC") and requiring that one be a terminal carbon by including that it has three attached hydrogens ("[CH3]").
-The order of the beads here matters--because technically all atoms could be mapped with the more general SMARTS string (CC), it is important to list the most specific strings first.
-The bonding and angles of the resulting coarse grain beads is then inferred based on the bonding of the mapped atoms.
+With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (in SMARTS notation a capital "C" denotes an alkyl carbon) and requiring that one be a terminal carbon by including that it has three attached hydrogens ("[CH3]").
+The order of the beads here matters because technically all the carbon atoms in hexane could be mapped with the more general SMARTS string (CC), so it is important to list the most specific strings first.
+The bonding and angles of the resulting coarse grain beads can then inferred based on the bonding of the mapped atoms.
 Basically what VOTCA's xml file does in 51 lines, I can do in 1 which is easier to read and makes chemical sense. 
 There are even benefits to the mapping being inline with the code:
-This allows the user to see the mapping as they progress through the workflow without having to search for multiple files and it may prevent common errors caused by manual file IO such as operating system specific line endings or whitespace characters like tab or space being treated differently.
+It allows the user to see the mapping as they progress through the workflow without having to search for multiple files.
+Not using an external file may prevent common errors caused by manual file IO such as operating system specific line endings or whitespace characters like tab or space being read differently by a program.
 Having the mapping in-line with the workflow also allows for the user to check that the mapping is correct with built in interactive visualizations, which can display the mapping as an overlay. 
-%%<show overlay>
+(Figure \ref{hexane-compare} is the output of one such visualization using py3Dmol.) %%cite py3Dmol
 
-We do not propose a new automated mapping, but instead a way to make the mapping and backmapping process easier for the user.
+We propose a way to make the mapping and backmapping process easier for the user.
 Simplified Molecular Input Line Entry System or SMILES was designed to represent organic molecules in an unambiguous way (similar to IUPAC) but in a line-entry system which is also readable by a computer\cite{Weininger1988}.
@@
 I have developed a minimum working example of how this can be done and then how the atomistic structure can be recovered.%%<cite grits>
-It could be fairly straightforward to implement a lookup to check if bead parameters already exist--say for the MARTINI model-- by going through and writing out the SMARTS pattern for each existing bead type.
-An initial headache that could make parameterizing new compounds for the MARTINI method more foolproof.
+%% another application?
+This mapping scheme could even be used to make the mapping process easier for established coarse grain models.
+It could be fairly straightforward to implement a lookup to check if bead parameters already exist (e.g., for the MARTINI model) by going through and writing out the SMARTS pattern for each existing bead type.
+This could make parameterizing new compounds for an existing method more foolproof.
 

### 2020-08-19 2pd.tex
got thru research plan. rough but better

@@
 %%<how cg potentials have been attained> 
+Deciding on a mapping operator is one part of creating a coarse grain model, the second step is to create an effective potential for the site.
 
@@
 % With lan - About excitonic splitting, using DFT, DNA. 
-Using density functional theory (DFT) to probe the excitonic splitting observed in cyanine dye dimers\cite{Fothergill2018}.
-
+An investigation of the excitonic splitting observed in cyanine dye dimers was done using density functional theory (DFT)\cite{Fothergill2018}.
+By comparing calculated with experimental absorption spectra it was found that the solvent may play a large role in the dimer formation and peak shifting.
 % With Matt - What intermolecular interactions guide diphenylurea crystal formation
-An investigation of the supramolecular interactions which guide crystal self-assembly in diphenylurea transition metal complexes using density functional theory\cite{Millard2019a}. 
+An investigation of the supramolecular interactions which guide crystal self-assembly in diphenylurea transition metal complexes was done using density functional theory\cite{Millard2019a}. 
 % With us - Perspective paper about all things
-My contributions to our perspective paper were mostly about my experience joining the lab and trying to reproduce and existing model--something which should be very straightforward in a computational field, but which any computational scientist can attest is not simple\cite{Jankowski2019}.
+My contributions to our perspective paper were mostly about my experience joining the lab and trying to reproduce an existing model; a task which should be very straightforward in a computational field but which any computational scientist can attest is far from simple\cite{Jankowski2019}.
  %% frame gixstapose as a tool for reproducible, approachable science
@@
 
-- I will build on existing tools (signac,freud,mbuild,foyer,tim moore's msibi)
-- create signac workflow which takes equilibrated atomistic trajectory (maybe checks if it's equilibrated?) maps the CG beads to it, runs IBI, gets tabulated FF, creates larger CG sim, runs it, does backmapping, then could do: RDF, charge transport, diffraction...
-if this workflow is streamlined--it can be applied to many different compounds allowing for us to compare the analyses between our zoo of compounds.
-- maybe the workflow could even involve getting the equilibrated trajectory (atomtyping/fill box/run) with the new hoomd 3 api we could even set decorrelation time as a stop trigger...
+My plan is to create a workflow which builds on existing tools: signac, freud, mbuild, openbabel, and a previously developed msibi package.
+This workflow could start with equilibrated atomistic trajectories from multiple statepoints, then use SMARTS strings to map the CG sites to each trajectory and calculate the effective potentials using MSIBI.
+Once we have a tabulated coarse grain force field, we can create a larger simulation using our coarse grain model.
+Finally, once we have an equilibrated coarse grain trajectory, we can using backmapping to regain the atomic positions and do analysese such as radial distribution function (RDF), charge transport, and diffraction.
+If this workflow is streamlined, it can be applied to many different compounds allowing for a high-throughput analysis of many potential OPV compounds.
 
@@
 
-build on existing tools (mbuild, openbabel, tim moores MSIBI code, hoomd, foyer?)
-use SMARTS matching to specify mapping operators with relative ease
-use MSIBI to parameterize forcefield parameters
+A minimum working example of this coarse graining workflow has been completed. %% cite grits
+However, it will still need to be tested with many more compounds and mapping operators.
+This package uses the chemical file format parsing and scriptable structure building capabilities of mbuild coupled with the SMARTS/SMILES string matching of the openbabel package to generate coarse grain structures mapped onto their atomistic counterparts with only a SMARTS string from the user.
+These coarse grain structures mapped to an atomistic target can then be used in an MSIBI workflow to obtain an effective potential.
+I have made a minimum working example of an MSIBI workflow; %https://bitbucket.org/cmelab/msibi_tests/src/master/ do i even mention this?
+although this was useful to me in getting a better understanding for the MSIBI process, I think for future, I will build off an existing MSIBI code. %%https://github.com/mosdef-hub/msibi
+The force field obtained using MSIBI will be used to run a large CG simulation.
+The end product of this first objective will be to obtain equilibrated CG trajectories.
 
@@
 
-Given an equilibrated CG morphology, retrieve the atomistic one by mapping the SMARTS structures onto the position of the CG beads and then relaxing them with some position restraint.
+Given an equilibrated CG trajectory, we can reintroduce the atomistic degrees of freedom by using the same SMARTS mappings used for coarse graining.
+The chemistries specified by the SMARTS strings will be mapped onto the centers of the CG sites and then equilibrated in a short MD run using the atomistic force field with addition position restraint.
+I have developed a minimum working example of this backmapping process, %% cite grits
+however, the specification of how the backmapped atomistic structures are bonded is still not intuitive for the user to specify and I am not sure yet how to make it better.
 
@@
 
-use signac to organize data
-I think there are not great CG models for these compounds (ITIC PTB7) I found this paper \cite{Meng2019} that claims to do CGMD with PTB7 ITIC but the details are hidden in the SI and seem fishy.
+Once Objectives 1 and 2 are complete, the next step will be putting them to use to investigate new OPV compounds.
+Currently, I have not found CG models for many NFA compounds (e.g, ITIC).
+%% I found this paper \cite{Meng2019} that claims to do CGMD with PTB7 ITIC but the details are hidden in the SI and seem fishy.
 seems like they use IBI but they dont say how they got their target distributions.
-can easily test out different mappings and "processing" conditions
+A simple, useable coarse graining tool will be helpful for determining the best mapping operator to use for these OPV compounds.
+To help organize the dataspace of the large parameter sweep, I plan to use the signac package to manage an ever-changing workspace.
+This will help easily and efficiently test out different mappings and "processing" conditions.
 
@@
 
-Use charge transfer, diffraction to tell which models are the best
-%%<cite a bunch of experimental papers we can compare to>
-%%<cite our papers that show we can do this comparison already>
-Our morphct paper says the mobilities we predict are 2x higher than experiment? why?
-
+Our lab has shown that we have the capability to compare our simulation results to experiment using hole mobilities from charge transport calculations\cite{Jones2017,Miller2018a} and grazing incedent X-ray scattering (GIXS) patterns\cite{Miller2018}.
+GIXS calculations on our backmapped trajectories can be used to validate that our simulations result in the same morphology as experiment.
+While charge transport calculations can be used to rate the efficacy of the active layer morphology.
+Using our lab's charge transport package (MorphCT) on new chemistries, however, will require some work.
+Many of the parameters and the definition of the chromophore are hard-coded for poly-3-hexylthiophene (P3HT).
+Moving this package away from a command line interface will also be a goal of this work.
+%%Our morphct paper says the mobilities we predict are 2x higher than experiment? why?
 %%<I need something in here about making morphct more user friendly and less hard-coded for p3ht.>

### 2020-08-19 2pd.tex
added moore figure

@@
 When using the MS IBI method, it is important to choose dissimilar states to minimize the potential overlap region.
-If this overlap region is large, there are many potentials which will provide matching RDFs. %%<show fig from moore>
+If this overlap region is large, there are many potentials which will provide matching RDFs.
+
+\begin{wrapfigure}{L}{0.5\linewidth}
+    \centering
+    \includegraphics[width=0.6\linewidth]{images/moorefig.pdf}
+    \caption{Visualization of the state space coverage of different potentials: if the thermodynamic states are too similar (b), then the overlap region is large enough that there are many potentials which will fit the target.
+Choosing states which are different (a) will better define the potential.
+Image taken from ref \cite{Moore2014}.}
+    \label{fig:lj}
+\end{wrapfigure}
+
 For some systems there may not be a potential that represents all states-- this is not unique to coarse potentials, atomistic potentials also have this limitation.

### 2020-08-20 2pd.tex
all words are sentences in english now

@@
 
-- understanding coarse graining (i'm stealing this from mike because I like it) how coarse is too coarse? for these new systems what is the minimal model which can reproduce the structural features
-- understanding the interactions which guide BHJ self assembly. understanding which functionalizations/processing conditions make best morphology
-- are smarts strings viable for use as mappings? where does using smarts strings break down?
-- does making science easier/more understandable make it better?
+As a result of this work, we expect the following outcomes:
+
+\begin{enumerate}
+    \item {\textbf{Gain insight into the limits of coarse-graining}}
+        This work will probe the limits of coarse graining to understand the minimal model necessary to represent different OPV chemistries.
+    \item {\textbf{Understand the interactions which guide BHJ self assembly}} 
+        This work will test a variety of different OPV compounds. 
+        Comparing the results may provide understanding into which moeities, intermolecular interactions, or processing conditions result in the morphology with the highest charge transport.
+    \item {\textbf{Understand the mapping operator}}
+        This work will test whether using a chemical string format (SMARTS/SMILES) to specify the atomistic to coarse grain site mapping is a viable alternative to other methods. 
+        Using SMARTS/SMILES strings allows a user to more easily and intuitively specify a mapping.
+        If specifying a mapping is easier, a user may be more willing to try out a greater number of different mappings.
+        This would allow for the comparison of a system parameterized with different mapping operators.
+    \item {\textbf{Benefits of Transferrable, Reproducible, Usable, Extensible research}} %%what am i trying to say here?
+        Does making science easier/more understandable make it better? %more reproducible? curb cuts
+        If parameterizing a coarse grain force field is easier and more approachable, it would open up more possibilities for trying different mapping schemes or different structural or thermodynamic targets rather than sticking to an existing force field.
+        Better coarse grain models could result in more accurate and efficient simulation of large length scale systems.
+\end{enumerate}
 
@@
 %%<what's going to be hard?> 
-maybe SMARTS SMILES won't work without careful choice of beads.
-This is a little annoying but still preferrable I think because at least the reasons may be understandable (the order of the beads matters) or chemically sensible (one SMILES string may contain another -- just as one chemical moeity may be composed of more submoeities %%<this is a word?>)
-coarse-graining NFAs might be hard--planar backbones and floppy side chains
+Although minimum working examples have been developed for botht the coarse graining and backmapping packages, I still expect to struggle when mapping new compounds.
+Sometimes the SMARTS/SMILES mapping won't work without careful choice of beads.
+This can be a little frustrating but is still preferrable to having to manually specify the mapping of each atom.
+At least the reasons that a SMARTS mapping fails are usually understandable (e.g., the order of the beads matters) or chemically sensible (e.g., one SMILES string may contain another -- just as one chemical moeity may be composed of more submoeities).
+%%<this is a word?>)
+
+It may also be difficult to find a good coarse graining scheme for the NFA compounds. 
+These compounds are often composed of large planar backbones with floppy side chains.
+Finding a suitable mapping to represent both aspects may be difficult.
 

### 2020-08-20 checkbibs.py
update library
* update checkbibs with when to use it bc i keep forgetting

@@ -11,6 +11,12 @@ def main():
     """I'm always worried that Mendeley is losing my papers.
     This script is to give me some peace of mind that
     my bibs aren't disappearing before I commit the new bib file.
+
+    usage:
+        first do
+            $cp library-link.bib library.bib
+        then
+            $python checkbibs.py
     """
     command = ["git", "diff", "library.bib"]
     p = sp.run(command, capture_output=True)

### 2020-08-20 2pd.tex
read out loud to mesoscale device sims

@@
 Harnessing solar energy is an important part of a green energy solution.
-Renewable energy accounts for 11\% of the U.S. energy consumption in 2019 and of that 11\% 9\% was solar\cite{USEIA2020}.
+Renewable energy accounted for 11\% of the U.S. energy consumption in 2019 and of that 9\% was from solar (solar accounted for approximately 1\% of the total energy)\cite{USEIA2020}.
 Our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar\cite{Wirth2017}.
-Traditionally, photovoltaic devices, materials which can convert incedent light into electric current, were made of inorganic materials like silicon.
+Traditionally, photovoltaic devices, which can convert incedent light into electric current, were made of inorganic materials like silicon.
 But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative\cite{Tang1986b}.
 The advantage of OPVs over inorganic PV devices is that OPVs are lightweight, low cost, easier to produce, and flexible. 
-However, in order to become a viable, cost-effective option they need better efficiency\cite{Mazzio2015}.
+OPVs can be manufactured large scale in a roll to roll printing process, similar to newspaper as shown in Figure \ref{fig:doufig}\cite{Dou2013}.
+\begin{wrapfigure}{L}{0.5\linewidth}
+    \centering
+    \includegraphics[width=0.6\linewidth]{images/doufig.pdf}
+    \caption{Schematic showing roll to roll printing process for OPVs (left) and example OPV device (right). Image adapted from ref \cite{Dou2013}.}
+    \label{fig:doufig}
+\end{wrapfigure}
+However, other devices still outperform OPVs (see Figure \ref{fig:nrel}) and in order to become a viable, cost-effective option OPVs need to be more efficient\cite{Mazzio2015}.
 
@@
     \includegraphics[width=0.9\linewidth]{images/NREL2020.pdf}
-    \caption{Efficiencies of photovoltaic technologies from 1976 to present.
-OPVS are denoted by red filled circles.
+    \caption{Efficiencies of all photovoltaic technologies from 1976 to present.
+OPVs are denoted by red filled circles.
 The current state-of-the-art research cell achieves 17.4\% efficiency.
-Image taken from ref \cite{NREL2020}}
+Image taken from ref \cite{NREL2020}.}
     \label{fig:nrel}
@@
 In order to make the most efficient OPVs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
-
 The active layer of an OPV is mixture of electron-donor and acceptor compounds: the ideal morphology is a micro phase-separated interpenetrating network called a bulk heterojunction (BHJ).
 The performance of an OPV device is intimately linked with the structure of the active layer:
-With minor modifcations, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
+With minor modifications, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
+
 Imagine, you are a chemist synthesizing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor, \textit{3,9-bis(2-ethylene-(3-(1,1-dicyanomethylene)-indanone))-5,5,11,11-tetrakis(4-hexylphenyl)-dithieno(2,3-d:2',3'-d')-s-indaceno(1,2-b:5,6-b')dithiophene} (\textbf{ITIC}), and a polymer donor, \textit{poly((4,8-bis((2ethylhexyl)oxy)benzo(1,2-b:4,5-b')dithiophene-2,6-diyl)(3-fluoro-2-((2-ethylhexyl)carbonyl)thieno(3,4-b)thiophenediyl))} (\textbf{PTB7}).
@@
 All this would be to determine the performance of just one donor/acceptor combination in one category of potential compounds\cite{Dou2013}.
+This is where molecular simulation can help.
 By using a simulation pipeline, we can help to streamline the process of determining which OPV materials will form the best morphology with the best charge transport, and in turn, help to solve the energy crisis.
@@
 These existing codebases can appear to a new user as monolithic and indecipherable because their design has been to solve a problem, which they do, instead of design with a focus on how people learn.
-These codebases also rely on users piecing together multiple, often incompatible, bits of software, using manually created xml files, or manually deciding how to classify a atom grouping based on the users chemical intuition.
-All of which contribute to a reproducibility crisis in the computational sciences\cite{Baker2016}.
+These codebases also rely on users piecing together multiple, often incompatible, bits of software, using manually created xml files, or deciding how to classify an atom grouping based on the user's chemical intuition.
+All of these factors contribute to a reproducibility crisis in the computational sciences\cite{Baker2016}.
 By keeping best practices for software development and teaching in mind throughout development, we can strive to make tools which make science more transferrable, reproducibile, usable, and extensible (TRUE)\cite{Thompson2020}.
@@
 Instead of writing dense, inseparable scripts which rely on the user manually following a command prompt or editing multiple text files, we aim to keep code small and modular to make it easier to use and understand\cite{Adorf2018a}.
-Following these guidelines not only makes our code easier to develop and debug, but reduces the cognitive load for a new user\cite{Jankowski2019}.
+Following these guidelines not only makes our code easier to develop and debug but also reduces the cognitive load for a new user\cite{Jankowski2019}.
 Providing good documentation and tutorials is also imperative for onboarding new users.
@@
 
-Use flexible method for specifying coarse grain models to obtain OPV polymer morphologies equilibrated on length scales relevant to charge transport.
-Use a backmapping method, which works on the same simple mapping operator, to restore the atomic positions in preparation for techniques which require atomic level resolutiuon e.g., charge transport calculations.
-This two step process is necessary because starting with the fully atomistic structure would not only be computationally inefficient the result may even be less accurate due to the difficulties of equilibrating polymers\cite{Gartner2019a}.
+For this research we propose to develop a flexible method for specifying coarse grain models to obtain OPV polymer morphologies equilibrated on length scales relevant to charge transport.
+We also propose to develop a backmapping method, which works on the same simple mapping operator, to restore the atomic positions in preparation for techniques which require atomic level resolutiuon e.g., charge transport calculations.
+This two step process is necessary because starting with the fully atomistic structure would not only be computationally inefficient but also the result may even be less accurate due to the difficulties of equilibrating polymers\cite{Gartner2019a}.
 This efficiency is important because the scope of potential OPV compounds is vast and the energy crisis necessitates expediency.
-The number of opv compounds to test quickly becomes intractable when we consider that the power conversion efficiency is strongly linked to minor chemical modifications or functionalization, device processing, and the interplay between donor and acceptor\cite{Mazzio2015,Swick2019a}.
-There are countless variations of electron donor polymers, fullerene acceptors, and more recently small molecule, non-fullerene acceptors (NFAs) have been recieving attention for their potential to achieve higher efficiencies\cite{Dou2013}.
-A P3HT:NFA blend was shown to have 11\% PCE, compared to the state-of-the-art 6.4\% in P3HT:PCBM\cite{Baran2017}.
+The number of OPV compounds to test quickly becomes intractable when we consider that the power conversion efficiency is strongly linked to minor chemical modifications or functionalization, device processing, and the interplay between donor and acceptor\cite{Mazzio2015,Swick2019a}.
+There are countless variations of electron donor polymers, fullerene acceptors, and more recently small molecule, non-fullerene acceptors (NFAs) have been recieving attention for their potential to achieve higher efficiencies than their fullerene counterparts\cite{Dou2013}.
+A poly-3-hexylthiophene (P3HT):NFA blend was shown to have 11\% PCE, compared to the state-of-the-art 6.4\% in P3HT:PCBM\cite{Baran2017}.
 Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70-80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h)\cite{Baran2017}.
@@
 Ultimately the goal this research is to help solve the global energy crisis. 
-Solar energy is a important part of a green energy solution.
+Solar energy is an important part of a green energy solution.
 This research aims to gain insight about new OPV compound morphologies using molecular simulation.
@@
 In order to model these OPV polymer systems on relevant length scales, it is necessary to develop new coarse grain models.
-A flexible and efficient coarse graining scheme will simplify the process of mapping and parameterizing (these coarse grain elements). %% reword
+A flexible and efficient coarse graining scheme will simplify the process of mapping and parameterizing these coarse grain elements. %% reword?
 
@@
 
+The performance of an OPV device can be quantified by many metrics.
 %% <what is PCE>
@@
 %% <history>
-Inorganic PV devices came first and are still most efficient, but they are more costly to produce, use rare elements, and their production causes other environmental issues, so they aren't the best solution for solar energy harvesting.
+Inorganic PV devices came first and are still the most efficient, but they are more costly to produce, use rare elements, and their production causes other environmental issues, so they aren't the best solution for solar energy harvesting.
 The first OPV was created by Tang in 1986 and used a bilyaer structure containing copper phthalocyanine and a perylene derivitive\cite{Tang1986b}. 
 This early device had a PCE of 0.95\%.
-In 1992, Saricifti and Heeger were the first to report using fullerene as an electron acceptor in a fullerene:polymer mixture\cite{Sariciftci1992}.
+In 1992, Sariciftci and Heeger were the first to report using a fullerene as an electron acceptor in a fullerene:polymer mixture\cite{Sariciftci1992}.
 And in 1995, Yu described the first bulk heterojunction (BHJ), as an interpenetrating network of donor and acceptor that maximizes the interfacial area, which is still the state of the art morphology to this day\cite{Yu1995}.
@@
 These changes in structure can strongly affect the device performance.
-Molecular simulation allows us to "see" these atomic interaction and gain a deeper view into the driving forces behind the self assembly of these OPV morphologies and to understand what conditions create the best devices.
+Molecular simulation allows us to "see" these atomic interactions and gain a deeper view into the driving forces behind the self assembly of these OPV morphologies and to understand what conditions create the best devices.
 %%<segue into simulation>
@@
 %%<md in general>
-MD separates the interactions between particles into non-bonded interactions and bond, angle, dihedral interactions.
-Non-bonded interactions are commonly modelled with a Lennard-Jones potential.
+MD separates the interactions between particles into non-bonded interactions and bond, angle, and dihedral interactions.
+Non-bonded interactions are commonly modelled with a Lennard-Jones potential:
 $$ U_{LJ}(r_{i,j}) = 4\epsilon\big[\big(\frac{\sigma}{r_{i,j}}\big)^{12}-\big(\frac{\sigma}{r_{i,j}}\big)^{6}\big]$$
@@
 Where $\phi$ is the angle between planes formed by particles in the dihedral (see Figure \ref{fig:bad}) and $k_{n}$ are the force coeffients.
+
 %% transition???
-The first MD simulation modelled a system of 108 particles, and completed 200 collisions in one hour on an IBM-704\cite{Alder1957}.
-Now GPUs are 100 millions times faster.
+The first MD simulation modelled a system of 108 particles and completed 200 collisions in one hour on an IBM-704\cite{Alder1957}.
+Now GPUs are a 100 millions times faster.
 %%<what is MD used for? why is MD the best technique for gettign these OPV morphologies?>
-Due to its efficient scaling, MD is now commonly used for modelling of protein folding \cite{levitt75} and other biological processes, and investigating the bulk properties of polymers \cite{Gartner2019a}.
+Due to its efficient scaling, MD is now commonly used for the modelling of protein folding \cite{levitt75} and other biological processes, and investigating the bulk properties of polymers\cite{Gartner2019a}.
+By abstracting away some of the atomic degrees of freedom, MD can be used to look at even larger systems. %%transition attempt
 
@@
 %%<what are the limits of atomistic md?>
-Even with these simplifications, we are still not able to simulate many systems efficiently on relevant length scales.
-Therefore we can use a technique called coarse graining to increase the length and time scale we can examine.
+Even with the simplifications of MD, we are still not able to simulate many systems efficiently on relevant length scales.
+Therefore we can use a technique called coarse graining to increase the length and time scales we can examine.
 %%<segue to why we need CG models>
@@
 
-Coarse-graining refers to grouping atoms in a structure into a "super-atom" and using an effective potential to represent the resulting coarse grain site.
-Coarse-grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models.
+Coarse graining refers to grouping atoms in a structure into a "super-atom" and using an effective potential to represent the resulting coarse grain site.
+Coarse grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models by abstracting away irrelevant degrees of freedom.
 %%<how do cg models let us access long length/time??>
@@
 Even if the simulation was to complete, there would be too much information to process accurately. 
-CGing allows scientists to FOCUS their experiments\cite{Baschnagel2000}.
+Coarse graining allows scientists to \textit{focus} their experiments\cite{Baschnagel2000}.
+
 The resolution of coarse grain systems is broad:
@@
 %%<examples of cg models and the cool things they do>
-General coarse grain models of opv thiophene polymers where only the spacing, regioregularity of the side chains were varied were able to predict different order disorder transitions and calculated scattering patterns of these simple systems were comparable to those obtained from experiment\cite{Jankowski2013, Marsh2014}.
-A coarse-grain model for phospholipids has allowed for bilayer formation from an initial random configuration to be observed even though the model was parameterized to the vapor-liquid phase transition\cite{Shelley2001}.
+General coarse grain models of OPV thiophene polymers where only the spacing and regioregularity of the side chains were varied were able to predict order disorder transitions and scattering patterns comparable to those obtained from experiment\cite{Jankowski2013, Marsh2014}.
+A coarse grain model for phospholipids has allowed for bilayer formation from an initial random configuration to be simulated even though the model was parameterized to the vapor-liquid phase transition\cite{Shelley2001}.
+%% transition?
 Which model is right depends on the length and time scale on which the property of interest can be observed.
+
 %%<multiscale sims>
 For many systems, however, we are interested in properties which span length scales.
-For instance, in a system like a opv polymer melt, it is not only computationally intractable to try and simulate the electron density on length scales proportional to the exciton dissociation length (~5-10 nm)\cite{Huang2010} -- it is the wrong tool for the job.
+For instance, in a system like a OPV polymer melt, it is not only computationally intractable to try and simulate the electron density on length scales proportional to the exciton dissociation length (~5-10 nm)\cite{Huang2010}; it is the wrong tool for the job.
 If what we are interested in is the properties of the polymer in the bulk heterojunction, then it is wise to abstract away any degrees of freedom which do not directly contribute to the self-assembly of the structure.
-Once a good bulk structure has been achieved, the atomistic details can be reintegrated much more easily--a process called backmapping.
+Once a good bulk structure has been achieved, the atomistic details can be reintegrated much more easily: a process called backmapping.
 In the same way that a coarse grain model can be mapped onto an atomistic one, we can get a reasonable starting structure for an atomistic simulation from a coarse grain structure.
 The large length scale, polymer level properties can be equilibrated during the coarse grain simulation, and then the atomic interactions can be equilibrated during the backmapped atomistic simulation.
-This can allow us the calculate properties such as charge transport, which depends upon the electronic structure of individual chromophores and the connectivity of these chromophores over distances proportional to the exciton dissociation length.
+This can allow us the calculate properties such as charge transport, which depends upon the electronic structure of individual chromophores \textit{and} the connectivity of these chromophores over distances proportional to the exciton dissociation length.
 %%<what stands in our way?>
@@
 Part of coarse graining that is not yet automated is choosing a mapping scheme or a mapping operator.
-A mapping operator defines which atoms are grouped into a "super atom" represented by one coarse grain site and where in the site is placed relative to the atom group.
-Mapping operators are chosen based on desired resolution of the coarse grain system and the information to be extracted.
-A straightforward way to define a mapping operator is to group a set number of heavy atoms (non hydrogen) together--this is the method used in the MARTINI force field\cite{Marrink2007}.
+A mapping operator defines which atoms are grouped into a "super atom" represented by one coarse grain site and where the site is placed relative to the atom group.
+Mapping operators are chosen based on the desired resolution of the coarse grain system and the information to be extracted.
+A straightforward way to define a mapping operator is to group a set number of heavy atoms (non hydrogen) together; this is the method used in the MARTINI force field\cite{Marrink2007}.
 In this scheme, four atoms (except rings, which are treated differently) are grouped and the site is classified as polar, non-polar, apolar, or charged depending on the atoms it is composed of.
-When parameterizing a new molecule you must pick a mapping and then compare the resulting beads to existing beads--a process which is time consuming and error prone\cite{martini-tutorial}.
-The MARTINI force field was first designed for lipids--further parameterization for proteins and nuclei acids have been added--and has shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.%%<cite
-Many mapping schemes are simply based on the user's chemical intuition (e.g., what parts of the molecule shouldn't be allowed to bend?
-What groups have the most dominant interactions in this structure %%<cite any model where rings are one bead><cite dna cg model>).
+When parameterizing a new molecule, you must pick a mapping and then compare the resulting beads to existing beads; a process which is time consuming and error prone\cite{martini-tutorial}.
+%%The MARTINI force field was first designed for lipids, further parameterization for proteins and nuclei acids has since been added, and it has been shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.%%<cite
+Many other mapping schemes are simply based on the user's chemical intuition (e.g., what parts of the molecule shouldn't be allowed to bend?
+What groups have the most dominant interactions in this structure).
+%%<cite any model where rings are one bead><cite dna cg model>).
 As the number of atoms in the fine grain structure increases, the number of possible mappings increase drastically.
-There have been efforts to create mapping schemes for automating the process of deciding which atoms are grouped in a "super-atom" bead.
+There have been efforts to create algorithms for automating the process of deciding which atoms are grouped in a "super-atom" bead.
 One study reduced the number of allowed mappings by only allowing those which do not change the symmetry group, then iterated over a graph of all possible mappings to find the "best" mapping by comparing the difference between the mapped RDF and velocity autocorrelation function\cite{Chakraborty2018b}.
-Another mapping scheme uses principle component analysis to choose a mapping scheme for biomolecules that best represents th essential dynamics\cite{Zhang2008}.
+Another uses principle component analysis to choose a mapping scheme for biomolecules that best represents th essential dynamics\cite{Zhang2008}.
 Mapping operators can be automated using machine learning: clustering methods combined with graph analysis were shown to predict the "expert" mapping chosen using chemical intuition reliably\cite{Li2020}.
 A mapping operator based on the centers of charge was shown to accurately model electrostatic properties\cite{Cao2015a}.
-
 %%<how cg potentials have been attained> 
@@
 Taking the Boltzmann Inverse of the RDF results in the potential of mean force (PMF). %%<add equation>
+%% equation
 Then a CG simulation can be run using the PMF as the non-bonded potential to achieve a new distribution.
@@
 The TraPPE force-field fits CG potentials using vapor-liquid equilibria to improve transferrability across thermodynamic states\cite{Maerzke2011}.
-But optimization to the liquid-vapor equilibriai, although useful for prediction of thermodynamic properties, may not be ideal for prediction of structure which will strongly influence charge transport.
+But optimization to the liquid-vapor equilibrium, although useful for prediction of thermodynamic properties, may not be ideal for prediction of structure which will strongly influence charge transport.
 %%<so we probably want to create our own potentials>
@@
 
-For some systems there may not be a potential that represents all states-- this is not unique to coarse potentials, atomistic potentials also have this limitation.
+For some systems there may not be a potential that represents all states; this is not unique to coarse potentials, atomistic potentials also have this limitation.
 %%<need some tie in back to why we would want to go from CG-->atomistic>

### 2020-08-20 2pd.tex
skimmed through rest. need more time before I can look at last sections

@@
 The HOMO levels of each chromophore site and the energy splitting induced in the chromophore pairs is used in the Marcus equation to calculate the charge hopping rate between pairs.
-A Monte Carlo simulation can then be run using these hopping rates.
-Because this is a quantum chemical calculation, the position of each atom is needed--therefore a backmapping process is required to calculate the charge transport in a CG morphology.
-MorphCT has some builtin backmapping tools which use xml file (which i will discuss why these are bad in the next section) and the package is bulky/CLI/hard-to-use...
+A Monte Carlo simulation can then be run using these hopping rates to calculate the movement of charges through the system.
+Because this is a quantum chemical calculation, the position of each atom is needed; therefore, a backmapping process is required to calculate the charge transport in a coarse grain morphology.
+%% MorphCT has some built in backmapping tools which use an xml file, but  (which i will discuss why these are bad in the next section) and the package is bulky/CLI/hard-to-use...
 %%<making morphct more modular to allow it to be used in a workflow not cli>
@@
 \section*{Preliminary Work}
+
 My prior work has involved probing the intermolecular interactions which govern dimer and crystal formation.
@@
 The second goal is accomplished by allowing all steps of the figure generation process (e.g., positioning the camera, setting the colors and lighting, etc) to be scripted and never \textit{requiring} use of the GUI.
-
 These prior works, although not directly related to OPVS or coarse grain models, have helped me think about how atomic interactions can shape a structure, the struggles that face a new computational scientist, and how I can help.

### 2020-08-21 1summ.tex
minor edits to summary

@@
 
-Already the effects of human-influenced climate change are %%<hurtng everyone in particular poor and disadvantaged groups>.
+Already the effects of human-influenced climate change are readily apparent and devastating. %%<hurtng everyone in particular poor and disadvantaged groups>.
 Burning fossil fuels for energy is the main contributor to rising $CO_{2}$ levels, and the energy demand is only increasing.
-This increase in energy demand along with the need to protect our precious climate makes finding efficient, renewable energy technologies of the utmost importance.
-Harvesting the abundant solar energy is a %%<good solution because it is renewable, non-polluting, sustainable>.
+This increase in energy demand along with the need to protect our climate makes finding efficient, renewable energy technologies of the utmost importance.
+Harvesting the abundant solar energy is a good solution because it is renewable, non-polluting, sustainable.
 Devices which convert light to electricity, called photovoltaics, were originally made of silicon and required rare elements and careful, clean-room processing.
@@
 The compounds and polymers used in OPVs are made of common elements and can be synthesized with relative ease.
-And the OPV BHJ can often be assembled using simple techniques like roll-to-roll printing in ambient conditions.
+And the OPV BHJ can often be assembled using simple techniques like roll to roll printing in ambient conditions.
 The process for OPV to generate electricity is as follows: 
@@
 Then we can use kinetic monte carlo (KMC) in concert with quantum chemical calculations (QCCs) to determine the charge mobility through these simulated morphologies.
-By understanding how charge move through these systems, one can predict which OPVs will be most efficient.
+By understanding how charges move through these systems, one can predict which OPVs will be most efficient.
 However, this simulation workflow suffers from a problem of length scales:
@@
 Coarse grain (CG) models, which group multiple atoms together into "super atoms" and using an effective potential to specify the forces acting upon the site, can be used to access length and time scales more relevant to the bulk polymer morphology.
-After a bulk morphology is obtained, we can use backmapping, a process in which the atomistic detail can be reintegrated into a coarse grain model, can be used to restore atomistic detail for use in simulations like KMC/QCC.
-This multiscale simulation workflow allows for OPV morphologies to be equilibrated at length scales relevant to the bulk polymer and to regain the atomistic detail necessary later and from a better starting structure.
+After a bulk morphology is obtained, we can use backmapping, a process in which the atomistic detail can be reintegrated into a coarse grain model, to restore atomistic detail for use in simulations like KMC/QCC.
+This multiscale simulation workflow allows for OPV morphologies to be equilibrated at length scales relevant to the bulk polymer and to regain the atomistic detail more efficiently using a better starting structure.
 Currently software packages exist that do this but they require tedious manual input and are highly susceptible to user error.

### 2020-08-21 2pd.tex
updated the opv fig

@@
 Consumption of fossil fuels for energy and transportation strongly contributes to atmospheric $CO_2$ the affects of which are global, long-term, and devastating\cite{Solomon2009a}.
+%% should I put examples? fires https://science2017.globalchange.gov/chapter/8/
 In our technology-driven society, it is unrealistic to think that energy demand will lessen, in fact global energy consumption is predicted to increase from 17 TW in 2010 to 27 TW in 2040\cite{Mazzio2015}.
@@
 The advantage of OPVs over inorganic PV devices is that OPVs are lightweight, low cost, easier to produce, and flexible. 
-OPVs can be manufactured large scale in a roll to roll printing process, similar to newspaper as shown in Figure \ref{fig:doufig}\cite{Dou2013}.
+OPVs can be manufactured large scale in a roll to roll printing process, similar to newspaper as shown in Figure \ref{fig:opv} a\cite{Dou2013}.
 \begin{wrapfigure}{L}{0.5\linewidth}
     \centering
-    \includegraphics[width=0.6\linewidth]{images/doufig.pdf}
-    \caption{Schematic showing roll to roll printing process for OPVs (left) and example OPV device (right). Image adapted from ref \cite{Dou2013}.}
-    \label{fig:doufig}
+    \includegraphics[width=0.6\linewidth]{images/dou-miller2018c-fig.pdf}
+    \caption{Schematic showing (a) roll to roll printing process for OPVs, (b) example OPV device, (c) bulk heterojunction structure, and (d) OPV energy generation process.
+Part (a) adapted from ref \cite{Dou2013}.
+Parts (b)-(d) adapted from ref \cite{Miller2018c}.}
+    \label{fig:opv}
 \end{wrapfigure}
-However, other devices still outperform OPVs (see Figure \ref{fig:nrel}) and in order to become a viable, cost-effective option OPVs need to be more efficient\cite{Mazzio2015}.
+However, other materials still outperform OPVs (see Figure \ref{fig:nrel}) and in order to become a viable, cost-effective option OPVs need to be more efficient\cite{Mazzio2015}.
 
@@
 OPVs are denoted by red filled circles.
-The current state-of-the-art research cell achieves 17.4\% efficiency.
+The current state-of-the-art OPV research cell achieves 17.4\% efficiency.
 Image taken from ref \cite{NREL2020}.}
@@
 
-In order to make the most efficient OPVs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
-The active layer of an OPV is mixture of electron-donor and acceptor compounds: the ideal morphology is a micro phase-separated interpenetrating network called a bulk heterojunction (BHJ).
+In order to make the most efficient OPVs we need to find the blend of compounds and processing conditions that result in the best structure for those compounds.
+The active layer of an OPV is mixture of electron-donor and acceptor compounds: the ideal morphology is a micro phase-separated interpenetrating network called a bulk heterojunction (BHJ) (see Figure \ref{fig:opv} c).
 The performance of an OPV device is intimately linked with the structure of the active layer:

### 2020-08-21 2pd.tex
notes from boss -- fixing objectives

@@
 The global climate crisis is one of the most pressing issue humanity faces today.
+\begin{wrapfigure}{l}{0.5\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{images/dou-miller2018c-fig.pdf}
+    \caption{Schematic showing (a) roll to roll printing process for OPVs, (b) example OPV device, (c) bulk heterojunction structure, and (d) OPV energy generation process.
+Part (a) adapted from ref \cite{Dou2013}.
+Parts (b)-(d) adapted from ref \cite{Miller2018c}.}
+    \label{fig:opv}
+\end{wrapfigure}
 Consumption of fossil fuels for energy and transportation strongly contributes to atmospheric $CO_2$ the affects of which are global, long-term, and devastating\cite{Solomon2009a}.
@@
 The advantage of OPVs over inorganic PV devices is that OPVs are lightweight, low cost, easier to produce, and flexible. 
-OPVs can be manufactured large scale in a roll to roll printing process, similar to newspaper as shown in Figure \ref{fig:opv} a\cite{Dou2013}.
-\begin{wrapfigure}{L}{0.5\linewidth}
-    \centering
-    \includegraphics[width=0.6\linewidth]{images/dou-miller2018c-fig.pdf}
-    \caption{Schematic showing (a) roll to roll printing process for OPVs, (b) example OPV device, (c) bulk heterojunction structure, and (d) OPV energy generation process.
-Part (a) adapted from ref \cite{Dou2013}.
-Parts (b)-(d) adapted from ref \cite{Miller2018c}.}
-    \label{fig:opv}
-\end{wrapfigure}
+OPVs can be manufactured large scale in a roll to roll printing process, similar to newspaper as shown in \autoref{fig:opv} a\cite{Dou2013}.
 However, other materials still outperform OPVs (see Figure \ref{fig:nrel}) and in order to become a viable, cost-effective option OPVs need to be more efficient\cite{Mazzio2015}.
@@
 \end{figure}
-
+%% TODO
+%% opvs are vast
+%% crystalline silicon levels off -- shottkey quessar (sp?) limit 34% efficient not much room for growth (blue)
+%% what you can buy vs champion devices
+%% opvs show room to grow
+%% paying for themselves
+%%underdog
 In order to make the most efficient OPVs we need to find the blend of compounds and processing conditions that result in the best structure for those compounds.
@@
 
-Imagine, you are a chemist synthesizing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor, \textit{3,9-bis(2-ethylene-(3-(1,1-dicyanomethylene)-indanone))-5,5,11,11-tetrakis(4-hexylphenyl)-dithieno(2,3-d:2',3'-d')-s-indaceno(1,2-b:5,6-b')dithiophene} (\textbf{ITIC}), and a polymer donor, \textit{poly((4,8-bis((2ethylhexyl)oxy)benzo(1,2-b:4,5-b')dithiophene-2,6-diyl)(3-fluoro-2-((2-ethylhexyl)carbonyl)thieno(3,4-b)thiophenediyl))} (\textbf{PTB7}).
+% TODO
+%% include fig of ITIC PTB7? p3ht, fullerene recent uptick with NFAs
+%% look up the 17% solar cell--whats in it?
+%% freedom in choosing our ingredients - can we get better than trial and error
+Imagine, you are a chemist synthesizing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor, ITIC, and a polymer donor, PTB7. 
 Each compound costs \$500 for 100 mg\cite{sigmaaldrich}.
@@
 
+%% make better opvs
+%% need to get a morphology on relevant lengthscale
+%% many different chemistries
+%% need a model that get a cg model from a chemistry
+
 My plan is to create a workflow which builds on existing tools: signac, freud, mbuild, openbabel, and a previously developed msibi package.
@@
 
-\subsection*{Objective 1: Develop a coarse graining workflow}
-
-A minimum working example of this coarse graining workflow has been completed. %% cite grits
+%% Objectives are like steps along the way
+%% objectives should be
+% 1. goal of the step
+% 2. how to do the step
+% how doing this achieves the goal
+%% how to coarse grain reproducibly
+\subsection*{Objective 1: Develop a generalized toolset for coarse graining and performing simulations of novel molecules for organic photovoltaics}
+% mapping
+% ff creation
+% infrastructure: porting ff to engine
+In order to model the morphologies of new OPV chemistries, we need a simple way to generate novel coarse grain models.
+This objective consists of three steps:
+\begin{enumerate}
+    \item {Create a tool that uses a mapping operator to go from atomistic to coarse grain structure}
+    \item {Use the mapped coarse grain structure to parameterize a force field using MSIBI}
+    \item {Develop the infrastructure to port this force field to a simulation engine}
+\end{enumerate}
+A minimum working example of this coarse grain mapping tool has been completed. %% cite grits, cg-tutorial
 However, it will still need to be tested with many more compounds and mapping operators.
@@
 These coarse grain structures mapped to an atomistic target can then be used in an MSIBI workflow to obtain an effective potential.
-I have made a minimum working example of an MSIBI workflow; %https://bitbucket.org/cmelab/msibi_tests/src/master/ do i even mention this?
-although this was useful to me in getting a better understanding for the MSIBI process, I think for future, I will build off an existing MSIBI code. %%https://github.com/mosdef-hub/msibi
-The force field obtained using MSIBI will be used to run a large CG simulation.
-The end product of this first objective will be to obtain equilibrated CG trajectories.
+A minimum working example of an MSIBI tool has also been started; %https://bitbucket.org/cmelab/msibi_tests/src/master/ do i even mention this?
+although the hands-on experience with MSIBI was useful to me in getting a better understanding for the process, I think for future, I will build off an existing MSIBI code.
+%%https://github.com/mosdef-hub/msibi
+The force field obtained using MSIBI will then be used to run a simulation of a novel coarse grain model.
+Therefore decisions about how to carry the forcefield information into a simulation engine will need to be made.
+Here we will focus on HOOMD, but transferrability among simulation engines will be a goal.
+The coarse graining workflow will be considered complete when it can be used to coarse grain a test set of 25 common OPV chemistried. % 25 is just in there as a random number
+% workflow is complete when we can cg these chemistries
+% use ff in different sim engines
 
-\subsection*{Objective 2: Develop a backmapping workflow}
+\subsection*{Objective 2: Develop a general tool to retrieve atomistic information from a coarse grain morphology}
 
-Given an equilibrated CG trajectory, we can reintroduce the atomistic degrees of freedom by using the same SMARTS mappings used for coarse graining.
-The chemistries specified by the SMARTS strings will be mapped onto the centers of the CG sites and then equilibrated in a short MD run using the atomistic force field with addition position restraint.
+In order to calculate the charge transport of a coarse grain OPV system, we need to be able to regain the atomic positions.
+Given an equilibrated coarse grain trajectory, we can reintroduce the atomistic degrees of freedom by using the same SMARTS mappings used for coarse graining.
+The chemistries specified by the SMARTS strings will be mapped onto the centers of the CG sites and then equilibrated in a short MD run using the atomistic force field with an additional position restraint to maintain the structure.
 I have developed a minimum working example of this backmapping process, %% cite grits
 however, the specification of how the backmapped atomistic structures are bonded is still not intuitive for the user to specify and I am not sure yet how to make it better.
+The backmapping workflow will be considered complete when it can backmap a test set of 25 common OPV chemistries from all possible mappings.
 
-\subsection*{Objective 3: Run CG simulation sweep of non-fullerene acceptor blends}
+\subsection*{Objective 3: Predict nanostructure of novel OPV chemistries}
 
@@
 
-\subsection*{Objective 4: Analysis}
+% predict nanostructure of new opv blends TODO new objective?
+% do math -- how long will it take me to graduate? how many sims can i do?
+
+\subsection*{Objective 4: Analysis} % calulcate mobilities compare structural properties to experiment
+% identify chemical features correlated to robust mobilities
 

### 2020-08-25 2pd.tex
new image for nrel data
* added SQ limit citation

*needs more work
added recent opv papers
fixing up figure positioning etc

@@
 %%<why do opvs matter>
-The global climate crisis is one of the most pressing issue humanity faces today.
 \begin{wrapfigure}{l}{0.5\linewidth}
@@
 Parts (b)-(d) adapted from ref \cite{Miller2018c}.}
-    \label{fig:opv}
+    \label{opv}
 \end{wrapfigure}
+
+The global climate crisis is one of the most pressing issue humanity faces today.
 Consumption of fossil fuels for energy and transportation strongly contributes to atmospheric $CO_2$ the affects of which are global, long-term, and devastating\cite{Solomon2009a}.
@@
 The advantage of OPVs over inorganic PV devices is that OPVs are lightweight, low cost, easier to produce, and flexible. 
-OPVs can be manufactured large scale in a roll to roll printing process, similar to newspaper as shown in \autoref{fig:opv} a\cite{Dou2013}.
-However, other materials still outperform OPVs (see Figure \ref{fig:nrel}) and in order to become a viable, cost-effective option OPVs need to be more efficient\cite{Mazzio2015}.
+OPVs can be manufactured large scale in a roll to roll printing process, similar to newspaper as shown in \autoref{opv} a\cite{Dou2013}.
+However, other materials still outperform OPVs (see \autoref{nrel}) and in order to become a viable, cost-effective option OPVs need to be more efficient\cite{Mazzio2015}.
 
 \begin{figure}[h!]
-    \includegraphics[width=0.9\linewidth]{images/NREL2020.pdf}
-    \caption{Efficiencies of all photovoltaic technologies from 1976 to present.
-OPVs are denoted by red filled circles.
+    \includegraphics[width=\linewidth]{images/NREL2020.pdf}
+    \caption{Comparision of efficiencies organic and silicon photovoltaic technologies from 1990 to present.
 The current state-of-the-art OPV research cell achieves 17.4\% efficiency.
-Image taken from ref \cite{NREL2020}.}
-    \label{fig:nrel}
+Data taken from \cite{NREL2020}.}
+    \label{nrel}
 \end{figure}
+
+\cite{Lin2019} 17.4 \% efficiency mixing polymer fullerene device with transition metal disulfide.
+\cite{Cui2019} champion solar cell chlorinated NFA 16.5\% efiiciency
+%% new figure
 %% TODO
@@
 In order to make the most efficient OPVs we need to find the blend of compounds and processing conditions that result in the best structure for those compounds.
-The active layer of an OPV is mixture of electron-donor and acceptor compounds: the ideal morphology is a micro phase-separated interpenetrating network called a bulk heterojunction (BHJ) (see Figure \ref{fig:opv} c).
+The active layer of an OPV is mixture of electron-donor and acceptor compounds: the ideal morphology is a micro phase-separated interpenetrating network called a bulk heterojunction (BHJ) (see \autoref{opv} c).
 The performance of an OPV device is intimately linked with the structure of the active layer:
@@
 %% freedom in choosing our ingredients - can we get better than trial and error
+\cite{Cui2019}
+chlorinated ladder backbone acceptor 16\% PCE 
+%% https://www.printedelectronicsworld.com/articles/15405/raynergy-new-world-record-on-certified-pce-13-28-single-junction-opv
+signle junction with NFA
+
 Imagine, you are a chemist synthesizing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor, ITIC, and a polymer donor, PTB7. 
@@
 %% <what is PCE>
-The power conversion efficiency (PCE or sometimes $\eta_{e}$) is the ratio of electrical power produced by the device over the power of incedent photons.
+The power conversion efficiency (PCE or sometimes $\eta_{e}$) is the ratio of electrical power produced by the device to the power of incedent photons.
 Higher PCE means the device is more efficient.  
@@
 
-\begin{wrapfigure}{L}{0.5\linewidth}
+\begin{wrapfigure}{l}{0.5\linewidth}
     \centering
-    \includegraphics[width=0.6\linewidth]{images/ITIC.pdf}
+    \includegraphics[width=\linewidth]{images/ITIC.pdf}
     \caption{ITIC chemical structure with \textcolor{red}{electron accepting regions in red} and \textcolor{blue}{electron donating regions in blue}}
-    \label{fig:itic}
+    \label{itic}
 \end{wrapfigure}
 
-The planar acceptor-donor-acceptor moeity seen in many NFA backbones (see Figure \ref{fig:itic}) may have more efficient exciton splitting, as compared to a fullerene acceptor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer\cite{Yi2018a}.
+The planar acceptor-donor-acceptor moeity seen in many NFA backbones (see \autoref{itic}) may have more efficient exciton splitting, as compared to a fullerene acceptor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer\cite{Yi2018a}.
 
@@
 %%<md in general>
-MD separates the interactions between particles into non-bonded interactions and bond, angle, and dihedral interactions.
+MD separates the interactions between particles into non-bonded interactions and bond, angle, and dihedral interactions (see \autoref{bad}).
+
+\begin{wrapfigure}{L}{0.5\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{images/bondangledihedral.pdf}
+    \caption{Bonded interactions: bond (top left), angle (top right), and dihedral (bottom). Image adapted from \cite{punma}.}
+    \label{bad}
+\end{wrapfigure}
+
 Non-bonded interactions are commonly modelled with a Lennard-Jones potential:
@@
 Where $i$ and $j$ are the particles separated by distance $r_{i,j}$.
-The equilibrium distance between particles is controlled by $\sigma$ and the depth of the potential well is controlled by $\epsilon$ (see Figure \ref{fig:lj}).
+The equilibrium distance between particles is controlled by $\sigma$ and the depth of the potential well is controlled by $\epsilon$ (see \autoref{lj}).
 A distance cutoff, $r_{cut}$, is often used to reduce the number of pairwise interactions and improve performance.
 
-\begin{wrapfigure}{L}{0.5\linewidth}
+\begin{wrapfigure}{l}{0.5\linewidth}
     \centering
-    \includegraphics[width=0.6\linewidth]{images/lj.pdf}
+    \includegraphics[width=\linewidth]{images/lj.pdf}
     \caption{The Lennard-Jones potential with relevant distances labelled}
-    \label{fig:lj}
+    \label{lj}
 \end{wrapfigure}
@@
 Particles connected by bonds are also modelled by classical forces, for example the bond potential may be treated as a harmonic oscillator:
-
-\begin{wrapfigure}{L}{0.5\linewidth}
-    \centering
-    \includegraphics[width=0.4\linewidth]{images/bondangledihedral.pdf}
-    \caption{Bonded interactions: bond (top left), angle (top right), and dihedral (bottom). Image adapted from \cite{punma}.}
-    \label{fig:bad}
-\end{wrapfigure}
-
 $$V_{bond}(r) = \frac{1}{2}k(r-r_{0})^{2}$$
@@
 $$V_{dihedral}(\phi)=\frac{1}{2}k_{1}(1-cos(\phi))+\frac{1}{2}k_{2}(1-cos(2\phi))+\frac{1}{2}k_{3}(1-cos(3\phi))\frac{1}{2}k_{4}(1-cos(4\phi))$$
-Where $\phi$ is the angle between planes formed by particles in the dihedral (see Figure \ref{fig:bad}) and $k_{n}$ are the force coeffients.
+Where $\phi$ is the angle between planes formed by particles in the dihedral (see \autoref{bad}) and $k_{n}$ are the force coeffients.
 
@@
 When using the MS IBI method, it is important to choose dissimilar states to minimize the potential overlap region.
-If this overlap region is large, there are many potentials which will provide matching RDFs.
+If this overlap region is large, there are many potentials which will provide matching RDFs (see \autoref{moore}).
 
-\begin{wrapfigure}{L}{0.5\linewidth}
+\begin{wrapfigure}{l}{0.5\linewidth}
     \centering
-    \includegraphics[width=0.6\linewidth]{images/moorefig.pdf}
+    \includegraphics[width=\linewidth]{images/moorefig.pdf}
     \caption{Visualization of the state space coverage of different potentials: if the thermodynamic states are too similar (b), then the overlap region is large enough that there are many potentials which will fit the target.
@@
 Image taken from ref \cite{Moore2014}.}
-    \label{fig:lj}
+    \label{moore}
 \end{wrapfigure}
@@
 The first goal is achieved through a graphical user interface (GUI) which allows users to interact with the structure using the mouse and the diffraction pattern is updated automatically.
-The second goal is accomplished by allowing all steps of the figure generation process (e.g., positioning the camera, setting the colors and lighting, etc) to be scripted and never \textit{requiring} use of the GUI.
+The second goal is accomplished by allowing all steps of the figure generation process (e.g., positioning the camera, setting the colors and lighting, etc) to be scripted and never \textit{requiring} use of the GUI\@.
 These prior works, although not directly related to OPVS or coarse grain models, have helped me think about how atomic interactions can shape a structure, the struggles that face a new computational scientist, and how I can help.
@@
 
-\begin{wrapfigure}{L}{0.5\linewidth}
+\begin{wrapfigure}{l}{0.5\linewidth}
     \centering
-    \includegraphics[width=0.6\linewidth]{images/hexane-compare.pdf}
+    \includegraphics[width=\linewidth]{images/hexane-compare.pdf}
     \caption{top: hexane chemical structure, bottom: hexane overlaid with coarse grain mapping \textcolor{blue}{A}-\textcolor{orange}{B}-}\textcolor{blue}{A}
-    \label{fig:hexane}
+    \label{hexane}
 \end{wrapfigure}
@@
 
-\begin{wrapfigure}{L}{0.5\linewidth}
+\begin{wrapfigure}{l}{0.5\linewidth}
     \centering
-    \includegraphics[width=0.6\linewidth]{images/hexanexml.pdf}
+    \includegraphics[width=\linewidth]{images/hexanexml.pdf}
     \caption{XML file used by VOTCA to specify a three site coarse grain mapping of n-hexane}
-    \label{fig:hexanexml}
+    \label{hexanexml}
 \end{wrapfigure}
@@
 \end{lstlisting}
-The result of using this code in the `coarse` function is a three-site hexane model A-B-A, same as VOTCA.%%<link to grits>
+The result of using this code in the \lstinline{coarse} function is a three-site hexane model A-B-A, same as VOTCA.%%<link to grits>
 The mapping here is specified as a list of bead name SMARTS string pairs.
 Although they do add some element of cognitive load, SMARTS strings are designed to be human and machine readable and can match atoms based on their chemical environment.
-With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (in SMARTS notation a capital "C" denotes an alkyl carbon) and requiring that one be a terminal carbon by including that it has three attached hydrogens ("[CH3]").
-The order of the beads here matters because technically all the carbon atoms in hexane could be mapped with the more general SMARTS string (CC), so it is important to list the most specific strings first.
+With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (in SMARTS notation a capital \lstinline{"C"} denotes an alkyl carbon) and requiring that one be a terminal carbon by including that it has three attached hydrogens (\lstinline{"[CH3]"}).
+The order of the beads here matters because technically all the carbon atoms in hexane could be mapped with the more general SMARTS string (\lstinline{"CC"}), so it is important to list the most specific strings first.
 The bonding and angles of the resulting coarse grain beads can then inferred based on the bonding of the mapped atoms.
@@
 Having the mapping in-line with the workflow also allows for the user to check that the mapping is correct with built in interactive visualizations, which can display the mapping as an overlay. 
-(Figure \ref{hexane-compare} is the output of one such visualization using py3Dmol.) %%cite py3Dmol
+(\autoref{hexane-compare} is the output of one such visualization using py3Dmol.) %%cite py3Dmol
 
@@
 My plan is to create a workflow which builds on existing tools: signac, freud, mbuild, openbabel, and a previously developed msibi package.
-This workflow could start with equilibrated atomistic trajectories from multiple statepoints, then use SMARTS strings to map the CG sites to each trajectory and calculate the effective potentials using MSIBI.
+This workflow could start with equilibrated atomistic trajectories from multiple statepoints, then use SMARTS strings to map the CG sites to each trajectory and calculate the effective potentials using MSIBI\@.
 Once we have a tabulated coarse grain force field, we can create a larger simulation using our coarse grain model.
@@
     \resizebox{\columnwidth}{!}{
-%\resizebox{\textwidth}{!}
-    %\centering
         \renewcommand{\arraystretch}{1.1}
-    \begin{tabular}{| c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c |}
+        \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
             \hline
-        \multirow{2}{*}{PROJECT TASK}& \multicolumn{4}{c}{YEAR 1} &  \multicolumn{4}{|c}{YEAR 2} & \multicolumn{4}{|c}{YEAR 3} & \multicolumn{4}{|c|}{YEAR 4} & \multicolumn{4}{c|}{YEAR 5} \\ 
+            \multirow{2}{*}{PROJECT TASK}
+                &\multicolumn{4}{c}{YEAR 1}
+                &\multicolumn{4}{|c}{YEAR 2} 
+                &\multicolumn{4}{|c}{YEAR 3} 
+                &\multicolumn{4}{|c|}{YEAR 4} 
+                &\multicolumn{4}{c|}{YEAR 5} \\ 
             \hhline{~--------------------}
@@
             \hline
-           Complete Coursework & \multicolumn{10}{|c|}{ {\cellcolor{lgray}} } &  &  &  &  &  &  &  &  &  &\\
+            Complete Coursework 
+                &\multicolumn{10}{|c|}{{\cellcolor{lgray}}} &  &  &  &  &  &  &  &  &  &\\
             \hline
-           Present at a Conference  &  &  &  &  &  &  &  &  &  &  & x &  &  &  &  &  &  &  &  &\\
+            Present at a Conference  
+                & & & & & & & & & & & x & & & & & & & & &\\
             \hline
-           Publish a First Author Paper  &  &  &  &  &  & x  &  &  &  &  &  &  &  &  &  &  &  &  &  &\\
+            Publish a First Author Paper
+                & & & & & & x & & & & & & & & & & & & & &\\
             \hline
-           Proposal and Comprehensive Exam  &  &  &  &  &  &  &  &  &  &  &  & * &  &  &  &  &  &  &  &\\
+            Proposal and Comprehensive Exam
+                & & & & & & & & & & & & * & & & & & & & &\\
             \hline
-           Expand Functionality of Open Source Packages & & & & & & \multicolumn{11}{|c|}{{\cellcolor{lgray}}} & & & &\\
+            Expand Functionality of Open Source Packages 
+                & & & & & & \multicolumn{11}{|c|}{{\cellcolor{lgray}}} & & & &\\
             \hline
-           Develop Coarse Graining Package              & & & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
+            Develop Coarse Graining Package              
+                & & & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
             \hline
-           Develop Automated MS-IBI Code                & & & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
+            Develop Automated MS-IBI Code                
+                & & & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
             \hline
-           Develop Backmapping Package                  & & & & & & & & & & & & \multicolumn{5}{|c|}{{\cellcolor{lgray}}}& & & &\\
+            Develop Backmapping Package                  
+                & & & & & & & & & & & & \multicolumn{5}{|c|}{{\cellcolor{lgray}}}& & & &\\
             \hline
-           Generate Coarse-Grain Morphologies           & & & & & & & & & & & & & & \multicolumn{4}{|c|}{{\cellcolor{lgray}}}& & &\\
+            Generate Coarse-Grain Morphologies           
+                & & & & & & & & & & & & & & \multicolumn{4}{|c|}{{\cellcolor{lgray}}}& & &\\
             \hline
-           Evaluate OPV Device Performance & & & & & & & & & & & & & & \multicolumn{4}{|c|}{{\cellcolor{lgray}}} & & &\\
+            Evaluate OPV Device Performance 
+                & & & & & & & & & & & & & & \multicolumn{4}{|c|}{{\cellcolor{lgray}}} & & &\\
             \hline
-           Write Dissertation & & & & & & & & & & & & & & & &{\cellcolor{lgray}}& {\cellcolor{lgray}}& {\cellcolor{lgray}} &  &\\
+            Write Dissertation 
+                & & & & & & & & & & & & & & & &\multicolumn{3}{|c|}{{\cellcolor{lgray}}} & &\\
             \hline
-           Present Dissertation Defense  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &&  & {\cellcolor{lgray}} &  &\\
+            Present Dissertation Defense  
+                & & & & & & & & & & & & & & & & & & {\cellcolor{lgray}} &  &\\
             \hline
@@
              %&  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
-    \end{tabular}}
-    \caption{Anticipated timeline. * indicates right now, X indicates already accomplished.}
+        \end{tabular}
+    }
+    \caption{Anticipated timeline. * indicates right now, x indicates already accomplished.}
 \end{table}

### 2020-08-25 2pd.tex
*restructured moore figure
* more figure fixin

@@
 
-\begin{wrapfigure}{l}{0.5\linewidth}
+\begin{wrapfigure}{L}{0.5\linewidth}
     \centering
@@
 
-Multistate iterative Boltzmann inversion (MS IBI) includes data from multiple targets to yield a less state dependent potential\cite{Moore2014}.
-The MS IBI potential is an average of the single state potentials with a weighting function to prioritize a state of interest.
-This method has been shown to accurately reproduce the true potential in monoatomic LJ fluid.
-
-When using the MS IBI method, it is important to choose dissimilar states to minimize the potential overlap region.
-If this overlap region is large, there are many potentials which will provide matching RDFs (see \autoref{moore}).
-
 \begin{wrapfigure}{l}{0.5\linewidth}
@@
 Choosing states which are different (a) will better define the potential.
-Image taken from ref \cite{Moore2014}.}
+Image adapted from ref \cite{Moore2014}.}
     \label{moore}
@@
 
+Multistate iterative Boltzmann inversion (MS IBI) includes data from multiple targets to yield a less state dependent potential\cite{Moore2014}.
+The MS IBI potential is an average of the single state potentials with a weighting function to prioritize a state of interest.
+This method has been shown to accurately reproduce the true potential in monoatomic LJ fluid.
+When using the MS IBI method, it is important to choose dissimilar states to minimize the potential overlap region.
+If this overlap region is large, there are many potentials which will provide matching RDFs (see \autoref{moore}).
 For some systems there may not be a potential that represents all states; this is not unique to coarse potentials, atomistic potentials also have this limitation.
@@
 This package will need further testing as it is tested on different compounds, but the proof of concept exists.
+
+\begin{wrapfigure}{l}{0.5\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{images/hexane-compare.pdf}
+    \caption{Hexane chemical structure (top) overlaid with coarse grain mapping \textcolor{blue}{A}-\textcolor{orange}{B}-\textcolor{blue}{A} (bottom)}
+    \label{hexane}
+\end{wrapfigure}
+
 %%<Talk about what exists and why it is not enough>
@@
 
-\begin{wrapfigure}{l}{0.5\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{images/hexane-compare.pdf}
-    \caption{top: hexane chemical structure, bottom: hexane overlaid with coarse grain mapping \textcolor{blue}{A}-\textcolor{orange}{B}-}\textcolor{blue}{A}
-    \label{hexane}
-\end{wrapfigure}
-
 VOTCA uses an xml file to do this:
 
-%%\lstinputlisting[breaklines]{hexane.xml}
+\lstinputlisting[breaklines, basicstyle=\scriptsize\ttfamily]{hexane.xml}
 
-\begin{wrapfigure}{l}{0.5\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{images/hexanexml.pdf}
-    \caption{XML file used by VOTCA to specify a three site coarse grain mapping of n-hexane}
-    \label{hexanexml}
-\end{wrapfigure}
+%%\begin{wrapfigure}{L}{0.5\linewidth}
+%%    \centering
+%%    \includegraphics[width=\linewidth]{images/hexanexml.pdf}
+%%    \caption{XML file used by VOTCA to specify a three site coarse grain mapping of n-hexane}
+%%    \label{hexanexml}
+%%\end{wrapfigure}
 

### 2020-08-25 2pd.tex
fix all chktex errors

@@
     \centering
-    \includegraphics[width=\linewidth]{images/dou-miller2018c-fig.pdf}
+    \includegraphics[width=\linewidth]{images/dou-miller2018c-fig.pdf}\label{opv}
     \caption{Schematic showing (a) roll to roll printing process for OPVs, (b) example OPV device, (c) bulk heterojunction structure, and (d) OPV energy generation process.
-Part (a) adapted from ref \cite{Dou2013}.
-Parts (b)-(d) adapted from ref \cite{Miller2018c}.}
-    \label{opv}
+Part (a) adapted from ref~\cite{Dou2013}.
+Parts (b -- d) adapted from ref~\cite{Miller2018c}.} % chktex 8
 \end{wrapfigure}
@@
 \begin{figure}[h!]
-    \includegraphics[width=\linewidth]{images/NREL2020.pdf}
+    \includegraphics[width=\linewidth]{images/NREL2020.pdf}\label{nrel}
     \caption{Comparision of efficiencies organic and silicon photovoltaic technologies from 1990 to present.
 The current state-of-the-art OPV research cell achieves 17.4\% efficiency.
-Data taken from \cite{NREL2020}.}
-    \label{nrel}
+Data taken from~\cite{NREL2020}.}
 \end{figure}
 
-\cite{Lin2019} 17.4 \% efficiency mixing polymer fullerene device with transition metal disulfide.
-\cite{Cui2019} champion solar cell chlorinated NFA 16.5\% efiiciency
+17.4 \% efficiency mixing polymer fullerene device with transition metal disulfide\cite{Lin2019}.
+champion solar cell chlorinated NFA 16.5\% efiiciency\cite{Cui2019}. 
 %% new figure
@@
 %% opvs are vast
-%% crystalline silicon levels off -- shottkey quessar (sp?) limit 34% efficient not much room for growth (blue)
+%% crystalline silicon levels off --- shottkey quessar (sp?) limit 34% efficient not much room for growth (blue)
 %% what you can buy vs champion devices
@@
 %% include fig of ITIC PTB7? p3ht, fullerene recent uptick with NFAs
-%% look up the 17% solar cell--whats in it?
+%% look up the 17% solar cell---whats in it?
 %% freedom in choosing our ingredients - can we get better than trial and error
-\cite{Cui2019}
-chlorinated ladder backbone acceptor 16\% PCE 
 %% https://www.printedelectronicsworld.com/articles/15405/raynergy-new-world-record-on-certified-pce-13-28-single-junction-opv
@@
 A poly-3-hexylthiophene (P3HT):NFA blend was shown to have 11\% PCE, compared to the state-of-the-art 6.4\% in P3HT:PCBM\cite{Baran2017}.
-Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70-80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h)\cite{Baran2017}.
+Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70--80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h)\cite{Baran2017}.
 Coarse grain models do not yet exist for many of these NFAs, and with so many varieties an adaptable pipeline makes more sense than a single model.%%<there aren't a lot of cg models that already exist for these new compounds>
@@
     \centering
-    \includegraphics[width=\linewidth]{images/ITIC.pdf}
+    \includegraphics[width=\linewidth]{images/ITIC.pdf}\label{itic}
     \caption{ITIC chemical structure with \textcolor{red}{electron accepting regions in red} and \textcolor{blue}{electron donating regions in blue}}
-    \label{itic}
 \end{wrapfigure}
@@
 These changes in structure can strongly affect the device performance.
-Molecular simulation allows us to "see" these atomic interactions and gain a deeper view into the driving forces behind the self assembly of these OPV morphologies and to understand what conditions create the best devices.
+Molecular simulation allows us to ``see'' these atomic interactions and gain a deeper view into the driving forces behind the self assembly of these OPV morphologies and to understand what conditions create the best devices.
 %%<segue into simulation>
@@
 Other tools, like Monte Carlo (MC), may allow us to sample equilibrium states of an ensemble, but we would lose information about the dynamics.
-MC is also inefficient for polymers because perturbing a long chain of particles requires a "cluster move", which is not parallelizable.
+MC is also inefficient for polymers because perturbing a long chain of particles requires a ``cluster move'', which is not parallelizable.
 
@@
     \centering
-    \includegraphics[width=\linewidth]{images/bondangledihedral.pdf}
-    \caption{Bonded interactions: bond (top left), angle (top right), and dihedral (bottom). Image adapted from \cite{punma}.}
-    \label{bad}
+    \includegraphics[width=\linewidth]{images/bondangledihedral.pdf}\label{bad}
+    \caption{Bonded interactions: bond (top left), angle (top right), and dihedral (bottom). Image adapted from~\cite{punma}.}
 \end{wrapfigure}
@@
 Non-bonded interactions are commonly modelled with a Lennard-Jones potential:
-$$ U_{LJ}(r_{i,j}) = 4\epsilon\big[\big(\frac{\sigma}{r_{i,j}}\big)^{12}-\big(\frac{\sigma}{r_{i,j}}\big)^{6}\big]$$
+\[
+    U_{LJ}(r_{i,j}) = 4\epsilon\big[
+        {\big(\frac{\sigma}{r_{i,j}}\big)}^{12}-
+        {\big(\frac{\sigma}{r_{i,j}}\big)}^{6}
+        \big]
+\]
 Where $i$ and $j$ are the particles separated by distance $r_{i,j}$.
@@
     \centering
-    \includegraphics[width=\linewidth]{images/lj.pdf}
+    \includegraphics[width=\linewidth]{images/lj.pdf}\label{lj}
     \caption{The Lennard-Jones potential with relevant distances labelled}
-    \label{lj}
 \end{wrapfigure}
@@
 Particles connected by bonds are also modelled by classical forces, for example the bond potential may be treated as a harmonic oscillator:
-$$V_{bond}(r) = \frac{1}{2}k(r-r_{0})^{2}$$
+\[
+    V_{bond}{(r)} = \frac{1}{2}k{(r-r_{0})}^{2}
+\]
 Where $r$ is the bond length, $r_{0}$ is the equilibrium bond length, and $k$ is the spring constant for the bond.
 The angle potential is also treated as a harmonic oscillator:
-$$V_{angle}(\theta)=\frac{1}{2}k(\theta-\theta_{0})^{2}$$
+\[
+    V_{angle}{(\theta)}=\frac{1}{2}k{(\theta-\theta_{0})}^{2}
+\]
 Where $\theta$ is the angle formed between three bonded particles, $\theta_{0}$ is the equilibrium angle, and $k$ is the spring contant for the angle.
 The dihedral potential can be defined by the follow Fourier series:
-$$V_{dihedral}(\phi)=\frac{1}{2}k_{1}(1-cos(\phi))+\frac{1}{2}k_{2}(1-cos(2\phi))+\frac{1}{2}k_{3}(1-cos(3\phi))\frac{1}{2}k_{4}(1-cos(4\phi))$$
+\[
+    V_{dihedral}(\phi)=\frac{1}{2}k_{1}(1-\cos(\phi))+\frac{1}{2}k_{2}(1-\cos(2\phi))+\frac{1}{2}k_{3}(1-\cos(3\phi))\frac{1}{2}k_{4}(1-\cos(4\phi))
+\]
 Where $\phi$ is the angle between planes formed by particles in the dihedral (see \autoref{bad}) and $k_{n}$ are the force coeffients.
@@
 %%<what is MD used for? why is MD the best technique for gettign these OPV morphologies?>
-Due to its efficient scaling, MD is now commonly used for the modelling of protein folding \cite{levitt75} and other biological processes, and investigating the bulk properties of polymers\cite{Gartner2019a}.
+Due to its efficient scaling, MD is now commonly used for the modelling of protein folding~\cite{levitt75} and other biological processes, and investigating the bulk properties of polymers\cite{Gartner2019a}.
 By abstracting away some of the atomic degrees of freedom, MD can be used to look at even larger systems. %%transition attempt
@@
 
-Coarse graining refers to grouping atoms in a structure into a "super-atom" and using an effective potential to represent the resulting coarse grain site.
+Coarse graining refers to grouping atoms in a structure into a ``super atom'' and using an effective potential to represent the resulting coarse grain site.
 Coarse grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models by abstracting away irrelevant degrees of freedom.
@@
 Simply grouping hydrogens with the heavy atom they are bonded to, called the united-atom model, has been shown to speed up dynamics and make polymer length scales more easily accesible\cite{Paul1995a, Yang2006a}.
-Other coarse-graining schemes may group functional groups together\cite{Berendsen2010, Jankowski2013, Marsh2014}, one bead per repeat unit in a polymer\cite{Lee2011}, or even represent an entire amino acid with a single site\cite{Peng2019}.
+Other coarse-graining schemes may group functional groups together\cite{Berendsen2010, Jankowski2013, Marsh2014}, one site per repeat unit in a polymer\cite{Lee2011}, or even represent an entire amino acid with a single site\cite{Peng2019}.
 %%<examples of cg models and the cool things they do>
@@
 For many systems, however, we are interested in properties which span length scales.
-For instance, in a system like a OPV polymer melt, it is not only computationally intractable to try and simulate the electron density on length scales proportional to the exciton dissociation length (~5-10 nm)\cite{Huang2010}; it is the wrong tool for the job.
+For instance, in a system like a OPV polymer melt, it is not only computationally intractable to try and simulate the electron density on length scales proportional to the exciton dissociation length (~5--10 nm)\cite{Huang2010}; it is the wrong tool for the job.
 If what we are interested in is the properties of the polymer in the bulk heterojunction, then it is wise to abstract away any degrees of freedom which do not directly contribute to the self-assembly of the structure.
@@
 Part of coarse graining that is not yet automated is choosing a mapping scheme or a mapping operator.
-A mapping operator defines which atoms are grouped into a "super atom" represented by one coarse grain site and where the site is placed relative to the atom group.
+A mapping operator defines which atoms are grouped into a ``super atom'' represented by one coarse grain site and where the site is placed relative to the atom group.
 Mapping operators are chosen based on the desired resolution of the coarse grain system and the information to be extracted.
-A straightforward way to define a mapping operator is to group a set number of heavy atoms (non hydrogen) together; this is the method used in the MARTINI force field\cite{Marrink2007}.
+A straightforward way to define a mapping operator is to group a set number of heavy atoms (non hydrogen) together; this is the method used in the notable MARTINI force field\cite{Marrink2007}.
 In this scheme, four atoms (except rings, which are treated differently) are grouped and the site is classified as polar, non-polar, apolar, or charged depending on the atoms it is composed of.
-When parameterizing a new molecule, you must pick a mapping and then compare the resulting beads to existing beads; a process which is time consuming and error prone\cite{martini-tutorial}.
+When parameterizing a new molecule for the MARTINI method, a user must pick a mapping and then compare the chemical structure of the resulting sites to those which have already been parameterized; a process which is time consuming and error prone\cite{martini-tutorial}.
+The published tutorial recommends searching through existing MARTINI topologies to find similar structures and then manually editing them to fit the new molecule.
+Whether the structure is similar then is based on the user's chemical knowledge, judgement, and intuition.
 %%The MARTINI force field was first designed for lipids, further parameterization for proteins and nuclei acids has since been added, and it has been shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.%%<cite
-Many other mapping schemes are simply based on the user's chemical intuition (e.g., what parts of the molecule shouldn't be allowed to bend?
+Many other mapping schemes also rely on the user's chemical intuition (e.g., what parts of the molecule shouldn't be allowed to bend?
 What groups have the most dominant interactions in this structure).
-%%<cite any model where rings are one bead><cite dna cg model>).
+%%<cite any model where rings are one site><cite dna cg model>).
 As the number of atoms in the fine grain structure increases, the number of possible mappings increase drastically.
-There have been efforts to create algorithms for automating the process of deciding which atoms are grouped in a "super-atom" bead.
-One study reduced the number of allowed mappings by only allowing those which do not change the symmetry group, then iterated over a graph of all possible mappings to find the "best" mapping by comparing the difference between the mapped RDF and velocity autocorrelation function\cite{Chakraborty2018b}.
+There have been efforts to create algorithms for automating the process of deciding which atoms are grouped in a ``super atom''.
+One study reduced the number of allowed mappings by only allowing those which do not change the symmetry group, then iterated over a graph of all possible mappings to find the ``best'' mapping by comparing the difference between the mapped RDF and velocity autocorrelation function\cite{Chakraborty2018b}.
 Another uses principle component analysis to choose a mapping scheme for biomolecules that best represents th essential dynamics\cite{Zhang2008}.
-Mapping operators can be automated using machine learning: clustering methods combined with graph analysis were shown to predict the "expert" mapping chosen using chemical intuition reliably\cite{Li2020}.
+Mapping operators can be automated using machine learning: clustering methods combined with graph analysis were shown to predict the ``expert'' mapping chosen using chemical intuition reliably\cite{Li2020}.
 A mapping operator based on the centers of charge was shown to accurately model electrostatic properties\cite{Cao2015a}.
@@
 
+%% TODO
+%% feedback from chris: Also, in the MSIBI section you could take a paragraph or 2 to define what an RDF is, what a Boltzman inverse is, what a potential mean force is, then go into the algorithm steps.
+I feel like defining those terms in a more general sense would be a good preface to describing the actual approach/steps used in the process.
+Also, one other question that popped up is how bonds and angles between coarse beads are handled in the MSIBI step.
 There are numerous methods for deriving coarse grain potentials from atomistic ones (e.g., force-matching, reverse Monte Carlo), but in this proposal we will focus on Iterative Boltzmann Inversion (IBI).
@@
 IBI is where a coarse grain potential is iteratively tuned to fit a target distribution\cite{Reith2003}.
-Here is the algorithm for determining the non-bonded potentials:
-First the coarse grain system is mapped onto an equilibrated atomistic one.
-Then the radial distribution function (RDF) of the mapped systems is calculated over the equilibrated frames of the trajectory--This is the target distribution.
-Given any particle, the RDF gives the probability of finding a neighboring particle at distance r.
-Taking the Boltzmann Inverse of the RDF results in the potential of mean force (PMF). %%<add equation>
-%% equation
-Then a CG simulation can be run using the PMF as the non-bonded potential to achieve a new distribution.
-Then the difference between the new and target distribution can be accounted for in the next iteration accoring to equation %%<add equation>.
-This process is repeated until the difference between the result and the target are sufficiently similar.
+The radial distribution function (RDF) describes the probability of finding a particle at a given distance from another particle.
+The RDF can be used to investigate properties such as the density or the phase of a system and the RDF is used in IBI as the target distribution for the non-bonded potentials. %%reword
+The process for determining the non-bonded potentials using IBI is as follows:
+\begin{enumerate}
+    \item {The coarse grain system is mapped onto an equilibrated atomistic one.}
+    \item {The average RDF of the mapped system is calculated over the equilibrated frames of the trajectory --- this is the target distribution.}
+    \item{Taking the Boltzmann Inverse (see \autoref{pmf}) of the RDF results in the potential of mean force (PMF).
+        \begin{equation}
+            \label{pmf}
+            F(r) = -k_{B}T \ln g(r)
+            \tag{\ref{pmf}}
+        \end{equation}
+        Where $F(r)$ is the PMF, $k_{B}T$ is the thermal energy, and $g(r)$ is the target distribution.
+        Although $F(r)$ is a free-energy and not a potential energy, it is sufficient to be used as the initial potential ($V_{0}$) in the iterative scheme\cite{Reith2003}.
+        }
+    \item{A simulation can be run using \autoref{pmf} as the non-bonded potential to achieve a new distribution.}
+    \item{The difference between the new and target distribution can be accounted for in the next iteration accoring to \autoref{ibi}.
+        \begin{equation}
+            \label{ibi}
+            V_{i+1}(r) = V_{i}(r) - k_{B}T \ln\big(\frac{g_{i}(r)}{g(r)}\big)
+            \tag{\ref{ibi}}
+        \end{equation}
+        Where $g_{i}(r)$ is the distribution obtained using the potential $V_{i}(r)$.
+        }
+\end{enumerate}
+This process is repeated until the difference between the result and the target is sufficiently small.
 
@@
 This is because the RDF is a property of the ensemble average at a given statepoint, so the potential derived from this property is also limited.
-For example, separate potentials are required to capture solid and fluid structures of a pure simple lipid \cite{Hadley2010a}.
+For example, separate potentials are required to capture solid and fluid structures of a pure simple lipid~\cite{Hadley2010a}.
 There are many attempts to create transferrable CG potentials, for example:
@@
 %%<so we probably want to create our own potentials>
-%%<IBI potentials are sometimes transferrable and it is not clear why sometimes they are and sometimes they aren't.> \cite{Moore2014}
+%%<IBI potentials are sometimes transferrable and it is not clear why sometimes they are and sometimes they aren't.>~\cite{Moore2014}
 
@@
     \centering
-    \includegraphics[width=\linewidth]{images/moorefig.pdf}
+    \includegraphics[width=\linewidth]{images/moorefig.pdf}\label{moore}
     \caption{Visualization of the state space coverage of different potentials: if the thermodynamic states are too similar (b), then the overlap region is large enough that there are many potentials which will fit the target.
 Choosing states which are different (a) will better define the potential.
-Image adapted from ref \cite{Moore2014}.}
-    \label{moore}
+Image adapted from ref~\cite{Moore2014}.}
 \end{wrapfigure}
@@
 For some systems there may not be a potential that represents all states; this is not unique to coarse potentials, atomistic potentials also have this limitation.
-%%<need some tie in back to why we would want to go from CG-->atomistic>
+%%<need some tie in back to why we would want to go from CG--->atomistic>
 
@@
 
-As for work towards my proposed plan, I have created a minimum working example of a coarse-graining and backmapping package which uses SMARTS strings to specify the bead chemistries. %%cite grits
+As for work towards my proposed plan, I have created a minimum working example of a coarse-graining and backmapping package which uses SMARTS strings to specify the site chemistries. %%cite grits
 This package will need further testing as it is tested on different compounds, but the proof of concept exists.
@@
     \centering
-    \includegraphics[width=\linewidth]{images/hexane-compare.pdf}
+    \includegraphics[width=\linewidth]{images/hexane-compare.pdf}\label{hexane}
     \caption{Hexane chemical structure (top) overlaid with coarse grain mapping \textcolor{blue}{A}-\textcolor{orange}{B}-\textcolor{blue}{A} (bottom)}
-    \label{hexane}
 \end{wrapfigure}
@@
 
-It may be easy to think that because the goal is simple, mapping two carbons and their attached hydrogens to a single bead so that six alkyl carbons becomes three coarse grain sites (A-B-A), that the process will also be simple.
-In order to specify a bead-mapping using VOTCA, we need to know the residue number, the residue name, and the atom name.
+It may be easy to think that because the goal is simple, mapping two carbons and their attached hydrogens to a single site so that six alkyl carbons becomes three coarse grain sites (A-B-A), that the process will also be simple.
+In order to specify a site-mapping using VOTCA, we need to know the residue number, the residue name, and the atom name.
 For a six atom system this is not too bad, but it could get tedious and error-prone for larger systems.
@@
 The result of using this code in the \lstinline{coarse} function is a three-site hexane model A-B-A, same as VOTCA.%%<link to grits>
-The mapping here is specified as a list of bead name SMARTS string pairs.
+The mapping here is specified as a list of site name SMARTS string pairs.
 Although they do add some element of cognitive load, SMARTS strings are designed to be human and machine readable and can match atoms based on their chemical environment.
 With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (in SMARTS notation a capital \lstinline{"C"} denotes an alkyl carbon) and requiring that one be a terminal carbon by including that it has three attached hydrogens (\lstinline{"[CH3]"}).
-The order of the beads here matters because technically all the carbon atoms in hexane could be mapped with the more general SMARTS string (\lstinline{"CC"}), so it is important to list the most specific strings first.
-The bonding and angles of the resulting coarse grain beads can then inferred based on the bonding of the mapped atoms.
+% chktex 18
+The order of the sites here matters because technically all the carbon atoms in hexane could be mapped with the more general SMARTS string (\lstinline{"CC"}), so it is important to list the most specific strings first.
+% chktex 18
+The bonding and angles of the resulting coarse grain sites can then inferred based on the bonding of the mapped atoms.
 Basically what VOTCA's xml file does in 51 lines, I can do in 1 which is easier to read and makes chemical sense. 
@@
 This mapping scheme could even be used to make the mapping process easier for established coarse grain models.
-It could be fairly straightforward to implement a lookup to check if bead parameters already exist (e.g., for the MARTINI model) by going through and writing out the SMARTS pattern for each existing bead type.
+It could be fairly straightforward to implement a lookup to check if site parameters already exist (e.g., for the MARTINI model) by going through and writing out the SMARTS pattern for each existing site type.
 This could make parameterizing new compounds for an existing method more foolproof.
@@
 Currently, I have not found CG models for many NFA compounds (e.g, ITIC).
-%% I found this paper \cite{Meng2019} that claims to do CGMD with PTB7 ITIC but the details are hidden in the SI and seem fishy.
+%% I found this paper~\cite{Meng2019} that claims to do CGMD with PTB7 ITIC but the details are hidden in the SI and seem fishy.
 seems like they use IBI but they dont say how they got their target distributions.
@@
 To help organize the dataspace of the large parameter sweep, I plan to use the signac package to manage an ever-changing workspace.
-This will help easily and efficiently test out different mappings and "processing" conditions.
+This will help easily and efficiently test out different mappings and ``processing'' conditions.
 
 % predict nanostructure of new opv blends TODO new objective?
-% do math -- how long will it take me to graduate? how many sims can i do?
+% do math --- how long will it take me to graduate? how many sims can i do?
 
@@
 Although minimum working examples have been developed for botht the coarse graining and backmapping packages, I still expect to struggle when mapping new compounds.
-Sometimes the SMARTS/SMILES mapping won't work without careful choice of beads.
+Sometimes the SMARTS/SMILES mapping won't work without careful choice of sites.
 This can be a little frustrating but is still preferrable to having to manually specify the mapping of each atom.
-At least the reasons that a SMARTS mapping fails are usually understandable (e.g., the order of the beads matters) or chemically sensible (e.g., one SMILES string may contain another -- just as one chemical moeity may be composed of more submoeities).
+At least the reasons that a SMARTS mapping fails are usually understandable (e.g., the order of the sites matters) or chemically sensible (e.g., one SMILES string may contain another --- just as one chemical moeity may be composed of more submoeities).
 %%<this is a word?>)
@@
 \begin{table}[h]
-    \resizebox{\columnwidth}{!}{
-        \renewcommand{\arraystretch}{1.1}
-        \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
-            \hline
+    \resizebox{\columnwidth}{!}{\renewcommand{\arraystretch}{1.1}
+    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|} % chktex 44
+        \hline % chktex 44
         \multirow{2}{*}{PROJECT TASK}
@@
         & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4\\
-            \hline
+        \hline % chktex 44
         Complete Coursework 
             &\multicolumn{10}{|c|}{{\cellcolor{lgray}}} &  &  &  &  &  &  &  &  &  &\\
-            \hline
+        \hline % chktex 44
         Present at a Conference  
             & & & & & & & & & & & x & & & & & & & & &\\
-            \hline
+        \hline % chktex 44
         Publish a First Author Paper
             & & & & & & x & & & & & & & & & & & & & &\\
-            \hline
+        \hline % chktex 44
         Proposal and Comprehensive Exam
             & & & & & & & & & & & & * & & & & & & & &\\
-            \hline
+        \hline % chktex 44
         Expand Functionality of Open Source Packages 
             & & & & & & \multicolumn{11}{|c|}{{\cellcolor{lgray}}} & & & &\\
-            \hline
+        \hline % chktex 44
         Develop Coarse Graining Package              
             & & & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
-            \hline
+        \hline % chktex 44
         Develop Automated MS-IBI Code                
             & & & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
-            \hline
+        \hline % chktex 44
         Develop Backmapping Package                  
             & & & & & & & & & & & & \multicolumn{5}{|c|}{{\cellcolor{lgray}}}& & & &\\
-            \hline
+        \hline % chktex 44
         Generate Coarse-Grain Morphologies           
             & & & & & & & & & & & & & & \multicolumn{4}{|c|}{{\cellcolor{lgray}}}& & &\\
-            \hline
+        \hline % chktex 44
         Evaluate OPV Device Performance 
             & & & & & & & & & & & & & & \multicolumn{4}{|c|}{{\cellcolor{lgray}}} & & &\\
-            \hline
+        \hline % chktex 44
         Write Dissertation 
             & & & & & & & & & & & & & & & &\multicolumn{3}{|c|}{{\cellcolor{lgray}}} & &\\
-            \hline
+        \hline % chktex 44
         Present Dissertation Defense  
             & & & & & & & & & & & & & & & & & & {\cellcolor{lgray}} &  &\\
-            \hline
+        \hline % chktex 44
          %Saved row template

### 2020-08-25 2pd.tex
fixed error about using equations in list

@@
 \begin{enumerate}
-    \item {The coarse grain system is mapped onto an equilibrated atomistic one.}
-    \item {The average RDF of the mapped system is calculated over the equilibrated frames of the trajectory --- this is the target distribution.}
-    \item{Taking the Boltzmann Inverse (see \autoref{pmf}) of the RDF results in the potential of mean force (PMF).
-        \begin{equation}
-            \label{pmf}
+    \item 
+        The coarse grain system is mapped onto an equilibrated atomistic one.
+
+    \item 
+        The average RDF of the mapped system is calculated over the equilibrated frames of the trajectory --- this is the target distribution.
+
+    \item 
+        Taking the Boltzmann Inverse of the RDF results in the potential of mean force (PMF):
+
+        \[
             F(r) = -k_{B}T \ln g(r)
-            \tag{\ref{pmf}}
-        \end{equation}
+        \]
+
         Where $F(r)$ is the PMF, $k_{B}T$ is the thermal energy, and $g(r)$ is the target distribution.
         Although $F(r)$ is a free-energy and not a potential energy, it is sufficient to be used as the initial potential ($V_{0}$) in the iterative scheme\cite{Reith2003}.
-        }
-    \item{A simulation can be run using \autoref{pmf} as the non-bonded potential to achieve a new distribution.}
-    \item{The difference between the new and target distribution can be accounted for in the next iteration accoring to \autoref{ibi}.
-        \begin{equation}
-            \label{ibi}
-            V_{i+1}(r) = V_{i}(r) - k_{B}T \ln\big(\frac{g_{i}(r)}{g(r)}\big)
-            \tag{\ref{ibi}}
-        \end{equation}
+
+    \item
+        A simulation can be run using the PMF as the non-bonded potential to achieve a new distribution.
+
+    \item
+        The difference between the new and target distribution can be accounted for in the next iteration accoring to the following equation:
+
+        \[
+            V_{i+1}(r) = V_{i}(r) - k_{B}T \ln\bigg(\frac{g_{i}(r)}{g(r)}\bigg)
+        \]
+
         Where $g_{i}(r)$ is the distribution obtained using the potential $V_{i}(r)$.
-        }
+
 \end{enumerate}

### 2020-08-26 2pd.tex
objective 1 edit, c g to c-g'd

@@
 
-For this research we propose to develop a flexible method for specifying coarse grain models to obtain OPV polymer morphologies equilibrated on length scales relevant to charge transport.
+For this research we propose to develop a flexible method for specifying coarse-grained models to obtain OPV polymer morphologies equilibrated on length scales relevant to charge transport.
 We also propose to develop a backmapping method, which works on the same simple mapping operator, to restore the atomic positions in preparation for techniques which require atomic level resolutiuon e.g., charge transport calculations.
@@
 %%create models for new opv compounds>
-In order to model these OPV polymer systems on relevant length scales, it is necessary to develop new coarse grain models.
-A flexible and efficient coarse graining scheme will simplify the process of mapping and parameterizing these coarse grain elements. %% reword?
+In order to model these OPV polymer systems on relevant length scales, it is necessary to develop new coarse-grained models.
+A flexible and efficient coarse graining scheme will simplify the process of mapping and parameterizing these coarse-grained elements. %% reword?
 
 %%gain insight into the limits of coarse graining>
-The flexibility of specifying a mapping will allow for the comparison of multiple mappings which may provide insight into the features of an OPV which govern its self-assembly and the limits of coarse grain models.
-Currently there is no agreed-upon ``best'' scheme for a coarse grain mapping operator.
+The flexibility of specifying a mapping will allow for the comparison of multiple mappings which may provide insight into the features of an OPV which govern its self-assembly and the limits of coarse-grained models.
+Currently there is no agreed-upon ``best'' scheme for a coarse-grained mapping operator.
 By making a simple and easy-to-use coarse graining tool, many mapping operators can be tested and the limits of a minimal model can be probed.
@@
 
-Coarse graining refers to grouping atoms in a structure into a ``super atom'' and using an effective potential to represent the resulting coarse grain site.
+Coarse graining refers to grouping atoms in a structure into a ``super atom'' and using an effective potential to represent the resulting coarse-grained site.
 Coarse grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models by abstracting away irrelevant degrees of freedom.
@@
 Processes which may have taken many time steps in an all atom simulation can take fewer time steps in a coarse simulation\cite{Berendsen2010}.
-Due to their long length and time scales, coarse grain models are ideal for examining polymer properties\cite{Gartner2019a}.
+Due to their long length and time scales, coarse-grained models are ideal for examining polymer properties\cite{Gartner2019a}.
 It is too big and too slow and also just a bad idea to simulate huge boxes of atomistic polymers.
@@
 
-The resolution of coarse grain systems is broad:
+The resolution of coarse-grained systems is broad:
 Simply grouping hydrogens with the heavy atom they are bonded to, called the united-atom model, has been shown to speed up dynamics and make polymer length scales more easily accesible\cite{Paul1995a, Yang2006a}.
@@
 %%<examples of cg models and the cool things they do>
-General coarse grain models of OPV thiophene polymers where only the spacing and regioregularity of the side chains were varied were able to predict order disorder transitions and scattering patterns comparable to those obtained from experiment\cite{Jankowski2013, Marsh2014}.
-A coarse grain model for phospholipids has allowed for bilayer formation from an initial random configuration to be simulated even though the model was parameterized to the vapor-liquid phase transition\cite{Shelley2001}.
+General coarse-grained models of OPV thiophene polymers where only the spacing and regioregularity of the side chains were varied were able to predict order disorder transitions and scattering patterns comparable to those obtained from experiment\cite{Jankowski2013, Marsh2014}.
+A coarse-grained model for phospholipids has allowed for bilayer formation from an initial random configuration to be simulated even though the model was parameterized to the vapor-liquid phase transition\cite{Shelley2001}.
 %% transition?
@@
 Once a good bulk structure has been achieved, the atomistic details can be reintegrated much more easily: a process called backmapping.
-In the same way that a coarse grain model can be mapped onto an atomistic one, we can get a reasonable starting structure for an atomistic simulation from a coarse grain structure.
-The large length scale, polymer level properties can be equilibrated during the coarse grain simulation, and then the atomic interactions can be equilibrated during the backmapped atomistic simulation.
+In the same way that a coarse-grained model can be mapped onto an atomistic one, we can get a reasonable starting structure for an atomistic simulation from a coarse-grained structure.
+The large length scale, polymer level properties can be equilibrated during the coarse-grained simulation, and then the atomic interactions can be equilibrated during the backmapped atomistic simulation.
 This can allow us the calculate properties such as charge transport, which depends upon the electronic structure of individual chromophores \textit{and} the connectivity of these chromophores over distances proportional to the exciton dissociation length.
@@
 Part of coarse graining that is not yet automated is choosing a mapping scheme or a mapping operator.
-A mapping operator defines which atoms are grouped into a ``super atom'' represented by one coarse grain site and where the site is placed relative to the atom group.
-Mapping operators are chosen based on the desired resolution of the coarse grain system and the information to be extracted.
+A mapping operator defines which atoms are grouped into a ``super atom'' represented by one coarse-grained site and where the site is placed relative to the atom group.
+Mapping operators are chosen based on the desired resolution of the coarse-grained system and the information to be extracted.
 A straightforward way to define a mapping operator is to group a set number of heavy atoms (non hydrogen) together; this is the method used in the notable MARTINI force field\cite{Marrink2007}.
@@
 %%<how cg potentials have been attained> 
-Deciding on a mapping operator is one part of creating a coarse grain model, the second step is to create an effective potential for the site.
+Deciding on a mapping operator is one part of creating a coarse-grained model, the second step is to create an effective potential for the site.
 
@@
 Also, one other question that popped up is how bonds and angles between coarse beads are handled in the MSIBI step.
-There are numerous methods for deriving coarse grain potentials from atomistic ones (e.g., force-matching, reverse Monte Carlo), but in this proposal we will focus on Iterative Boltzmann Inversion (IBI).
+There are numerous methods for deriving coarse-grained potentials from atomistic ones (e.g., force-matching, reverse Monte Carlo), but in this proposal we will focus on Iterative Boltzmann Inversion (IBI).
 %%<IBI>
-IBI is where a coarse grain potential is iteratively tuned to fit a target distribution\cite{Reith2003}.
+IBI is where a coarse-grained potential is iteratively tuned to fit a target distribution\cite{Reith2003}.
 The radial distribution function (RDF) describes the probability of finding a particle at a given distance from another particle.
@@
     \item 
-        The coarse grain system is mapped onto an equilibrated atomistic one.
+        The coarse-grained system is mapped onto an equilibrated atomistic one.
 
@@
 
-The coarse grain potential derived from IBI is not transferrable to different thermodynamic statepoints.
+The coarse-grained potential derived from IBI is not transferrable to different thermodynamic statepoints.
 This is because the RDF is a property of the ensemble average at a given statepoint, so the potential derived from this property is also limited.
@@
 A Monte Carlo simulation can then be run using these hopping rates to calculate the movement of charges through the system.
-Because this is a quantum chemical calculation, the position of each atom is needed; therefore, a backmapping process is required to calculate the charge transport in a coarse grain morphology.
+Because this is a quantum chemical calculation, the position of each atom is needed; therefore, a backmapping process is required to calculate the charge transport in a coarse-grained morphology.
 %% MorphCT has some built in backmapping tools which use an xml file, but  (which i will discuss why these are bad in the next section) and the package is bulky/CLI/hard-to-use...
@@
 The second goal is accomplished by allowing all steps of the figure generation process (e.g., positioning the camera, setting the colors and lighting, etc) to be scripted and never \textit{requiring} use of the GUI\@.
-These prior works, although not directly related to OPVS or coarse grain models, have helped me think about how atomic interactions can shape a structure, the struggles that face a new computational scientist, and how I can help.
+These prior works, although not directly related to OPVS or coarse-grained models, have helped me think about how atomic interactions can shape a structure, the struggles that face a new computational scientist, and how I can help.
 
@@
     \includegraphics[width=\linewidth]{images/hexane-compare.pdf}\label{hexane}
-    \caption{Hexane chemical structure (top) overlaid with coarse grain mapping \textcolor{blue}{A}-\textcolor{orange}{B}-\textcolor{blue}{A} (bottom)}
+    \caption{Hexane chemical structure (top) overlaid with coarse-grained mapping \textcolor{blue}{A}-\textcolor{orange}{B}-\textcolor{blue}{A} (bottom)}
 \end{wrapfigure}
@@
 For an example of what I mean by cognitive load, let's compare an example of my proposed coarse-graining scheme to VOTCAs.
-In the following example we will take a hexane molecule and map it to three coarse grain sites (two carbon atoms per site).
+In the following example we will take a hexane molecule and map it to three coarse-grained sites (two carbon atoms per site).
 
@@
 %%    \includegraphics[width=\linewidth]{images/hexanexml.pdf}
-%%    \caption{XML file used by VOTCA to specify a three site coarse grain mapping of n-hexane}
+%%    \caption{XML file used by VOTCA to specify a three site coarse-grained mapping of n-hexane}
 %%    \label{hexanexml}
@@
 
-It may be easy to think that because the goal is simple, mapping two carbons and their attached hydrogens to a single site so that six alkyl carbons becomes three coarse grain sites (A-B-A), that the process will also be simple.
+It may be easy to think that because the goal is simple, mapping two carbons and their attached hydrogens to a single site so that six alkyl carbons becomes three coarse-grained sites (A-B-A), that the process will also be simple.
 In order to specify a site-mapping using VOTCA, we need to know the residue number, the residue name, and the atom name.
@@
 % chktex 18
-The bonding and angles of the resulting coarse grain sites can then inferred based on the bonding of the mapped atoms.
+The bonding and angles of the resulting coarse-grained sites can then inferred based on the bonding of the mapped atoms.
 Basically what VOTCA's xml file does in 51 lines, I can do in 1 which is easier to read and makes chemical sense. 
@@
 %% another application?
-This mapping scheme could even be used to make the mapping process easier for established coarse grain models.
+This mapping scheme could even be used to make the mapping process easier for established coarse-grained models.
 It could be fairly straightforward to implement a lookup to check if site parameters already exist (e.g., for the MARTINI model) by going through and writing out the SMARTS pattern for each existing site type.
@@
 This workflow could start with equilibrated atomistic trajectories from multiple statepoints, then use SMARTS strings to map the CG sites to each trajectory and calculate the effective potentials using MSIBI\@.
-Once we have a tabulated coarse grain force field, we can create a larger simulation using our coarse grain model.
-Finally, once we have an equilibrated coarse grain trajectory, we can using backmapping to regain the atomic positions and do analysese such as radial distribution function (RDF), charge transport, and diffraction.
+Once we have a tabulated coarse-grained force field, we can create a larger simulation using our coarse-grained model.
+Finally, once we have an equilibrated coarse-grained trajectory, we can using backmapping to regain the atomic positions and do analysese such as radial distribution function (RDF), charge transport, and diffraction.
 If this workflow is streamlined, it can be applied to many different compounds allowing for a high-throughput analysis of many potential OPV compounds.
@@
 % how doing this achieves the goal
-%% how to coarse grain reproducibly
+%% how to coarse-grained reproducibly
 \subsection*{Objective 1: Develop a generalized toolset for coarse graining and performing simulations of novel molecules for organic photovoltaics}
@@
 % infrastructure: porting ff to engine
-In order to model the morphologies of new OPV chemistries, we need a simple way to generate novel coarse grain models.
+In order to model the morphologies of new OPV chemistries, we need a simple way to generate novel coarse-grained models.
 This objective consists of three steps:
 \begin{enumerate}
-    \item {Create a tool that uses a mapping operator to go from atomistic to coarse grain structure}
-    \item {Use the mapped coarse grain structure to parameterize a force field using MSIBI}
+    \item {Create a tool that uses a mapping operator to go from atomistic to coarse-grained structure}
+    \item {Use the mapped coarse-grained structure to parameterize a force field using MSIBI}
     \item {Develop the infrastructure to port this force field to a simulation engine}
 \end{enumerate}
-A minimum working example of this coarse grain mapping tool has been completed. %% cite grits, cg-tutorial
+A minimum working example of this coarse-grained mapping tool has been completed. %% cite grits, cg-tutorial
 However, it will still need to be tested with many more compounds and mapping operators.
-This package uses the chemical file format parsing and scriptable structure building capabilities of mbuild coupled with the SMARTS/SMILES string matching of the openbabel package to generate coarse grain structures mapped onto their atomistic counterparts with only a SMARTS string from the user.
-These coarse grain structures mapped to an atomistic target can then be used in an MSIBI workflow to obtain an effective potential.
+This package uses the chemical file format parsing and scriptable structure building capabilities of mbuild coupled with the SMARTS/SMILES string matching of the openbabel package to generate coarse-grained structures mapped onto their atomistic counterparts with only a SMARTS string from the user.
+These coarse-grained structures mapped to an atomistic target can then be used in an MSIBI workflow to obtain an effective potential.
 A minimum working example of an MSIBI tool has also been started; %https://bitbucket.org/cmelab/msibi_tests/src/master/ do i even mention this?
@@
 %%https://github.com/mosdef-hub/msibi
-The force field obtained using MSIBI will then be used to run a simulation of a novel coarse grain model.
+The force field obtained using MSIBI will then be used to run a simulation of a novel coarse-grained model.
 Therefore decisions about how to carry the forcefield information into a simulation engine will need to be made.
 Here we will focus on HOOMD, but transferrability among simulation engines will be a goal.
-The coarse graining workflow will be considered complete when it can be used to coarse grain a test set of 25 common OPV chemistried. % 25 is just in there as a random number
+\textbf{Completion Critera:} Force fields and initial configurations usable with HOOMD-Blue that enable the equilibration of: 5 polymers, 5 fullerene derivatives, and 5 ITIC derivatives. 
 % workflow is complete when we can cg these chemistries
@@
 
-\subsection*{Objective 2: Develop a general tool to retrieve atomistic information from a coarse grain morphology}
+\subsection*{Objective 2: Develop a general tool to retrieve atomistic information from a coarse-grained morphology}
 
-In order to calculate the charge transport of a coarse grain OPV system, we need to be able to regain the atomic positions.
-Given an equilibrated coarse grain trajectory, we can reintroduce the atomistic degrees of freedom by using the same SMARTS mappings used for coarse graining.
+In order to calculate the charge transport of a coarse-grained representation of a morphology, we need to be able to regain the atomic positions.
+Given an equilibrated coarse-grained trajectory, we can reintroduce the atomistic degrees of freedom by using the same SMARTS mappings used for coarse graining.
 The chemistries specified by the SMARTS strings will be mapped onto the centers of the CG sites and then equilibrated in a short MD run using the atomistic force field with an additional position restraint to maintain the structure.
@@
     \item {\textbf{Understand the mapping operator}}
-        This work will test whether using a chemical string format (SMARTS/SMILES) to specify the atomistic to coarse grain site mapping is a viable alternative to other methods. 
+        This work will test whether using a chemical string format (SMARTS/SMILES) to specify the atomistic to coarse-grained site mapping is a viable alternative to other methods. 
         Using SMARTS/SMILES strings allows a user to more easily and intuitively specify a mapping.
@@
         Does making science easier/more understandable make it better? %more reproducible? curb cuts
-        If parameterizing a coarse grain force field is easier and more approachable, it would open up more possibilities for trying different mapping schemes or different structural or thermodynamic targets rather than sticking to an existing force field.
-        Better coarse grain models could result in more accurate and efficient simulation of large length scale systems.
+        If parameterizing a coarse-grained force field is easier and more approachable, it would open up more possibilities for trying different mapping schemes or different structural or thermodynamic targets rather than sticking to an existing force field.
+        Better coarse-grained models could result in more accurate and efficient simulation of large length scale systems.
 \end{enumerate}

### 2020-08-26 2pd.tex
coarse graining -> coarse-graining

@@
 In order to model these OPV polymer systems on relevant length scales, it is necessary to develop new coarse-grained models.
-A flexible and efficient coarse graining scheme will simplify the process of mapping and parameterizing these coarse-grained elements. %% reword?
+A flexible and efficient coarse-graining scheme will simplify the process of mapping and parameterizing these coarse-grained elements. %% reword?
 
-%%gain insight into the limits of coarse graining>
+%%gain insight into the limits of coarse-graining>
 The flexibility of specifying a mapping will allow for the comparison of multiple mappings which may provide insight into the features of an OPV which govern its self-assembly and the limits of coarse-grained models.
 Currently there is no agreed-upon ``best'' scheme for a coarse-grained mapping operator.
-By making a simple and easy-to-use coarse graining tool, many mapping operators can be tested and the limits of a minimal model can be probed.
+By making a simple and easy-to-use coarse-graining tool, many mapping operators can be tested and the limits of a minimal model can be probed.
 %% What is the minimum structure needed to represent a complex molecule? %% reword? omit?
@@
 Even with the simplifications of MD, we are still not able to simulate many systems efficiently on relevant length scales.
-Therefore we can use a technique called coarse graining to increase the length and time scales we can examine.
+Therefore we can use a technique called coarse-graining to increase the length and time scales we can examine.
 %%<segue to why we need CG models>
@@
 Similarly to how we don't need to look at the working of a plant cell to understand the growth of a forest, we don't need to consider atomic level properties when we are interested in the bulk morphology\cite{Muller-Plathe2002}.
-The heart of coarse graining is the removal of degrees of freedom. 
+The heart of coarse-graining is the removal of degrees of freedom. 
 This effective potential used to represent the reduced system results in a smoothed free energy landscape. 
@@
 %%<mapping operator has to be decided by hand> <is this section too big?>
-Part of coarse graining that is not yet automated is choosing a mapping scheme or a mapping operator.
+Part of coarse-graining that is not yet automated is choosing a mapping scheme or a mapping operator.
 A mapping operator defines which atoms are grouped into a ``super atom'' represented by one coarse-grained site and where the site is placed relative to the atom group.
@@
 %% how to coarse-grained reproducibly
-\subsection*{Objective 1: Develop a generalized toolset for coarse graining and performing simulations of novel molecules for organic photovoltaics}
+\subsection*{Objective 1: Develop a generalized toolset for coarse-graining and performing simulations of novel molecules for organic photovoltaics}
 % mapping
@@
 In order to calculate the charge transport of a coarse-grained representation of a morphology, we need to be able to regain the atomic positions.
-Given an equilibrated coarse-grained trajectory, we can reintroduce the atomistic degrees of freedom by using the same SMARTS mappings used for coarse graining.
+Given an equilibrated coarse-grained trajectory, we can reintroduce the atomistic degrees of freedom by using the same SMARTS mappings used for coarse-graining.
 The chemistries specified by the SMARTS strings will be mapped onto the centers of the CG sites and then equilibrated in a short MD run using the atomistic force field with an additional position restraint to maintain the structure.
@@
 seems like they use IBI but they dont say how they got their target distributions.
-A simple, useable coarse graining tool will be helpful for determining the best mapping operator to use for these OPV compounds.
+A simple, useable coarse-graining tool will be helpful for determining the best mapping operator to use for these OPV compounds.
 To help organize the dataspace of the large parameter sweep, I plan to use the signac package to manage an ever-changing workspace.
@@
     \item {\textbf{Gain insight into the limits of coarse-graining}}
-        This work will probe the limits of coarse graining to understand the minimal model necessary to represent different OPV chemistries.
+        This work will probe the limits of coarse-graining to understand the minimal model necessary to represent different OPV chemistries.
     \item {\textbf{Understand the interactions which guide BHJ self assembly}} 
@@
 %%<what's going to be hard?> 
-Although minimum working examples have been developed for botht the coarse graining and backmapping packages, I still expect to struggle when mapping new compounds.
+Although minimum working examples have been developed for both the coarse-graining and backmapping packages, I still expect to struggle when mapping new compounds.
 Sometimes the SMARTS/SMILES mapping won't work without careful choice of sites.
@@
 
-It may also be difficult to find a good coarse graining scheme for the NFA compounds. 
+It may also be difficult to find a good coarse-graining scheme for the NFA compounds. 
 These compounds are often composed of large planar backbones with floppy side chains.

### 2020-08-26 2pd.tex
Updated makefile so pdf target works and added line for make one
final thoughts for today in Objectives and Outcomes

@@
 Here we will focus on HOOMD, but transferrability among simulation engines will be a goal.
+\ej{If we're going to mention engine transferability we should say how we'll do it. If it's not germane to our completion criteria we can omit it. }
+
 \textbf{Completion Critera:} Force fields and initial configurations usable with HOOMD-Blue that enable the equilibration of: 5 polymers, 5 fullerene derivatives, and 5 ITIC derivatives. 
@@
 \subsection*{Objective 2: Develop a general tool to retrieve atomistic information from a coarse-grained morphology}
+\ej{Nitpick: Are we retreiving atomistic info from morphology, or calculating where the atoms should be based on the coarse-grained sites we have?
+In what ways is this going to be fundamentally similar or different to past back-mapping techniques?}
 
@@
 however, the specification of how the backmapped atomistic structures are bonded is still not intuitive for the user to specify and I am not sure yet how to make it better.
-The backmapping workflow will be considered complete when it can backmap a test set of 25 common OPV chemistries from all possible mappings.
 
-\subsection*{Objective 3: Predict nanostructure of novel OPV chemistries}
+\textbf{Completion Critera:} The ability to perform charge-transport calculations of 5 polymer, 5 fullerene-derivative, and 5 ITIC-derived OPV morphologies that have been back-mapped from coarse-grained representations.
+\ej{Here's candidate text with being able to USE the back-mapped morphologies, but maybe we want something easier here?}
+
+\subsection*{Objective 3: Predict nanostructures of novel OPV chemistries}
 
 Once Objectives 1 and 2 are complete, the next step will be putting them to use to investigate new OPV compounds.
+\ej{In principle we could also start this without new models: That's what Gwen and Emily are doing!}
 Currently, I have not found CG models for many NFA compounds (e.g, ITIC).
@@
 
+\textbf{Completion Critera:} \ej{Some number of predicted morphologies and/or some number of morphologies validated against experiments. }
 % predict nanostructure of new opv blends TODO new objective?
@@
 % identify chemical features correlated to robust mobilities
+\ej{Need to update Objective 4's title. I think a variant your second one is pretty good: ``Identify chemical features correlated with robust self-assembly and good charge transport''}
 
@@
 
+\textbf{Completion Critera:} \ej{todo}
+
 \section*{Predicted Outcomes}
 
+\ej{One thing this section is missing right now are tangible things that we specified in our Research Objectives.
+These include: XX new models of OPV chemistries; XX new tutorial notebooks for doing YY; XX predictions of OPV morphologies; Implementations of best practices others can copy or extend; }
 As a result of this work, we expect the following outcomes:

### 2020-08-26 2pd.tex
* addressing EJ's notes
* adding in needed citations

* deleting resolved comments

@@
 
-%%<why do opvs matter>
 \begin{wrapfigure}{l}{0.5\linewidth}
@@
 Consumption of fossil fuels for energy and transportation strongly contributes to atmospheric $CO_2$ the affects of which are global, long-term, and devastating\cite{Solomon2009a}.
-%% should I put examples? fires https://science2017.globalchange.gov/chapter/8/
 In our technology-driven society, it is unrealistic to think that energy demand will lessen, in fact global energy consumption is predicted to increase from 17 TW in 2010 to 27 TW in 2040\cite{Mazzio2015}.
@@
 champion solar cell chlorinated NFA 16.5\% efiiciency\cite{Cui2019}. 
-%% new figure
 %% TODO
@@
 %% paying for themselves
-%%underdog
+%% underdog
 In order to make the most efficient OPVs we need to find the blend of compounds and processing conditions that result in the best structure for those compounds.
@@
 %% https://www.printedelectronicsworld.com/articles/15405/raynergy-new-world-record-on-certified-pce-13-28-single-junction-opv
-signle junction with NFA
+single junction with NFA
 
@@
 Already good open-source packages exist to address the problem of coarse-graining and/or backmapping\cite{Marrink2007,Ruhle2009,Maerzke2011,MorphCT,Wassenaar2014b}.
-%%these citations are martini, votca, trappe, morphct, backwards.py
+%% these citations are martini, votca, trappe, morphct, backwards.py
 By making code open source and freely availiable, we contribute to the knowledge of a global community. 
@@
 By keeping best practices for software development and teaching in mind throughout development, we can strive to make tools which make science more transferrable, reproducibile, usable, and extensible (TRUE)\cite{Thompson2020}.
-%%TRUE
 Best software development practices include using version control software, such as git, to facilitate the process of tracking and merging changes to a code repository, especially important when working collaboratively.
@@
 Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70--80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h)\cite{Baran2017}.
-Coarse grain models do not yet exist for many of these NFAs, and with so many varieties an adaptable pipeline makes more sense than a single model.%%<there aren't a lot of cg models that already exist for these new compounds>
-It is necessary to develop a simple, useable, and flexible pipeline to adapt to the constantly changing chemistries of current OPV technologies. %EJ: NIIICE SENTENCE.
+Coarse grain models do not yet exist for many of these NFAs, and with so many varieties an adaptable pipeline makes more sense than a single model.
+It is necessary to develop a simple, useable, and flexible pipeline to adapt to the constantly changing chemistries of current OPV technologies.
 
@@
 
-%EJ: Nice. Attempting to reorder based on heirarchy
-%%use that science to help solve energy crisis???????>
 Ultimately the goal this research is to help solve the global energy crisis. 
@@
 
-%%create models for new opv compounds>
 In order to model these OPV polymer systems on relevant length scales, it is necessary to develop new coarse-grained models.
-A flexible and efficient coarse-graining scheme will simplify the process of mapping and parameterizing these coarse-grained elements. %% reword?
+A flexible and efficient coarse-graining scheme will simplify the process of mapping and parameterizing these coarse-grained elements.
 
-%%gain insight into the limits of coarse-graining>
 The flexibility of specifying a mapping will allow for the comparison of multiple mappings which may provide insight into the features of an OPV which govern its self-assembly and the limits of coarse-grained models.
@@
 By making a simple and easy-to-use coarse-graining tool, many mapping operators can be tested and the limits of a minimal model can be probed.
-%% What is the minimum structure needed to represent a complex molecule? %% reword? omit?
 
-%%develop new tools that help humans do science>
-Making this tool usable will also hopefully contribute to reproducibile science. 
+Making this tool usable will also contribute to reproducibile science. 
 Integrating with existing open source software packages will provide the most benefit and also increase transferrability and usability.
-We will use packages like signac for managing dataspaces, foyer for version control of forcefields, mbuild for building chemical structures, hoomd for running molecular dynamics simulations, freud for simulation trajectory analysis, and openbabel for recognizing chemical patterns.
-%%cite!
+We will use packages like signac for managing dataspaces, foyer for version control of forcefields, mbuild for building chemical structures, hoomd for running molecular dynamics simulations, freud for simulation trajectory analysis, and Open Babel for recognizing chemical patterns\cite{signac, foyer, mbuild, hoomd, freud, openbabel}.
 These are established codebases which are actively developed and engine agnostic (except hoomd which is in itself an engine).
 
-%%create a workflow that will make creating new models more accessible>
 Demonstrating a workflow from start to finish with explanations using easy-to-understand language, diagrams, and figures makes a codebase more usable and approachable but does not interfere with it being modular or efficient.
@@
 The performance of an OPV device can be quantified by many metrics.
-%% <what is PCE>
 The power conversion efficiency (PCE or sometimes $\eta_{e}$) is the ratio of electrical power produced by the device to the power of incedent photons.
@@
 
-%% <history>
 Inorganic PV devices came first and are still the most efficient, but they are more costly to produce, use rare elements, and their production causes other environmental issues, so they aren't the best solution for solar energy harvesting.
@@
 
-%%<how opvs work>
 The compounds which compose an OPV are synthesizable molecules (often polymers) composed of abundant elements (carbon, hydrogen, nitrogen, sulfur, oxygen).
@@
 
-%%<why morphology matters>
 The morphology of the device can be affected by the processing conditions: temperature, solvents, and concentrations/ratios of the active compounds\cite{Ma2005,Hoppe2004a,Li2007}.
@@
 Molecular simulation allows us to ``see'' these atomic interactions and gain a deeper view into the driving forces behind the self assembly of these OPV morphologies and to understand what conditions create the best devices.
-%%<segue into simulation>
 
 \subsection*{Molecular Dynamics}
-%EJ: Here or above: Why MD the right tool?
+
 Molecular dynamics (MD) is a simulation tool which uses classical physics and statistical thermodynamics to sample the equilibrium states of a thermodynamic ensemble.
@@
 
-%%<md in general>
 MD separates the interactions between particles into non-bonded interactions and bond, angle, and dihedral interactions (see \autoref{bad}).
@@
 Now GPUs are a 100 millions times faster.
-%%<what is MD used for? why is MD the best technique for gettign these OPV morphologies?>
 Due to its efficient scaling, MD is now commonly used for the modelling of protein folding~\cite{levitt75} and other biological processes, and investigating the bulk properties of polymers\cite{Gartner2019a}.
@@
 
-%%<what assumptions does md make?>
 Even all-atom MD is not without assumptions:
@@
 
-%%<what are the limits of atomistic md?>
 Even with the simplifications of MD, we are still not able to simulate many systems efficiently on relevant length scales.
 Therefore we can use a technique called coarse-graining to increase the length and time scales we can examine.
-%%<segue to why we need CG models>
 
@@
 Coarse grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models by abstracting away irrelevant degrees of freedom.
-%%<how do cg models let us access long length/time??>
 Similarly to how we don't need to look at the working of a plant cell to understand the growth of a forest, we don't need to consider atomic level properties when we are interested in the bulk morphology\cite{Muller-Plathe2002}.
@@
 
-%%<multiscale sims>
 For many systems, however, we are interested in properties which span length scales.
@@
 Whether the structure is similar then is based on the user's chemical knowledge, judgement, and intuition.
-%%The MARTINI force field was first designed for lipids, further parameterization for proteins and nuclei acids has since been added, and it has been shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.%%<cite
 Many other mapping schemes also rely on the user's chemical intuition (e.g., what parts of the molecule shouldn't be allowed to bend?
-What groups have the most dominant interactions in this structure).
-%%<cite any model where rings are one site><cite dna cg model>).
+What groups have the most dominant interactions in this structure)\cite{Huang2010, Knotts2007}.
 As the number of atoms in the fine grain structure increases, the number of possible mappings increase drastically.
@@
 There are numerous methods for deriving coarse-grained potentials from atomistic ones (e.g., force-matching, reverse Monte Carlo), but in this proposal we will focus on Iterative Boltzmann Inversion (IBI).
-%%<IBI>
 IBI is where a coarse-grained potential is iteratively tuned to fit a target distribution\cite{Reith2003}.
@@
 My prior work has involved probing the intermolecular interactions which govern dimer and crystal formation.
-% With lan - About excitonic splitting, using DFT, DNA. 
 An investigation of the excitonic splitting observed in cyanine dye dimers was done using density functional theory (DFT)\cite{Fothergill2018}.
 By comparing calculated with experimental absorption spectra it was found that the solvent may play a large role in the dimer formation and peak shifting.
-% With Matt - What intermolecular interactions guide diphenylurea crystal formation
 An investigation of the supramolecular interactions which guide crystal self-assembly in diphenylurea transition metal complexes was done using density functional theory\cite{Millard2019a}. 
-% With us - Perspective paper about all things
 My contributions to our perspective paper were mostly about my experience joining the lab and trying to reproduce an existing model; a task which should be very straightforward in a computational field but which any computational scientist can attest is far from simple\cite{Jankowski2019}.
- %% frame gixstapose as a tool for reproducible, approachable science
-I also presented a tool I've developed, called GIXStapose, at the Scientific Python conference (SciPy2020). %%cite scipy and gixstapose
+I also presented a tool I've developed, called GIXStapose, at the Scientific Python conference (SciPy2020)\cite{gixstapose, scipy2020}
 GIXStapose is an interactive structure viewer alongside its simulated diffraction pattern.
@@
 %%<how do I relate this to what I want to do??>
-I have contributed to development of open-source packages including mbuild, foyer, signac, and fresnel. %%cite
+I have contributed to development of open-source packages including mbuild, foyer, signac, and fresnel\cite{mbuild, foyer, signac, fresnel}.
 These contributions have given me ample opportunity to excercise best software development practices like writing good documentation, using version control, writing unit tests, employing CI, using a fork \& pull workflow, etc.
@@
 I have completed Software Carpentry training which has taught me how to break down complex ideas and give learners a chance to use their knowledge.
-With these principles in mind, I have created tutorial examples to help current and future students understand scientific concepts and how to use computational tools. %% cite notebook examples
+With these principles in mind, I have created tutorial examples to help current and future students understand scientific concepts and how to use computational tools\cite{notebooktutorials}
 %%- started development on UFF repo for foyer.
@@
 
-As for work towards my proposed plan, I have created a minimum working example of a coarse-graining and backmapping package which uses SMARTS strings to specify the site chemistries. %%cite grits
+As for work towards my proposed plan, I have created a minimum working example of a coarse-graining and backmapping package which uses SMARTS strings to specify the site chemistries\cite{grits}.
 This package will need further testing as it is tested on different compounds, but the proof of concept exists.
@@
 
-%%<Talk about what exists and why it is not enough>
-%%<votca, Peng2019a> 
 Packages which do coarse-graining and backmapping already exist, so why is another one necessary?
@@
 It also allows for charge transport calculations using KMC similar to MorphCT\cite{Lukyanov2010}.
-%%<compare VOTCA's backmapping to my proposed scheme>
 VOTCA makes some progress towards a TRUE simulation pipeline: they include a docker container with their pre-built software stack and example input files.
@@
 While including example inputs and a prebuilt software stack via docker is a great first step, these tutorials give very little walkthrough aside from code comments buried in the xml\cite{votca-github}.
-A manual is provided but the example files and the explanation given in the manual is disconnected. %%cite <https://github.com/votca/csg-manual/releases>.
 The code is a mix of C++, shell commands, and python, and the user is required to interact with compiled programs through the command-line which makes adding this code into an existing workflow a little more difficult.
-And judging by the amount of confusion in their mailing list, there is room for improvement in the API.%% cite <https://groups.google.com/forum/\#!forum/votca>
 Overall though this project has many features, interfaces with many popular MD engines (LAMMPS, GROMACS, HOOMD), and is under active, collaborative development, it is near-overwhelming in its scope and is not designed for the new user.
-By choosing a pure python API I will be able to make use of Jupyter Notebooks which can be run on cloud servers using tools like MyBinder which can combine executable code with markdown text and images.%%<cite link mybinder, link to tutorials I;ve made>
+By choosing a pure python API I will be able to make use of Jupyter Notebooks which can be run on cloud servers using tools like MyBinder which can combine executable code with markdown text and images\cite{mybinder, jupyter, notebooktutorials}.
 In this way a tutorial can provide exact commands needed to reproduce the example intimately connected with the rationale and justification of that example.
@@
 \end{lstlisting}
-The result of using this code in the \lstinline{coarse} function is a three-site hexane model A-B-A, same as VOTCA.%%<link to grits>
+The result of using this code in the \lstinline{coarse} function is a three-site hexane model A-B-A, same as VOTCA\cite{grits}.
 The mapping here is specified as a list of site name SMARTS string pairs.
@@
 Having the mapping in-line with the workflow also allows for the user to check that the mapping is correct with built in interactive visualizations, which can display the mapping as an overlay. 
-(\autoref{hexane-compare} is the output of one such visualization using py3Dmol.) %%cite py3Dmol
+(\autoref{hexane-compare} is the output of one such visualization using py3Dmol\cite{py3dmol}.)
 
@@
 Simplified Molecular Input Line Entry System or SMILES was designed to represent organic molecules in an unambiguous way (similar to IUPAC) but in a line-entry system which is also readable by a computer\cite{Weininger1988}.
-This makes it a good candidate for specifying a coarse-grain mapping scheme.The open-source package, Openbabel, allows for a SMILES string to be converted to a chemical structure and vice versa.
-SMARTS is similar to SMILES but instead of representing a single molecule unambiguously, it has multiple wildcards which can be used for pattern matching.%%<cite openbabel,SMILES, SMARTS>
-This pattern matching is also implemented in the Openbabel package.
+This makes it a good candidate for specifying a coarse-grain mapping scheme.
+The open-source package, Open Babel, allows for a SMILES string to be converted to a chemical structure and vice versa\cite{openbabel, OBoyle2011}.
+SMARTS is similar to SMILES but instead of representing a single molecule unambiguously, it has multiple wildcards which can be used for pattern matching\cite{daylight}.
+This pattern matching is also implemented in the Open Babel package.
 If we know the SMARTS string for any given CG mapping, we can map the CG site to its center of mass or geometric center.
-I have developed a minimum working example of how this can be done and then how the atomistic structure can be recovered.%%<cite grits>
+I have developed a minimum working example of how this can be done and then how the atomistic structure can be recovered\cite{grits}.
 %% another application?
@@
 
-My plan is to create a workflow which builds on existing tools: signac, freud, mbuild, openbabel, and a previously developed msibi package.
+My plan is to create a workflow which builds on existing tools: signac, freud, mbuild, Open Babel, and a previously developed msibi package.
 This workflow could start with equilibrated atomistic trajectories from multiple statepoints, then use SMARTS strings to map the CG sites to each trajectory and calculate the effective potentials using MSIBI\@.
@@
 \end{enumerate}
-A minimum working example of this coarse-grained mapping tool has been completed. %% cite grits, cg-tutorial
+A minimum working example of this coarse-grained mapping tool has been completed\cite{grits}.
 However, it will still need to be tested with many more compounds and mapping operators.
-This package uses the chemical file format parsing and scriptable structure building capabilities of mbuild coupled with the SMARTS/SMILES string matching of the openbabel package to generate coarse-grained structures mapped onto their atomistic counterparts with only a SMARTS string from the user.
+This package uses the chemical file format parsing and scriptable structure building capabilities of mbuild coupled with the SMARTS/SMILES string matching of the Open Babel package to generate coarse-grained structures mapped onto their atomistic counterparts with only a SMARTS string from the user.
 These coarse-grained structures mapped to an atomistic target can then be used in an MSIBI workflow to obtain an effective potential.
-A minimum working example of an MSIBI tool has also been started; %https://bitbucket.org/cmelab/msibi_tests/src/master/ do i even mention this?
-although the hands-on experience with MSIBI was useful to me in getting a better understanding for the process, I think for future, I will build off an existing MSIBI code.
-%%https://github.com/mosdef-hub/msibi
+A minimum working example of an MSIBI tool has also been started; however, although the hands-on experience with MSIBI was useful to me in getting a better understanding for the process, I think for future, I will build off an existing MSIBI code\cite{msibi, Moore2014}.
 The force field obtained using MSIBI will then be used to run a simulation of a novel coarse-grained model.
 Therefore decisions about how to carry the forcefield information into a simulation engine will need to be made.
-Here we will focus on HOOMD, but transferrability among simulation engines will be a goal.
-\ej{If we're going to mention engine transferability we should say how we'll do it. If it's not germane to our completion criteria we can omit it. }
+For this, we will make use of and build upon the simulation setup capabilities of mbuild.
 
 \textbf{Completion Critera:} Force fields and initial configurations usable with HOOMD-Blue that enable the equilibration of: 5 polymers, 5 fullerene derivatives, and 5 ITIC derivatives.
-% workflow is complete when we can cg these chemistries
-% use ff in different sim engines
 
-\subsection*{Objective 2: Develop a general tool to retrieve atomistic information from a coarse-grained morphology}
-\ej{Nitpick: Are we retreiving atomistic info from morphology, or calculating where the atoms should be based on the coarse-grained sites we have?
-In what ways is this going to be fundamentally similar or different to past back-mapping techniques?}
+\subsection*{Objective 2: Develop a general tool to calculate atomistic positions from a coarse-grained morphology}
 
-In order to calculate the charge transport of a coarse-grained representation of a morphology, we need to be able to regain the atomic positions.
+In order to calculate the charge transport of a coarse-grained representation of a morphology, we need to be able to estimate the atomic positions.
 Given an equilibrated coarse-grained trajectory, we can reintroduce the atomistic degrees of freedom by using the same SMARTS mappings used for coarse-graining.
 The chemistries specified by the SMARTS strings will be mapped onto the centers of the CG sites and then equilibrated in a short MD run using the atomistic force field with an additional position restraint to maintain the structure.
-I have developed a minimum working example of this backmapping process, %% cite grits
-however, the specification of how the backmapped atomistic structures are bonded is still not intuitive for the user to specify and I am not sure yet how to make it better.
+This method is not fundamentally different from many existing backmapping routines in that the atomistic structure is naively positioned over the coarse site and then relaxed --- the main difference lies in the amount of additional work required from the user\cite{Wassenar2014b, MorphCT, Ruhle2009}.
+Since the user has already specified the mapping to go from atomistic to coarse, it can be reused for backmapping.
+The bonding between the atomistic structures of the sites is lost, so this information will need to be provided: either specified by the user or recorded during the coarse graining step.
+I have developed a minimum working example of this backmapping process\cite{grits},
+however, the specification of how the backmapped atomistic structures are bonded is still not intuitive for the user to specify and I have yet to implement automated tracking of the conds during the coarse graining.
 
@@
 
-\subsection*{Objective 4: Analysis} % calulcate mobilities compare structural properties to experiment
-% identify chemical features correlated to robust mobilities
-\ej{Need to update Objective 4's title. I think a variant your second one is pretty good: ``Identify chemical features correlated with robust self-assembly and good charge transport''}
+\subsection*{Objective 4: Identify chemical features correlated with robust self-assembly and good charge transport}
 
@@
 \ej{One thing this section is missing right now are tangible things that we specified in our Research Objectives.
-These include: XX new models of OPV chemistries; XX new tutorial notebooks for doing YY; XX predictions of OPV morphologies; Implementations of best practices others can copy or extend; }
+These include: XX new models of OPV chemistries; XX new tutorial notebooks for doing YY\@; XX predictions of OPV morphologies; Implementations of best practices others can copy or extend; }
 As a result of this work, we expect the following outcomes:

### 2020-08-26 2pd.tex
better words arounf the nrel figure

@@
 Our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar\cite{Wirth2017}.
-Traditionally, photovoltaic devices, which can convert incedent light into electric current, were made of inorganic materials like silicon.
+Traditionally, photovoltaic (PV) devices, which can convert incedent light into electric current, were made of inorganic materials like silicon.
 But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative\cite{Tang1986b}.
@@
     \caption{Comparision of efficiencies organic and silicon photovoltaic technologies from 1990 to present.
-The current state-of-the-art OPV research cell achieves 17.4\% efficiency.
+The current state-of-the-art OPV, polymer-fullerene device coupled with transition metal disulfide, achieves 17.4\% efficiency\cite{Lin2019}.
 Data taken from~\cite{NREL2020}.}
@@
 
-17.4 \% efficiency mixing polymer fullerene device with transition metal disulfide\cite{Lin2019}.
-champion solar cell chlorinated NFA 16.5\% efiiciency\cite{Cui2019}. 
-%% TODO
-%% opvs are vast
-%% crystalline silicon levels off --- shottkey quessar (sp?) limit 34% efficient not much room for growth (blue)
-%% what you can buy vs champion devices
-%% opvs show room to grow
-%% paying for themselves
-%% underdog
+The theoretical efficiency limit (Shockley-Queisser limit) for a p-n single junction solar cell is about 30\%\cite{Shockley1961}.
+Multijuction cells may achieve efficiencies that surpass this limit, but they often do not have lower energy payback times as their production is more costly.
+\autoref{nrel} shows the efficiency gains made by single junction silicon and organic photovoltaic devices over the last 30 years.
+These are merely a selection among the many categories of PV devices.
+The trend of the silicon cells shows that the efficiency gain is levelling off as the devices approach the Shockley-Queisser limit.
+However, efficiency gains can still be made with OPV devices, and recent progress shows this.
+Many of the recent advancements in OPV technology have been through specialized processing or combinations of new chemistries.
+One new chemical moiety which has recieved attention is the ladder backbone structure seen in many non-fullerene acceptors (NFAs).
+A solar cell using a NFA functionalized with chlorine groups was found to achieve 16.5\% efficiency\cite{Cui2019}. 
+Prior to this a single junction cell using an NFA achieved a record-breaking 13.25\% efficiency\cite{raynergy}.
+
 In order to make the most efficient OPVs we need to find the blend of compounds and processing conditions that result in the best structure for those compounds.
@@
 %% include fig of ITIC PTB7? p3ht, fullerene recent uptick with NFAs
-%% look up the 17% solar cell---whats in it?
 %% freedom in choosing our ingredients - can we get better than trial and error
-%% https://www.printedelectronicsworld.com/articles/15405/raynergy-new-world-record-on-certified-pce-13-28-single-junction-opv
-single junction with NFA
 

### 2020-08-27 2pd.tex
added new figure with chemical structures
read through out loud -- made minor edits
* addressed all comments I felt able to -- marked others with %% HELP

@@
 
-The global climate crisis is one of the most pressing issue humanity faces today.
-Consumption of fossil fuels for energy and transportation strongly contributes to atmospheric $CO_2$ the affects of which are global, long-term, and devastating\cite{Solomon2009a}.
+The global climate crisis is one of the most pressing issues humanity faces today.
+Consumption of fossil fuels for energy and transportation strongly contributes to rising atmospheric $CO_{2}$ levels the effects of which are global, long-term, and devastating\cite{Solomon2009a}.
 In our technology-driven society, it is unrealistic to think that energy demand will lessen, in fact global energy consumption is predicted to increase from 17 TW in 2010 to 27 TW in 2040\cite{Mazzio2015}.
@@
 Harnessing solar energy is an important part of a green energy solution.
-Renewable energy accounted for 11\% of the U.S. energy consumption in 2019 and of that 9\% was from solar (solar accounted for approximately 1\% of the total energy)\cite{USEIA2020}.
-Our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar\cite{Wirth2017}.
+Renewable energy accounted for 11\% of the U.S. energy consumption in 2019 and of that 9\% was from solar (approximately 1\% of the total energy)\cite{USEIA2020}.
+However, our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar\cite{Wirth2017}.
 Traditionally, photovoltaic (PV) devices, which can convert incedent light into electric current, were made of inorganic materials like silicon.
@@
 The advantage of OPVs over inorganic PV devices is that OPVs are lightweight, low cost, easier to produce, and flexible. 
-OPVs can be manufactured large scale in a roll to roll printing process, similar to newspaper as shown in \autoref{opv} a\cite{Dou2013}.
-However, other materials still outperform OPVs (see \autoref{nrel}) and in order to become a viable, cost-effective option OPVs need to be more efficient\cite{Mazzio2015}.
+OPVs can be manufactured large scale in a roll to roll printing process, similar to newspaper, as shown in \autoref{opv} a\cite{Dou2013}.
+However, other materials still outperform OPVs (see \autoref{nrel}), and in order to become a viable, cost-effective option OPVs need to be more efficient\cite{Mazzio2015}.
 
@@
 The trend of the silicon cells shows that the efficiency gain is levelling off as the devices approach the Shockley-Queisser limit.
-However, efficiency gains can still be made with OPV devices, and recent progress shows this.
+OPV devices, however, still have a lot of room for improvement, and recent increases in OPV device efficiency reflects this.
 Many of the recent advancements in OPV technology have been through specialized processing or combinations of new chemistries.
-One new chemical moiety which has recieved attention is the ladder backbone structure seen in many non-fullerene acceptors (NFAs).
-A solar cell using a NFA functionalized with chlorine groups was found to achieve 16.5\% efficiency\cite{Cui2019}. 
-Prior to this a single junction cell using an NFA achieved a record-breaking 13.25\% efficiency\cite{raynergy}.
+One new chemical moiety which has recieved attention is the ladder backbone structure seen in many non-fullerene acceptors (NFAs), see \autoref{chemistries}.
+In 2018, a single junction cell using an NFA achieved a record-breaking 13.25\% efficiency\cite{raynergy}.
+And in 2019, a cell using an NFA functionalized with chlorine groups was found to achieve 16.5\% efficiency\cite{Cui2019}.
 
 In order to make the most efficient OPVs we need to find the blend of compounds and processing conditions that result in the best structure for those compounds.
-The active layer of an OPV is mixture of electron-donor and acceptor compounds: the ideal morphology is a micro phase-separated interpenetrating network called a bulk heterojunction (BHJ) (see \autoref{opv} c).
+The active layer of an OPV is mixture of electron-donor and acceptor compounds: The ideal morphology is a micro phase-separated interpenetrating network called a bulk heterojunction (BHJ) (see \autoref{opv} c).
 The performance of an OPV device is intimately linked with the structure of the active layer:
 With minor modifications, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
+\autoref{chemistries} shows a selection of possible OPV donor and acceptor chemistries.
+This wide range of compounds provides the freedom to tune our OPVs, but it also increases the scope of the problem.
 
-% TODO
-%% include fig of ITIC PTB7? p3ht, fullerene recent uptick with NFAs
-%% freedom in choosing our ingredients - can we get better than trial and error
+\begin{wrapfigure}{l}{0.5\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{images/chem_structures.pdf}\label{chemistries}
+    \caption{Chemical structures of polymer donors (P3HT and PTB7) and acceptors --- fullerene (PC$_{61}$BM) and non-fullerene (ITIC).}
+\end{wrapfigure}
 
@@
 This is where molecular simulation can help.
-By using a simulation pipeline, we can help to streamline the process of determining which OPV materials will form the best morphology with the best charge transport, and in turn, help to solve the energy crisis.
+By using a simulation pipeline, we can help to streamline the process of determining which OPV materials will form the morphology with the best charge transport, and in turn, help to solve the energy crisis.
 
@@
 The atomic and electronic properties are important for light absorption, in which an exciton is created, and charge transfer, where the exciton is dissociated into a free electron and hole\cite{Scharber2006a,Hoppe2004,Mazzio2015}.
-At the same time, the exciton finding an interface at which to dissociates depends on the bulk morphology, as do the charges, once separated, finding a path to an electrode in order to generate current and produce electricity.
+At the same time, the exciton finding an interface at which to dissociate and the separated charges finding a path to an electrode both depend on the morphology of the active layer.
 So, in order to model this system, a multiscale approach is necessary.
@@
 
-Already good open-source packages exist to address the problem of coarse-graining and/or backmapping\cite{Marrink2007,Ruhle2009,Maerzke2011,MorphCT,Wassenaar2014b}.
+Already good, open-source packages exist to address the problem of coarse-graining and/or backmapping\cite{Marrink2007,Ruhle2009,Maerzke2011,MorphCT,Wassenaar2014b}.
 %% these citations are martini, votca, trappe, morphct, backwards.py
-By making code open source and freely availiable, we contribute to the knowledge of a global community. 
+By making code open source and freely availiable, developers contribute to the knowledge of a global community. 
 But just because something is availiable doesn't mean it is accessible: often just figuring out how to use an existing package can be very difficult\cite{Cummings2019}.
@@
 All of these factors contribute to a reproducibility crisis in the computational sciences\cite{Baker2016}.
-By keeping best practices for software development and teaching in mind throughout development, we can strive to make tools which make science more transferrable, reproducibile, usable, and extensible (TRUE)\cite{Thompson2020}.
+By keeping best practices for software development and teaching in mind, we can strive to make tools which make science more transferrable, reproducibile, usable, and extensible (TRUE)\cite{Thompson2020}.
 Best software development practices include using version control software, such as git, to facilitate the process of tracking and merging changes to a code repository, especially important when working collaboratively.
@@
 Providing good documentation and tutorials is also imperative for onboarding new users.
-Jupyter Notebooks, which are a combination of interactive code and formatted text and images, can be used like a lab notebook for computational scientists in order to demonstrate the process, rationale, and the story of each experiment and the exact steps to get the results shown\cite{Rule2019a}.
+Jupyter Notebooks, which are a combination of interactive code and formatted text and images, can be used like a lab notebook for computational scientists in order to demonstrate the process, rationale, and the story of each experiment and the exact steps to get the results shown\cite{jupyter, Rule2019a}.
 When writing these tutorials, it is wise to remember that the data never speaks for itself: although including input and output files of a calculation is a good first step, they must be accompanied by the story of what the data means and how a user can know that meaning for themselves\cite{SWC, Wilson2016}.
@@
 For this research we propose to develop a flexible method for specifying coarse-grained models to obtain OPV polymer morphologies equilibrated on length scales relevant to charge transport.
-We also propose to develop a backmapping method, which works on the same simple mapping operator, to restore the atomic positions in preparation for techniques which require atomic level resolutiuon e.g., charge transport calculations.
-This two step process is necessary because starting with the fully atomistic structure would not only be computationally inefficient but also the result may even be less accurate due to the difficulties of equilibrating polymers\cite{Gartner2019a}.
+We also propose to develop a backmapping method, which works on the same simple mapping operator, to restore the atomic positions in preparation for techniques which require atomic level resolution, e.g., charge transport calculations.
+This two step process is necessary because starting with the fully atomistic structure would not only be computationally inefficient but also the result may be less accurate due to the difficulties of equilibrating polymers\cite{Gartner2019a}.
 This efficiency is important because the scope of potential OPV compounds is vast and the energy crisis necessitates expediency.
@@
 The compounds which compose an OPV are synthesizable molecules (often polymers) composed of abundant elements (carbon, hydrogen, nitrogen, sulfur, oxygen).
-Due to the conjugated pi-orbitals in these molecules the absorption of sunlight can excite an electron into a frontier orbital and generate an exciton.
+Due to the conjugated pi-orbitals in these molecules the absorption of sunlight can excite an electron into a frontier orbital and generate an exciton, a couloubicly bound electron-hole pair.
 OPVs are made as a mixture of electron-donor and electron-acceptor compounds in a structure called a bulk-heterojunction.
@@
 MD separates the interactions between particles into non-bonded interactions and bond, angle, and dihedral interactions (see \autoref{bad}).
-
 \begin{wrapfigure}{L}{0.5\linewidth}
@@
 \end{wrapfigure}
-
 Non-bonded interactions are commonly modelled with a Lennard-Jones potential:
@@
 The first MD simulation modelled a system of 108 particles and completed 200 collisions in one hour on an IBM-704\cite{Alder1957}.
-Now GPUs are a 100 millions times faster.
-Due to its efficient scaling, MD is now commonly used for the modelling of protein folding~\cite{levitt75} and other biological processes, and investigating the bulk properties of polymers\cite{Gartner2019a}.
-By abstracting away some of the atomic degrees of freedom, MD can be used to look at even larger systems. %%transition attempt
+Now GPUs are a 100 million times faster.
+Due to its the simplicity and efficient scaling, MD is now commonly used for the modelling of protein folding\cite{levitt75} and other biological processes, and investigating the bulk properties of polymers\cite{Gartner2019a}.
 
-Even all-atom MD is not without assumptions:
-In general, during an MD simulation bonds aren't formed or broken, so without careful consideration this prevents the study of chemical reactions.
-MD does not consider electrons, instead atoms are treated as point particles. 
-This makes modelling systems which depend on hydrogen bonding or dispersion more difficult.
+%Even all-atom MD is not without assumptions:
+%In general, during an MD simulation bonds aren't formed or broken, so without careful consideration this prevents the study of chemical reactions.
+%MD does not consider electrons, instead atoms are treated as point particles. 
+%This makes modelling systems which depend on hydrogen bonding or dispersion more difficult.
 
 Even with the simplifications of MD, we are still not able to simulate many systems efficiently on relevant length scales.
-Therefore we can use a technique called coarse-graining to increase the length and time scales we can examine.
+By abstracting away some of the atomic degrees of freedom which do not contribute as much to the bulk structure, MD can be used to look at even larger systems.
+Coarse grain models are one such technique to increase the length and time scales examined by a simulation.
 
@@
 Coarse graining refers to grouping atoms in a structure into a ``super atom'' and using an effective potential to represent the resulting coarse-grained site.
+This effective potential used to represent the reduced system results in a smoothed free energy landscape. 
+The heart of coarse-graining is the removal of degrees of freedom. 
 Coarse grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models by abstracting away irrelevant degrees of freedom.
-Similarly to how we don't need to look at the working of a plant cell to understand the growth of a forest, we don't need to consider atomic level properties when we are interested in the bulk morphology\cite{Muller-Plathe2002}.
-The heart of coarse-graining is the removal of degrees of freedom. 
-This effective potential used to represent the reduced system results in a smoothed free energy landscape. 
 Processes which may have taken many time steps in an all atom simulation can take fewer time steps in a coarse simulation\cite{Berendsen2010}.
 Due to their long length and time scales, coarse-grained models are ideal for examining polymer properties\cite{Gartner2019a}.
-It is too big and too slow and also just a bad idea to simulate huge boxes of atomistic polymers.
+Similarly to how monitoring the working of a plant cell is not necessary to understanding the growth of a forest, some atomic level properties do not need consideration when simulating the bulk morphology\cite{Muller-Plathe2002}.
+It is too big, too slow, and unwise to simulate huge boxes of atomistic polymers.
 Even if the simulation was to complete, there would be too much information to process accurately. 
@@
 Other coarse-graining schemes may group functional groups together\cite{Berendsen2010, Jankowski2013, Marsh2014}, one site per repeat unit in a polymer\cite{Lee2011}, or even represent an entire amino acid with a single site\cite{Peng2019}.
-%%<examples of cg models and the cool things they do>
 General coarse-grained models of OPV thiophene polymers where only the spacing and regioregularity of the side chains were varied were able to predict order disorder transitions and scattering patterns comparable to those obtained from experiment\cite{Jankowski2013, Marsh2014}.
 A coarse-grained model for phospholipids has allowed for bilayer formation from an initial random configuration to be simulated even though the model was parameterized to the vapor-liquid phase transition\cite{Shelley2001}.
-%% transition?
 Which model is right depends on the length and time scale on which the property of interest can be observed.
@@
 This can allow us the calculate properties such as charge transport, which depends upon the electronic structure of individual chromophores \textit{and} the connectivity of these chromophores over distances proportional to the exciton dissociation length.
+
+%% HELP transition?
 %%<what stands in our way?>
-
 %%<coarse-grain models are specific>
 
-%%<segue from automated creation of forcefields to...>
-%%<mapping operator has to be decided by hand> <is this section too big?>
-Part of coarse-graining that is not yet automated is choosing a mapping scheme or a mapping operator.
+%% HELP is the following paragraph/section too big? 
+Part of coarse-graining process that is not yet automated is choosing a mapping scheme or a mapping operator.
 A mapping operator defines which atoms are grouped into a ``super atom'' represented by one coarse-grained site and where the site is placed relative to the atom group.
@@
 A mapping operator based on the centers of charge was shown to accurately model electrostatic properties\cite{Cao2015a}.
-%%<how cg potentials have been attained> 
 Deciding on a mapping operator is one part of creating a coarse-grained model, the second step is to create an effective potential for the site.
@@
 
-%% TODO
 %% feedback from chris: Also, in the MSIBI section you could take a paragraph or 2 to define what an RDF is, what a Boltzman inverse is, what a potential mean force is, then go into the algorithm steps.
@@
 There are numerous methods for deriving coarse-grained potentials from atomistic ones (e.g., force-matching, reverse Monte Carlo), but in this proposal we will focus on Iterative Boltzmann Inversion (IBI).
-IBI is where a coarse-grained potential is iteratively tuned to fit a target distribution\cite{Reith2003}.
+IBI is where a coarse-grained potential is iteratively tuned to fit a target distribution usually from an atomistic simulation\cite{Reith2003}.
 The radial distribution function (RDF) describes the probability of finding a particle at a given distance from another particle.
@@
 This process is repeated until the difference between the result and the target is sufficiently small. 
+The bonded distributions can be similarly iterated to obtain the bonded potentials; however, in some cases the Boltzmann inverse of the bonded distribution may be used without iteration\cite{Reith2003}.
 
@@
 For some systems there may not be a potential that represents all states; this is not unique to coarse potentials, atomistic potentials also have this limitation.
+
+%% HELP transition
 %%<need some tie in back to why we would want to go from CG--->atomistic>
@@
 
-%%<I DONT WANT TO FOCUS ON THIS TOO MUCH. It's only here as a rationale for why backmapping>
-%%<how morphct pipeline would work: cg-backmap-ct>
+In order to use coarse grain models to predict charge transport, we need a way to translate from the coarse to the atomistic morphology.
+%% HELP transition
 MorphCT, a software previously developed by our lab, can simulate charge transport through an OPV morphology using kinetic Monte Carlo\cite{Miller2018a,MorphCT,morphct2.2}.
@@
 
+%% HELP this section is rough... not sure what to do.
 My prior work has involved probing the intermolecular interactions which govern dimer and crystal formation.
@@
 Having the mapping in-line with the workflow also allows for the user to check that the mapping is correct with built in interactive visualizations, which can display the mapping as an overlay. 
-(\autoref{hexane-compare} is the output of one such visualization using py3Dmol\cite{py3dmol}.)
+(\autoref{hexane} is the output of one such visualization using py3Dmol\cite{py3dmol}.)
 
@@
 Once we have a tabulated coarse-grained force field, we can create a larger simulation using our coarse-grained model.
-Finally, once we have an equilibrated coarse-grained trajectory, we can using backmapping to regain the atomic positions and do analysese such as radial distribution function (RDF), charge transport, and diffraction.
+Finally, once we have an equilibrated coarse-grained trajectory, we can using backmapping to regain the atomic positions and do analyses, e.g., radial distribution function (RDF), charge transport, and diffraction.
 If this workflow is streamlined, it can be applied to many different compounds allowing for a high-throughput analysis of many potential OPV compounds.
@@
 \textbf{Completion Critera:} The ability to perform charge-transport calculations of 5 polymer, 5 fullerene-derivative, and 5 ITIC-derived OPV morphologies that have been back-mapped from coarse-grained representations.
-\ej{Here's candidate text with being able to USE the back-mapped morphologies, but maybe we want something easier here?}
+%%\ej{Here's candidate text with being able to USE the back-mapped morphologies, but maybe we want something easier here?} - i'm ok with this goal.
 
@@
 Once Objectives 1 and 2 are complete, the next step will be putting them to use to investigate new OPV compounds. 
-\ej{In principle we could also start this without new models: That's what Gwen and Emily are doing!}
+%%\ej{In principle we could also start this without new models: That's what Gwen and Emily are doing!}
 Currently, I have not found CG models for many NFA compounds (e.g, ITIC).
@@
 
-\textbf{Completion Critera:} \ej{Some number of predicted morphologies and/or some number of morphologies validated against experiments. }
+\textbf{Completion Critera:} 
+Validation using diffraction or RDF of simulated morphologies composed of 5 polymers, 5 fullerene derivatives, and 5 ITIC derivatives. 
+%%\ej{Some number of predicted morphologies and/or some number of morphologies validated against experiments. }
 % predict nanostructure of new opv blends TODO new objective?

### 2020-08-27 2pd.tex
deleting comments that have been resolved

@@
 Because this is a quantum chemical calculation, the position of each atom is needed; therefore, a backmapping process is required to calculate the charge transport in a coarse-grained morphology.
-%% MorphCT has some built in backmapping tools which use an xml file, but  (which i will discuss why these are bad in the next section) and the package is bulky/CLI/hard-to-use...
-%%<making morphct more modular to allow it to be used in a workflow not cli>
 
@@
 
-%%<how do I relate this to what I want to do??>
 I have contributed to development of open-source packages including mbuild, foyer, signac, and fresnel\cite{mbuild, foyer, signac, fresnel}.
@@
 
-%% experience teaching and creating material for people to learn
 I have completed Software Carpentry training which has taught me how to break down complex ideas and give learners a chance to use their knowledge.
 With these principles in mind, I have created tutorial examples to help current and future students understand scientific concepts and how to use computational tools\cite{notebooktutorials}
-%%- started development on UFF repo for foyer.
-%%This is an example of how to create a version controlled forcefield which can be automatically applied to a compound.
-%%<atom typing is a pain and doing it manually is bad cite foyer paper>
 
@@
 I have developed a minimum working example of how this can be done and then how the atomistic structure can be recovered\cite{grits}.
-%% another application?
 This mapping scheme could even be used to make the mapping process easier for established coarse-grained models.
@@
 \section*{Research Plan}
-
-%% make better opvs
-%% need to get a morphology on relevant lengthscale
-%% many different chemistries
-%% need a model that get a cg model from a chemistry
 
@@
 
-%% Objectives are like steps along the way
-%% objectives should be
-% 1. goal of the step
-% 2. how to do the step
-% how doing this achieves the goal
-%% how to coarse-grained reproducibly
 \subsection*{Objective 1: Develop a generalized toolset for coarse-graining and performing simulations of novel molecules for organic photovoltaics}
-% mapping
-% ff creation
-% infrastructure: porting ff to engine
 In order to model the morphologies of new OPV chemistries, we need a simple way to generate novel coarse-grained models.
@@
 %%\ej{Some number of predicted morphologies and/or some number of morphologies validated against experiments. }
-% predict nanostructure of new opv blends TODO new objective?
-% do math --- how long will it take me to graduate? how many sims can i do?
 
@@
 %%Our morphct paper says the mobilities we predict are 2x higher than experiment? why?
-%%<I need something in here about making morphct more user friendly and less hard-coded for p3ht.>
 %%<adding in calculation of reorganization energy??> 
@@
 
-%%<what's going to be hard?> 
 Although minimum working examples have been developed for both the coarse-graining and backmapping packages, I still expect to struggle when mapping new compounds.

### 2020-08-27 2pd.tex
fix very strange errors with chktex and autoref

@@
     \centering
-    \includegraphics[width=\linewidth]{images/dou-miller2018c-fig.pdf}\label{opv}
+    \includegraphics[width=\linewidth]{images/dou-miller2018c-fig.pdf}
     \caption{Schematic showing (a) roll to roll printing process for OPVs, (b) example OPV device, (c) bulk heterojunction structure, and (d) OPV energy generation process.
 Part (a) adapted from ref~\cite{Dou2013}.
-Parts (b -- d) adapted from ref~\cite{Miller2018c}.} % chktex 8
+Parts (b,c,d) adapted from ref~\cite{Miller2018c}.}\label{opv}
 \end{wrapfigure}
@@
 The advantage of OPVs over inorganic PV devices is that OPVs are lightweight, low cost, easier to produce, and flexible. 
-OPVs can be manufactured large scale in a roll to roll printing process, similar to newspaper, as shown in \autoref{opv} a\cite{Dou2013}.
+OPVs can be manufactured large scale in a roll to roll printing process, similar to newspaper, as shown in~\autoref{opv} a\cite{Dou2013}.
 However, other materials still outperform OPVs (see \autoref{nrel}), and in order to become a viable, cost-effective option OPVs need to be more efficient\cite{Mazzio2015}.
@@
 \begin{figure}[h!]
-    \includegraphics[width=\linewidth]{images/NREL2020.pdf}\label{nrel}
+    \includegraphics[width=\linewidth]{images/NREL2020.pdf}
     \caption{Comparision of efficiencies organic and silicon photovoltaic technologies from 1990 to present.
 The current state-of-the-art OPV, polymer-fullerene device coupled with transition metal disulfide, achieves 17.4\% efficiency\cite{Lin2019}.
-Data taken from~\cite{NREL2020}.}
+Data taken from~\cite{NREL2020}.}\label{nrel}
 \end{figure}
@@
     \centering
-    \includegraphics[width=\linewidth]{images/chem_structures.pdf}\label{chemistries}
-    \caption{Chemical structures of polymer donors (P3HT and PTB7) and acceptors --- fullerene (PC$_{61}$BM) and non-fullerene (ITIC).}
+    \includegraphics[width=\linewidth]{images/chem_structures.pdf}
+    \caption{Chemical structures of polymer donors (P3HT and PTB7) and acceptors --- fullerene (PC$_{61}$BM) and non-fullerene (ITIC).}\label{chemistries}
 \end{wrapfigure}
@@
     \centering
-    \includegraphics[width=\linewidth]{images/ITIC.pdf}\label{itic}
-    \caption{ITIC chemical structure with \textcolor{red}{electron accepting regions in red} and \textcolor{blue}{electron donating regions in blue}}
+    \includegraphics[width=\linewidth]{images/ITIC.pdf}
+    \caption{ITIC chemical structure with \textcolor{red}{electron accepting regions in red} and \textcolor{blue}{electron donating regions in blue}}\label{itic}
 \end{wrapfigure}
@@
     \centering
-    \includegraphics[width=\linewidth]{images/bondangledihedral.pdf}\label{bad}
-    \caption{Bonded interactions: bond (top left), angle (top right), and dihedral (bottom). Image adapted from~\cite{punma}.}
+    \includegraphics[width=\linewidth]{images/bondangledihedral.pdf}
+    \caption{Bonded interactions: bond (top left), angle (top right), and dihedral (bottom). Image adapted from~\cite{punma}.}\label{bad}
 \end{wrapfigure}
@@
     \centering
-    \includegraphics[width=\linewidth]{images/lj.pdf}\label{lj}
-    \caption{The Lennard-Jones potential with relevant distances labelled}
+    \includegraphics[width=\linewidth]{images/lj.pdf}
+    \caption{The Lennard-Jones potential with relevant distances labelled}\label{lj}
 \end{wrapfigure}
@@
     \centering
-    \includegraphics[width=\linewidth]{images/moorefig.pdf}\label{moore}
+    \includegraphics[width=\linewidth]{images/moorefig.pdf}
     \caption{Visualization of the state space coverage of different potentials: if the thermodynamic states are too similar (b), then the overlap region is large enough that there are many potentials which will fit the target.
 Choosing states which are different (a) will better define the potential.
-Image adapted from ref~\cite{Moore2014}.}
+Image adapted from ref~\cite{Moore2014}.}\label{moore}
 \end{wrapfigure}
@@
     \centering
-    \includegraphics[width=\linewidth]{images/hexane-compare.pdf}\label{hexane}
-    \caption{Hexane chemical structure (top) overlaid with coarse-grained mapping \textcolor{blue}{A}-\textcolor{orange}{B}-\textcolor{blue}{A} (bottom)}
+    \includegraphics[width=\linewidth]{images/hexane-compare.pdf}
+    \caption{Hexane chemical structure (top) overlaid with coarse-grained mapping \textcolor{blue}{A}-\textcolor{orange}{B}-\textcolor{blue}{A} (bottom)}\label{hexane}
 \end{wrapfigure}
@@
 With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (in SMARTS notation a capital \lstinline{"C"} denotes an alkyl carbon) and requiring that one be a terminal carbon by including that it has three attached hydrogens (\lstinline{"[CH3]"}).
-% chktex 18
 The order of the sites here matters because technically all the carbon atoms in hexane could be mapped with the more general SMARTS string (\lstinline{"CC"}), so it is important to list the most specific strings first.
-% chktex 18
 The bonding and angles of the resulting coarse-grained sites can then inferred based on the bonding of the mapped atoms.
@@
 The chemistries specified by the SMARTS strings will be mapped onto the centers of the CG sites and then equilibrated in a short MD run using the atomistic force field with an additional position restraint to maintain the structure.
-This method is not fundamentally different from many existing backmapping routines in that the atomistic structure is naively positioned over the coarse site and then relaxed --- the main difference lies in the amount of additional work required from the user\cite{Wassenar2014b, MorphCT, Ruhle2009}.
+This method is not fundamentally different from many existing backmapping routines in that the atomistic structure is naively positioned over the coarse site and then relaxed --- the main difference lies in the amount of additional work required from the user\cite{Wassenaar2014b, MorphCT, Ruhle2009}.
 Since the user has already specified the mapping to go from atomistic to coarse, it can be reused for backmapping.
@@
     \resizebox{\columnwidth}{!}{\renewcommand{\arraystretch}{1.1}
-    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|} % chktex 44
-        \hline % chktex 44
+    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
+        \hline
         \multirow{2}{*}{PROJECT TASK}
@@
         & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4\\
-        \hline % chktex 44
+        \hline
         Complete Coursework 
             &\multicolumn{10}{|c|}{{\cellcolor{lgray}}} &  &  &  &  &  &  &  &  &  &\\
-        \hline % chktex 44
+        \hline
         Present at a Conference  
             & & & & & & & & & & & x & & & & & & & & &\\
-        \hline % chktex 44
+        \hline
         Publish a First Author Paper
             & & & & & & x & & & & & & & & & & & & & &\\
-        \hline % chktex 44
+        \hline
         Proposal and Comprehensive Exam
             & & & & & & & & & & & & * & & & & & & & &\\
-        \hline % chktex 44
+        \hline
         Expand Functionality of Open Source Packages 
             & & & & & & \multicolumn{11}{|c|}{{\cellcolor{lgray}}} & & & &\\
-        \hline % chktex 44
+        \hline
         Develop Coarse Graining Package              
             & & & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
-        \hline % chktex 44
+        \hline
         Develop Automated MS-IBI Code                
             & & & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
-        \hline % chktex 44
+        \hline
         Develop Backmapping Package                  
             & & & & & & & & & & & & \multicolumn{5}{|c|}{{\cellcolor{lgray}}}& & & &\\
-        \hline % chktex 44
+        \hline
         Generate Coarse-Grain Morphologies           
             & & & & & & & & & & & & & & \multicolumn{4}{|c|}{{\cellcolor{lgray}}}& & &\\
-        \hline % chktex 44
+        \hline
         Evaluate OPV Device Performance 
             & & & & & & & & & & & & & & \multicolumn{4}{|c|}{{\cellcolor{lgray}}} & & &\\
-        \hline % chktex 44
+        \hline
         Write Dissertation 
             & & & & & & & & & & & & & & & &\multicolumn{3}{|c|}{{\cellcolor{lgray}}} & &\\
-        \hline % chktex 44
+        \hline
         Present Dissertation Defense  
             & & & & & & & & & & & & & & & & & & {\cellcolor{lgray}} &  &\\
-        \hline % chktex 44
+        \hline
          %Saved row template

### 2020-08-28 2pd.tex
moving figures around

@@
 \begin{figure}[h!]
-    \includegraphics[width=\linewidth]{images/NREL2020.pdf}
+    \centering
+    \includegraphics[width=0.8\linewidth]{images/NREL2020.pdf}
     \caption{Comparision of efficiencies organic and silicon photovoltaic technologies from 1990 to present.
@@
 In order to make the most efficient OPVs we need to find the blend of compounds and processing conditions that result in the best structure for those compounds.
-The active layer of an OPV is mixture of electron-donor and acceptor compounds: The ideal morphology is a micro phase-separated interpenetrating network called a bulk heterojunction (BHJ) (see \autoref{opv} c).
-The performance of an OPV device is intimately linked with the structure of the active layer:
-With minor modifications, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
-\autoref{chemistries} shows a selection of possible OPV donor and acceptor chemistries.
-This wide range of compounds provides the freedom to tune our OPVs, but it also increases the scope of the problem.
-
 \begin{wrapfigure}{l}{0.5\linewidth}
@@
 \end{wrapfigure}
+\leavevmode
+The active layer of an OPV is mixture of electron-donor and acceptor compounds: 
+The ideal morphology is a micro phase-separated interpenetrating network called a bulk heterojunction (BHJ) (see \autoref{opv} c).
+The performance of an OPV device is intimately linked with the structure of the active layer:
+With minor modifications, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
+\autoref{chemistries} shows a selection of possible OPV donor and acceptor chemistries.
+This wide range of compounds provides the freedom to tune our OPVs, but it also increases the scope of the problem.
 
@@
 
+\begin{wrapfigure}{l}{0.5\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{images/bondangledihedral.pdf}
+    \caption{Bonded interactions: bond (top left), angle (top right), and dihedral (bottom). Image adapted from~\cite{punma}.}\label{bad}
+\end{wrapfigure}
 Molecular dynamics (MD) is a simulation tool which uses classical physics and statistical thermodynamics to sample the equilibrium states of a thermodynamic ensemble.
@@
 
+\begin{wrapfigure}{l}{0.5\linewidth}
+    \begin{center}
+        \includegraphics[width=\linewidth]{images/lj.pdf}
+        \end{center}
+    \caption{The Lennard-Jones potential with relevant distances labelled}\label{lj}
+\end{wrapfigure}
 MD separates the interactions between particles into non-bonded interactions and bond, angle, and dihedral interactions (see \autoref{bad}).
-\begin{wrapfigure}{L}{0.5\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{images/bondangledihedral.pdf}
-    \caption{Bonded interactions: bond (top left), angle (top right), and dihedral (bottom). Image adapted from~\cite{punma}.}\label{bad}
-\end{wrapfigure}
 Non-bonded interactions are commonly modelled with a Lennard-Jones potential:
@@
 A distance cutoff, $r_{cut}$, is often used to reduce the number of pairwise interactions and improve performance.
-
-\begin{wrapfigure}{L}{0.5\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{images/lj.pdf}
-    \caption{The Lennard-Jones potential with relevant distances labelled}\label{lj}
-\end{wrapfigure}
-
 Particles connected by bonds are also modelled by classical forces, for example the bond potential may be treated as a harmonic oscillator:
@@
 
-\begin{wrapfigure}{l}{0.5\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{images/hexane-compare.pdf}
-    \caption{Hexane chemical structure (top) overlaid with coarse-grained mapping \textcolor{blue}{A}-\textcolor{orange}{B}-\textcolor{blue}{A} (bottom)}\label{hexane}
-\end{wrapfigure}
-
 Packages which do coarse-graining and backmapping already exist, so why is another one necessary?
@@
 While including example inputs and a prebuilt software stack via docker is a great first step, these tutorials give very little walkthrough aside from code comments buried in the xml\cite{votca-github}.
+\begin{wrapfigure}{l}{0.5\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{images/hexane-compare.pdf}
+    \caption{Hexane chemical structure (top) overlaid with coarse-grained mapping \textcolor{blue}{A}-\textcolor{orange}{B}-\textcolor{blue}{A} (bottom)}\label{hexane}
+\end{wrapfigure}
 The code is a mix of C++, shell commands, and python, and the user is required to interact with compiled programs through the command-line which makes adding this code into an existing workflow a little more difficult.
@@
 For an example of what I mean by cognitive load, let's compare an example of my proposed coarse-graining scheme to VOTCAs.
-In the following example we will take a hexane molecule and map it to three coarse-grained sites (two carbon atoms per site).
+In the following example we will take a hexane molecule and map it to three coarse-grained sites (two carbon atoms per site, see~\autoref{hexane}).
 

### 2020-08-31 2pd.tex
cleaning up resolved comments
Loading paper into brain and quick comments before call
moving figures around

@@
 \section*{Motivation}
-
-\begin{wrapfigure}{l}{0.5\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{images/dou-miller2018c-fig.pdf}
-    \caption{Schematic showing (a) roll to roll printing process for OPVs, (b) example OPV device, (c) bulk heterojunction structure, and (d) OPV energy generation process.
-Part (a) adapted from ref~\cite{Dou2013}.
-Parts (b,c,d) adapted from ref~\cite{Miller2018c}.}\label{opv}
-\end{wrapfigure}
 
@@
 
-\begin{figure}[h!]
+\begin{wrapfigure}{l}{0.5\linewidth}
     \centering
-    \includegraphics[width=0.8\linewidth]{images/NREL2020.pdf}
-    \caption{Comparision of efficiencies organic and silicon photovoltaic technologies from 1990 to present.
-The current state-of-the-art OPV, polymer-fullerene device coupled with transition metal disulfide, achieves 17.4\% efficiency\cite{Lin2019}.
-Data taken from~\cite{NREL2020}.}\label{nrel}
-\end{figure}
+    \includegraphics[width=\linewidth]{images/dou-miller2018c-fig.pdf}
+    \caption{Schematic showing (a) roll to roll printing process for OPVs, (b) example OPV device, (c) bulk heterojunction structure, and (d) OPV energy generation process.
+Part (a) adapted from ref~\cite{Dou2013}.
+Parts (b,c,d) adapted from ref~\cite{Miller2018c}.}\label{opv}
+\end{wrapfigure}
 
@@
 
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{images/NREL2020.pdf}
+    \caption{Comparision of efficiencies organic and silicon photovoltaic technologies from 1990 to present.
+The current state-of-the-art OPV, polymer-fullerene device coupled with transition metal disulfide, achieves 17.4\% efficiency\cite{Lin2019}.
+Data taken from~\cite{NREL2020}.}\label{nrel}
+\end{figure}
+
 In order to make the most efficient OPVs we need to find the blend of compounds and processing conditions that result in the best structure for those compounds.
+
 \begin{wrapfigure}{l}{0.5\linewidth}
@@
 \end{wrapfigure}
-\leavevmode
+
 The active layer of an OPV is mixture of electron-donor and acceptor compounds: 
@@
 
+%% remove?
 %Even all-atom MD is not without assumptions:
@@
 %%<coarse-grain models are specific>
+%% EJ: Discuss in-person?
 
 %% HELP is the following paragraph/section too big? 
+%% EJ: It's a little rambly, but definitely not bad.
+One check we can do in the background is check for each paragraph or subsection, have we clearly identified outstanding problems or gaps in knowledge, and check whether mention them in the motivation?
+I expect this kind of check will help "tidy up" this paragraph.
 Part of coarse-graining process that is not yet automated is choosing a mapping scheme or a mapping operator.
@@
 
-%% feedback from chris: Also, in the MSIBI section you could take a paragraph or 2 to define what an RDF is, what a Boltzman inverse is, what a potential mean force is, then go into the algorithm steps.
-I feel like defining those terms in a more general sense would be a good preface to describing the actual approach/steps used in the process.
-Also, one other question that popped up is how bonds and angles between coarse beads are handled in the MSIBI step.
 There are numerous methods for deriving coarse-grained potentials from atomistic ones (e.g., force-matching, reverse Monte Carlo), but in this proposal we will focus on Iterative Boltzmann Inversion (IBI).
@@
 The radial distribution function (RDF) describes the probability of finding a particle at a given distance from another particle.
-The RDF can be used to investigate properties such as the density or the phase of a system and the RDF is used in IBI as the target distribution for the non-bonded potentials. %%reword
+The RDF can be used to investigate properties such as the density or the phase of a system and the RDF is used in IBI as the target distribution for the non-bonded potentials. %%reword?
 The process for determining the non-bonded potentials using IBI is as follows:
@@
 For some systems there may not be a potential that represents all states; this is not unique to coarse potentials, atomistic potentials also have this limitation.
+\ej{the second half of this sentence is a big idea that we might consider unpacking more, or maybe omitting?}
 
@@
 %%<need some tie in back to why we would want to go from CG--->atomistic>
+%% EJ: Chat in-person
 

### 2020-08-31 1summ.tex
notes from meeting with boss

@@
 
+this proposal has the potential to transform the manufacturing of sustainable low-cost power generation
+this proposal has a the potential to transform the norms of molecular simulation.
+screening of materials
+original: users of the software not the problem
+while we recognise the proposed work is <aspirational challenging>, we are positioned for success based on our prior work developing proofs of concept and molecular simulation on gpus
+we have adequate resources--
 IM - Potential to advance knowledge and understanding within own and across different fields

### 2020-08-31 2pd.tex
notes from meeting with boss

@@
 The global climate crisis is one of the most pressing issues humanity faces today.
-Consumption of fossil fuels for energy and transportation strongly contributes to rising atmospheric $CO_{2}$ levels the effects of which are global, long-term, and devastating\cite{Solomon2009a}.
-In our technology-driven society, it is unrealistic to think that energy demand will lessen, in fact global energy consumption is predicted to increase from 17 TW in 2010 to 27 TW in 2040\cite{Mazzio2015}.
+Consumption of fossil fuels for energy and transportation is the primary contributor to rising atmospheric $CO_{2}$ levels\cite{Solomon2009a}.
+%% The effects of rising CO2 inequitable long-lasting global devasting
+Global energy consumption is predicted to increase from 17 TW in 2010 to 27 TW in 2040\cite{Mazzio2015}.
+%% get 2020/2019 number
+%% replace next four sentences
 In order to protect our climate, we need a non-polluting, cost-efficient way to provide electricity.
@@
 However, our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar\cite{Wirth2017}.
+%% solar power represents one way to sustainably meet our energy demands yet.
+generating electricity with solar panels is a sustainable way to meet growing energy demands.
+and there is opportunity to increase the contribution of solar energy generation to the green energy
+%% we need to make the economic case for OPVs 
+%% despite improvements in solar power generation over the last 40 years, the cost photovoltaics has prevented solar power from being a large part of the energy generation portfolio
 Traditionally, photovoltaic (PV) devices, which can convert incedent light into electric current, were made of inorganic materials like silicon.
@@
 However, other materials still outperform OPVs (see \autoref{nrel}), and in order to become a viable, cost-effective option OPVs need to be more efficient\cite{Mazzio2015}.
+%% make this sentence better
 
@@
 
+% how can OPVs be more efficient?
+%% organic photovoltaics are a focus of this research because they represent the best opportunity
+%% this paragraph focus on cost/efficiency
+%% espinosa 2013
 The theoretical efficiency limit (Shockley-Queisser limit) for a p-n single junction solar cell is about 30\%\cite{Shockley1961}.
@@
 And in 2019, a cell using an NFA functionalized with chlorine groups was found to achieve 16.5\% efficiency\cite{Cui2019}. 
-
+%% cost and efficiency all depend on self assembly of the active layer
+%% last sentence
+%% include shockley-q limit - maybe also delta
 \begin{figure}[h!]
@@
     \caption{Comparision of efficiencies organic and silicon photovoltaic technologies from 1990 to present.
-The current state-of-the-art OPV, polymer-fullerene device coupled with transition metal disulfide, achieves 17.4\% efficiency\cite{Lin2019}.
+The current state-of-the-art OPV, polymer-fullerene device coupled with a transition metal disulfide, achieves 17.4\% efficiency\cite{Lin2019}.
 Data taken from~\cite{NREL2020}.}\label{nrel}
@@
 In order to make the most efficient OPVs we need to find the blend of compounds and processing conditions that result in the best structure for those compounds.
-
 \begin{wrapfigure}{l}{0.5\linewidth}
@@
 \end{wrapfigure}
-
 The active layer of an OPV is mixture of electron-donor and acceptor compounds: 
-The ideal morphology is a micro phase-separated interpenetrating network called a bulk heterojunction (BHJ) (see \autoref{opv} c).
-The performance of an OPV device is intimately linked with the structure of the active layer:
-With minor modifications, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
-\autoref{chemistries} shows a selection of possible OPV donor and acceptor chemistries.
+With minor modifications, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment (see~\autoref{chemistries}).
 This wide range of compounds provides the freedom to tune our OPVs, but it also increases the scope of the problem.
-
-Imagine, you are a chemist synthesizing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor, ITIC, and a polymer donor, PTB7. 
+Imagine, you are a chemist preparing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor, ITIC, and a polymer donor, PTB7. 
 Each compound costs \$500 for 100 mg\cite{sigmaaldrich}.
@@
 
+%% length-scale problem
 Molecular simulation also gives us insight into the atomic interactions which drive the self assembly of an OPV morphology.
@@
 By breaking our simulation apart into separate steps and equilibrating different lengths scales individually, we can get equilibrated morphologies on multiple length scales more efficiently.
-
-Already good, open-source packages exist to address the problem of coarse-graining and/or backmapping\cite{Marrink2007,Ruhle2009,Maerzke2011,MorphCT,Wassenaar2014b}.
-%% these citations are martini, votca, trappe, morphct, backwards.py
-By making code open source and freely availiable, developers contribute to the knowledge of a global community. 
-But just because something is availiable doesn't mean it is accessible: often just figuring out how to use an existing package can be very difficult\cite{Cummings2019}.
-These existing codebases can appear to a new user as monolithic and indecipherable because their design has been to solve a problem, which they do, instead of design with a focus on how people learn.
-These codebases also rely on users piecing together multiple, often incompatible, bits of software, using manually created xml files, or deciding how to classify an atom grouping based on the user's chemical intuition.
-All of these factors contribute to a reproducibility crisis in the computational sciences\cite{Baker2016}.
+If this project is going to have the impact we desire using molsim to identify opvs, we need every step of the way and the resulting data is can be verified we need workflows that enable us working infrastructure using our models/ morphologies
+the key to doing this is ensuring that our sims are
 By keeping best practices for software development and teaching in mind, we can strive to make tools which make science more transferrable, reproducibile, usable, and extensible (TRUE)\cite{Thompson2020}.
-Best software development practices include using version control software, such as git, to facilitate the process of tracking and merging changes to a code repository, especially important when working collaboratively.
-Also among these best practices are using unit tests and continuous integration to ensure that errors are quickly and automatically caught\cite{Wilson2014}.
-Instead of writing dense, inseparable scripts which rely on the user manually following a command prompt or editing multiple text files, we aim to keep code small and modular to make it easier to use and understand\cite{Adorf2018a}.
-Following these guidelines not only makes our code easier to develop and debug but also reduces the cognitive load for a new user\cite{Jankowski2019}.
-Providing good documentation and tutorials is also imperative for onboarding new users.
-Jupyter Notebooks, which are a combination of interactive code and formatted text and images, can be used like a lab notebook for computational scientists in order to demonstrate the process, rationale, and the story of each experiment and the exact steps to get the results shown\cite{jupyter, Rule2019a}.
-When writing these tutorials, it is wise to remember that the data never speaks for itself: although including input and output files of a calculation is a good first step, they must be accompanied by the story of what the data means and how a user can know that meaning for themselves\cite{SWC, Wilson2016}.
 
@@
 \section*{Research Objectives}
-
+%% reflective numbered objectives
+% were breaking this project into four steps
 Ultimately the goal this research is to help solve the global energy crisis. 
@@
 
+\subsection*{Molecular Simulation Infrastructure}
+
+Already good, open-source packages exist to address the problem of coarse-graining and/or backmapping\cite{Marrink2007,Ruhle2009,Maerzke2011,MorphCT,Wassenaar2014b}.
+%% these citations are martini, votca, trappe, morphct, backwards.py
+By making code open source and freely availiable, developers contribute to the knowledge of a global community. 
+But just because something is availiable doesn't mean it is accessible: often just figuring out how to use an existing package can be very difficult\cite{Cummings2019}.
+These existing codebases can appear to a new user as monolithic and indecipherable because their design has been to solve a problem, which they do, instead of design with a focus on how people learn.
+These codebases also rely on users piecing together multiple, often incompatible, bits of software, using manually created xml files, or deciding how to classify an atom grouping based on the user's chemical intuition.
+All of these factors contribute to a reproducibility crisis in the computational sciences\cite{Baker2016}.
+By keeping best practices for software development and teaching in mind, we can strive to make tools which make science more transferrable, reproducibile, usable, and extensible (TRUE)\cite{Thompson2020}.
+Best software development practices include using version control software, such as git, to facilitate the process of tracking and merging changes to a code repository, especially important when working collaboratively.
+Also among these best practices are using unit tests and continuous integration to ensure that errors are quickly and automatically caught\cite{Wilson2014}.
+Instead of writing dense, inseparable scripts which rely on the user manually following a command prompt or editing multiple text files, we aim to keep code small and modular to make it easier to use and understand\cite{Adorf2018a}.
+Following these guidelines not only makes our code easier to develop and debug but also reduces the cognitive load for a new user\cite{Jankowski2019}.
+Providing good documentation and tutorials is also imperative for onboarding new users.
+Jupyter Notebooks, which are a combination of interactive code and formatted text and images, can be used like a lab notebook for computational scientists in order to demonstrate the process, rationale, and the story of each experiment and the exact steps to get the results shown\cite{jupyter, Rule2019a}.
+When writing these tutorials, it is wise to remember that the data never speaks for itself: although including input and output files of a calculation is a good first step, they must be accompanied by the story of what the data means and how a user can know that meaning for themselves\cite{SWC, Wilson2016}.
 \section*{Preliminary Work}

### 2020-08-31 2pd.tex
addressed most comments that I remember from meeting

@@
 Consumption of fossil fuels for energy and transportation is the primary contributor to rising atmospheric $CO_{2}$ levels\cite{Solomon2009a}.
-%% The effects of rising CO2 inequitable long-lasting global devasting
-Global energy consumption is predicted to increase from 17 TW in 2010 to 27 TW in 2040\cite{Mazzio2015}.
-%% get 2020/2019 number
-%% replace next four sentences
-In order to protect our climate, we need a non-polluting, cost-efficient way to provide electricity.
-Harnessing solar energy is an important part of a green energy solution.
-Renewable energy accounted for 11\% of the U.S. energy consumption in 2019 and of that 9\% was from solar (approximately 1\% of the total energy)\cite{USEIA2020}.
-However, our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar\cite{Wirth2017}.
-%% solar power represents one way to sustainably meet our energy demands yet.
-generating electricity with solar panels is a sustainable way to meet growing energy demands.
-and there is opportunity to increase the contribution of solar energy generation to the green energy
-%% we need to make the economic case for OPVs 
-%% despite improvements in solar power generation over the last 40 years, the cost photovoltaics has prevented solar power from being a large part of the energy generation portfolio
-Traditionally, photovoltaic (PV) devices, which can convert incedent light into electric current, were made of inorganic materials like silicon.
-But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative\cite{Tang1986b}.
-The advantage of OPVs over inorganic PV devices is that OPVs are lightweight, low cost, easier to produce, and flexible. 
-OPVs can be manufactured large scale in a roll to roll printing process, similar to newspaper, as shown in~\autoref{opv} a\cite{Dou2013}.
-However, other materials still outperform OPVs (see \autoref{nrel}), and in order to become a viable, cost-effective option OPVs need to be more efficient\cite{Mazzio2015}.
-%% make this sentence better
+Changes in the climate influenced by atmospheric $CO_{2}$ are long-lasting, devasting, and inequitable, often impacting the poorest nations the hardest.
+Global energy consumption is predicted to increase from 19 TW in 2020 to 27 TW in 2040\cite{Mazzio2015, ieo2020}.
+Solar power represents one way to sustainably meet our energy demands and there is opportunity to increase the contribution of solar energy generation to green energy.
+Despite improvements in solar power generation over the last 40 years, the cost of photovoltaics (PVs) has prevented solar power from being a large part of the energy generation portfolio.
+In order for solar power to be a viable option, large scale PV technology needs to be more economical and efficient\cite{Mazzio2015,Espinosa2012}.
 
@@
 
-% how can OPVs be more efficient?
-%% organic photovoltaics are a focus of this research because they represent the best opportunity
-%% this paragraph focus on cost/efficiency
+Organic photovoltaics (OPVs) are a focus of this research because they represent the best opportunity for cost effective solar power.
 %% espinosa 2013
@@
 The trend of the silicon cells shows that the efficiency gain is levelling off as the devices approach the Shockley-Queisser limit.
-OPV devices, however, still have a lot of room for improvement, and recent increases in OPV device efficiency reflects this.
-Many of the recent advancements in OPV technology have been through specialized processing or combinations of new chemistries.
+OPV devices, however, still have a lot of room for improvement, and recent increases in efficiency reflect this.
+Many of the latest advancements in OPV technology have been through specialized processing or combinations of new chemistries.
 One new chemical moiety which has recieved attention is the ladder backbone structure seen in many non-fullerene acceptors (NFAs), see \autoref{chemistries}.
@@
 And in 2019, a cell using an NFA functionalized with chlorine groups was found to achieve 16.5\% efficiency\cite{Cui2019}. 
-%% cost and efficiency all depend on self assembly of the active layer
-%% last sentence
-%% include shockley-q limit - maybe also delta
+Ultimately, the efficiency of a solar cell depends on the self-assembly of its active layer.
+
 \begin{figure}[h!]
@@
 
-%% length-scale problem
-Molecular simulation also gives us insight into the atomic interactions which drive the self assembly of an OPV morphology.
+Simulating an OPV morphology requires careful consideration. %% reword
 A complication of the simulation of OPV polymers is that the properties which predict a device's efficiency, for example charge transport, span multiple length scales.
-The atomic and electronic properties are important for light absorption, in which an exciton is created, and charge transfer, where the exciton is dissociated into a free electron and hole\cite{Scharber2006a,Hoppe2004,Mazzio2015}.
-At the same time, the exciton finding an interface at which to dissociate and the separated charges finding a path to an electrode both depend on the morphology of the active layer.
 So, in order to model this system, a multiscale approach is necessary.
 By breaking our simulation apart into separate steps and equilibrating different lengths scales individually, we can get equilibrated morphologies on multiple length scales more efficiently.
-If this project is going to have the impact we desire using molsim to identify opvs, we need every step of the way and the resulting data is can be verified we need workflows that enable us working infrastructure using our models/ morphologies
-the key to doing this is ensuring that our sims are
-By keeping best practices for software development and teaching in mind, we can strive to make tools which make science more transferrable, reproducibile, usable, and extensible (TRUE)\cite{Thompson2020}.
+Another complication of this research is its computational scope.
+If this project is going to have the desired impact (i.e., using molecular simulation to identify novel OPVs), every step of the process and the resulting data must be reproducible and validated.
+The nature of a multiscale simulation requires translation between formats and units and accurate handling of large data, and thus requires infrastructure to reduce error.
+By adhering to recent guidelines in the computational sciences community, we can strive to make tools which make science more transferrable, reproducibile, usable, and extensible (TRUE)\cite{Thompson2020}.
+Although the molecular and computational scope of this project is broad, by using and building upon existing architectures we can manage the multiscale nature of this project and contribute reproducible science.
+%% omg help words are hard.
 
@@
 \section*{Research Objectives}
-%% reflective numbered objectives
-% were breaking this project into four steps
+
 Ultimately the goal this research is to help solve the global energy crisis. 
@@
 This research aims to gain insight about new OPV compound morphologies using molecular simulation.
+In order to achieve this goal, we have defined the following objectives:
+\begin{enumerate}
+    \item {Develop a generalized toolset for coarse-graining and performing simulations of novel molecules for organic photovoltaics}
+    \item {Develop a general tool to calculate atomistic positions from a coarse-grained morphology}
+    \item {Predict nanostructures of novel OPV chemistries}
+    \item {Identify chemical features correlated with robust self-assembly and good charge transport}
+\end{enumerate}
 
@@
 
+Renewable energy accounted for 11\% of the U.S. energy consumption in 2019 and of that 9\% was from solar (approximately 1\% of the total energy)\cite{USEIA2020}.
+However, our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar\cite{Wirth2017}.
+
 The performance of an OPV device can be quantified by many metrics.
@@
 
+Traditionally, photovoltaic (PV) devices, which can convert incedent light into electric current, were made of inorganic materials like silicon.
+But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative\cite{Tang1986b}.
+The advantage of OPVs over inorganic PV devices is that OPVs are lightweight, low cost, easier to produce, and flexible. 
+OPVs can be manufactured large scale in a roll to roll printing process, similar to newspaper, as shown in~\autoref{opv} a\cite{Dou2013}.
 Inorganic PV devices came first and are still the most efficient, but they are more costly to produce, use rare elements, and their production causes other environmental issues, so they aren't the best solution for solar energy harvesting.
@@
 
+The atomic and electronic properties are important for light absorption, in which an exciton is created, and charge transfer, where the exciton is dissociated into a free electron and hole\cite{Scharber2006a,Hoppe2004,Mazzio2015}.
+At the same time, the exciton finding an interface at which to dissociate and the separated charges finding a path to an electrode both depend on the morphology of the active layer.
 \subsection*{Molecular Dynamics}

### 2020-08-31 2pd.tex
updating library and moving figures

@@
 
-\begin{wrapfigure}{l}{0.5\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{images/dou-miller2018c-fig.pdf}
-    \caption{Schematic showing (a) roll to roll printing process for OPVs, (b) example OPV device, (c) bulk heterojunction structure, and (d) OPV energy generation process.
-Part (a) adapted from ref~\cite{Dou2013}.
-Parts (b,c,d) adapted from ref~\cite{Miller2018c}.}\label{opv}
-\end{wrapfigure}
-
-Organic photovoltaics (OPVs) are a focus of this research because they represent the best opportunity for cost effective solar power.
+Organic photovoltaics (OPVs, see~\autoref{opv}) are a focus of this research because they represent the best opportunity for cost effective solar power.
 %% espinosa 2013
@@
 OPV devices, however, still have a lot of room for improvement, and recent increases in efficiency reflect this.
+\begin{wrapfigure}{l}{0.5\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{images/dou-miller2018c-fig.pdf}
+    \caption{(a) roll to roll printing process for OPVs, (b) example OPV device, (c) bulk heterojunction structure, and (d) OPV energy generation process.
+Part (a) adapted from ref~\cite{Dou2013}.
+Parts (b,c,d) adapted from ref~\cite{Miller2018c}.}\label{opv}
+\end{wrapfigure}
 Many of the latest advancements in OPV technology have been through specialized processing or combinations of new chemistries.
@@
 In order to make the most efficient OPVs we need to find the blend of compounds and processing conditions that result in the best structure for those compounds.
+The active layer of an OPV is mixture of electron-donor and acceptor compounds: 
+With minor modifications, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment (see~\autoref{chemistries}).
+This wide range of compounds provides the freedom to tune our OPVs, but it also increases the scope of the problem.
+Imagine, you are a chemist preparing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor, ITIC, and a polymer donor, PTB7.
+
 \begin{wrapfigure}{l}{0.5\linewidth}
@@
 \end{wrapfigure}
-The active layer of an OPV is mixture of electron-donor and acceptor compounds: 
-With minor modifications, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment (see~\autoref{chemistries}).
-This wide range of compounds provides the freedom to tune our OPVs, but it also increases the scope of the problem.
-Imagine, you are a chemist preparing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor, ITIC, and a polymer donor, PTB7. 
-Each compound costs \$500 for 100 mg\cite{sigmaaldrich}.
+\noindent Each compound costs \$500 for 100 mg\cite{sigmaaldrich}.
 The solvent you use and the concentrations of your active compounds changes the device performance\cite{Hoppe2004a}.
@@
 There are countless variations of electron donor polymers, fullerene acceptors, and more recently small molecule, non-fullerene acceptors (NFAs) have been recieving attention for their potential to achieve higher efficiencies than their fullerene counterparts\cite{Dou2013}.
-A poly-3-hexylthiophene (P3HT):NFA blend was shown to have 11\% PCE, compared to the state-of-the-art 6.4\% in P3HT:PCBM\cite{Baran2017}.
+A P3HT:NFA blend was shown to have 11\% PCE, compared to the state-of-the-art 6.4\% in P3HT:PCBM\cite{Baran2017}.
 Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70--80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h)\cite{Baran2017}.

### 2020-08-31 2pd.tex
commenting out some moved stuff that i'll delete maybe later?

@@
 Organic photovoltaics (OPVs, see~\autoref{opv}) are a focus of this research because they represent the best opportunity for cost effective solar power.
-%% espinosa 2013
 The theoretical efficiency limit (Shockley-Queisser limit) for a p-n single junction solar cell is about 30\%\cite{Shockley1961}.
@@
 
-Renewable energy accounted for 11\% of the U.S. energy consumption in 2019 and of that 9\% was from solar (approximately 1\% of the total energy)\cite{USEIA2020}.
-However, our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar\cite{Wirth2017}.
+%Renewable energy accounted for 11\% of the U.S. energy consumption in 2019 and of that 9\% was from solar (approximately 1\% of the total energy)\cite{USEIA2020}.
+%However, our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar\cite{Wirth2017}.
 
@@
 
-The atomic and electronic properties are important for light absorption, in which an exciton is created, and charge transfer, where the exciton is dissociated into a free electron and hole\cite{Scharber2006a,Hoppe2004,Mazzio2015}.
-At the same time, the exciton finding an interface at which to dissociate and the separated charges finding a path to an electrode both depend on the morphology of the active layer.
+%The atomic and electronic properties are important for light absorption, in which an exciton is created, and charge transfer, where the exciton is dissociated into a free electron and hole\cite{Scharber2006a,Hoppe2004,Mazzio2015}.
+%At the same time, the exciton finding an interface at which to dissociate and the separated charges finding a path to an electrode both depend on the morphology of the active layer.
 \subsection*{Molecular Dynamics}

### 2020-09-01 reading-notes.tex
replaced all missing citations
writing. filling in gaps
new papers

@@
 
-\cite{Mazzio2015}
+\cite{Mazzio2015} **
 
@@
 
-\cite{Berendsen2010}
+\cite{Berendsen2010} *
 
@@
 
+\cite{Gao2020}
+polymer solar cells with nonfullerene acceptors - analysing morphology formation of nonfullerene/polymer cells with effective polymer thermodynamic quantity: Flory-Huggins interaction parameter.
+>1000 NFAs
+they cite a material getting over 18\% PCE?? refs 13,14
+good starting point is miscibility
+(flory huggins is related to miscibility but takes into account size differences between polymer/solvent)
+this metric is useful for narrowing down what might be a good solar cell
+
+\cite{Lee2020}
+solvent evaporation study using MD
+explicit solvent is removed intermittently from far above the surface to mimic the open air
+this is different than other simulations where a solvent molecule was removed at random
+they want to see the effects of concentration gradients
+They see that some solvent molecules are trapped in the film and many species move less (based on MSD) as the ismulation progresses
+
 \bibliography{library}

### 2020-09-01 2pd.tex
rewriting some of motivation, opvs,
* movinf figures

@@
 Solar power represents one way to sustainably meet our energy demands and there is opportunity to increase the contribution of solar energy generation to green energy.
-Despite improvements in solar power generation over the last 40 years, the cost of photovoltaics (PVs) has prevented solar power from being a large part of the energy generation portfolio.
+Despite improvements over the last 40 years, the cost of photovoltaic (PV) devices has prevented solar power from being a large part of the energy generation portfolio.
 In order for solar power to be a viable option, large scale PV technology needs to be more economical and efficient\cite{Mazzio2015,Espinosa2012}.
 
-Organic photovoltaics (OPVs, see~\autoref{opv}) are a focus of this research because they represent the best opportunity for cost effective solar power.
+Organic photovoltaics (OPVs, see~\autoref{opv}) are a focus of this research because they represent the best opportunity for cost-effective solar power.
 The theoretical efficiency limit (Shockley-Queisser limit) for a p-n single junction solar cell is about 30\%\cite{Shockley1961}.
@@
 And in 2019, a cell using an NFA functionalized with chlorine groups was found to achieve 16.5\% efficiency\cite{Cui2019}. 
+Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70--80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h)\cite{Baran2017}.
+(but how these molecules interact with donor polymers is not yet known and there's >1000 of them and there have been some metrics devised to figure out how to narrow them down like flory-huggins interaction parameter, but it's still really hard.) \cite{Gao2020} %% transition attempt
 Ultimately, the efficiency of a solar cell depends on the self-assembly of its active layer.
@@
 In order to make the most efficient OPVs we need to find the blend of compounds and processing conditions that result in the best structure for those compounds.
-The active layer of an OPV is mixture of electron-donor and acceptor compounds: 
-With minor modifications, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment (see~\autoref{chemistries}).
-This wide range of compounds provides the freedom to tune our OPVs, but it also increases the scope of the problem.
-Imagine, you are a chemist preparing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor, ITIC, and a polymer donor, PTB7.
+The active layer of an OPV is a mixture of electron-donor and acceptor compounds:
 
@@
 \end{wrapfigure}
-\noindent Each compound costs \$500 for 100 mg\cite{sigmaaldrich}.
+\noindent With minor modifications, the number of compounds and the processing conditions can become an intractable problem for experiment (see~\autoref{chemistries}).
+The number of possibilities compounds provides an opportunity for better OPVs, but it also increases the scope of the problem.
+Imagine, you are a chemist preparing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor, ITIC, and a polymer donor, PTB7. 
+Each compound costs \$500 for 100 mg\cite{sigmaaldrich}.
 The solvent you use and the concentrations of your active compounds changes the device performance\cite{Hoppe2004a}.
@@
 The distribution of polymer lengths affects the device performance\cite{Zhao2013b}.
-Changing the functional groups on ITIC changes how it packs in a crystal, its electron affinity, and thus its performance in a device\cite{Swick2019a}.
-All this would be to determine the performance of just one donor/acceptor combination in one category of potential compounds\cite{Dou2013}.
+Seemingly minor changes to the functional groups on either species affects the device performance\cite{Swick2019a}.
+All these parameter require consideration just to determine the performance of one donor/acceptor combination in one category of potential compounds\cite{Dou2013}.
 This is where molecular simulation can help.
@@
 The nature of a multiscale simulation requires translation between formats and units and accurate handling of large data, and thus requires infrastructure to reduce error.
-By adhering to recent guidelines in the computational sciences community, we can strive to make tools which make science more transferrable, reproducibile, usable, and extensible (TRUE)\cite{Thompson2020}.
-Although the molecular and computational scope of this project is broad, by using and building upon existing architectures we can manage the multiscale nature of this project and contribute reproducible science.
+By adhering to recent guidelines in the computational sciences community, we can strive to design tools which are transferrable, reproducibile, usable, and extensible (TRUE)\cite{Thompson2020}.
+Although the molecular and computational scope of this project is broad, by using and building upon existing architectures we can manage the multiscale nature of this project and contribute to reproducible science.
 %% omg help words are hard.
@@
 There are countless variations of electron donor polymers, fullerene acceptors, and more recently small molecule, non-fullerene acceptors (NFAs) have been recieving attention for their potential to achieve higher efficiencies than their fullerene counterparts\cite{Dou2013}.
-A P3HT:NFA blend was shown to have 11\% PCE, compared to the state-of-the-art 6.4\% in P3HT:PCBM\cite{Baran2017}.
-Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70--80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h)\cite{Baran2017}.
 Coarse grain models do not yet exist for many of these NFAs, and with so many varieties an adaptable pipeline makes more sense than a single model.
@@
 
-The performance of an OPV device can be quantified by many metrics.
-The power conversion efficiency (PCE or sometimes $\eta_{e}$) is the ratio of electrical power produced by the device to the power of incedent photons.
+%%<is there a citation for why charge transport is a good proxy for PCE?>
+
+Traditionally, photovoltaic (PV) devices, which can convert incedent light into electric current, were made of inorganic materials like silicon.
+But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative\cite{Tang1986b}.
+Compared to inorganic PV devices, OPVs are lightweight, low cost, easier to produce, and flexible. 
+OPVs can be manufactured large scale in a roll to roll printing process, similar to newspaper, as shown in~\autoref{opv} a\cite{Dou2013}.
+Inorganic PV devices came first and are still the most efficient, but they are more costly to produce, use rare elements, and their production causes other environmental issues, so they aren't the best solution for solar energy harvesting.
+
+A common metric to quantify the performance of a PV is the power conversion efficiency (PCE or sometimes $\eta_{e}$).
+The PCE is the ratio of electrical power produced by the device to the power of incedent photons.
 Higher PCE means the device is more efficient.  
@@
 Finally, the the number of charges which reach the electrode depends on the driving force or gradient resulting from the potentials of the electrons and holes\cite{Hoppe2004}.
-%%<is there a citation for why charge transport is a good proxy for PCE?>
 
-Traditionally, photovoltaic (PV) devices, which can convert incedent light into electric current, were made of inorganic materials like silicon.
-But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative\cite{Tang1986b}.
-The advantage of OPVs over inorganic PV devices is that OPVs are lightweight, low cost, easier to produce, and flexible. 
-OPVs can be manufactured large scale in a roll to roll printing process, similar to newspaper, as shown in~\autoref{opv} a\cite{Dou2013}.
-Inorganic PV devices came first and are still the most efficient, but they are more costly to produce, use rare elements, and their production causes other environmental issues, so they aren't the best solution for solar energy harvesting.
-The first OPV was created by Tang in 1986 and used a bilyaer structure containing copper phthalocyanine and a perylene derivitive\cite{Tang1986b}. 
+The first OPV was created by Tang in 1986 and used a bilayer structure containing copper phthalocyanine and a perylene derivitive\cite{Tang1986b}. 
 This early device had a PCE of 0.95\%.
@@
 
-The planar acceptor-donor-acceptor moeity seen in many NFA backbones (see \autoref{itic}) may have more efficient exciton splitting, as compared to a fullerene acceptor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer\cite{Yi2018a}.
+\noindent The planar acceptor-donor-acceptor moeity seen in many NFA backbones (see \autoref{itic}) may have more efficient exciton splitting, as compared to a fullerene acceptor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer\cite{Yi2018a}.
 
@@
 Due to the conjugated pi-orbitals in these molecules the absorption of sunlight can excite an electron into a frontier orbital and generate an exciton, a couloubicly bound electron-hole pair.
-OPVs are made as a mixture of electron-donor and electron-acceptor compounds in a structure called a bulk-heterojunction.
+OPVs are made as a mixture of electron-donor and electron-acceptor compounds in a structure called a bulk heterojunction.
 Depending on the bulk morphology of these compounds, the exciton can travel to an acceptor-donor interface and dissociate into free electron and hole then these free charges generate current if they can subsequently make their way to an electrode.
@@
 %% EJ: Discuss in-person?
-
 %% HELP is the following paragraph/section too big? 
@@
 Whether the structure is similar then is based on the user's chemical knowledge, judgement, and intuition.
-Many other mapping schemes also rely on the user's chemical intuition (e.g., what parts of the molecule shouldn't be allowed to bend?
-What groups have the most dominant interactions in this structure)\cite{Huang2010, Knotts2007}.
-As the number of atoms in the fine grain structure increases, the number of possible mappings increase drastically.
+Many other mapping schemes also rely on the user's chemical intuition (e.g., grouping the atoms in ring structures which move less or grouping structures based on the dominant interactions, like the base pairs in DNA)\cite{Huang2010, Knotts2007}.
+As the number of atoms in the fine grain structure increases, the number of possible mappings increase drastically and manually deciding a mapping operator becomes more difficult.
+
 There have been efforts to create algorithms for automating the process of deciding which atoms are grouped in a ``super atom''.
@@
 A mapping operator based on the centers of charge was shown to accurately model electrostatic properties\cite{Cao2015a}.
-Deciding on a mapping operator is one part of creating a coarse-grained model, the second step is to create an effective potential for the site.
+However, there is still no best method for choosing the mapping operator.
+Deciding on a mapping operator is just the first step of creating a coarse-grained model, next is to create an effective potential for the site.
 
@@
 But optimization to the liquid-vapor equilibrium, although useful for prediction of thermodynamic properties, may not be ideal for prediction of structure which will strongly influence charge transport.
-%%<so we probably want to create our own potentials>
-%%<IBI potentials are sometimes transferrable and it is not clear why sometimes they are and sometimes they aren't.>~\cite{Moore2014}
 
@@
 All of these factors contribute to a reproducibility crisis in the computational sciences\cite{Baker2016}.
+
 By keeping best practices for software development and teaching in mind, we can strive to make tools which make science more transferrable, reproducibile, usable, and extensible (TRUE)\cite{Thompson2020}.
@@
 When writing these tutorials, it is wise to remember that the data never speaks for itself: although including input and output files of a calculation is a good first step, they must be accompanied by the story of what the data means and how a user can know that meaning for themselves\cite{SWC, Wilson2016}.
+By keeping these ideas in mind throughout development, we can develop more efficiently and create tools which are easier to use and produce reproducible results.
+
 \section*{Preliminary Work}
@@
 \textbf{Completion Critera:} The ability to perform charge-transport calculations of 5 polymer, 5 fullerene-derivative, and 5 ITIC-derived OPV morphologies that have been back-mapped from coarse-grained representations.
-%%\ej{Here's candidate text with being able to USE the back-mapped morphologies, but maybe we want something easier here?} - i'm ok with this goal.
 

### 2020-09-02 abstract.tex
first draft abstract and title from project summary

--- 2020-08-21 1summ.tex
@@
-%%%%%%%%% PROJECT SUMMARY -- 1 page, third person
-% e.g:  "The PI will prove" not "I will prove"
-
-%Below are the pagination, font size, spacing and margin
-%instructions for NSF proposals: \\
-%
-%FastLane does not automatically paginate a proposal.
-%Each section of the proposal must be individually
-%paginated prior to upload to the system. \\
-%
-%Use Computer Modern family of fonts at a font size of 11 points or
-%larger. A font size of less than 10 points may be used for mathematical
-%formulas or equations, figure, table or diagram captions and when
-%using a Symbol font to insert Greek letters or special characters.
-%The text must still be readable. The use of small type not in compliance with the NSF guidelines
-%may be grounds for NSF to return the proposal without review. \\
-%
-%No more than 6 lines of text within a vertical space of 1 inch. \\
-%
-%Margins, in all directions, must be at least an inch. \\
-%
-%
-
+\documentclass{article}
+\begin{document}
 \begin{center}
-\large{\textbf{Title}} %%TODO
-%\large{\textbf{ADVANCEMENT OF ORGANIC PHOTOVOLTAICS THROUGH ARTIFICIAL NEURAL NETWORKS}}
+    \large{\textbf{Simple, flexible generation of coarse grain models for novel organic photovoltaics}}
 \end{center}
@@
 \end{center}
-%\begin{center}
-%\emph{Maximum of 1 page}
-%\end{center}
-% This should be a brief statement of the problem you plan to address.
-% It should look something like an abstract.
 
-%The project summary should be a description of the proposed activity suitable
-%for publication, no more than one page in length. It should not be
-%an abstract of the proposal, but rather a self-contained description of
-%the activity that would result if the proposal were funded. The summary
-%should be written in the third person and include a statement of objectives
-%and methods to be employed. It should be informative to other persons
-%working in the same or related fields and understandable to a scientifically
-%or technically literate lay reader. \\
-%
-%The summary must clearly address in separate statements (within the one-page summary):
-%the intellectual merit of the proposed activity; and the broader impacts
-%resulting from the proposed activity. Proposals that do not separately
-%address both criteria within the one-page Project Summary will be returned without
-%review. \\
+Consumption of fossil fuels for energy is the main contributor to rising atmospheric $CO_{2}$. 
+Solar power provides a renewable, non-polluting, sustainable option.
+Organic photovoltaic (OPV) devices, which can convert incedent sunlight to electricity, are the focus of this research because they represent the best opportunity for cost-effective solar power.
+The active layer of an OPV consists of an interpenetrating network of electron donor and acceptor compounds.
+The efficiency of the device depends on the morphology of the active layer.
+In this research we will use molecular simulation to predict the active layer morphology and, in turn, the device efficiency.
 
-Already the effects of human-influenced climate change are readily apparent and devastating. %%<hurtng everyone in particular poor and disadvantaged groups>.
-Burning fossil fuels for energy is the main contributor to rising $CO_{2}$ levels, and the energy demand is only increasing.
-This increase in energy demand along with the need to protect our climate makes finding efficient, renewable energy technologies of the utmost importance.
-Harvesting the abundant solar energy is a good solution because it is renewable, non-polluting, sustainable.
-Devices which convert light to electricity, called photovoltaics, were originally made of silicon and required rare elements and careful, clean-room processing.
-More recently, organic photovoltaic (OPV) devices have recieved attention for their simple, inexpensive manufacture.
-Generally OPV devices are made of a multicompound mixture: usually an electron donor and acceptor which form a mosaic-like structure called a bulk-heterojunction (BHJ).
-The compounds and polymers used in OPVs are made of common elements and can be synthesized with relative ease.
-And the OPV BHJ can often be assembled using simple techniques like roll to roll printing in ambient conditions.
-The process for OPV to generate electricity is as follows: 
-Sunlight excites an electron, which forms an exciton.
-This exciton travels to an acceptor/donor interface and is dissociated into free electron and hole.
-Then the free charges travel to an electrode which generates current.
-However, in order for OPV devices to be a viable solution, they need to be more efficient.
-The efficiency of an OPV device can be improved by changing the chemistry of the electron acceptor and donor compounds, the polymer properties, and tuning the processing conditions of the BHJ.
-With so many parameters, quickly this becomes an intractable problem for experiments to solve.
-This is where molecular simulation comes in.
-
-Molecular dynamics (MD), a simulation technique where atoms are represented by classical forces and their interactions are specified by attractive/repulsive potentials, can be used to probe the thermodynamic processes which determine how OPV compounds will self-assemble into a BHJ morphology.
-Then we can use kinetic monte carlo (KMC) in concert with quantum chemical calculations (QCCs) to determine the charge mobility through these simulated morphologies.
+Molecular dynamics (MD), a simulation technique where atoms are represented by classical forces and their interactions are specified by attractive/repulsive potentials, can be used to probe the thermodynamics of OPV self assembly.
+The charge mobility through these morphologies can be calculated using kinetic monte carlo (KMC) in concert with quantum chemical calculations (QCCs).
 By understanding how charges move through these systems, one can predict which OPVs will be most efficient.
@@
 
-Coarse grain (CG) models, which group multiple atoms together into "super atoms" and using an effective potential to specify the forces acting upon the site, can be used to access length and time scales more relevant to the bulk polymer morphology.
+Coarse grain (CG) models, which group multiple atoms together into ``super atoms'' with the net force on these atoms represented an effective potential, can be used to access length and time scales more relevant to the bulk polymer morphology.
 After a bulk morphology is obtained, we can use backmapping, a process in which the atomistic detail can be reintegrated into a coarse grain model, to restore atomistic detail for use in simulations like KMC/QCC.
 This multiscale simulation workflow allows for OPV morphologies to be equilibrated at length scales relevant to the bulk polymer and to regain the atomistic detail more efficiently using a better starting structure.
-Currently software packages exist that do this but they require tedious manual input and are highly susceptible to user error.
 PI Fothergill will design a simple, chemically sensible coarse graining and backmapping package based on the SMILES chemical input language with a focus on OPVs.
 This will allow for easier setup and execution of multiscale simulation, which can be part of the process to finding the next great OPV technology.
-
-\begin{center}
-    \textbf{Intellectual Merit}
-\end{center}
-% This is why your project is interesting and will help further
-% knowledge in the field of science. 
-%How important is the proposed activity to advancing
-%knowledge and understanding within its own field or across different fields?
-%How well qualified is the proposer (individual or team) to conduct the project?
-%(If appropriate, the reviewer will comment on the quality of prior work.)
-%To what extent does the proposed activity suggest and explore creative, original,
-%or potentially transformative concepts? How well conceived and organized is the
-%proposed activity? Is there sufficient access to resources?  \\
-
-IM - Potential to advance knowledge and understanding within own and across different fields
-- Activities explore creative, original, or potentially transformative concepts?
-A coarse graining pipeline will help make multi-scale simulations more accesible and useable for others. 
-This can be useful for screening of potential OPV compounds.
-what makes a good NFA?
-
-- Plan well-reasoned, well organized, based on sound rationale?
-
-- Mechanism to assess success?
-%%<comparing mobilities, diffraction to experiment>
-
-- How qualified is team?
-%%<talk about what I've done already?>
-
-- Adequate resources to carry out activities?
-%%<talk about our supercomputer allocations?>
-
-%\required{Broader Impacts}
-\begin{center}
-    \textbf{Broader Impacts}
-\end{center}
-% There are 4 kinds of broader impacts.
-% 1. advance discovery and understanding while promoting teaching,
-% training and learning
-% 2. broaden the participation of underrepresented groups
-% 3. disseminated broadly to enhance scientific and technological
-% understanding
-% 4. benefits of the proposed activity to society
-
-%OPV devices reaching consistent efficacies of 15\% have the potential to create a global energy revolution.
-%At this efficiency, OPV devices will surpass inorganic solar cells, and even gas and coal in terms of cost per watt of electricity generation.
-%Thus, regardless of the current administration's reluctance to accept the reality of climate change, OPV devices will be seen superior to 'dirty' power production methods due to their competitive price.
-
-BI - Potential to benefit society, contribute to achievement of desired societal outcomes
-- Activities explore creative, original, or potentially transformative concepts?
-%%<talk about VOTCA?>
-%%<talk about TRUE simulations and reproducibility in the field>
-
-- Plan well-reasoned, well organized, based on sound rationale?
-
-- Mechanism to assess success?
-a sign of well-written, understandable code is if other people use it. 
-It's tricky because this is completely out of my control, but if other people find my code useful--it is a success.
-by integrating what I do with other existing codebases I can help to achieve this goal.
-Also having good tutorials and documentation.
-
-- How qualified is team?
-Helping to make research transferrable, reproducible, useable, and extensible. 
-Writing tutorials and documentation while keep in mind principles of oftware carpentry instructor training. 
-Using software dev best practices to be efficient and make sure that I'm not making code for someone else to struggle through later. 
-Training/teaching undergrads.
-Working as part of a team.
-
-- Adequate resources to carry out activities?
-oss community
-software carpentry training
-experience with teaching/training undergrads
+\end{document}

### 2020-09-03 abstract.tex
delete many sentences

@@
 \begin{center}
-    \large{\textbf{Simple, flexible generation of coarse grain models for novel organic photovoltaics}}
+    \large{\textbf{Advancing organic photovoltaics with reproducible, transferable coarse grain models}}
 \end{center}
@@
 \end{center}
-\begin{center}
-    \textbf{Project Summary}
-\end{center}
 
 Consumption of fossil fuels for energy is the main contributor to rising atmospheric $CO_{2}$. 
-Solar power provides a renewable, non-polluting, sustainable option.
+Solar power provides a non-polluting, sustainable option.
 Organic photovoltaic (OPV) devices, which can convert incedent sunlight to electricity, are the focus of this research because they represent the best opportunity for cost-effective solar power.
@@
 
-Molecular dynamics (MD), a simulation technique where atoms are represented by classical forces and their interactions are specified by attractive/repulsive potentials, can be used to probe the thermodynamics of OPV self assembly.
-The charge mobility through these morphologies can be calculated using kinetic monte carlo (KMC) in concert with quantum chemical calculations (QCCs).
-By understanding how charges move through these systems, one can predict which OPVs will be most efficient.
 However, this simulation workflow suffers from a problem of length scales:
@@
 But equilibrating this morphology at volumes which exceed the exciton dissociation length (~5-10 nm) is prohibitive if every individual atom is considered.
-
-Coarse grain (CG) models, which group multiple atoms together into ``super atoms'' with the net force on these atoms represented an effective potential, can be used to access length and time scales more relevant to the bulk polymer morphology.
-After a bulk morphology is obtained, we can use backmapping, a process in which the atomistic detail can be reintegrated into a coarse grain model, to restore atomistic detail for use in simulations like KMC/QCC.
 This multiscale simulation workflow allows for OPV morphologies to be equilibrated at length scales relevant to the bulk polymer and to regain the atomistic detail more efficiently using a better starting structure.
@@
 This will allow for easier setup and execution of multiscale simulation, which can be part of the process to finding the next great OPV technology.
+
 \end{document}

### 2020-09-03 abstract.tex
Abstract edits

@@
 The efficiency of the device depends on the morphology of the active layer.
+
 In this research we will use molecular simulation to predict the active layer morphology and, in turn, the device efficiency.
-
-However, this simulation workflow suffers from a problem of length scales:
-Probing charge transport properties with QCCs requires the calculation of electron densities around each atom, which requires knowing the positions of each atom.
-But equilibrating this morphology at volumes which exceed the exciton dissociation length (~5-10 nm) is prohibitive if every individual atom is considered.
-This multiscale simulation workflow allows for OPV morphologies to be equilibrated at length scales relevant to the bulk polymer and to regain the atomistic detail more efficiently using a better starting structure.
-PI Fothergill will design a simple, chemically sensible coarse graining and backmapping package based on the SMILES chemical input language with a focus on OPVs.
-This will allow for easier setup and execution of multiscale simulation, which can be part of the process to finding the next great OPV technology.
+A key challenge herein is spanning the length and time scales relevant to active layer morphology kinetics and charge transport processes, demanding use of tools including density functional theory all the way up to coarse-grained models.
+We propose developing new simulation tools that solve longstanding problems with simulation management, transferability, reproducibility, usability, and extensibility
+Specifically, we develop tools in the Molecular Simulation Design Framework (MoSDeF) for automating the coarse-graining of organic photovoltaic chemistries, and predicting and analyzing equilibrated OPV morphologies.
 

### 2020-09-03 abstract.tex
hi, phen!
some more wordsmithing

@@
 \begin{center}
-    \large{\textbf{Advancing organic photovoltaics with reproducible, transferable coarse grain models}}
+    \large{\textbf{Advancing organic photovoltaics with reproducible, transferable coarse-grained models}}
 \end{center}
@@
 The active layer of an OPV consists of an interpenetrating network of electron donor and acceptor compounds.
-The efficiency of the device depends on the morphology of the active layer.
+The efficiency of OPV devices depends on how the active layer morphology facilitates processes including light absorption and charge transport.
 
-In this research we will use molecular simulation to predict the active layer morphology and, in turn, the device efficiency.
-A key challenge herein is spanning the length and time scales relevant to active layer morphology kinetics and charge transport processes, demanding use of tools including density functional theory all the way up to coarse-grained models.
-We propose developing new simulation tools that solve longstanding problems with simulation management, transferability, reproducibility, usability, and extensibility
+In this research we will use molecular simulation to predict the active layer morphology and how it contributes to device efficiency.
+A key challenge herein is connecting fast processes like charge transport with larger length scales (nanometers) and the timescales of active layer morphology evolution, demanding tools including density functional theory all the way up to coarse-grained models.
+We propose developing new simulation infrastructure that solve longstanding problems with simulation management, transferability, reproducibility, usability, and extensibility
 Specifically, we develop tools in the Molecular Simulation Design Framework (MoSDeF) for automating the coarse-graining of organic photovoltaic chemistries, and predicting and analyzing equilibrated OPV morphologies.

### 2020-09-03 abstract.tex
final draft abs?

@@
 Consumption of fossil fuels for energy is the main contributor to rising atmospheric $CO_{2}$. 
-Solar power provides a non-polluting, sustainable option.
+Solar power provides a non-polluting, sustainable alternative.
 Organic photovoltaic (OPV) devices, which can convert incedent sunlight to electricity, are the focus of this research because they represent the best opportunity for cost-effective solar power.
-The active layer of an OPV consists of an interpenetrating network of electron donor and acceptor compounds.
 The efficiency of OPV devices depends on how the active layer morphology facilitates processes including light absorption and charge transport.
@@
 A key challenge herein is connecting fast processes like charge transport with larger length scales (nanometers) and the timescales of active layer morphology evolution, demanding tools including density functional theory all the way up to coarse-grained models.
-We propose developing new simulation infrastructure that solve longstanding problems with simulation management, transferability, reproducibility, usability, and extensibility
-Specifically, we develop tools in the Molecular Simulation Design Framework (MoSDeF) for automating the coarse-graining of organic photovoltaic chemistries, and predicting and analyzing equilibrated OPV morphologies.
+We propose developing new simulation infrastructure that solves longstanding problems with simulation management, transferability, reproducibility, usability, and extensibility.
+Specifically, we develop tools in the Molecular Simulation Design Framework (MoSDeF) for automating the coarse-graining of OPV chemistries, and predicting and analyzing equilibrated OPV morphologies.
 

### 2020-09-03 abstract.tex
reword and new title

@@
 \begin{center}
-    \large{\textbf{Advancing organic photovoltaics with reproducible, transferable coarse-grained models}}
+    \large{\textbf{Advancing organic photovoltaics with infrastructure for transferable, reproducible, useable, and extensible (TRUE) multiscale models}}
 \end{center}
@@
 Organic photovoltaic (OPV) devices, which can convert incedent sunlight to electricity, are the focus of this research because they represent the best opportunity for cost-effective solar power.
-The efficiency of OPV devices depends on how the active layer morphology facilitates processes including light absorption and charge transport.
+OPV device efficiency depends on how the active layer morphology facilitates processes including light absorption and charge transport.
 
-In this research we will use molecular simulation to predict the active layer morphology and how it contributes to device efficiency.
-A key challenge herein is connecting fast processes like charge transport with larger length scales (nanometers) and the timescales of active layer morphology evolution, demanding tools including density functional theory all the way up to coarse-grained models.
+In this research we will use molecular simulations to predict the active layer morphologies for combinations of chemistries and how they contribute to device efficiency.
+Connecting electronic processes like charge transport with larger length scales of active layer morphology demands simulation workflows between tools which has exposed significant interoperability challenges.
 We propose developing new simulation infrastructure that solves longstanding problems with simulation management, transferability, reproducibility, usability, and extensibility.
-Specifically, we develop tools in the Molecular Simulation Design Framework (MoSDeF) for automating the coarse-graining of OPV chemistries, and predicting and analyzing equilibrated OPV morphologies.
+Specifically, we develop tools in the Molecular Simulation Design Framework (MoSDeF) for automating the coarse-graining of OPV chemistries and predicting and analyzing equilibrated OPV morphologies.
 

### 2020-09-03 abstract.tex
send to undergrads next

@@
 In this research we will use molecular simulations to predict the active layer morphologies for combinations of chemistries and how they contribute to device efficiency.
-Connecting electronic processes like charge transport with larger length scales of active layer morphology demands simulation workflows between tools which has exposed significant interoperability challenges.
-We propose developing new simulation infrastructure that solves longstanding problems with simulation management, transferability, reproducibility, usability, and extensibility.
+Connecting electronic processes like charge transport with larger length scales of active layer morphology demands simulation pipelines, which have exposed significant challenges to software interoperability.
+We propose developing new simulation infrastructure that solves these longstanding problems with simulation management.
 Specifically, we develop tools in the Molecular Simulation Design Framework (MoSDeF) for automating the coarse-graining of OPV chemistries and predicting and analyzing equilibrated OPV morphologies.

### 2020-09-03 1summ.tex
draft pass at im and bi sections

--- 2020-08-21 1summ.tex
@@
 
-IM - Potential to advance knowledge and understanding within own and across different fields
-- Activities explore creative, original, or potentially transformative concepts?
+This proposal has the potential to transform the manufacturing of sustainable low-cost power generation
 A coarse graining pipeline will help make multi-scale simulations more accesible and useable for others. 
-This can be useful for screening of potential OPV compounds.
-what makes a good NFA?
+This is an important step for screening potential OPV compounds.
 
-- Plan well-reasoned, well organized, based on sound rationale?
+This proposal has a the potential to transform the norms of molecular simulation.
+By developing software with a focus on transferrability, reproducibility, usability, and extensibility and thinking beyond just solving a problem but thinking about how to solve the problem for the end-user we can help to change the norms in the computational sciences.
+While we recognise the proposed work is challenging, we are positioned for success based on our prior work developing proofs of concept and molecular simulation on gpus.
 
-- Mechanism to assess success?
-%%<comparing mobilities, diffraction to experiment>
-
-- How qualified is team?
-%%<talk about what I've done already?>
-
-- Adequate resources to carry out activities?
-%%<talk about our supercomputer allocations?>
-
-%\required{Broader Impacts}
 \begin{center}
@@
 
-BI - Potential to benefit society, contribute to achievement of desired societal outcomes
-- Activities explore creative, original, or potentially transformative concepts?
-%%<talk about VOTCA?>
-%%<talk about TRUE simulations and reproducibility in the field>
-
-- Plan well-reasoned, well organized, based on sound rationale?
-
-- Mechanism to assess success?
-a sign of well-written, understandable code is if other people use it. 
-It's tricky because this is completely out of my control, but if other people find my code useful--it is a success.
-by integrating what I do with other existing codebases I can help to achieve this goal.
-Also having good tutorials and documentation.
-
-- How qualified is team?
+Bring new students in to the software development process.
 Helping to make research transferrable, reproducible, useable, and extensible. 
@@
 
-- Adequate resources to carry out activities?
-oss community
-software carpentry training
-experience with teaching/training undergrads
+All code-bases will be free and open source with tutorial and documentation so that not only are they available but accessible.
+By integrating what I do with other existing codebases I can help to achieve this goal.

### 2020-09-08 2pd.tex
added msibi equation

@@
 Multistate iterative Boltzmann inversion (MS IBI) includes data from multiple targets to yield a less state dependent potential\cite{Moore2014}.
-The MS IBI potential is an average of the single state potentials with a weighting function to prioritize a state of interest.
-This method has been shown to accurately reproduce the true potential in monoatomic LJ fluid.
+The MS IBI potential is an average of the single state potentials with a weighting function to prioritize a state of interest, as shown in the following equation:
+\[
+    V_{s,i+1}(r) = V_{s,i}(r) - \frac{1}{N}\sum_{s}\alpha_{s}(r)k_{B}T_{s} \ln\bigg(\frac{g_{s}^{i}(r)}{g_{s}(r)}\bigg)
+\]
+where the subscript $s$ represents the property at that state, $N$ is the total number of states, and $\alpha_{s}(r)$ is a weighting factor allowing for more or less emphasis on each state.
+This method has been shown to accurately reproduce the true potential in monoatomic LJ fluid\cite{Moore2014}.
 When using the MS IBI method, it is important to choose dissimilar states to minimize the potential overlap region.
 If this overlap region is large, there are many potentials which will provide matching RDFs (see \autoref{moore}).
-For some systems there may not be a potential that represents all states; this is not unique to coarse potentials, atomistic potentials also have this limitation.
-\ej{the second half of this sentence is a big idea that we might consider unpacking more, or maybe omitting?}
+For some systems there may not be a potential that represents all states.
 

### 2020-09-09 2pd.tex
update timeline
meeting with boss

@@
 %% HELP this section is rough... not sure what to do.
-My prior work has involved probing the intermolecular interactions which govern dimer and crystal formation.
-An investigation of the excitonic splitting observed in cyanine dye dimers was done using density functional theory (DFT)\cite{Fothergill2018}.
+My prior work has focused on developing and using computational tools to predict and understand self assembly of electronically active molecules.
+The resulting three manuscripts and one poster span all scales from first-principles calculation of electronically active dimers to new tools for analyzing the long-range periodicities of large scale atomistic and coarse-grain simulations.
+In my first publication on dimer formation, an investigation of the excitonic splitting observed in cyanine dye dimers was done using density functional theory (DFT)\cite{Fothergill2018}.
 By comparing calculated with experimental absorption spectra it was found that the solvent may play a large role in the dimer formation and peak shifting.
-An investigation of the supramolecular interactions which guide crystal self-assembly in diphenylurea transition metal complexes was done using density functional theory\cite{Millard2019a}. 
+In my second publication, an investigation of the supramolecular interactions which guide crystal self-assembly in diphenylurea transition metal complexes was done using density functional theory\cite{Millard2019a}.
 My contributions to our perspective paper were mostly about my experience joining the lab and trying to reproduce an existing model; a task which should be very straightforward in a computational field but which any computational scientist can attest is far from simple\cite{Jankowski2019}.
-I also presented a tool I've developed, called GIXStapose, at the Scientific Python conference (SciPy2020)\cite{gixstapose, scipy2020}
-GIXStapose is an interactive structure viewer alongside its simulated diffraction pattern.
-This work had two goals: helping users to see the connections between a structure and it's diffraction pattern and making reproducible figure generation easier.
-The first goal is achieved through a graphical user interface (GUI) which allows users to interact with the structure using the mouse and the diffraction pattern is updated automatically.
-The second goal is accomplished by allowing all steps of the figure generation process (e.g., positioning the camera, setting the colors and lighting, etc) to be scripted and never \textit{requiring} use of the GUI\@.
-These prior works, although not directly related to OPVS or coarse-grained models, have helped me think about how atomic interactions can shape a structure, the struggles that face a new computational scientist, and how I can help.
+In my first poster contribution to the SciPy conference, I presented a tool called GIXStapose, an interactive structure viewer alongside its simulated diffraction pattern\cite{gixstapose, scipy2020}.
+In sum, working at all scales important to OPV morphology has crystallized the need for pipelines emphasizing transferrability, reproducibility, useability, and extensibility.
 
+To improve the useability and extensibility of molecular simulation tools, I have been intentional about incorporating Software Carpentry priniciples into my work.
+Background for thinking about users
+pedagogy for thinking about how users take in new information
+useability
+I have completed Software Carpentry training which has taught me how to break down complex ideas and give learners a chance to use their knowledge.
+With these principles in mind, I have created tutorial examples to help current and future students understand scientific concepts and how to use computational tools\cite{notebooktutorials}
+
+In my scientific software development with the Molecular Simulation and Design Framework (MoSDeF) team
 I have contributed to development of open-source packages including mbuild, foyer, signac, and fresnel\cite{mbuild, foyer, signac, fresnel}.
@@
 As I plan to integrate my future work with existing projects, good collaborative skills will be necessary.
+growth -- nervousness to participate or submit prs empower and shape the way i think about my thesis
 
-I have completed Software Carpentry training which has taught me how to break down complex ideas and give learners a chance to use their knowledge.
-With these principles in mind, I have created tutorial examples to help current and future students understand scientific concepts and how to use computational tools\cite{notebooktutorials}
-
+A specific example of what we mean by improving the transferrability, reproducibility, useability, and extensibility is the coarse-graining tools that I have developed on route to fufilling Objective 1 of this proposal.
 As for work towards my proposed plan, I have created a minimum working example of a coarse-graining and backmapping package which uses SMARTS strings to specify the site chemistries\cite{grits}.
@@
 
-\subsection*{Objective 2: Develop a general tool to calculate atomistic positions from a coarse-grained morphology}
+\subsection*{Objective 2: Develop a general tool to calculate atomistic positions from coarse-grained morphologies}
 
@@
 
-\subsection*{Objective 4: Identify chemical features correlated with robust self-assembly and good charge transport}
+\subsection*{Objective 4: Identify chemical features correlated with robust self-assembly}
+
+- perform lots of simulations, get lots of morphologies, observe state-dependence of self-assembly
+- replicate trials 5 of each thermodynamic state, molecules, concentrations temperature, density
+- how many out of 5 get to the same morphology? (same morphology could be measured by RDF GIXS)
+- machine learning?
+- quantify robustness of assembly relaxation time to equilibrium and proportion of simulations that reach the same equilibrated structure
+- once robustness metric is defined correlate to identify robust self assembly
+- part of this objective will be investigating techniques to probe this correlation including machine learning
+
+\textbf{Completion Critera:} identify measure of robustness to segment our statepoints into 5ths of top 5ths of best assemblers what's similar between them -- top three chemical features
+
+\subsection*{Objective 5: Identify chemical features correlated with good charge transport}
+
+- similar to objective 4 use correlation to determine except replace robustness metric with hole mobility 
+- for all of the morphologies that come out weve got a network that comes out we can easily chop the network to see what matters
+- network analysis of charge transport network to identify morhological features that result in good charge transport see which matters most
+
+\textbf{Completion Critera:} we dont need to make an objective function, chemical and morphological features that result in high hole mobility
 
@@
 GIXS calculations on our backmapped trajectories can be used to validate that our simulations result in the same morphology as experiment.
-While charge transport calculations can be used to rate the efficacy of the active layer morphology.
+While charge transport calculations can be used to measure the efficacy of the active layer morphology.
 Using our lab's charge transport package (MorphCT) on new chemistries, however, will require some work.
@@
 
-\textbf{Completion Critera:} \ej{todo}
-
 \section*{Predicted Outcomes}
@@
 
+- Deeper understanding of using thermodynamics to self-assemble advanced electronic materials
+- Chemical features which correlate with robust self assembly
+- Chemical and morphological features correlated with good charge transport
+- A library of equilibrated OPV morphologies hosted publically through scholarworks freely available
+- An updated understanding of best practices for coarse-graining organic photovoltaics Coarse-grain models
+- new coarse grain models designed for transferrability and usebility - design for mosdef tools
+- Our repository of coarse-graining tool including tutorials designed for onboarding new users
 \begin{enumerate}
@@
 
-Although minimum working examples have been developed for both the coarse-graining and backmapping packages, I still expect to struggle when mapping new compounds.
-Sometimes the SMARTS/SMILES mapping won't work without careful choice of sites.
-This can be a little frustrating but is still preferrable to having to manually specify the mapping of each atom.
-At least the reasons that a SMARTS mapping fails are usually understandable (e.g., the order of the sites matters) or chemically sensible (e.g., one SMILES string may contain another --- just as one chemical moeity may be composed of more submoeities).
-%%<this is a word?>)
-
-It may also be difficult to find a good coarse-graining scheme for the NFA compounds. 
-These compounds are often composed of large planar backbones with floppy side chains.
-Finding a suitable mapping to represent both aspects may be difficult.
+- obj 4 and 5 maybe there aren't descriptors that classify good CT or assemblers?
+our past work with artificial net has done a better than expected job with p3ht and ct is confidence inspiring but if we dont find the top three-- at least we'll have a dataset that is a stepping stone toward solving but we should be able to generate features of NFAs and polymers
+- obj 3 needs models and  access to computational resources.
+some of the coarse graining and pipelining work might be limited if objective 1 doesn't go to plan but we can still use naiive models like UA bsu, xsede, inl, and local HPC resources inspire confidence that wwe will have adequate resources
+- obj 1 and 2 no specific this stand in the way, stitching together existing software and trying out new approaches.
+thing that inspires confidence around getting these done is active participation in mosdef, software development enroute to this.
 
@@
         Generate Coarse-Grain Morphologies           
-            & & & & & & & & & & & & & & \multicolumn{4}{|c|}{{\cellcolor{lgray}}}& & &\\
+            & & & & & & & & & & & & & & \multicolumn{5}{|c|}{{\cellcolor{lgray}}}& &\\
         \hline
         Evaluate OPV Device Performance 
-            & & & & & & & & & & & & & & \multicolumn{4}{|c|}{{\cellcolor{lgray}}} & & &\\
+            & & & & & & & & & & & & & & \multicolumn{6}{|c|}{{\cellcolor{lgray}}} &\\
         \hline
         Write Dissertation 
-            & & & & & & & & & & & & & & & &\multicolumn{3}{|c|}{{\cellcolor{lgray}}} & &\\
+            & & & & & & & & & & & & & & & &\multicolumn{5}{|c|}{{\cellcolor{lgray}}}\\
         \hline
         Present Dissertation Defense  
-            & & & & & & & & & & & & & & & & & & {\cellcolor{lgray}} &  &\\
+            & & & & & & & & & & & & & & & & & & & &{\cellcolor{lgray}}\\
         \hline

### 2020-09-09 2pd.tex
contingency

@@
 
-- obj 4 and 5 maybe there aren't descriptors that classify good CT or assemblers?
-our past work with artificial net has done a better than expected job with p3ht and ct is confidence inspiring but if we dont find the top three-- at least we'll have a dataset that is a stepping stone toward solving but we should be able to generate features of NFAs and polymers
-- obj 3 needs models and  access to computational resources.
-some of the coarse graining and pipelining work might be limited if objective 1 doesn't go to plan but we can still use naiive models like UA bsu, xsede, inl, and local HPC resources inspire confidence that wwe will have adequate resources
-- obj 1 and 2 no specific this stand in the way, stitching together existing software and trying out new approaches.
-thing that inspires confidence around getting these done is active participation in mosdef, software development enroute to this.
+No specific obstacles stand in the way of Objectives 1 and 2. 
+These objectives involve stitching together existing software and trying out some new approaches.
+These objectives will require persistent and efficient code development.
+My active participation in MoSDeF and other software development project should inspire confidence that I can complete these objectives.
+
+Objective 3 will require the models from Objective 1 and access to computational resources.
+Some of the coarse-graining and pipelining work might be limited if Objective 1 doesn't go to plan, but we can still use naiive models like the united-atom model.
+As for computational resources, our lab has access to high-performance computing resources from Boise State University, XSEDE, Idaho National Lab, and our lab's local cluster.
+Foregoing any catastrophic hardware failure, we will have adequate resources to complete this objective.
+
+Objectives 4 and 5 rely on the assumption that chemical and morphological features exist to correlate with good charge transfer and robust self assembly.
+However, perhaps this assumption is wrong and there simply aren't good descriptors for these outcomes.
+Our past work with artificial neural nets has done a better than expected job predicting charge transport in p3ht, which should inspire some confidence.
+Even if we dont find the top three features that correlate with charge transport or self assembly, at least we'll have a dataset that is a stepping stone toward answering these questions.
 

### 2020-09-09 2pd.tex
preliminary work

@@
     \item {Predict nanostructures of novel OPV chemistries}
-    \item {Identify chemical features correlated with robust self-assembly and good charge transport}
+    \item {Identify chemical features correlated with robust self-assembly}
+    \item {Identify chemical features correlated with good charge transport}
 \end{enumerate}
@@
 To improve the useability and extensibility of molecular simulation tools, I have been intentional about incorporating Software Carpentry priniciples into my work.
-Background for thinking about users
-pedagogy for thinking about how users take in new information
-useability
-I have completed Software Carpentry training which has taught me how to break down complex ideas and give learners a chance to use their knowledge.
+My experience as a Software Carpentry instructor has given me the pedagocial foundation to think about how users take in new information.
 With these principles in mind, I have created tutorial examples to help current and future students understand scientific concepts and how to use computational tools\cite{notebooktutorials}
 
-In my scientific software development with the Molecular Simulation and Design Framework (MoSDeF) team
+An area where transferrability, reproducibility, useability, and extensibility is really brought to the forefront is in my experience developing scientific software with the Molecular Simulation and Design Framework (MoSDeF) team.
 I have contributed to development of open-source packages including mbuild, foyer, signac, and fresnel\cite{mbuild, foyer, signac, fresnel}.
@@
 As I plan to integrate my future work with existing projects, good collaborative skills will be necessary.
-growth -- nervousness to participate or submit prs empower and shape the way i think about my thesis
+I have also found this experience to be very empowering: submitting changes to reputable codebases has helped me to place myself in the computational science community.
+Helping others to realise this feeling for themselves is part of the reason I so strongly believe in the principles of TRUE science.
 
-A specific example of what we mean by improving the transferrability, reproducibility, useability, and extensibility is the coarse-graining tools that I have developed on route to fufilling Objective 1 of this proposal.
-As for work towards my proposed plan, I have created a minimum working example of a coarse-graining and backmapping package which uses SMARTS strings to specify the site chemistries\cite{grits}.
-This package will need further testing as it is tested on different compounds, but the proof of concept exists.
-
-Packages which do coarse-graining and backmapping already exist, so why is another one necessary?
-One such package, Versatile Object-oriented Toolkit for Coarse-graining Applications (VOTCA)\cite{Ruhle2011b}, includes a coarse-graining, forcefield creation with reverse MC or IBI, and back-mapping modules.
+A specific example of what I mean by improving the transferrability, reproducibility, useability, and extensibility is the coarse-graining tools that I have developed on route to fufilling Objective 1 of this proposal.
+I have created a minimum working example of a coarse-graining and backmapping package which uses SMARTS strings to specify the site chemistries\cite{grits}.
+Many packages which do coarse-graining and backmapping already exist, so it is worth asking why is another one necessary?
+To asnwer, let's look at one such package, Versatile Object-oriented Toolkit for Coarse-graining Applications (VOTCA)\cite{Ruhle2011b}, which includes coarse-graining, forcefield creation with reverse MC or IBI, and back-mapping modules.
 It also allows for charge transport calculations using KMC similar to MorphCT\cite{Lukyanov2010}.
@@
 While including example inputs and a prebuilt software stack via docker is a great first step, these tutorials give very little walkthrough aside from code comments buried in the xml\cite{votca-github}.
+
 \begin{wrapfigure}{l}{0.5\linewidth}
@@
 The code is a mix of C++, shell commands, and python, and the user is required to interact with compiled programs through the command-line which makes adding this code into an existing workflow a little more difficult.
-Overall though this project has many features, interfaces with many popular MD engines (LAMMPS, GROMACS, HOOMD), and is under active, collaborative development, it is near-overwhelming in its scope and is not designed for the new user.
-By choosing a pure python API I will be able to make use of Jupyter Notebooks which can be run on cloud servers using tools like MyBinder which can combine executable code with markdown text and images\cite{mybinder, jupyter, notebooktutorials}.
-In this way a tutorial can provide exact commands needed to reproduce the example intimately connected with the rationale and justification of that example.
+Overall, although this project has many features, interfaces with many popular MD engines (LAMMPS, GROMACS, HOOMD), and is under active, collaborative development, it is near-overwhelming in its scope and is not designed for the new user.
 
-For an example of what I mean by cognitive load, let's compare an example of my proposed coarse-graining scheme to VOTCAs.
+For an example of what I mean by cognitive load, let's compare my proposed coarse-graining scheme to VOTCA's.
 In the following example we will take a hexane molecule and map it to three coarse-grained sites (two carbon atoms per site, see~\autoref{hexane}).
-
 VOTCA uses an xml file to do this:
@@
 
-It may be easy to think that because the goal is simple, mapping two carbons and their attached hydrogens to a single site so that six alkyl carbons becomes three coarse-grained sites (A-B-A), that the process will also be simple.
-In order to specify a site-mapping using VOTCA, we need to know the residue number, the residue name, and the atom name.
+The goal is simple---mapping two carbons and their attached hydrogens to a single site, so six alkyl carbons becomes three coarse-grained sites (A-B-A).
+However, in order to specify a mapping using VOTCA, we need to know the residue number, the residue name, and the atom name.
 For a six atom system this is not too bad, but it could get tedious and error-prone for larger systems.
-And keep in mind that these xml files need to be created manually for each compound which is coarse grained or  backmapped.
-VOTCA's scheme also requires that the bonding and the angles resulting from those bonds are specified, another process which is tedious, error-prone, and probably unecessary. 
+And, keep in mind, these xml files need to be created manually for each compound which is coarse grained or backmapped.
+VOTCA's scheme also requires that the resulting bonds and angles are specified, another process which is tedious, error-prone, and probably unecessary. 
 To explain, let's discuss my proposed alternative:
@@
 The result of using this code in the \lstinline{coarse} function is a three-site hexane model A-B-A, same as VOTCA\cite{grits}.
-The mapping here is specified as a list of site name SMARTS string pairs.
-Although they do add some element of cognitive load, SMARTS strings are designed to be human and machine readable and can match atoms based on their chemical environment.
-With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (in SMARTS notation a capital \lstinline{"C"} denotes an alkyl carbon) and requiring that one be a terminal carbon by including that it has three attached hydrogens (\lstinline{"[CH3]"}).
+The mapping here is specified as a list containing pairs of site name and SMARTS string.
+Although they do add some cognitive load, SMARTS strings are designed to be human and machine readable and can be used to match atoms based on their chemical environment.
+Simplified Molecular Input Line Entry System or SMILES was designed to represent organic molecules in an unambiguous way (similar to IUPAC) but in a line-entry system which is also readable by a computer\cite{Weininger1988}.
+SMARTS is similar to SMILES but instead of representing a single molecule unambiguously, it has multiple wildcards which can be used for pattern matching\cite{daylight}.
+This makes it a good candidate for specifying a coarse-grain mapping scheme.
+The open-source package, Open Babel, allows for a SMILES string to be converted to a chemical structure and for chemical pattern matching\cite{openbabel, OBoyle2011}.
+If we know the SMARTS string for any given CG mapping, we can map the CG site to its center of mass or geometric center.
+With this scheme, there is no need to look up the name or number of each residue, a user simply specifies that they want two alkyl carbons (in SMARTS notation a capital \lstinline{"C"} denotes an alkyl carbon) and requiring that one be a terminal carbon by including that it has three attached hydrogens (\lstinline{"[CH3]"}).
 The order of the sites here matters because technically all the carbon atoms in hexane could be mapped with the more general SMARTS string (\lstinline{"CC"}), so it is important to list the most specific strings first.
@@
 Basically what VOTCA's xml file does in 51 lines, I can do in 1 which is easier to read and makes chemical sense.
-There are even benefits to the mapping being inline with the code:
-It allows the user to see the mapping as they progress through the workflow without having to search for multiple files.
+
+Beyond just the mapping operator being shorter and easier to understand, there are other ways this codebase considers TRUE principles in its development.
+By choosing a pure python API I will be able to make use of Jupyter Notebooks which can be run on cloud servers using tools like MyBinder which can combine executable code with markdown text and images\cite{mybinder, jupyter, notebooktutorials}.
+In this way a tutorial can provide exact commands needed to reproduce the example intimately connected with the rationale and justification of that example.
+The mapping operator being inline with the code allows the user to see the mapping as they progress through the workflow without having to search for multiple files.
 Not using an external file may prevent common errors caused by manual file IO such as operating system specific line endings or whitespace characters like tab or space being read differently by a program.
@@
 (\autoref{hexane} is the output of one such visualization using py3Dmol\cite{py3dmol}.)
-
-We propose a way to make the mapping and backmapping process easier for the user.
-Simplified Molecular Input Line Entry System or SMILES was designed to represent organic molecules in an unambiguous way (similar to IUPAC) but in a line-entry system which is also readable by a computer\cite{Weininger1988}.
-This makes it a good candidate for specifying a coarse-grain mapping scheme.
-The open-source package, Open Babel, allows for a SMILES string to be converted to a chemical structure and vice versa\cite{openbabel, OBoyle2011}.
-SMARTS is similar to SMILES but instead of representing a single molecule unambiguously, it has multiple wildcards which can be used for pattern matching\cite{daylight}.
-This pattern matching is also implemented in the Open Babel package.
-If we know the SMARTS string for any given CG mapping, we can map the CG site to its center of mass or geometric center.
-I have developed a minimum working example of how this can be done and then how the atomistic structure can be recovered\cite{grits}.
-This mapping scheme could even be used to make the mapping process easier for established coarse-grained models.
-It could be fairly straightforward to implement a lookup to check if site parameters already exist (e.g., for the MARTINI model) by going through and writing out the SMARTS pattern for each existing site type.
-This could make parameterizing new compounds for an existing method more foolproof.
+By keeping these principles in mind throughout development we can make things better. %% help
 

### 2020-09-11 1summ.tex
add title

@@
 \begin{center}
-\large{\textbf{Title}} %%TODO
+    \large{\textbf{Advancing organic photovoltaics with infrastructure for transferable, reproducible, useable, and extensible (TRUE) multiscale models}}
 %\large{\textbf{ADVANCEMENT OF ORGANIC PHOTOVOLTAICS THROUGH ARTIFICIAL NEURAL NETWORKS}}
@@
 
-This proposal has the potential to transform the manufacturing of sustainable low-cost power generation
-A coarse graining pipeline will help make multi-scale simulations more accesible and useable for others. 
-This is an important step for screening potential OPV compounds.
-
-This proposal has a the potential to transform the norms of molecular simulation.
-By developing software with a focus on transferrability, reproducibility, usability, and extensibility and thinking beyond just solving a problem but thinking about how to solve the problem for the end-user we can help to change the norms in the computational sciences.
-While we recognise the proposed work is challenging, we are positioned for success based on our prior work developing proofs of concept and molecular simulation on gpus.
+The proposed work is original, taking a systems view of software interoperability needed to improve organic photovoltaics with molecular simulation.
+Through focus on transferable, reproducible, usable, and extensible simulation infrastructure, the proposed work is positioned to transform both the manufacturing of sustainable power technologies and the norms of practice in computational materials science.
+The intellectual merit of project components---coarse-graining pipelines and multiscale simulations---includes the potential to transform materials simulations adjacent to organic photovoltaics, including polymers for structural composites and molecules of biomedical interest.
+The specific insight into structure-property relationships in OPV materials also has intellectual transferability to broader polymer assembly problems, and charge transport problems of interest in piezoelectric materials, induction welding of polymers, and organic electronics broadly.
+PI Fothergill is positioned to be successful in the propsed work, with published expertise in quantum chemical methods applied to charge transport in organic dyes, organometallic crystals, and coarse-grained materials simulation; and as a trained Software Carpentry instructor, and open-source project contributor.
+Ample computational resources are available to complete the proposed work, in the form of local HPC resources (Fry: 32 NVIDIA Pascal P100 gpus, R2: 28 P100 GPUs, Borah: ~30 GPUs coming online this year), Idaho resources (Idaho National Lab facilities: 100's of V100 GPUs) and national resources (125,000 GPU-hour allocation on XSEDE Bridges ).
 
@@
 % 4. benefits of the proposed activity to society
-
 %OPV devices reaching consistent efficacies of 15\% have the potential to create a global energy revolution.
@@
 
-Bring new students in to the software development process.
-Helping to make research transferrable, reproducible, useable, and extensible. 
-Writing tutorials and documentation while keep in mind principles of oftware carpentry instructor training. 
-Using software dev best practices to be efficient and make sure that I'm not making code for someone else to struggle through later. 
-Training/teaching undergrads.
-Working as part of a team.
-
-All code-bases will be free and open source with tutorial and documentation so that not only are they available but accessible.
-By integrating what I do with other existing codebases I can help to achieve this goal.
+The proposed work directly advances discovery and understanding of organic photovoltaic materials physics, molecular simulation, and scientific software development, while promoting teaching: Applying Software Carpentry pedagogical methods to tutorial development and TRUE simulations is the mechanism for simultanesouly advancing discovery while promoting teaching.
+A direct consequence of applying The Carpentries' inclusivity-based pedagogical practices is that this work helps broaden participation of underrepresented groups: My own trajectory as a female in a STEM PhD program is empowered by this approach.
+The products of this work---journal publications, data sets,  and open source software---are to be dissemenated free of subscription costs to users online.
+By disseminating work broadly in this way, this work is positioned to have both broad impact in the application of the transferable tools we develop, and in the opportunity to influence the norms of scientific software development.
+Finally, while undoubtebly aspirational, the proposed work is positioned to identify formulations of organic photovoltaics that can benefit society by significantly ameliorating global climate change.

### 2020-09-14 1summ.tex
incorporating edits and final pass

@@
 This increase in energy demand along with the need to protect our climate makes finding efficient, renewable energy technologies of the utmost importance.
-Harvesting the abundant solar energy is a good solution because it is renewable, non-polluting, sustainable.
+Harvesting the abundant solar energy is a good solution because it is renewable, non-polluting, and sustainable.
 Devices which convert light to electricity, called photovoltaics, were originally made of silicon and required rare elements and careful, clean-room processing.
@@
 
-Coarse grain (CG) models, which group multiple atoms together into "super atoms" and using an effective potential to specify the forces acting upon the site, can be used to access length and time scales more relevant to the bulk polymer morphology.
+Coarse grain (CG) models, which group multiple atoms together into "super atoms" and use an effective potential to specify the forces acting upon the site, can be used to access length and time scales more relevant to the bulk polymer morphology.
 After a bulk morphology is obtained, we can use backmapping, a process in which the atomistic detail can be reintegrated into a coarse grain model, to restore atomistic detail for use in simulations like KMC/QCC.
@@
 The specific insight into structure-property relationships in OPV materials also has intellectual transferability to broader polymer assembly problems, and charge transport problems of interest in piezoelectric materials, induction welding of polymers, and organic electronics broadly.
-PI Fothergill is positioned to be successful in the propsed work, with published expertise in quantum chemical methods applied to charge transport in organic dyes, organometallic crystals, and coarse-grained materials simulation; and as a trained Software Carpentry instructor, and open-source project contributor.
+PI Fothergill is positioned to be successful in the proposed work, as a trained Software Carpentry instructor and open-source project contributor with published expertise in quantum chemical methods applied to charge transport in organic dyes, organometallic crystals, and coarse-grained materials simulation.
 Ample computational resources are available to complete the proposed work, in the form of local HPC resources (Fry: 32 NVIDIA Pascal P100 gpus, R2: 28 P100 GPUs, Borah: ~30 GPUs coming online this year), Idaho resources (Idaho National Lab facilities: 100's of V100 GPUs) and national resources (125,000 GPU-hour allocation on XSEDE Bridges ).

### 2020-09-14 2pd.tex
incorporating edits and final pass

@@
 Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70--80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h)\cite{Baran2017}.
-(but how these molecules interact with donor polymers is not yet known and there's >1000 of them and there have been some metrics devised to figure out how to narrow them down like flory-huggins interaction parameter, but it's still really hard.) \cite{Gao2020} %% transition attempt
-Ultimately, the efficiency of a solar cell depends on the self-assembly of its active layer.
+But how these new chemistries will interact with donor polymers is still an active area of research.
+With thousands of variations, attempts to predict which combinations of chemistries will result in the best structure are vital to narrowing the search\cite{Gao2020} as ultimately the efficiency of a solar cell depends on the self-assembly of its active layer.
 
@@
 \noindent With minor modifications, the number of compounds and the processing conditions can become an intractable problem for experiment (see~\autoref{chemistries}).
-The number of possibilities compounds provides an opportunity for better OPVs, but it also increases the scope of the problem.
+The number of possible compounds provides an opportunity for better OPVs, but it also increases the scope of the problem.
 Imagine, you are a chemist preparing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor, ITIC, and a polymer donor, PTB7. 
@@
 Seemingly minor changes to the functional groups on either species affects the device performance\cite{Swick2019a}.
-All these parameter require consideration just to determine the performance of one donor/acceptor combination in one category of potential compounds\cite{Dou2013}.
+All these parameters require consideration just to determine the performance of one donor/acceptor combination in one category of potential compounds\cite{Dou2013}.
 This is where molecular simulation can help.
-By using a simulation pipeline, we can help to streamline the process of determining which OPV materials will form the morphology with the best charge transport, and in turn, help to solve the energy crisis.
+By using a simulation pipeline, we can help to streamline the process of determining which OPV materials will robustly self-assemble into the morphology with the best charge transport, and in turn, help to solve the energy crisis.
 
-Simulating an OPV morphology requires careful consideration. %% reword
+Simulating an OPV morphology, however, requires careful consideration. %% reword
 A complication of the simulation of OPV polymers is that the properties which predict a device's efficiency, for example charge transport, span multiple length scales.
 So, in order to model this system, a multiscale approach is necessary.
-By breaking our simulation apart into separate steps and equilibrating different lengths scales individually, we can get equilibrated morphologies on multiple length scales more efficiently.
+By breaking our simulation apart into separate steps and equilibrating different length scales individually, we can get equilibrated morphologies more efficiently.
 Another complication of this research is its computational scope.
@@
 
-For this research we propose to develop a flexible method for specifying coarse-grained models to obtain OPV polymer morphologies equilibrated on length scales relevant to charge transport.
-We also propose to develop a backmapping method, which works on the same simple mapping operator, to restore the atomic positions in preparation for techniques which require atomic level resolution, e.g., charge transport calculations.
-This two step process is necessary because starting with the fully atomistic structure would not only be computationally inefficient but also the result may be less accurate due to the difficulties of equilibrating polymers\cite{Gartner2019a}.
+For this research we propose to develop a flexible method for specifying coarse grain (CG) models to obtain OPV polymer morphologies equilibrated on length scales relevant to charge transport.
+We also propose to develop a backmapping method, which works on the same mapping operator, to restore the atomic positions in preparation for techniques which require atomic level resolution, e.g., charge transport calculations.
+This two step process is necessary because starting with the fully atomistic structure would not only be computationally inefficient, but also the result may be less accurate due to the difficulties of equilibrating polymers\cite{Gartner2019a}.
 This efficiency is important because the scope of potential OPV compounds is vast and the energy crisis necessitates expediency.
 The number of OPV compounds to test quickly becomes intractable when we consider that the power conversion efficiency is strongly linked to minor chemical modifications or functionalization, device processing, and the interplay between donor and acceptor\cite{Mazzio2015,Swick2019a}.
-There are countless variations of electron donor polymers, fullerene acceptors, and more recently small molecule, non-fullerene acceptors (NFAs) have been recieving attention for their potential to achieve higher efficiencies than their fullerene counterparts\cite{Dou2013}.
-Coarse grain models do not yet exist for many of these NFAs, and with so many varieties an adaptable pipeline makes more sense than a single model.
+There are countless variations of electron donor polymers, fullerene acceptors, and more recently small molecule, non-fullerene acceptors have been recieving attention for their potential to achieve higher efficiencies than their fullerene counterparts\cite{Dou2013}.
+Coarse-grain models do not yet exist for many of these NFAs, and with so many varieties an adaptable pipeline makes more sense than a single model.
 It is necessary to develop a simple, useable, and flexible pipeline to adapt to the constantly changing chemistries of current OPV technologies.
@@
 \begin{enumerate}
-    \item {Develop a generalized toolset for coarse-graining and performing simulations of novel molecules for organic photovoltaics}
-    \item {Develop a general tool to calculate atomistic positions from a coarse-grained morphology}
+    \item {Develop a generalized toolset for creating CG models and performing simulations of novel molecules for organic photovoltaics}
+    \item {Develop a general tool to calculate atomistic positions from a CG morphology}
     \item {Predict nanostructures of novel OPV chemistries}
@@
 
-In order to model these OPV polymer systems on relevant length scales, it is necessary to develop new coarse-grained models.
-A flexible and efficient coarse-graining scheme will simplify the process of mapping and parameterizing these coarse-grained elements.
+In order to model these OPV polymer systems on relevant length scales, it is necessary to develop new CG models.
+A flexible and efficient CGing scheme will simplify the process of mapping and parameterizing these models.
 
-The flexibility of specifying a mapping will allow for the comparison of multiple mappings which may provide insight into the features of an OPV which govern its self-assembly and the limits of coarse-grained models.
-Currently there is no agreed-upon ``best'' scheme for a coarse-grained mapping operator.
-By making a simple and easy-to-use coarse-graining tool, many mapping operators can be tested and the limits of a minimal model can be probed.
+The flexibility of specifying a mapping will allow for the comparison of multiple mappings which may provide insight into the features of an OPV which govern its self-assembly and the limits of CG models.
+Currently there is no agreed-upon ``best'' scheme for a mapping operator.
+By making a simple and easy-to-use CGing tool, many mapping operators can be tested and the limits of a minimal model can be probed.
 
@@
 And in 1995, Yu described the first bulk heterojunction (BHJ), as an interpenetrating network of donor and acceptor that maximizes the interfacial area, which is still the state of the art morphology to this day\cite{Yu1995}.
-Most recently, non-fullerene acceptors (NFAs), like ITIC, are contributing to the PCE increase of modern OPVs\cite{S.Gurney2019b}.
+Most recently, NFAs like ITIC are contributing to the PCE increase of modern OPVs\cite{S.Gurney2019b}.
 
@@
 
-The compounds which compose an OPV are synthesizable molecules (often polymers) composed of abundant elements (carbon, hydrogen, nitrogen, sulfur, oxygen).
-Due to the conjugated pi-orbitals in these molecules the absorption of sunlight can excite an electron into a frontier orbital and generate an exciton, a couloubicly bound electron-hole pair.
+The compounds which compose an OPV are synthesizable molecules (often polymers) composed of abundant elements.
+Due to the conjugated pi-orbitals in these molecules the absorption of sunlight can excite an electron into a frontier orbital and generate an exciton, a couloubically bound electron-hole pair.
 OPVs are made as a mixture of electron-donor and electron-acceptor compounds in a structure called a bulk heterojunction.
-Depending on the bulk morphology of these compounds, the exciton can travel to an acceptor-donor interface and dissociate into free electron and hole then these free charges generate current if they can subsequently make their way to an electrode.
+Depending on the bulk morphology of the compound mixture, the exciton can travel to an acceptor-donor interface and dissociate into free electron and hole.
+Then the free charges can generate current if they can subsequently make their way to an electrode.
 
@@
 Now GPUs are a 100 million times faster.
-Due to its the simplicity and efficient scaling, MD is now commonly used for the modelling of protein folding\cite{levitt75} and other biological processes, and investigating the bulk properties of polymers\cite{Gartner2019a}.
+Due to its simplicity and efficient scaling, MD is now commonly used for the modelling of protein folding\cite{levitt75} and other biological processes, and investigating the bulk properties of polymers\cite{Gartner2019a}.
 
@@
 By abstracting away some of the atomic degrees of freedom which do not contribute as much to the bulk structure, MD can be used to look at even larger systems.
-Coarse grain models are one such technique to increase the length and time scales examined by a simulation.
+Coarse-grain models are one such technique to increase the length and time scales examined by a simulation.
 
-\subsection*{Coarse Grain Models}
+\subsection*{Coarse-Grain Models}
 
-Coarse graining refers to grouping atoms in a structure into a ``super atom'' and using an effective potential to represent the resulting coarse-grained site.
+Coarse-graining refers to grouping atoms in a structure into a ``super atom'' and using an effective potential to represent the resulting CG site.
 This effective potential used to represent the reduced system results in a smoothed free energy landscape. 
-The heart of coarse-graining is the removal of degrees of freedom. 
-Coarse grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models by abstracting away irrelevant degrees of freedom.
+The heart of CGing is the removal of degrees of freedom. 
+Coarse-grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models by abstracting away irrelevant degrees of freedom.
 Processes which may have taken many time steps in an all atom simulation can take fewer time steps in a coarse simulation\cite{Berendsen2010}.
-Due to their long length and time scales, coarse-grained models are ideal for examining polymer properties\cite{Gartner2019a}.
+Due to their long length and time scales, CG models are ideal for examining polymer properties\cite{Gartner2019a}.
 Similarly to how monitoring the working of a plant cell is not necessary to understanding the growth of a forest, some atomic level properties do not need consideration when simulating the bulk morphology\cite{Muller-Plathe2002}.
@@
 Even if the simulation was to complete, there would be too much information to process accurately. 
-Coarse graining allows scientists to \textit{focus} their experiments\cite{Baschnagel2000}.
+Coarse-graining allows scientists to \textit{focus} their experiments\cite{Baschnagel2000}.
 
-The resolution of coarse-grained systems is broad:
+The resolution of CG systems is broad:
 Simply grouping hydrogens with the heavy atom they are bonded to, called the united-atom model, has been shown to speed up dynamics and make polymer length scales more easily accesible\cite{Paul1995a, Yang2006a}.
-Other coarse-graining schemes may group functional groups together\cite{Berendsen2010, Jankowski2013, Marsh2014}, one site per repeat unit in a polymer\cite{Lee2011}, or even represent an entire amino acid with a single site\cite{Peng2019}.
-General coarse-grained models of OPV thiophene polymers where only the spacing and regioregularity of the side chains were varied were able to predict order disorder transitions and scattering patterns comparable to those obtained from experiment\cite{Jankowski2013, Marsh2014}.
-A coarse-grained model for phospholipids has allowed for bilayer formation from an initial random configuration to be simulated even though the model was parameterized to the vapor-liquid phase transition\cite{Shelley2001}.
+Other CGing schemes may group functional groups together\cite{Berendsen2010, Jankowski2013, Marsh2014}, one site per repeat unit in a polymer\cite{Lee2011}, or even represent an entire amino acid with a single site\cite{Peng2019}.
+General CG models of OPV thiophene polymers where only the spacing and regioregularity of the side chains were varied were able to predict order disorder transitions and scattering patterns comparable to those obtained from experiment\cite{Jankowski2013, Marsh2014}.
+A CG model for phospholipids has allowed for bilayer formation from an initial random configuration to be simulated even though the model was parameterized to the vapor-liquid phase transition\cite{Shelley2001}.
 Which model is right depends on the length and time scale on which the property of interest can be observed.
@@
 Once a good bulk structure has been achieved, the atomistic details can be reintegrated much more easily: a process called backmapping.
-In the same way that a coarse-grained model can be mapped onto an atomistic one, we can get a reasonable starting structure for an atomistic simulation from a coarse-grained structure.
-The large length scale, polymer level properties can be equilibrated during the coarse-grained simulation, and then the atomic interactions can be equilibrated during the backmapped atomistic simulation.
+In the same way that a CG model can be mapped onto an atomistic one, we can get a reasonable starting structure for an atomistic simulation from a CG structure.
+The large length scale, polymer level properties can be equilibrated during the CG simulation, and then the atomic interactions can be equilibrated during the backmapped atomistic simulation.
 This can allow us the calculate properties such as charge transport, which depends upon the electronic structure of individual chromophores \textit{and} the connectivity of these chromophores over distances proportional to the exciton dissociation length.
@@
 %%<what stands in our way?>
-%%<coarse-grain models are specific>
+%%<CG models are specific>
 %% EJ: Discuss in-person?
@@
 I expect this kind of check will help "tidy up" this paragraph.
-Part of coarse-graining process that is not yet automated is choosing a mapping scheme or a mapping operator.
-A mapping operator defines which atoms are grouped into a ``super atom'' represented by one coarse-grained site and where the site is placed relative to the atom group.
-Mapping operators are chosen based on the desired resolution of the coarse-grained system and the information to be extracted.
-A straightforward way to define a mapping operator is to group a set number of heavy atoms (non hydrogen) together; this is the method used in the notable MARTINI force field\cite{Marrink2007}.
+Part of CGing process that is not yet automated is choosing a mapping scheme or a mapping operator.
+A mapping operator defines which atoms are grouped into a CG site and where the site is placed relative to the atom group.
+Mapping operators are chosen based on the desired resolution of the CG system and the information to be extracted.
+A straightforward way to define a mapping operator is to group a set number of heavy (non hydrogen) atoms together; this is the method used in the notable MARTINI force field\cite{Marrink2007}.
 In this scheme, four atoms (except rings, which are treated differently) are grouped and the site is classified as polar, non-polar, apolar, or charged depending on the atoms it is composed of.
@@
 
-There have been efforts to create algorithms for automating the process of deciding which atoms are grouped in a ``super atom''.
+There have been efforts to create algorithms for automating the mapping operator.
 One study reduced the number of allowed mappings by only allowing those which do not change the symmetry group, then iterated over a graph of all possible mappings to find the ``best'' mapping by comparing the difference between the mapped RDF and velocity autocorrelation function\cite{Chakraborty2018b}.
@@
 However, there is still no best method for choosing the mapping operator.
-Deciding on a mapping operator is just the first step of creating a coarse-grained model, next is to create an effective potential for the site.
+Deciding on a mapping operator is just the first step of creating a CG model, next is to create an effective potential for the site.
 
@@
 
-There are numerous methods for deriving coarse-grained potentials from atomistic ones (e.g., force-matching, reverse Monte Carlo), but in this proposal we will focus on Iterative Boltzmann Inversion (IBI).
-IBI is where a coarse-grained potential is iteratively tuned to fit a target distribution usually from an atomistic simulation\cite{Reith2003}.
+There are numerous methods for deriving CG potentials from atomistic ones (e.g., force-matching, reverse Monte Carlo), but in this proposal we will focus on Iterative Boltzmann Inversion (IBI).
+In IBI a CG potential is iteratively tuned to fit a target distribution usually from an atomistic simulation\cite{Reith2003}.
 The radial distribution function (RDF) describes the probability of finding a particle at a given distance from another particle.
@@
     \item 
-        The coarse-grained system is mapped onto an equilibrated atomistic one.
+        The CG system is mapped onto an equilibrated atomistic trajectory.
 
@@
 
-        Where $F(r)$ is the PMF, $k_{B}T$ is the thermal energy, and $g(r)$ is the target distribution.
+        Where $k_{B}T$ is the thermal energy and $g(r)$ is the target distribution.
         Although $F(r)$ is a free-energy and not a potential energy, it is sufficient to be used as the initial potential ($V_{0}$) in the iterative scheme\cite{Reith2003}.
@@
     \item
-        A simulation can be run using the PMF as the non-bonded potential to achieve a new distribution.
+        A simulation is run using the PMF as the non-bonded potential to achieve a new distribution.
 
     \item
-        The difference between the new and target distribution can be accounted for in the next iteration accoring to the following equation:
+        The potential is adjusted by the ratio of the new and target distribution in the next iteration accoring to the following equation:
 
@@
 
-The coarse-grained potential derived from IBI is not transferrable to different thermodynamic statepoints.
+The CG potential derived from IBI is not transferrable to different thermodynamic statepoints.
 This is because the RDF is a property of the ensemble average at a given statepoint, so the potential derived from this property is also limited.
-For example, separate potentials are required to capture solid and fluid structures of a pure simple lipid~\cite{Hadley2010a}.
-There are many attempts to create transferrable CG potentials, for example:
+For example, it was found that separate potentials are required to capture solid and fluid structures of a pure simple lipid~\cite{Hadley2010a}.
+There are many efforts to create transferrable CG potentials, for example:
 The TraPPE force-field fits CG potentials using vapor-liquid equilibria to improve transferrability across thermodynamic states\cite{Maerzke2011}.
@@
 Multistate iterative Boltzmann inversion (MS IBI) includes data from multiple targets to yield a less state dependent potential\cite{Moore2014}.
-The MS IBI potential is an average of the single state potentials with a weighting function to prioritize a state of interest, as shown in the following equation:
+The MS IBI potential is a weighted average of the single state potentials, as shown in the following equation:
 \[
@@
 \]
-where the subscript $s$ represents the property at that state, $N$ is the total number of states, and $\alpha_{s}(r)$ is a weighting factor allowing for more or less emphasis on each state.
-This method has been shown to accurately reproduce the true potential in monoatomic LJ fluid\cite{Moore2014}.
+Where the subscript $s$ represents the property at that state, $N$ is the total number of states, and $\alpha_{s}(r)$ is a weighting function allowing for more or less emphasis on a particular state.
+The MS IBI method has been shown to accurately reproduce the true potential in monoatomic LJ fluid\cite{Moore2014}.
+And it has been successfully extended to n-dodecane\cite{Moore2014}, biomolecular systems\cite{Moore2016}, and semi-crystalline polyethylene\cite{Agrawal2016}.
 When using the MS IBI method, it is important to choose dissimilar states to minimize the potential overlap region.
@@
 For some systems there may not be a potential that represents all states.
-
+With these considerations, the MS IBI method can be automated and fits well into a workflow for parameterizing forcefields for novel OPV chemistries.
+The potential obtained using MS IBI can then be used to equilibrate a CG system which is the first step to predicting the efficiency of an OPV morphology.
 %% HELP transition
@@
 
-In order to use coarse grain models to predict charge transport, we need a way to translate from the coarse to the atomistic morphology.
+In order to use CG models to predict charge transport, we need a way to translate from the coarse to the atomistic morphology.
 %% HELP transition
@@
 A Monte Carlo simulation can then be run using these hopping rates to calculate the movement of charges through the system.
-Because this is a quantum chemical calculation, the position of each atom is needed; therefore, a backmapping process is required to calculate the charge transport in a coarse-grained morphology.
+Because this is a quantum chemical calculation, the position of each atom is needed; therefore, a backmapping process is required to calculate the charge transport in a CG morphology.
 
@@
 
-Already good, open-source packages exist to address the problem of coarse-graining and/or backmapping\cite{Marrink2007,Ruhle2009,Maerzke2011,MorphCT,Wassenaar2014b}.
+Already good, open-source packages exist to address the problem of CGing and/or backmapping\cite{Marrink2007,Ruhle2009,Maerzke2011,MorphCT,Wassenaar2014b}.
 %% these citations are martini, votca, trappe, morphct, backwards.py
@@
 My prior work has focused on developing and using computational tools to predict and understand self assembly of electronically active molecules.
-The resulting three manuscripts and one poster span all scales from first-principles calculation of electronically active dimers to new tools for analyzing the long-range periodicities of large scale atomistic and coarse-grain simulations.
+The resulting three manuscripts and one poster span all scales from first-principles calculation of electronically active dimers to new tools for analyzing the long-range periodicities of large scale atomistic and CG simulations.
 In my first publication on dimer formation, an investigation of the excitonic splitting observed in cyanine dye dimers was done using density functional theory (DFT)\cite{Fothergill2018}.
 By comparing calculated with experimental absorption spectra it was found that the solvent may play a large role in the dimer formation and peak shifting.
-In my second publication, an investigation of the supramolecular interactions which guide crystal self-assembly in diphenylurea transition metal complexes was done using density functional theory\cite{Millard2019a}.
-My contributions to our perspective paper were mostly about my experience joining the lab and trying to reproduce an existing model; a task which should be very straightforward in a computational field but which any computational scientist can attest is far from simple\cite{Jankowski2019}.
+In my second publication, an investigation of the supramolecular interactions which guide crystal self-assembly in diphenylurea transition metal complexes was done using DFT\cite{Millard2019a}. 
+My contribution to the lab's perspective paper were mostly about my on-boarding experience trying to reproduce an existing model; a task which should be very straightforward but, which any computational scientist can attest, is far from simple\cite{Jankowski2019}.
 In my first poster contribution to the SciPy conference, I presented a tool called GIXStapose, an interactive structure viewer alongside its simulated diffraction pattern\cite{gixstapose, scipy2020}.
@@
 
-To improve the useability and extensibility of molecular simulation tools, I have been intentional about incorporating Software Carpentry priniciples into my work.
+To improve the useability and extensibility of molecular simulation tools, I have been intentional about incorporating Software Carpentry priniciples into my work\cite{swc}.
 My experience as a Software Carpentry instructor has given me the pedagocial foundation to think about how users take in new information.
@@
 
-A specific example of what I mean by improving the transferrability, reproducibility, useability, and extensibility is the coarse-graining tools that I have developed on route to fufilling Objective 1 of this proposal.
-I have created a minimum working example of a coarse-graining and backmapping package which uses SMARTS strings to specify the site chemistries\cite{grits}.
-Many packages which do coarse-graining and backmapping already exist, so it is worth asking why is another one necessary?
-To asnwer, let's look at one such package, Versatile Object-oriented Toolkit for Coarse-graining Applications (VOTCA)\cite{Ruhle2011b}, which includes coarse-graining, forcefield creation with reverse MC or IBI, and back-mapping modules.
+\begin{wrapfigure}{l}{0.5\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{images/hexane-compare.pdf}
+    \caption{Hexane chemical structure (top) overlaid with CG mapping \textcolor{blue}{A}-\textcolor{orange}{B}-\textcolor{blue}{A} (bottom)}\label{hexane}
+\end{wrapfigure}
+
+A specific example of what I mean by improving the transferrability, reproducibility, useability, and extensibility of scientific work is the CGing tools that I have developed on route to fufilling Objective 1 of this proposal.
+I have created a minimum working example of a CGing and backmapping package which uses SMARTS strings to specify the site chemistries\cite{grits}.
+Many packages already exist which do CGing and backmapping, so it is worth asking why is another one necessary?
+To answer, let's look at one such package called the Versatile Object-oriented Toolkit for Coarse-graining Applications (VOTCA)\cite{Ruhle2011b}, which includes CGing, forcefield creation with reverse MC or IBI, and back-mapping modules.
 It also allows for charge transport calculations using KMC similar to MorphCT\cite{Lukyanov2010}.
@@
 While including example inputs and a prebuilt software stack via docker is a great first step, these tutorials give very little walkthrough aside from code comments buried in the xml\cite{votca-github}.
+The code is a mix of C++, shell commands, and python, and the user is required to interact with compiled programs through the command-line which makes adding this code into an existing workflow a little more difficult.
+Overall, although this project has many features, interfaces with many popular MD engines (LAMMPS, GROMACS, HOOMD), and is under active, collaborative development, it is near-overwhelming in its scope and is not designed for the new user due to cognitive load.
 
-\begin{wrapfigure}{l}{0.5\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{images/hexane-compare.pdf}
-    \caption{Hexane chemical structure (top) overlaid with coarse-grained mapping \textcolor{blue}{A}-\textcolor{orange}{B}-\textcolor{blue}{A} (bottom)}\label{hexane}
-\end{wrapfigure}
-The code is a mix of C++, shell commands, and python, and the user is required to interact with compiled programs through the command-line which makes adding this code into an existing workflow a little more difficult.
-Overall, although this project has many features, interfaces with many popular MD engines (LAMMPS, GROMACS, HOOMD), and is under active, collaborative development, it is near-overwhelming in its scope and is not designed for the new user.
-
-For an example of what I mean by cognitive load, let's compare my proposed coarse-graining scheme to VOTCA's.
-In the following example we will take a hexane molecule and map it to three coarse-grained sites (two carbon atoms per site, see~\autoref{hexane}).
+For an example of what I mean by cognitive load, let's compare my proposed CGing scheme to VOTCA's.
+In the following example we will take a hexane molecule and map it to three CG sites (two carbon atoms per site, see~\autoref{hexane}).
 VOTCA uses an xml file to do this:
@@
 %%    \includegraphics[width=\linewidth]{images/hexanexml.pdf}
-%%    \caption{XML file used by VOTCA to specify a three site coarse-grained mapping of n-hexane}
+%%    \caption{XML file used by VOTCA to specify a three site CG mapping of n-hexane}
 %%    \label{hexanexml}
@@
 
-The goal is simple---mapping two carbons and their attached hydrogens to a single site, so six alkyl carbons becomes three coarse-grained sites (A-B-A).
+The goal is simple---mapping two carbons and their attached hydrogens to a single site, so six alkyl carbons becomes three CG sites (A-B-A).
 However, in order to specify a mapping using VOTCA, we need to know the residue number, the residue name, and the atom name.
 For a six atom system this is not too bad, but it could get tedious and error-prone for larger systems.
-And, keep in mind, these xml files need to be created manually for each compound which is coarse grained or backmapped.
+And, keep in mind, these xml files need to be created manually for each compound which is CG or backmapped.
 VOTCA's scheme also requires that the resulting bonds and angles are specified, another process which is tedious, error-prone, and probably unecessary. 
@@
 \end{lstlisting}
-The result of using this code in the \lstinline{coarse} function is a three-site hexane model A-B-A, same as VOTCA\cite{grits}.
-The mapping here is specified as a list containing pairs of site name and SMARTS string.
+The result of using the above mapping is a three-site hexane model A-B-A, same as VOTCA\cite{grits}.
+The mapping here is specified as a list of (site name, SMARTS string) pairs.
 Although they do add some cognitive load, SMARTS strings are designed to be human and machine readable and can be used to match atoms based on their chemical environment.
-Simplified Molecular Input Line Entry System or SMILES was designed to represent organic molecules in an unambiguous way (similar to IUPAC) but in a line-entry system which is also readable by a computer\cite{Weininger1988}.
-SMARTS is similar to SMILES but instead of representing a single molecule unambiguously, it has multiple wildcards which can be used for pattern matching\cite{daylight}.
-This makes it a good candidate for specifying a coarse-grain mapping scheme.
+SMARTS strings are based on the Simplified Molecular Input Line Entry System or SMILES, but instead of representing a single molecule unambiguously, it has multiple wildcards which can be used for pattern matching\cite{daylight}.
+SMILES was designed to represent organic molecules in an unambiguous way (similar to IUPAC) but in a line-entry system which is also readable by a computer\cite{Weininger1988}.
+The human and computer readability is what make SMARTS/SMILES a good candidate for specifying a CG mapping scheme.
 The open-source package, Open Babel, allows for a SMILES string to be converted to a chemical structure and for chemical pattern matching\cite{openbabel, OBoyle2011}.
@@
 The order of the sites here matters because technically all the carbon atoms in hexane could be mapped with the more general SMARTS string (\lstinline{"CC"}), so it is important to list the most specific strings first.
-The bonding and angles of the resulting coarse-grained sites can then inferred based on the bonding of the mapped atoms.
+The bonding and angles of the resulting CG sites can then inferred based on the bonding of the mapped atoms.
 Basically what VOTCA's xml file does in 51 lines, I can do in 1 which is easier to read and makes chemical sense.
@@
 By choosing a pure python API I will be able to make use of Jupyter Notebooks which can be run on cloud servers using tools like MyBinder which can combine executable code with markdown text and images\cite{mybinder, jupyter, notebooktutorials}.
-In this way a tutorial can provide exact commands needed to reproduce the example intimately connected with the rationale and justification of that example.
-The mapping operator being inline with the code allows the user to see the mapping as they progress through the workflow without having to search for multiple files.
+In this way a tutorial can provide exact commands needed to reproduce the example intimately connected with the rationale and justification of that example while also eliminating the need for the user to construct their own software stack.
+The mapping operator being inline with the code allows the user to see the mapping as they progress through the workflow without having to search through multiple files.
 Not using an external file may prevent common errors caused by manual file IO such as operating system specific line endings or whitespace characters like tab or space being read differently by a program.
@@
 (\autoref{hexane} is the output of one such visualization using py3Dmol\cite{py3dmol}.)
-By keeping these principles in mind throughout development we can make things better. %% help
+By keeping these principles in mind throughout development we can help to contribute to TRUE and open scientific software.
 
@@
 
-My plan is to create a workflow which builds on existing tools: signac, freud, mbuild, Open Babel, and a previously developed msibi package.
-This workflow could start with equilibrated atomistic trajectories from multiple statepoints, then use SMARTS strings to map the CG sites to each trajectory and calculate the effective potentials using MSIBI\@.
-Once we have a tabulated coarse-grained force field, we can create a larger simulation using our coarse-grained model.
-Finally, once we have an equilibrated coarse-grained trajectory, we can using backmapping to regain the atomic positions and do analyses, e.g., radial distribution function (RDF), charge transport, and diffraction.
+My plan is to create a workflow which builds on existing tools: signac, freud, mbuild, Open Babel, and an MS IBI package developed by the MoSDeF community.
+This workflow would start with equilibrated atomistic trajectories from multiple statepoints, then use SMARTS strings to map the CG sites to each trajectory and calculate the effective potentials using MS IBI\@.
+Once we have a tabulated CG force field, we can create a larger simulation using our CG model.
+Finally, once we have an equilibrated CG trajectory, we can using backmapping to regain the atomic positions and do analyses, e.g., radial distribution function (RDF), charge transport, and diffraction.
 If this workflow is streamlined, it can be applied to many different compounds allowing for a high-throughput analysis of many potential OPV compounds.
 
-\subsection*{Objective 1: Develop a generalized toolset for coarse-graining and performing simulations of novel molecules for organic photovoltaics}
-In order to model the morphologies of new OPV chemistries, we need a simple way to generate novel coarse-grained models.
+\subsection*{Objective 1: Develop a generalized toolset for CGing and performing simulations of novel molecules for organic photovoltaics}
+In order to model the morphologies of new OPV chemistries, we need a simple way to generate novel CG models.
 This objective consists of three steps:
 \begin{enumerate}
-    \item {Create a tool that uses a mapping operator to go from atomistic to coarse-grained structure}
-    \item {Use the mapped coarse-grained structure to parameterize a force field using MSIBI}
+    \item {Create a tool that uses a mapping operator to go from atomistic to CG structure}
+    \item {Use the mapped CG structure to parameterize a force field using MS IBI}
     \item {Develop the infrastructure to port this force field to a simulation engine}
 \end{enumerate}
-A minimum working example of this coarse-grained mapping tool has been completed\cite{grits}.
+A minimum working example of this CG mapping tool has been completed\cite{grits}.
 However, it will still need to be tested with many more compounds and mapping operators.
-This package uses the chemical file format parsing and scriptable structure building capabilities of mbuild coupled with the SMARTS/SMILES string matching of the Open Babel package to generate coarse-grained structures mapped onto their atomistic counterparts with only a SMARTS string from the user.
-These coarse-grained structures mapped to an atomistic target can then be used in an MSIBI workflow to obtain an effective potential.
-A minimum working example of an MSIBI tool has also been started; however, although the hands-on experience with MSIBI was useful to me in getting a better understanding for the process, I think for future, I will build off an existing MSIBI code\cite{msibi, Moore2014}.
-The force field obtained using MSIBI will then be used to run a simulation of a novel coarse-grained model.
+This package uses the chemical file format parsing and scriptable structure building capabilities of mbuild coupled with the SMARTS/SMILES string matching of the Open Babel package to generate CG structures mapped onto their atomistic counterparts with only a SMARTS string from the user.
+These CG structures mapped to an atomistic target can then be used in an MS IBI workflow to obtain an effective potential.
+A minimum working example of an MS IBI tool has also been started; however, although the hands-on experience with MS IBI was useful to me in getting a better understanding for the process, I think for future, I will build off an existing MS IBI code\cite{msibi, Moore2014}.
+The force field obtained using MS IBI will then be used to run a simulation of a novel CG model.
 Therefore decisions about how to carry the forcefield information into a simulation engine will need to be made.
@@
 
-\subsection*{Objective 2: Develop a general tool to calculate atomistic positions from coarse-grained morphologies}
+\subsection*{Objective 2: Develop a general tool to calculate atomistic positions from CG morphologies}
 
-In order to calculate the charge transport of a coarse-grained representation of a morphology, we need to be able to estimate the atomic positions.
-Given an equilibrated coarse-grained trajectory, we can reintroduce the atomistic degrees of freedom by using the same SMARTS mappings used for coarse-graining.
+In order to calculate the charge transport of a CG representation of a morphology, we need to be able to estimate the atomic positions.
+Given an equilibrated CG trajectory, we can reintroduce the atomistic degrees of freedom by using the same SMARTS mappings used for CGing.
 The chemistries specified by the SMARTS strings will be mapped onto the centers of the CG sites and then equilibrated in a short MD run using the atomistic force field with an additional position restraint to maintain the structure.
@@
 Since the user has already specified the mapping to go from atomistic to coarse, it can be reused for backmapping.
-The bonding between the atomistic structures of the sites is lost, so this information will need to be provided: either specified by the user or recorded during the coarse graining step.
+The bonding between the atomistic structures of the sites is lost, so this information will need to be provided: either specified by the user or recorded during the CGing step.
 I have developed a minimum working example of this backmapping process\cite{grits},
-however, the specification of how the backmapped atomistic structures are bonded is still not intuitive for the user to specify and I have yet to implement automated tracking of the conds during the coarse graining.
+however, the specification of how the backmapped atomistic structures are bonded is still not intuitive for the user to specify and I have yet to implement automated tracking of the bonds during the CGing process.
 
-\textbf{Completion Critera:} The ability to perform charge-transport calculations of 5 polymer, 5 fullerene-derivative, and 5 ITIC-derived OPV morphologies that have been back-mapped from coarse-grained representations.
+\textbf{Completion Critera:} The ability to perform charge-transport calculations of 5 polymer, 5 fullerene-derivative, and 5 ITIC-derived OPV morphologies that have been backmapped from CG representations.
 
@@
 %%\ej{In principle we could also start this without new models: That's what Gwen and Emily are doing!}
-Currently, I have not found CG models for many NFA compounds (e.g, ITIC).
+Currently, I have not found CG models for many NFA compounds (e.g, ITIC), so this will have potential to contribute novel results.
 %% I found this paper~\cite{Meng2019} that claims to do CGMD with PTB7 ITIC but the details are hidden in the SI and seem fishy.
 seems like they use IBI but they dont say how they got their target distributions.
-A simple, useable coarse-graining tool will be helpful for determining the best mapping operator to use for these OPV compounds.
+A simple, useable CGing tool will be helpful for determining the best mapping operator to use for these OPV compounds.
 To help organize the dataspace of the large parameter sweep, I plan to use the signac package to manage an ever-changing workspace.
@@
 
-- perform lots of simulations, get lots of morphologies, observe state-dependence of self-assembly
-- replicate trials 5 of each thermodynamic state, molecules, concentrations temperature, density
-- how many out of 5 get to the same morphology? (same morphology could be measured by RDF GIXS)
-- machine learning?
-- quantify robustness of assembly relaxation time to equilibrium and proportion of simulations that reach the same equilibrated structure
-- once robustness metric is defined correlate to identify robust self assembly
-- part of this objective will be investigating techniques to probe this correlation including machine learning
+Completion of this objective will require many simulation replicates in order to observe equilibrated morphologies and the state-dependence of self-assembly.
+We will use these statistically independent replicates to quantify robustness of self-assembly using the relaxation time to equilibrium and proportion of simulations that reach the same equilibrated structure to determine a robustness metric.
+Once robustness metric is defined, it will be uses to correlate with chemical features to identify and predict which chemistries have robust self assembly.
+Part of this objective will be investigating techniques to probe this correlation including machine learning.
 
-\textbf{Completion Critera:} identify measure of robustness to segment our statepoints into 5ths of top 5ths of best assemblers what's similar between them -- top three chemical features
+\textbf{Completion Critera:}
+Perform replicate trials (5) of each thermodynamic state: molecules, concentrations, temperature, density.
+Use this dataset to quantify a measure of robustness, and use this metric to identify the best assemblers.
+Use a correlation method (e.g., machine learning) to identify the top three chemical features which result in good self-assembly.
 
-\subsection*{Objective 5: Identify chemical features correlated with good charge transport}
+\subsection*{Objective 5: Identify chemical and morphological features correlated with good charge transport}
 
-- similar to objective 4 use correlation to determine except replace robustness metric with hole mobility 
-- for all of the morphologies that come out weve got a network that comes out we can easily chop the network to see what matters
-- network analysis of charge transport network to identify morhological features that result in good charge transport see which matters most
+Similar to Objective 4, this Objective will use a correlation method to determine the features associated with good charge transport as determined by KMC calculations.
+Because charge transport is so dependent on structure, additional morphological features will also be included in the feature set.
+Network analysis of the OPV polymer network will be performed to identify morhological features that result in good charge transport see which matters most
 
-\textbf{Completion Critera:} we dont need to make an objective function, chemical and morphological features that result in high hole mobility
+\textbf{Completion Critera:} Determine charge mobilities of all replicates. Use correlation method to identify top three chemical and morphological features which result in the highest mobilities.
 
 Our lab has shown that we have the capability to compare our simulation results to experiment using hole mobilities from charge transport calculations\cite{Jones2017,Miller2018a} and grazing incedent X-ray scattering (GIXS) patterns\cite{Miller2018}.
-GIXS calculations on our backmapped trajectories can be used to validate that our simulations result in the same morphology as experiment.
-While charge transport calculations can be used to measure the efficacy of the active layer morphology.
+GIXS calculations on our backmapped trajectories can be used to validate that our simulations result in the same morphology as experiment while charge transport calculations can be used to measure the efficacy of the active layer morphology.
 Using our lab's charge transport package (MorphCT) on new chemistries, however, will require some work.
@@
 
-\ej{One thing this section is missing right now are tangible things that we specified in our Research Objectives.
-These include: XX new models of OPV chemistries; XX new tutorial notebooks for doing YY\@; XX predictions of OPV morphologies; Implementations of best practices others can copy or extend; }
 As a result of this work, we expect the following outcomes:
-
-- Deeper understanding of using thermodynamics to self-assemble advanced electronic materials
-- Chemical features which correlate with robust self assembly
-- Chemical and morphological features correlated with good charge transport
-- A library of equilibrated OPV morphologies hosted publically through scholarworks freely available
-- An updated understanding of best practices for coarse-graining organic photovoltaics Coarse-grain models
-- new coarse grain models designed for transferrability and usebility - design for mosdef tools
-- Our repository of coarse-graining tool including tutorials designed for onboarding new users
-\begin{enumerate}
-    \item {\textbf{Gain insight into the limits of coarse-graining}}
-        This work will probe the limits of coarse-graining to understand the minimal model necessary to represent different OPV chemistries.
-    \item {\textbf{Understand the interactions which guide BHJ self assembly}} 
-        This work will test a variety of different OPV compounds. 
-        Comparing the results may provide understanding into which moeities, intermolecular interactions, or processing conditions result in the morphology with the highest charge transport.
-    \item {\textbf{Understand the mapping operator}}
-        This work will test whether using a chemical string format (SMARTS/SMILES) to specify the atomistic to coarse-grained site mapping is a viable alternative to other methods. 
-        Using SMARTS/SMILES strings allows a user to more easily and intuitively specify a mapping.
-        If specifying a mapping is easier, a user may be more willing to try out a greater number of different mappings.
-        This would allow for the comparison of a system parameterized with different mapping operators.
-    \item {\textbf{Benefits of Transferrable, Reproducible, Usable, Extensible research}} %%what am i trying to say here?
-        Does making science easier/more understandable make it better? %more reproducible? curb cuts
-        If parameterizing a coarse-grained force field is easier and more approachable, it would open up more possibilities for trying different mapping schemes or different structural or thermodynamic targets rather than sticking to an existing force field.
-        Better coarse-grained models could result in more accurate and efficient simulation of large length scale systems.
-\end{enumerate}
+A deeper understanding of using thermodynamics to self-assemble advanced electronic materials. 
+The chemical features which correlate with robust self assembly. 
+The chemical and morphological features correlated with good charge transport. 
+A freely available library of equilibrated OPV morphologies hosted publically through scholarworks.
+An updated understanding of best practices for CGing organic photovoltaics.
+Novel CG models designed for transferrability and usebility and easy integration into MoSDeF tools.
+A repository including our CGing tool and tutorials designed for onboarding new users.
+If parameterizing a CG force field is easier and more approachable, it may open up more possibilities for trying different mapping schemes or different structural or thermodynamic targets rather than sticking to an existing force field.
+Better CG models could result in more accurate and efficient simulation of large length scale systems.
 
@@
 Objective 3 will require the models from Objective 1 and access to computational resources.
-Some of the coarse-graining and pipelining work might be limited if Objective 1 doesn't go to plan, but we can still use naiive models like the united-atom model.
+Some of the CGing and pipelining work might be limited if Objective 1 doesn't go to plan, but we can still use naiive models like the united-atom model.
 As for computational resources, our lab has access to high-performance computing resources from Boise State University, XSEDE, Idaho National Lab, and our lab's local cluster.
@@
 Our past work with artificial neural nets has done a better than expected job predicting charge transport in p3ht, which should inspire some confidence.
-Even if we dont find the top three features that correlate with charge transport or self assembly, at least we'll have a dataset that is a stepping stone toward answering these questions.
+Even if we don't find the top three features that correlate with charge transport or self assembly, at least we'll have a dataset that is a stepping stone toward answering these questions.
 
 \section*{Timeline for Implementation and Evaluation}
+
 \begin{table}[h]
     \resizebox{\columnwidth}{!}{\renewcommand{\arraystretch}{1.1}
-    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
+    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
         \hline
         \multirow{2}{*}{PROJECT TASK}
-            &\multicolumn{4}{c}{YEAR 1}
-            &\multicolumn{4}{|c}{YEAR 2} 
-            &\multicolumn{4}{|c}{YEAR 3} 
-            &\multicolumn{4}{|c|}{YEAR 4} 
-            &\multicolumn{4}{c|}{YEAR 5} \\ 
+            &\multicolumn{3}{c}{YEAR 1}
+            &\multicolumn{3}{|c}{YEAR 2} 
+            &\multicolumn{3}{|c}{YEAR 3} 
+            &\multicolumn{3}{|c|}{YEAR 4} 
+            &\multicolumn{3}{c|}{YEAR 5}
+            &\multicolumn{3}{c|}{YEAR 6} \\ 
         \hhline{~--------------------}
-        & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4\\
+        & 1 & 2 & 3 & 1 & 2 & 3 & 1 & 2 & 3 & 1 & 2 & 3 & 1 & 2 & 3 & 1 & 2 & 3\\
         \hline
         Complete Coursework 
-            &\multicolumn{10}{|c|}{{\cellcolor{lgray}}} &  &  &  &  &  &  &  &  &  &\\
+            &\multicolumn{7}{|c|}{{\cellcolor{lgray}}} & & & & & & & & & & &\\
         \hline
         Present at a Conference  
-            & & & & & & & & & & & x & & & & & & & & &\\
+            & & & & & & & x & & & & & & & & & & &\\
         \hline
         Publish a First Author Paper
-            & & & & & & x & & & & & & & & & & & & & &\\
+            & & & & x & & & & & & & & & & & & & &\\
         \hline
         Proposal and Comprehensive Exam
-            & & & & & & & & & & & & * & & & & & & & &\\
+            & & & & & & & & * & & & & & & & & & &\\
         \hline
         Expand Functionality of Open Source Packages 
-            & & & & & & \multicolumn{11}{|c|}{{\cellcolor{lgray}}} & & & &\\
+            & & & & & \multicolumn{12}{|c|}{{\cellcolor{lgray}}} & &\\
         \hline
-        Develop Coarse Graining Package              
-            & & & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
+        Develop Coarse-Graining Package              
+            & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
         \hline
-        Develop Automated MS-IBI Code                
-            & & & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
+        Develop Automated MS IBI Code                
+            & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
         \hline
         Develop Backmapping Package                  
-            & & & & & & & & & & & & \multicolumn{5}{|c|}{{\cellcolor{lgray}}}& & & &\\
+            & & & & & & & & & & \multicolumn{6}{|c|}{{\cellcolor{lgray}}}& & &\\
         \hline
         Generate Coarse-Grain Morphologies           
-            & & & & & & & & & & & & & & \multicolumn{5}{|c|}{{\cellcolor{lgray}}}& &\\
+            & & & & & & & & & & & \multicolumn{6}{|c|}{{\cellcolor{lgray}}}& &\\
         \hline
         Evaluate OPV Device Performance 
-            & & & & & & & & & & & & & & \multicolumn{6}{|c|}{{\cellcolor{lgray}}} &\\
+            & & & & & & & & & & & & \multicolumn{6}{|c|}{{\cellcolor{lgray}}} &\\
         \hline
         Write Dissertation 
-            & & & & & & & & & & & & & & & &\multicolumn{5}{|c|}{{\cellcolor{lgray}}}\\
+            & & & & & & & & & & & & & &\multicolumn{5}{|c|}{{\cellcolor{lgray}}}\\
         \hline
         Present Dissertation Defense  
-            & & & & & & & & & & & & & & & & & & & &{\cellcolor{lgray}}\\
+            & & & & & & & & & & & & & & & & & &{\cellcolor{lgray}}\\
         \hline
-         %Saved row template
-         %&  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
-        \end{tabular}
-    }
-    \caption{Anticipated timeline. * indicates right now, x indicates already accomplished.}
+    \end{tabular}}\caption{Anticipated timeline. * indicates right now, x indicates already accomplished.}
 \end{table}

### 2020-09-14 2pd.tex
fixed table and citations

@@
 
-To improve the useability and extensibility of molecular simulation tools, I have been intentional about incorporating Software Carpentry priniciples into my work\cite{swc}.
+To improve the useability and extensibility of molecular simulation tools, I have been intentional about incorporating Software Carpentry priniciples into my work\cite{swc-main}.
 My experience as a Software Carpentry instructor has given me the pedagocial foundation to think about how users take in new information.
@@
 
+\pagebreak
 \section*{Timeline for Implementation and Evaluation}
-
-\begin{table}[h]
-    \resizebox{\columnwidth}{!}{\renewcommand{\arraystretch}{1.1}
-    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
+\begin{table}[h!]
+\centering
+    \resizebox{\textwidth}{!}{%
+\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|}
 \hline
-        \multirow{2}{*}{PROJECT TASK}
-            &\multicolumn{3}{c}{YEAR 1}
-            &\multicolumn{3}{|c}{YEAR 2} 
-            &\multicolumn{3}{|c}{YEAR 3} 
-            &\multicolumn{3}{|c|}{YEAR 4} 
-            &\multicolumn{3}{c|}{YEAR 5}
-            &\multicolumn{3}{c|}{YEAR 6} \\ 
-        \hhline{~--------------------}
-        & 1 & 2 & 3 & 1 & 2 & 3 & 1 & 2 & 3 & 1 & 2 & 3 & 1 & 2 & 3 & 1 & 2 & 3\\
-        \hline
-        Complete Coursework 
-            &\multicolumn{7}{|c|}{{\cellcolor{lgray}}} & & & & & & & & & & &\\
-        \hline
-        Present at a Conference  
-            & & & & & & & x & & & & & & & & & & &\\
-        \hline
-        Publish a First Author Paper
-            & & & & x & & & & & & & & & & & & & &\\
-        \hline
-        Proposal and Comprehensive Exam
-            & & & & & & & & * & & & & & & & & & &\\
-        \hline
-        Expand Functionality of Open Source Packages 
-            & & & & & \multicolumn{12}{|c|}{{\cellcolor{lgray}}} & &\\
-        \hline
-        Develop Coarse-Graining Package              
-            & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
-        \hline
-        Develop Automated MS IBI Code                
-            & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
-        \hline
-        Develop Backmapping Package                  
-            & & & & & & & & & & \multicolumn{6}{|c|}{{\cellcolor{lgray}}}& & &\\
-        \hline
-        Generate Coarse-Grain Morphologies           
-            & & & & & & & & & & & \multicolumn{6}{|c|}{{\cellcolor{lgray}}}& &\\
-        \hline
-        Evaluate OPV Device Performance 
-            & & & & & & & & & & & & \multicolumn{6}{|c|}{{\cellcolor{lgray}}} &\\
-        \hline
-        Write Dissertation 
-            & & & & & & & & & & & & & &\multicolumn{5}{|c|}{{\cellcolor{lgray}}}\\
-        \hline
-        Present Dissertation Defense  
-            & & & & & & & & & & & & & & & & & &{\cellcolor{lgray}}\\
-        \hline
-    \end{tabular}}\caption{Anticipated timeline. * indicates right now, x indicates already accomplished.}
+\multicolumn{1}{|c|}{} & \multicolumn{3}{l|}{YEAR 1} & \multicolumn{3}{l|}{YEAR 2} & \multicolumn{3}{l|}{YEAR 3} & \multicolumn{3}{l|}{YEAR 4} & \multicolumn{3}{l|}{YEAR 5} & \multicolumn{3}{l|}{YEAR 6} \\ \cline{2-19}
+\multicolumn{1}{|c|}{\multirow{-2}{*}{PROJECT TASK}} & 1 & 2 & 3 & 1 & 2 & 3 & 1 & 2 & 3 & 1 & 2 & 3 & 1 & 2 & 3 & 1 & 2 & 3 \\ \hline
+Complete Coursework & \multicolumn{7}{l|}{\cellcolor[HTML]{C0C0C0}} &  &  &  &  &  &  &  &  &  &  &  \\ \hline
+Present at a Conference &  &  &  &  &  &  &  & x &  &  &  &  &  &  &  &  &  &  \\ \hline
+Publish a First Author Paper &  &  &  & x &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ \hline
+Proposal and Comprehensive Exam &  &  &  &  &  &  &  &  & * &  &  &  &  &  &  &  &  &  \\ \hline
+Expand Functionality of Open Source Packages &  &  &  &  & \multicolumn{12}{l|}{\cellcolor[HTML]{C0C0C0}} &  &  \\ \hline
+Develop Coarse-Graining Package &  &  &  &  &  &  & \multicolumn{8}{l|}{\cellcolor[HTML]{C0C0C0}} &  &  &  &  \\ \hline
+Implement Automated MS IBI Package &  &  &  &  &  &  &  &  &  & \multicolumn{5}{l|}{\cellcolor[HTML]{C0C0C0}} &  &  &  &  \\ \hline
+Develop Backmapping Package &  &  &  &  &  &  &  & \multicolumn{7}{l|}{\cellcolor[HTML]{C0C0C0}} &  &  &  &  \\ \hline
+Generate Coarse-Grain Morphologies &  &  &  &  &  &  &  &  &  &  &  & \multicolumn{5}{l|}{\cellcolor[HTML]{C0C0C0}} &  &  \\ \hline
+Evaluate OPV Performance Metrics &  &  &  &  &  &  &  &  &  &  &  &  & \multicolumn{5}{l|}{\cellcolor[HTML]{C0C0C0}} &  \\ \hline
+Write Dissertation &  &  &  &  &  &  &  &  &  &  &  &  &  & \multicolumn{5}{l|}{\cellcolor[HTML]{C0C0C0}} \\ \hline
+Present Dissertation Defense &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \cellcolor[HTML]{C0C0C0} \\ \hline
+\end{tabular}%
+}
+\caption{Anticipated timeline. * indicates right now, x indicates already accomplished.}
 \end{table}
